### 2018-02-20 manuscript.Rnw
initial commit

\documentclass[a4paper,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{setspace}
\renewcommand{\thefigure}{S\arabic{figure}}
\usepackage[normalem]{ulem}
\usepackage{sectsty}
\subsectionfont{\normalfont\large\underline}

\title{Measuring Subgroup Preferences in Conjoint Experiments}
\author{Sara Hobolt, Thomas J. Leeper, and James Tilley}

\begin{document}

\maketitle

{\abstract Conjoint analysis has experienced a recent resurgence. The driving force for this change has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a fully randomized conjoint design and an associated analytic approach that emphasizes a single causal quantity of interest: namely, the average marginal component effect (AMCE). The AMCE convey the degree to which a given value of a feature increases or decreases respondents' support for a conjoint profile, averaging across all respondents and all other profile features. While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses use AMCEs for descriptive purposes: that is, not map variation in preferences across attributes of a multidimensional object, such as a candidate individual or public policy. And many authors also engage in subgroup analyses, wherein they compare subsets of respondents to one another with respect to AMCEs. This paper argues that such approaches can substantially mislead researchers about the degree of agreement or disagreement between subgroups, demonstrates the problem using several example datasets, and provides several suggestions for improved reporting and interpretation. Most importantly, it highlights that the difference in AMCEs between groups is sensitive to the choice of reference categories of features, while the difference in the marginal means is not sensitive in this way. When groups substantially differ in preferences, the difference in marginal means rather than the difference better conveys the size of such disagreements.}

<<r hidden, eval=FALSE, echo=FALSE, results="hide">>=
# setwd("c:/users/thomas/dropbox/brexit identity/papers/subgroupanalysis")
# knitr::knit2pdf("manuscript.Rnw")
@

<<r knitr_options, echo=FALSE, results="hide">>=
knitr::opts_chunk$set(cache = TRUE, echo=FALSE, results="hold", warning=FALSE)
options(scipen = 10)
@

\clearpage

Conjoint analysis has experienced a recent resurgence in the social sciences and especially in political science. The driving force has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE). By capturing the multidimensionality of target objects, such as a candidate individual or public policy, the conjoint design breaks any explicit or implicit confounding between those features, thus giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' support for a packaged conjoint profile, averaging across all respondents and all other profile features.

While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object. For example, \citet{HainmuellerHopkinsYamamoto2014} describe some of the results of their conjoint analysis of congressional candidate preferences:

\begin{quote}
We also see a bias against Mormon candidates, whose estimated level of support is 0.06 (SE = 0.03) lower when compared to a baseline candidate with no stated religion. Support for Evangelical Protestants is also 0.04 percentage points lower (SE = 0.02) than the baseline. Mainline Protestants, Catholics, and Jews all receive ratings indistinguishable from those of a baseline candidate. (19)
\end{quote}

This characterization of the results has a distinctly descriptive flavor. While a given religious characteristic \textit{causes} respondents to evaluate a given candidate more or less favorably, the gist of the analysis is that there are differences in the evaluations of candidates of different religious persuasions. \citeauthor{HainmuellerHopkinsYamamoto2014}'s phrasing highlights another feature of conjoint analysis that is not widely discussed: the baseline (or reference category) in the estimation of AMCEs significantly colors which pairwise comparisons between features are highlighted and the degree to which preferences are stated in positive or negative terms. By choosing a non-religious candidate as a baseline, the AMCEs are all expressed relative to this baseline; the difference (if any) between evaluations of Mormon and Evangelical candidates, for example, is not obvious and while it is likely that Mainline Protestant, Catholic, and Jewish candidates are all preferred over Mormon or Evangelical candidates, the AMCEs for these categories are indistinguishable from zero (rather than the positive values they would take if Mormon or Evangelical were the reference category). Similarly, by selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), some AMCEs are positive while others are negative. Yet because any feature level could be used as the reference cateory, the size but also \textit{direction} of AMCEs is arbitrary. Were the category with the lowest favorability chosen as the reference, all AMCEs would be positive; were the category with the highest favorability chosen as the reference, all AMCEs would be negative. The results would be \textit{numerically equivalent} --- because ultimately the choice of reference category is completely arbitrary and mathematicaly irrelevant --- but the choice as sizable consequences for the interpretation of conjoint analyses.

This is particularly the case when researchers engage in subgroup analyses of conjoint experiments. For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.\footnote{This is achieved by subsetting the data based upon the measure of ethnocentrism and performing separate regressions for high- and low-ethnocentrism respondents.} The interpretation therefore focuses not just on the arbitrarily signed AMCEs within each subgroup (what Hainmueller et al. term ``conditional AMCEs''; 13) but also on an implied quantity of interest: the difference between conditional AMCEs. This comparison seems intuitively correct but because the conditional AMCEs are causal effects expressed relative to an arbitrary baseline, the differences between AMCEs only convey a difference in preference to the extent that the reference category is equally liked by both groups. When the preferences toward the reference category differ substantially between groups, the difference in AMCEs is a biased estimate of the difference in preferences between the two groups. For example, \citet{HainmuellerHopkinsYamamoto2014} eyeball the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22). Yet simply because the AMCEs are similar does not necessarily mean that \textit{preferences} are similar.

To bring some intuition to this problem, consider a simple two-condition experiment in which the effect of the treatment, $x \in {0,1}$, is compared across a single two-category covariate, $z \in {0,1}$. Subgroup regression equations might be:

\begin{align*}
\hat{y} &= \beta_0 + \beta_1 x, \quad \forall z = 0 \\
\hat{y} &= \beta_2 + \beta_3 x, \quad \forall z = 1
\end{align*}

\noindent The effect of $x$ when $z=0$ is given by $\beta_1$. The effect of $x$ when $z=1$ is given by $\beta_3$. These are, in essence, the conditional AMCEs in a conjoint analysis. yet the difference in AMCEs ($\beta_3 - \beta_1$) is not equal to the differnce in preferences between the two groups, which is $\bar{y}_{z=1|x=1} - \bar{y}_{z=0|x=1}$, or estimated by $(\beta_2 + \beta_3) - (\beta_0 + \beta_1)$. The difference in AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$. Yet the standard AMCE-centric conjoint analysis does not present or characterize either of these quantities. And given that the reference category is arbitrary, there is never any reason to expect that an arbitrarily selected reference category satisfies that equality assumption, meaining that when one uses a difference in AMCEs to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.

Worse, because conjoint analysis generates a sparse feature matrix (where there is never any guarantee that a particular combination of feature levels is observed in the data), it is also not possible to empirically select an appropriate set of reference categories using data. And while it might seem possible to select a \textit{marginally} appropriate reference category (i.e., one where preferences are similar with respect to a given feaure), preferences toward that reference category may differ across other dimensions in the analysis. Thus, there is no way to use conditional AMCEs or differences-in-AMCEs to convey the underlying similarity or differences in preferences across sample subgroups.

In what follows, we formalize how the arbitrary selection of a reference category can mislead researchers about the pattern of preferences exposed by a conjoint experiment and demonstrates how this problem is especially problematic when researchers engage in the now-common practice of comparing conditional AMCEs across respondent subgroups. The paper then demonstrates the problem using several example datasets and provides suggestions for improved reporting and interpretation based around a purely descriptive quantity of interest: namely, the unadjusted marginal means. Software for the R programming language to easily calculate marginal means (as well as AMCEs) is also discussed.

\section{Quantities of Interest}

% AMCE

% Difference in conditional AMCEs

\citet{RatkovicTingley2017} considered efficient methods for performing subgroup analyses in conjoint designs. Our focus here is on the narrower problem of interpreting subgroup analyses as traditionally performed.

\begin{table}
\caption{Uses of Subgroup Analysis in Published Work}
\begin{center}
\footnotesize
\begin{tabular}{p{2.5in} p{2in} p{2in}}\toprule
\textbf{Paper} & \textbf{Topic} & \textbf{Subgroup Comparisons} \\ \midrule
Hainmueller, Hopkins, and Yamamoto (2014) & Immigration Preferences & Ethnocentrism \\
Bechtel and Scheve (2013) & Climate agreement preferences & Environmentalism and International Reciprocity Attitudes \\
Bechtel, Genovese, and Scheve (2017) & Climate agreement preferences & Employment sector emissions \\
Hansen, Olsen, and Bech (2015) & Policy Preferences & Partisanship \\
Carlson (2015) & Candidate Choice & Co-ethnicity \\
Franchino and Zucchini (2015) & Candidate Choice & Political Interest, Left-right self-placement\\
Carnes and Lupu (2016) & Candidate Choice & Partisanship \\
Mummolo (2016) & News Selection & Various\\
Mummolo and Nall (2016) & Mobility preferences & Partisanship \\
Ballard-Rosa, Martin, and Scheve (2016) & Tax Preferences & Various\\
Bechtel, Hainmueller, and Margalit (2017) & International bailout preferences & Various\\
Sen (2017) & Judicial candidate preferences & Partisanship \\
Campbell, Cowley, Vivyan, and Wagner (2016) & Candiate preferences & Partisanship \\
Kirkland, Coppock (2017) & Candidate choice & Partisanship \\ \bottomrule
\end{tabular}
\end{center}
\end{table}

% Marginal means

\section{Challenges of Interpretation}

% baseline levels of features

% subgroup analyses

% difference in AMCEs versus difference in marginal means

<<r setup>>=
library("ggplot2")
requireNamespace("ggstance")
library("cregg")
@

<<r data>>=
data(hainmueller)
hainmueller$ethnocentrism_split <- ifelse(is.na(hainmueller$ethnocentrism), NA_real_, ifelse(hainmueller$ethnocentrism > 10, 1, 0))
hainmueller$ethnocentrism_split <- factor(hainmueller$ethnocentrism_split, levels = c(0,1), labels = c("low", "high"))
@

The following figure provides a replication of Hainmueller et al.'s (2014) results:

<<r hainmueller_immigration, dependson=c("data"), fig.height=10, fig.width=8>>=
plot(
  cj(
   hainmueller, 
   ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
   id = ~ CaseID
  )
)
@

\clearpage

<<r functions>>=
amces_by_reference <- function(data, variable, formula) {
    # get levels
    levs <- levels(data[[variable]])

    # loop over levels
    out <- list()
    for (i in seq_along(levs)) {
        data[[variable]] <- relevel(data[[variable]], levs[i])
        out[[i]] <- cj(data, formula, id = ~ CaseID)
        out[[i]][["ref_category"]] <- levs[i]
    }

    # return value
    out <- do.call("rbind", out)
    out[["ref_category"]] <- factor(out[["ref_category"]], levels = levs)
    class(out) <- c("cj_amce", "data.frame")
    out
}
@

\section{Arbitrary reference category choice}

<<r reference_category, dependson=c("data"), fig.width=8, fig.height=5>>=
x <- amces_by_reference(hainmueller, "CountryOfOrigin", ChosenImmigrant ~ CountryOfOrigin)

ggplot(x, aes(x = estimate, y = level, group = ref_category, colour = level)) +
  geom_vline(xintercept = 0, colour = "gray") +
  geom_point(position = ggstance::position_dodgev(height = 0.75)) +
  geom_errorbarh(aes(xmin = lower, xmax = upper),  
                 size = 0.2, height = 0,
                 position = ggstance::position_dodgev(height = 0.75)) + 
  scale_colour_discrete(guide = ggplot2::guide_legend(title = "Reference Category")) +
  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
  ylab("") +
  xlab("Estimated AMCE") + 
  theme_minimal() + 
      ggplot2::theme(
        legend.position = "bottom",
        panel.grid.major = ggplot2::element_blank(),
        panel.grid.minor = ggplot2::element_blank()
      )
@

<<r marginal_means, fig.width=8, fig.height=5>>=
plot(mm(hainmueller, ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID), vline = 0.5, xlim = c(0,1))
@

\clearpage

\section{Subgroup Analysis}

A conventional presentation of subgroup analyses in a conjoint design is as follows. Note how the conditional AMCEs for several levels - Somalia, Sudan, China, Mexico, and France - flip signs. Yet the largest differences in preferences between the two groups are for Germany, France, Poland, and Somalia. Apparently similar patterns of AMCE mask where and in what direction preferences for the two subgroups differ.

<<r subgroup_results_amce, dependson=c("data"), fig.width=8, fig.height=5>>=
by_split <- lapply(c("low","high"), function(x) {
    out <- cj(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "amce")
    out$ethnocentrism_split <- x
    out
})
x <- do.call("rbind", by_split)

ggplot(x, aes(x = estimate, y = level, group = ethnocentrism_split, colour = ethnocentrism_split)) +
  geom_vline(xintercept = 0, colour = "gray") +
  geom_point(position = ggstance::position_dodgev(height = 0.75)) +
  geom_errorbarh(aes(xmin = lower, xmax = upper),  
                 size = 0.2, height = 0,
                 position = ggstance::position_dodgev(height = 0.75)) + 
  scale_colour_discrete(guide = ggplot2::guide_legend(title = "Ethnocentrism")) +
  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
  ylab("") +
  xlab("Estimated AMCE") + 
  theme_minimal() + 
      ggplot2::theme(
        legend.position = "bottom",
        panel.grid.major = ggplot2::element_blank(),
        panel.grid.minor = ggplot2::element_blank()
      )
@

<<r subgroup_marginal_means, dependson=c("data"), fig.width=8, fig.height=5>>=
plot(cj(hainmueller, ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "mm", by = ~ethnocentrism_split), vline = 0.5, group = "ethnocentrism_split")
@

As we can see, however, while the difference in marginal means conveys the fixed difference in preferences between the two groups, the apparent difference in preferences between groups conveyed by a difference-in-AMCEs is sensitive to the reference category chosen when estimating the effects:

\clearpage

<<r subgroup_results_mm, dependson=c("data"), fig.width=10, fig.height=10>>=
# difference in marginal means
by_split_mm <- lapply(levels(hainmueller$ethnocentrism_split), function(x) {
    out <- cj(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "mm")
    out$ethnocentrism_split <- x
    out
})
x_mm <- merge(by_split_mm[[1]], by_split_mm[[2]], by = c("level"), suffixes = c(".low", ".high"))
## difference
x_mm[["diff"]] <- x_mm[["estimate.high"]] - x_mm[["estimate.low"]]
## standard error of difference
x_mm[["diff_se"]] <- sqrt(x_mm[["std.error.high"]]^2 + x_mm[["std.error.low"]]^2)
x_mm[["ref_category"]] <- "Marginal Mean"

# difference in AMCEs
by_split_amce <- lapply(levels(hainmueller$ethnocentrism_split), function(x) {
    out <- amces_by_reference(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), "CountryOfOrigin", ChosenImmigrant ~ CountryOfOrigin)
    out$ethnocentrism_split <- x
    out
})
x_amce <- merge(by_split_amce[[1]], by_split_amce[[2]], by = c("level", "ref_category"), suffixes = c(".low", ".high"))
## difference
x_amce[["diff"]] <- x_amce[["estimate.high"]] - x_amce[["estimate.low"]]
## standard error of difference
x_amce[["diff_se"]] <- sqrt(x_amce[["std.error.high"]]^2 + x_amce[["std.error.low"]]^2)

x_merged <- rbind(x_mm[c("level", "diff", "diff_se", "ref_category")], x_amce[c("level", "diff", "diff_se", "ref_category")])
x_merged[["ref_category"]] <- factor(x_merged[["ref_category"]], levels = c("Marginal Mean", levels(x_amce[["ref_category"]])))
x_merged[["is_mm"]] <- ifelse(x_merged[["ref_category"]] == "Marginal Mean", "Difference in MMs", "Difference in AMCEs")

ggplot(x_merged, aes(x = diff, y = level, group = ref_category, colour = is_mm, shape = is_mm)) +
  geom_vline(xintercept = 0, colour = "gray") +
  geom_point(aes(shape = is_mm), position = ggstance::position_dodgev(height = 0.75)) +
  scale_shape_manual(values = c(16,15), guide = FALSE) + 
  geom_errorbarh(aes(xmin = diff - diff_se, xmax = diff + diff_se),  
                 size = 0.2, height = 0,
                 position = ggstance::position_dodgev(height = 0.75)) + 
  #scale_colour_discrete(guide = ggplot2::guide_legend(title = "Reference Category")) +
  scale_colour_manual(values = c("gray", "red"), guide = ggplot2::guide_legend(title = "Estimate Type")) +
  scale_x_continuous(oob = scales::rescale_none) +
  ylab("") +
  xlab("Estimated Difference") + 
  theme_minimal() + 
      ggplot2::theme(
        legend.position = "right",
        panel.grid.major = ggplot2::element_blank(),
        panel.grid.minor = ggplot2::element_blank()
      )
@

Indeed, the difference in AMCEs most closely approximates the difference in marginal means (and thus the descriptive difference in preferences) when the true difference in preferences in the reference category is close to zero. For example, in the above figure differences in AMCEs are shown in gray and differences in marginal means are shown in red, for respondents scoring above-median (high) and below-median (low) in ethnocentrism for each possible country of origin in Hainmueller et al.'s (2014) immigration experiment. The difference in marginal means between high and low ethnocentrism respondents is smallest for immigrants arriving from Iraq. When Iraq is used as the reference category, the AMCE of Iraq is fixed at zero and the between-group difference in AMCEs is thus, by definition, also fixed at zero. These estimates are shown at the top of each grouping - as should be readily clear, when Iraq is used as the reference category, the difference in AMCEs for each of the other possible origin countries closely approximates (but does not exactly equal) the difference in marginal means for that origin country. Were there no feature level for which the two groups held similar preferences, then there would be no reference category that would generate differences in AMCES that were close to the difference in underlying marginal means.

When other origin countries are used as the reference category (wherein the underlying difference in preferences between high ethnocentrism and low enthnocentrism respondents is greater), then the difference in AMCEs provides biased estimates of the difference in preferences. Take, for example, the difference in preferences over immigrants from China, where high ethnocentrism respondents are less favourable to these immigrants than low ethnocentrism respondents. The difference in marginal means is -0.033. Yet differences in AMCEs for Chinese immigrants vary substantially depending on which other category is chosen as the baseline. If China is the baseline, the apparent difference in preferences is zero (definitionally). While in most cases the difference in AMCEs takes the same sign as the difference in marginal means, when either Mexico or Sudan is used as the reference category the apparent difference in preferences flips signs: high ethnocentrism respondents appear to be more rather than less favorable toward Chinese immigrants when the AMCEs are estimated in that way.

Yet the graph also makes clear that the differences in AMCEs all center upon the true difference in marginal means in a fixed manner.

Thus the choice of reference category - while seemingly irrelevant - has dramatic inferential consequences.

\section{Suggested Approaches}

% Present marginal means overall and for specific subgroups of interest

\section{Conclusion}

This paper has several identified challenges related to the analysis and reporting of conjoint experimental designs, particularly analyses of subgroup differences. It suggests that authors should report not only average marginal component effects (AMCEs) but also descriptive quantities that better convey subgroup differences.

\singlespacing
\bibliographystyle{apsa-leeper}
\bibliography{References}
\clearpage

\end{document}

### 2018-02-20 manuscript.tex
initial commit

--- 2018-02-20 manuscript.Rnw
@@
-\documentclass[a4paper,12pt]{article}
+\documentclass[a4paper,12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 \usepackage[margin=1in]{geometry}
@@
 \author{Sara Hobolt, Thomas J. Leeper, and James Tilley}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 When groups substantially differ in preferences, the difference in marginal means rather than the difference better conveys the size of such disagreements.}
-
-<<r hidden, eval=FALSE, echo=FALSE, results="hide">>=
-# setwd("c:/users/thomas/dropbox/brexit identity/papers/subgroupanalysis")
-# knitr::knit2pdf("manuscript.Rnw")
-@
-
-<<r knitr_options, echo=FALSE, results="hide">>=
-knitr::opts_chunk$set(cache = TRUE, echo=FALSE, results="hold", warning=FALSE)
-options(scipen = 10)
-@
 
@@
 
-<<r setup>>=
-library("ggplot2")
-requireNamespace("ggstance")
-library("cregg")
-@
-
-<<r data>>=
-data(hainmueller)
-hainmueller$ethnocentrism_split <- ifelse(is.na(hainmueller$ethnocentrism), NA_real_, ifelse(hainmueller$ethnocentrism > 10, 1, 0))
-hainmueller$ethnocentrism_split <- factor(hainmueller$ethnocentrism_split, levels = c(0,1), labels = c("low", "high"))
-@
-
 The following figure provides a replication of Hainmueller et al.'s (2014) results:
 
-<<r hainmueller_immigration, dependson=c("data"), fig.height=10, fig.width=8>>=
-plot(
-  cj(
-   hainmueller, 
-   ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
-   id = ~ CaseID
-  )
-)
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required namespace: ggstance}}\end{kframe}
+\includegraphics[width=\maxwidth]{figure/r_hainmueller_immigration-1}
+
+\end{knitrout}
 
@@
 
-<<r functions>>=
-amces_by_reference <- function(data, variable, formula) {
-    # get levels
-    levs <- levels(data[[variable]])
-
-    # loop over levels
-    out <- list()
-    for (i in seq_along(levs)) {
-        data[[variable]] <- relevel(data[[variable]], levs[i])
-        out[[i]] <- cj(data, formula, id = ~ CaseID)
-        out[[i]][["ref_category"]] <- levs[i]
-    }
-
-    # return value
-    out <- do.call("rbind", out)
-    out[["ref_category"]] <- factor(out[["ref_category"]], levels = levs)
-    class(out) <- c("cj_amce", "data.frame")
-    out
-}
-@
-
 \section{Arbitrary reference category choice}
 
-<<r reference_category, dependson=c("data"), fig.width=8, fig.height=5>>=
-x <- amces_by_reference(hainmueller, "CountryOfOrigin", ChosenImmigrant ~ CountryOfOrigin)
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/r_reference_category-1}
 
-ggplot(x, aes(x = estimate, y = level, group = ref_category, colour = level)) +
-  geom_vline(xintercept = 0, colour = "gray") +
-  geom_point(position = ggstance::position_dodgev(height = 0.75)) +
-  geom_errorbarh(aes(xmin = lower, xmax = upper),  
-                 size = 0.2, height = 0,
-                 position = ggstance::position_dodgev(height = 0.75)) + 
-  scale_colour_discrete(guide = ggplot2::guide_legend(title = "Reference Category")) +
-  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
-  ylab("") +
-  xlab("Estimated AMCE") + 
-  theme_minimal() + 
-      ggplot2::theme(
-        legend.position = "bottom",
-        panel.grid.major = ggplot2::element_blank(),
-        panel.grid.minor = ggplot2::element_blank()
-      )
-@
+\end{knitrout}
 
-<<r marginal_means, fig.width=8, fig.height=5>>=
-plot(mm(hainmueller, ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID), vline = 0.5, xlim = c(0,1))
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/r_marginal_means-1}
+
+\end{knitrout}
 
@@
 
-<<r subgroup_results_amce, dependson=c("data"), fig.width=8, fig.height=5>>=
-by_split <- lapply(c("low","high"), function(x) {
-    out <- cj(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "amce")
-    out$ethnocentrism_split <- x
-    out
-})
-x <- do.call("rbind", by_split)
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/r_subgroup_results_amce-1}
 
-ggplot(x, aes(x = estimate, y = level, group = ethnocentrism_split, colour = ethnocentrism_split)) +
-  geom_vline(xintercept = 0, colour = "gray") +
-  geom_point(position = ggstance::position_dodgev(height = 0.75)) +
-  geom_errorbarh(aes(xmin = lower, xmax = upper),  
-                 size = 0.2, height = 0,
-                 position = ggstance::position_dodgev(height = 0.75)) + 
-  scale_colour_discrete(guide = ggplot2::guide_legend(title = "Ethnocentrism")) +
-  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
-  ylab("") +
-  xlab("Estimated AMCE") + 
-  theme_minimal() + 
-      ggplot2::theme(
-        legend.position = "bottom",
-        panel.grid.major = ggplot2::element_blank(),
-        panel.grid.minor = ggplot2::element_blank()
-      )
-@
+\end{knitrout}
 
-<<r subgroup_marginal_means, dependson=c("data"), fig.width=8, fig.height=5>>=
-plot(cj(hainmueller, ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "mm", by = ~ethnocentrism_split), vline = 0.5, group = "ethnocentrism_split")
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/r_subgroup_marginal_means-1}
+
+\end{knitrout}
 
@@
 
-<<r subgroup_results_mm, dependson=c("data"), fig.width=10, fig.height=10>>=
-# difference in marginal means
-by_split_mm <- lapply(levels(hainmueller$ethnocentrism_split), function(x) {
-    out <- cj(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "mm")
-    out$ethnocentrism_split <- x
-    out
-})
-x_mm <- merge(by_split_mm[[1]], by_split_mm[[2]], by = c("level"), suffixes = c(".low", ".high"))
-## difference
-x_mm[["diff"]] <- x_mm[["estimate.high"]] - x_mm[["estimate.low"]]
-## standard error of difference
-x_mm[["diff_se"]] <- sqrt(x_mm[["std.error.high"]]^2 + x_mm[["std.error.low"]]^2)
-x_mm[["ref_category"]] <- "Marginal Mean"
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/r_subgroup_results_mm-1}
 
-# difference in AMCEs
-by_split_amce <- lapply(levels(hainmueller$ethnocentrism_split), function(x) {
-    out <- amces_by_reference(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), "CountryOfOrigin", ChosenImmigrant ~ CountryOfOrigin)
-    out$ethnocentrism_split <- x
-    out
-})
-x_amce <- merge(by_split_amce[[1]], by_split_amce[[2]], by = c("level", "ref_category"), suffixes = c(".low", ".high"))
-## difference
-x_amce[["diff"]] <- x_amce[["estimate.high"]] - x_amce[["estimate.low"]]
-## standard error of difference
-x_amce[["diff_se"]] <- sqrt(x_amce[["std.error.high"]]^2 + x_amce[["std.error.low"]]^2)
-
-x_merged <- rbind(x_mm[c("level", "diff", "diff_se", "ref_category")], x_amce[c("level", "diff", "diff_se", "ref_category")])
-x_merged[["ref_category"]] <- factor(x_merged[["ref_category"]], levels = c("Marginal Mean", levels(x_amce[["ref_category"]])))
-x_merged[["is_mm"]] <- ifelse(x_merged[["ref_category"]] == "Marginal Mean", "Difference in MMs", "Difference in AMCEs")
-
-ggplot(x_merged, aes(x = diff, y = level, group = ref_category, colour = is_mm, shape = is_mm)) +
-  geom_vline(xintercept = 0, colour = "gray") +
-  geom_point(aes(shape = is_mm), position = ggstance::position_dodgev(height = 0.75)) +
-  scale_shape_manual(values = c(16,15), guide = FALSE) + 
-  geom_errorbarh(aes(xmin = diff - diff_se, xmax = diff + diff_se),  
-                 size = 0.2, height = 0,
-                 position = ggstance::position_dodgev(height = 0.75)) + 
-  #scale_colour_discrete(guide = ggplot2::guide_legend(title = "Reference Category")) +
-  scale_colour_manual(values = c("gray", "red"), guide = ggplot2::guide_legend(title = "Estimate Type")) +
-  scale_x_continuous(oob = scales::rescale_none) +
-  ylab("") +
-  xlab("Estimated Difference") + 
-  theme_minimal() + 
-      ggplot2::theme(
-        legend.position = "right",
-        panel.grid.major = ggplot2::element_blank(),
-        panel.grid.minor = ggplot2::element_blank()
-      )
-@
+\end{knitrout}
 

### 2018-02-20 data/hainmueller.R

@@ -1,0 +1,669 @@
+
+# scripts for plots in Causal Inference in Conjoint Analysis:
+# Understanding Multidimensional Choices via Stated Preference Experiments
+# Jens Hainmueller, Daniel Hopkins, Teppei Yamamoto
+rm(list=ls())
+library("ggplot2")
+
+# Figure 2: Candidate Conjoint
+results   <- c("Candrating.txt","Candchoiche.txt")
+ffilenames<- c("Fig2a","Fig2b")
+yylabs <- c("Change: Candidate Rating (0 'never support' - 1 'always support')",
+            "Change: Pr(Prefer Candidate for President)")
+yylims <- list(c(-.2, .2),c(-.4, .4))
+
+for(i in 1:2){
+
+# load estimatesfrom Stata 
+d <- read.table(paste(results[i]))
+ffilename <- ffilenames[i]
+yylab <- yylabs[i]
+yylim <- yylims[[i]]
+
+d$var <- rownames(d)
+colnames(d)[2] <- c("se")
+colnames(d) <- c("pe","se","var")
+
+# compute Cis
+d$upper <-d$pe + 1.96*d$se
+d$lower <-d$pe - 1.96*d$se
+
+# group vars
+Military     <- paste(c("1b",2),".atmilitary",sep="")
+Religion     <- paste(c("1b",2:6),".atreligion",sep="")
+Education    <- paste(c("1b",2:6),".ated",sep="")
+Profession   <- paste(c("1b",2:6),".atprof",sep="")
+Gender       <- paste(c("1b",2),".atmale",sep="")
+Income       <- paste(c("1b",2:6),".atinc",sep="")
+Race         <- paste(c("1b",2:6),".atrace",sep="")
+Age          <- paste(c("1b",2:6),".atage",sep="")
+
+d$gruppe <- NA
+d$gruppe[d$var %in% Military]       <- "Military"
+d$gruppe[d$var %in% Religion]       <- "Religion"
+d$gruppe[d$var %in% Education]       <- "Education"
+d$gruppe[d$var %in% Profession]       <- "Profession"
+d$gruppe[d$var %in% Gender]       <- "Gender"
+d$gruppe[d$var %in% Income]       <- "Income"
+d$gruppe[d$var %in% Race]       <- "Race"
+d$gruppe[d$var %in% Age]       <- "Age"
+
+offset <- c("   ")
+
[…]

### 2018-02-22 manuscript.Rnw
continue working on graphs and manuscript

@@
 
-<<r hidden, eval=FALSE, echo=FALSE, results="hide">>=
+<<hidden, eval=FALSE, echo=FALSE, results="hide">>=
 # setwd("c:/users/thomas/dropbox/brexit identity/papers/subgroupanalysis")
@@
 
-<<r knitr_options, echo=FALSE, results="hide">>=
+<<knitr_options, echo=FALSE, results="hide">>=
 knitr::opts_chunk$set(cache = TRUE, echo=FALSE, results="hold", warning=FALSE)
 options(scipen = 10)
+@
+
+<<setup>>=
+library("ggplot2")
+requireNamespace("ggstance", quietly = TRUE)
+library("cregg")
+@
+
+<<data>>=
+data(hainmueller)
+hainmueller$ethnocentrism_split <- ifelse(is.na(hainmueller$ethnocentrism), NA_real_, ifelse(hainmueller$ethnocentrism > 10, 1, 0))
+hainmueller$ethnocentrism_split <- factor(hainmueller$ethnocentrism_split, levels = c(0,1), labels = c("low", "high"))
 @
@@
 While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object.
+This is particularly the case when researchers engage in subgroup analyses of conjoint experiments.
+For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.\footnote{This is achieved by subsetting the data based upon the measure of ethnocentrism and performing separate regressions for high- and low-ethnocentrism respondents.} The interpretation therefore focuses not just on the arbitrarily signed AMCEs within each subgroup (what Hainmueller et al.
+term ``conditional AMCEs''; 13) but also on an implied quantity of interest: the difference between conditional AMCEs.
+The difference in AMCEs is then used to \textit{descriptively} interpret apparent differences in preferences between the two groups.
+Yet what is not obvious in such analyses is that differences-in-preferences are not directly reflected in such differences-in-AMCEs.
+Indeed, where preferences between the groups are similar, the difference in AMCEs can be large and where preferences diverge, the difference-in-AMCEs can be small.
+This is because the AMCE as a quantity of interest calculated against an arbitrarily chosen reference category for each factor level; where preferences between subgroups diverge in the reference category, the difference-in-AMCEs mislead about underlying preferences.
+
+In what follows, we formalize this problem of reference category choice and demonstrates how it is especially problematic when researchers engage in the now-common practice of comparing conditional AMCEs across respondent subgroups.
+The paper then demonstrates the problem using several example datasets and provides suggestions for improved reporting and interpretation based around a purely descriptive quantity of interest: namely, the unadjusted marginal means.
+Software for the R programming language that can be used to examine sensitivity of conjoint analysis to reference category selection and to calculate marginal means (as well as AMCEs) is also discussed.
+
+\section{Quantities of Interest}\label{sec:quantities}
+
+% AMCE
+<<hainmueller_immigration, dependson=c("data"), fig.height=10, fig.width=8, fig.cap="Replication of Hainmueller et al. (2014) Results">>=
+plot(
+  cj(
+   hainmueller, 
+   ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
+   id = ~ CaseID
+  )
+)
+@
+
+A fully randomized conjoint design (without constraints between profile features) is simply a full-factorial experiment.
+The ways of analyzing this experiment are numerous, including various forms of linear model statistics such pairwise comparisons between cell or factor means, linear regression, ANOVA, and so forth.
+In this section, we describe four quantities of interest that arise when analysing conjoint designs: average marginal component effects (AMCEs), conditional AMCEs, differences in conditional AMCEs, and marginal means.
+We discuss each in turn.
+
+First, in the \citet{HainmuellerHopkinsYamamoto2014} approach, the quantity of interest is shifted from the traditional linear model statistics used in traditional analysis of factorial experiments to a statistic nearly equivalent to the average marginal effect of each profile feature level, namely the \textit{average marginal component effect} (AMCE).
+In a fully randomized design, this statistic is equivalent to the average marginal effect of each feature level for a model where each feature is converted into a matrix of indicator variables for each level with one left out as a reference category.\footnote{In designs that entail constraints between profile features, the average marginal effect is a weighted average of effects across each combination of the constrained features where the weights of the effects are the design (display) probabilities of the feature combinations.}
+
+As an example, Figure \ref{fig:hainmueller_immigration} provides a replication of Hainmueller et al.'s (2014) results, showing the AMCEs for each experiment.
+The AMCEs provide for both causal and descriptive inferences.
+Because features are randomly assigned to respondents, differences in evaluations of profiles that vary according to a given feature are causally interpretable as the effect of that randomly assigned profile variation.
+Yet while randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object.
 For example, \citet{HainmuellerHopkinsYamamoto2014} describe some of the results of their conjoint analysis of congressional candidate preferences:
@@
 The results would be \textit{numerically equivalent} --- because ultimately the choice of reference category is completely arbitrary and mathematicaly irrelevant --- but the choice as sizable consequences for the interpretation of conjoint analyses.
-
-This is particularly the case when researchers engage in subgroup analyses of conjoint experiments.
-For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.\footnote{This is achieved by subsetting the data based upon the measure of ethnocentrism and performing separate regressions for high- and low-ethnocentrism respondents.} The interpretation therefore focuses not just on the arbitrarily signed AMCEs within each subgroup (what Hainmueller et al.
-term ``conditional AMCEs''; 13) but also on an implied quantity of interest: the difference between conditional AMCEs.
-This comparison seems intuitively correct but because the conditional AMCEs are causal effects expressed relative to an arbitrary baseline, the differences between AMCEs only convey a difference in preference to the extent that the reference category is equally liked by both groups.
-When the preferences toward the reference category differ substantially between groups, the difference in AMCEs is a biased estimate of the difference in preferences between the two groups.
-For example, \citet{HainmuellerHopkinsYamamoto2014} eyeball the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22).
-Yet simply because the AMCEs are similar does not necessarily mean that \textit{preferences} are similar.
-
-To bring some intuition to this problem, consider a simple two-condition experiment in which the effect of the treatment, $x \in {0,1}$, is compared across a single two-category covariate, $z \in {0,1}$.
-Subgroup regression equations might be:
-
-\begin{align*}
-\hat{y} &= \beta_0 + \beta_1 x, \quad \forall z = 0 \\
-\hat{y} &= \beta_2 + \beta_3 x, \quad \forall z = 1
-\end{align*}
-
-\noindent The effect of $x$ when $z=0$ is given by $\beta_1$.
-The effect of $x$ when $z=1$ is given by $\beta_3$.
-These are, in essence, the conditional AMCEs in a conjoint analysis.
-yet the difference in AMCEs ($\beta_3 - \beta_1$) is not equal to the differnce in preferences between the two groups, which is $\bar{y}_{z=1|x=1} - \bar{y}_{z=0|x=1}$, or estimated by $(\beta_2 + \beta_3) - (\beta_0 + \beta_1)$.
-The difference in AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$.
-Yet the standard AMCE-centric conjoint analysis does not present or characterize either of these quantities.
-And given that the reference category is arbitrary, there is never any reason to expect that an arbitrarily selected reference category satisfies that equality assumption, meaining that when one uses a difference in AMCEs to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.
-
-Worse, because conjoint analysis generates a sparse feature matrix (where there is never any guarantee that a particular combination of feature levels is observed in the data), it is also not possible to empirically select an appropriate set of reference categories using data.
-And while it might seem possible to select a \textit{marginally} appropriate reference category (i.e., one where preferences are similar with respect to a given feaure), preferences toward that reference category may differ across other dimensions in the analysis.
-Thus, there is no way to use conditional AMCEs or differences-in-AMCEs to convey the underlying similarity or differences in preferences across sample subgroups.
-
-In what follows, we formalize how the arbitrary selection of a reference category can mislead researchers about the pattern of preferences exposed by a conjoint experiment and demonstrates how this problem is especially problematic when researchers engage in the now-common practice of comparing conditional AMCEs across respondent subgroups.
-The paper then demonstrates the problem using several example datasets and provides suggestions for improved reporting and interpretation based around a purely descriptive quantity of interest: namely, the unadjusted marginal means.
-Software for the R programming language to easily calculate marginal means (as well as AMCEs) is also discussed.
-
-\section{Quantities of Interest}
-
-% AMCE
+We return to this issue below.
 
 % Difference in conditional AMCEs
-
-\citet{RatkovicTingley2017} considered efficient methods for performing subgroup analyses in conjoint designs.
-Our focus here is on the narrower problem of interpreting subgroup analyses as traditionally performed.
-
 \begin{table}
-\caption{Uses of Subgroup Analysis in Published Work}
+\caption{Uses of Subgroup Analysis in Published Work}\label{tab:papers}
 \begin{center}
@@
 
+Second, in practice, researchers do not only analyze conjoint designs using the AMCE statistic for the sample as a whole.
+They also frequently report \textit{conditional} AMCEs, wherein AMCEs are calculated separately for subgroups of respondents and those conditional estimates are directly compared.
+Table \ref{tab:papers} reports a list of recent published articles in political science that engage in this form of subgroup analysis.\footnote{\citet{RatkovicTingley2017} considered efficient methods for performing subgroup analyses in conjoint designs.
+Our focus here is on the narrower problem of interpreting subgroup analyses as traditionally performed.}
+
+Third, while analyzing subgroup preferences is in principle unproblematic, the comparison of subgroup conditional AMCEs involves an implied quantity of interest that \citet{HainmuellerHopkinsYamamoto2014} did not explicitly discuss: namely, the \textit{difference-in-AMCEs}.
+For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} eyeball the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22).
+The difference in AMCEs is thus used as a way of characterizing differences in underlying preferences between groups.
+While AMCEs do provide insight into the descriptive variation in preferences within-group and across-features, this act of interpretation is not necessarily valid between-groups.
+This is an issue we return to below.
+
 % Marginal means
+Finally, an alternative quantity of interest in any experiment (but one not discussed by \citealt{HainmuellerHopkinsYamamoto2014}) is the treatment group mean outcome.
+Comparisons of this quantity of interest across experimental conditions ultimately underlies causal inference yet it is not widely used in conjoint analysis.
+One reason for this is that the high-dimensionality of conjoint designs --- and the resulting data sparsity --- means that it is not typically possible to calculate mean outcomes for every possible combination of feature levels.
 
-\section{Challenges of Interpretation}
+Yet traditional analysis of factorial experiments provides a closely related measure that leverages the independent randomization of experimental factors to provide a useful insight into the distribution of outcomes across levels of each feature.
+This \textit{marginal mean} is, in essence, the mean outcome in each treatment condition taking factors one-at-a-time; in the case of conjoint designs, this means examining the mean outcome when a given feature level is present versus not present.
+In conjoint designs, the marginal mean outcome for a given feature level is a descriptively useful quantity that conveys the preferences of respondents toward profiles that have that feature level, averaging across co-occurrences with levels of all other features.
+In a forced-choice design, this quantity can be read as: given a profile contains level $x_i$ of feature $x$, the proportion of times respondents choose that profile is the marginal mean for that feature level.
+In forced choice designs (with two alternatives), this bounds the marginal means between 0 and 1 with the further constraint that the average of marginal means for levels of a given factor is definitionally equal to 0.5.\footnote{It is not possible for the marginal mean to ever equal zero or one if it possible for pairs of profiles shown together to both have the same level of a given feature (for example, both immigrants are from Germany).
+Instead, the marginal mean can range from the probability of co-occurrence to 1 minus that probability.
+If there are five levels of a feature, each shown with equal probability, then $Pr(Co-occurrence) = \frac{1}{5}*\frac{1}{5} = 0.04$ such that the marginal mean can take values in the range $(0.04,0.96)$.
+If the design is constrained so that features cannot be the same for both immigrants, then the marginal means fully range from zero to one.} In non-forced designs, the marginal means can vary arbitrarily along the outcome scale used.
 
-% baseline levels of features
-
-% subgroup analyses
-
-% difference in AMCEs versus difference in marginal means
-
-<<r setup>>=
-library("ggplot2")
-requireNamespace("ggstance")
-library("cregg")
-@
-
-<<r data>>=
-data(hainmueller)
-hainmueller$ethnocentrism_split <- ifelse(is.na(hainmueller$ethnocentrism), NA_real_, ifelse(hainmueller$ethnocentrism > 10, 1, 0))
-hainmueller$ethnocentrism_split <- factor(hainmueller$ethnocentrism_split, levels = c(0,1), labels = c("low", "high"))
-@
-
-The following figure provides a replication of Hainmueller et al.'s (2014) results:
-
-<<r hainmueller_immigration, dependson=c("data"), fig.height=10, fig.width=8>>=
+<<hainmueller_immigration_mm, dependson=c("data"), fig.height=10, fig.width=8, fig.cap="Replication of Hainmueller et al. (2014) using Marginal Means">>=
 plot(
@@
    ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
-   id = ~ CaseID
-  )
+   id = ~ CaseID,
+   estimate = "mm"
+  ), vline = 0.5
 )
@@
 
-\clearpage
+As an example, Figure \ref{fig:hainmueller_immigration_mm} shows marginal means for the immigration experiment from \citet{HainmuellerHopkinsYamamoto2014}.
+The results provide a close visual analogue to the AMCEs shown in Figure \ref{fig:hainmueller_immigration}.
+The differences are, however, two-fold: 1) rather than a single level of feature being set aside as a reference category, marginal means (and their variances) are estimated for all levels of every feature; and 2) the marginal means vary around the grand mean of the outcome rather than around 0.
+In the forced-choice design used by Hainmueller et al., this means all marginal means center at 0.5.
 
-<<r functions>>=
-amces_by_reference <- function(data, variable, formula) {
-    # get levels
-    levs <- levels(data[[variable]])
+\section{Challenges of Interpretation}\label{sec:challenges}
 
-    # loop over levels
-    out <- list()
-    for (i in seq_along(levs)) {
-        data[[variable]] <- relevel(data[[variable]], levs[i])
-        out[[i]] <- cj(data, formula, id = ~ CaseID)
-        out[[i]][["ref_category"]] <- levs[i]
-    }
+With quantities of interest now defined, this section describes three issues related to the focus on average marginal component effects as the main quantity of interest in the analysis of conjoint designs.
+First, that the selection of the reference category for each feature level is arbitrary thus leading to potential failures of intuition due to the numerical equivalence but intuitive distinctions in results using different reference categories.
+Second, that subgroup analyses of conjoint designs that rely upon AMCEs analytically confuse differences in conditional AMCEs with differences-in-preferences, despite their non-equivalence.
+And finally, that unadjusted marginal means as a quantity of interest are not susceptible to either of the preceding two concerns and therefore provide a more useful measure for describing preferences in conjoint designs than analysis based upon causally interpretable AMCEs.
 
-    # return value
-    out <- do.call("rbind", out)
-    out[["ref_category"]] <- factor(out[["ref_category"]], levels = levs)
-    class(out) <- c("cj_amce", "data.frame")
-    out
-}
-@
+\subsection{Arbitrary reference category choice}\label{sec:reference}
 
-\section{Arbitrary reference category choice}
+<<reference_category, dependson=c("data"), fig.width=8, fig.height=5, fig.cap="Reference Category Diagnostic for the 'Country of Origin' Feature from Hainmueller et al. (2014)">>=
+x <- amce_by_reference(hainmueller, ChosenImmigrant ~ CountryOfOrigin, ~ CountryOfOrigin, id = ~CaseID)
 
-<<r reference_category, dependson=c("data"), fig.width=8, fig.height=5>>=
-x <- amces_by_reference(hainmueller, "CountryOfOrigin", ChosenImmigrant ~ CountryOfOrigin)
-
-ggplot(x, aes(x = estimate, y = level, group = ref_category, colour = level)) +
+ggplot(x, aes(x = estimate, y = level, group = .reference, colour = .reference)) +
   geom_vline(xintercept = 0, colour = "gray") +
@@
 
-<<r marginal_means, fig.width=8, fig.height=5>>=
-plot(mm(hainmueller, ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID), vline = 0.5, xlim = c(0,1))
+\subsection{Subgroup Analysis}\label{sec:subgroup}
+
+A conventional presentation of subgroup analyses in a conjoint design is shown in the top panel of Figure \ref{fig:subgroup_results}.
+Note how the conditional AMCEs for several levels --- Somalia, Sudan, China, Mexico, and Philippines --- flip signs.
+While both negative, it also appears that high ethnocentrism respondents are substantially more negative toward immigrants from Iraq.
+By contrast, the AMCEs for the two groups for immigrants from Poland, France, Germany (and India, the reference category) are quite similar.
+The lower panel of Figure \ref{fig:subgroup_results} shows an alternative analysis: namely, marginal means for both subgroups.
+
+While the differences in preferences as measured by unadjusted marginal means for the two subgroups for immigrants from Somalia and Sudan do appear to differ (as reflected in the AMCEs), the differences in preferences for immigrants from Iraq, China, and the Philippines are indistinguishable from zero.
+Apparent similarity in the patterns of AMCE mask where and in what direction preferences for the two subgroups differ.
+
+<<subgroup_results, dependson=c("data"), fig.width=8, fig.height=5, fig.cap="Subgroup Analysis for the 'Country of Origin' Feature from Hainmueller et al. (2014)">>=
+# AMCEs
+plot(cj(hainmueller, ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "amce", by = ~ ethnocentrism_split), vline = 0, group = "ethnocentrism_split", legend_title = "Ethnocentrism")
+# Marginal Means
+plot(cj(hainmueller, ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "mm", by = ~ethnocentrism_split), vline = 0.5, group = "ethnocentrism_split", legend_title = "Ethnocentrism")
 @
 
-\clearpage
+Take, for example, the fact that underlying differences in preferences between the two groups are largest for immigrants from Mexico and Poland.
+While low ethnocentrism respondents are indifferent about respondents from Poland, high ethnocentrism respondents favor them substantially.
+While low ethnocentrism are slightly favorable toward immigrants from Mexico, high ethnocentrism respondents are slightly opposed to immigrants from that country.
+The difference in preferences toward immigrants from Mexico is reflected in the pattern of AMCEs but the difference in preferences toward immigrants from Poland is not.
+Why?
 
-\section{Subgroup Analysis}
-
-A conventional presentation of subgroup analyses in a conjoint design is as follows.
-Note how the conditional AMCEs for several levels - Somalia, Sudan, China, Mexico, and France - flip signs.
-Yet the largest differences in preferences between the two groups are for Germany, France, Poland, and Somalia.
-Apparently similar patterns of AMCE mask where and in what direction preferences for the two subgroups differ.
-
-<<r subgroup_results_amce, dependson=c("data"), fig.width=8, fig.height=5>>=
-by_split <- lapply(c("low","high"), function(x) {
-    out <- cj(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "amce")
-    out$ethnocentrism_split <- x
-    out
-})
-x <- do.call("rbind", by_split)
-
-ggplot(x, aes(x = estimate, y = level, group = ethnocentrism_split, colour = ethnocentrism_split)) +
-  geom_vline(xintercept = 0, colour = "gray") +
-  geom_point(position = ggstance::position_dodgev(height = 0.75)) +
-  geom_errorbarh(aes(xmin = lower, xmax = upper),  
-                 size = 0.2, height = 0,
-                 position = ggstance::position_dodgev(height = 0.75)) + 
-  scale_colour_discrete(guide = ggplot2::guide_legend(title = "Ethnocentrism")) +
-  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
-  ylab("") +
-  xlab("Estimated AMCE") + 
-  theme_minimal() + 
-      ggplot2::theme(
-        legend.position = "bottom",
-        panel.grid.major = ggplot2::element_blank(),
-        panel.grid.minor = ggplot2::element_blank()
-      )
-@
-
-<<r subgroup_marginal_means, dependson=c("data"), fig.width=8, fig.height=5>>=
-plot(cj(hainmueller, ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "mm", by = ~ethnocentrism_split), vline = 0.5, group = "ethnocentrism_split")
-@
-
-As we can see, however, while the difference in marginal means conveys the fixed difference in preferences between the two groups, the apparent difference in preferences between groups conveyed by a difference-in-AMCEs is sensitive to the reference category chosen when estimating the effects:
-
-\clearpage
-
-<<r subgroup_results_mm, dependson=c("data"), fig.width=10, fig.height=10>>=
+<<hainmueller_subgroup_differences, dependson=c("data"), fig.width=10, fig.height=10, fig.cap="Differences in Marginal Means and AMCEs, by Ethnocentrism, from Hainmueller et al. (2014)">>=
 # difference in marginal means
@@
 x_mm[["diff_se"]] <- sqrt(x_mm[["std.error.high"]]^2 + x_mm[["std.error.low"]]^2)
-x_mm[["ref_category"]] <- "Marginal Mean"
+x_mm[[".reference"]] <- "Marginal Mean"
 
@@
 by_split_amce <- lapply(levels(hainmueller$ethnocentrism_split), function(x) {
-    out <- amces_by_reference(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), "CountryOfOrigin", ChosenImmigrant ~ CountryOfOrigin)
+    out <- amce_by_reference(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), ChosenImmigrant ~ CountryOfOrigin, ~ CountryOfOrigin, id = ~ CaseID)
     out$ethnocentrism_split <- x
@@
 })
-x_amce <- merge(by_split_amce[[1]], by_split_amce[[2]], by = c("level", "ref_category"), suffixes = c(".low", ".high"))
+x_amce <- merge(by_split_amce[[1]], by_split_amce[[2]], by = c("level", ".reference"), suffixes = c(".low", ".high"))
 ## difference
@@
 
-x_merged <- rbind(x_mm[c("level", "diff", "diff_se", "ref_category")], x_amce[c("level", "diff", "diff_se", "ref_category")])
-x_merged[["ref_category"]] <- factor(x_merged[["ref_category"]], levels = c("Marginal Mean", levels(x_amce[["ref_category"]])))
-x_merged[["is_mm"]] <- ifelse(x_merged[["ref_category"]] == "Marginal Mean", "Difference in MMs", "Difference in AMCEs")
+x_merged <- rbind(x_mm[c("level", "diff", "diff_se", ".reference")], x_amce[c("level", "diff", "diff_se", ".reference")])
+x_merged[[".reference"]] <- factor(x_merged[[".reference"]], levels = c("Marginal Mean", levels(x_amce[[".reference"]])))
+x_merged[["is_mm"]] <- ifelse(x_merged[[".reference"]] == "Marginal Mean", "Difference in MMs", "Difference in AMCEs")
 
-ggplot(x_merged, aes(x = diff, y = level, group = ref_category, colour = is_mm, shape = is_mm)) +
+ggplot(x_merged, aes(x = diff, y = level, group = .reference, colour = is_mm, shape = is_mm)) +
   geom_vline(xintercept = 0, colour = "gray") +
@@
 
-Indeed, the difference in AMCEs most closely approximates the difference in marginal means (and thus the descriptive difference in preferences) when the true difference in preferences in the reference category is close to zero.
-For example, in the above figure differences in AMCEs are shown in gray and differences in marginal means are shown in red, for respondents scoring above-median (high) and below-median (low) in ethnocentrism for each possible country of origin in Hainmueller et al.'s (2014) immigration experiment.
-The difference in marginal means between high and low ethnocentrism respondents is smallest for immigrants arriving from Iraq.
-When Iraq is used as the reference category, the AMCE of Iraq is fixed at zero and the between-group difference in AMCEs is thus, by definition, also fixed at zero.
-These estimates are shown at the top of each grouping - as should be readily clear, when Iraq is used as the reference category, the difference in AMCEs for each of the other possible origin countries closely approximates (but does not exactly equal) the difference in marginal means for that origin country.
-Were there no feature level for which the two groups held similar preferences, then there would be no reference category that would generate differences in AMCES that were close to the difference in underlying marginal means.
+While the difference in marginal means conveys the fixed difference in revealed preferences between the two groups, the apparent difference in preferences between groups conveyed by a difference-in-AMCEs is sensitive to the reference category chosen when estimating the effects.
+Figure \ref{fig:fig:hainmueller_subgroup_differences} shows the results of a diagnostic procedure for examining the sensitivity of differences-in-AMCEs to the choice of reference category.
+The difference in preferences as measured by marginal means for each feature level is shown in red.
+The differences in preferences as measured by difference-in-AMCEs are shown in gray, with the difference calculated separately for each of the 10 possible reference categories.
 
-When other origin countries are used as the reference category (wherein the underlying difference in preferences between high ethnocentrism and low enthnocentrism respondents is greater), then the difference in AMCEs provides biased estimates of the difference in preferences.
-Take, for example, the difference in preferences over immigrants from China, where high ethnocentrism respondents are less favourable to these immigrants than low ethnocentrism respondents.
-The difference in marginal means is -0.033.
-Yet differences in AMCEs for Chinese immigrants vary substantially depending on which other category is chosen as the baseline.
-If China is the baseline, the apparent difference in preferences is zero (definitionally).
-While in most cases the difference in AMCEs takes the same sign as the difference in marginal means, when either Mexico or Sudan is used as the reference category the apparent difference in preferences flips signs: high ethnocentrism respondents appear to be more rather than less favorable toward Chinese immigrants when the AMCEs are estimated in that way.
+Thus, in the top-most set of bars (labelled ``Iraq''), the difference-in-AMCEs when Iraq is the reference category is definitionally fixed at zero and not estimated.
+Iterating through the other possible reference categories, the estimated difference-in-AMCEs when Somalia, Sudan, China, Poland, or the Philippines is chosen as a reference category and negative otherwise.
+In other words, when any of those five countries is chosen as the reference category, it appears that high ethnocentrism respondents are more favorable toward immigrants from Iraq than low ethnocentrism respondents; when any other country is chosen, the apparent difference in preferences toward immigrants from Germany is the opposite.
+That is deeply problematic.
 
-Yet the graph also makes clear that the differences in AMCEs all center upon the true difference in marginal means in a fixed manner.
+This sign-flipping demonstrates why the differences in subgroup preferences toward immigrants from Mexico is demonstrated in the AMCEs but the difference in preferences toward immigrants from Poland is not.
+Because India is used as the baseline level and the difference preferences of the two groups toward immigrants from India is similar to the difference in preferences of the two groups toward immigrants from Poland (i.e., the difference-in-differences is close to zero), the subgroup AMCEs are similar.
+The difference in preferences between the groups for immigrants from Mexico is opposite that of the difference in preferences for the reference category (India), so the difference in AMCEs is substantial.
 
-Thus the choice of reference category - while seemingly irrelevant - has dramatic inferential consequences.
+To generalize this problem away from the specific example at-hand, the conditional AMCEs are causal effects expressed relative to an arbitrary baseline such that the differences between AMCEs only convey a difference in preference to the extent that the reference category is equally liked by both groups.
+When the preferences toward the reference category differ substantially between groups, the difference in AMCEs is a biased estimate of the difference in preferences between the two groups.
+Similarly, even if the AMCEs are similar, it does not necessarily mean that \textit{preferences} are similar.
 
-\section{Suggested Approaches}
+To bring some general intuition to this problem, consider a simple two-condition experiment in which the effect of the treatment, $x \in {0,1}$, is compared across a single two-category covariate, $z \in {0,1}$.
+Subgroup regression equations might be:
 
-% Present marginal means overall and for specific subgroups of interest
+\begin{align*}
+\hat{y} &= \beta_0 + \beta_1 x, \quad \forall z = 0 \\
+\hat{y} &= \beta_2 + \beta_3 x, \quad \forall z = 1
+\end{align*}
 
-\section{Conclusion}
+\noindent The effect of $x$ when $z=0$ is given by $\beta_1$.
+The effect of $x$ when $z=1$ is given by $\beta_3$.
+These are, in essence, the conditional AMCEs in a conjoint analysis.
+yet the difference in AMCEs ($\beta_3 - \beta_1$) is not equal to the differnce in preferences between the two groups, which is $\bar{y}_{z=1|x=1} - \bar{y}_{z=0|x=1}$, or estimated by $(\beta_2 + \beta_3) - (\beta_0 + \beta_1)$.
+The difference in AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$.
+Yet the standard AMCE-centric conjoint analysis does not present or characterize either of these quantities.
+And given that the reference category is arbitrary, there is never any reason to expect that an arbitrarily selected reference category satisfies that equality assumption, meaning that when one uses a difference in AMCEs to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.
+
+Worse, because conjoint analysis generates a sparse feature matrix (where there is never any guarantee that a particular combination of feature levels is observed in the data), it is also not possible to empirically select an appropriate set of reference categories using the data.
+And while it might seem possible to select a \textit{marginally} appropriate reference category (i.e., one where preferences are similar with respect to a given feaure), preferences toward that reference category may differ across other dimensions in the analysis.
+Thus, there is no way to use conditional AMCEs or differences-in-AMCEs to convey the underlying similarity or differences in preferences across sample subgroups.
+
+\subsection{Analysing Subgroup Preferences Using Marginal Means}\label{sec:marginalmeans}
+
+It is worth highlighting two important and perhaps obvious feature of the reference category diagnostic, such as that shown in Figure \ref{fig:fig:hainmueller_subgroup_differences}.
+First, the differences in AMCEs mechanically vary around the difference in marginal means, as the reference category varies.
+Thus the pattern of variation in differences in AMCEs for all of the countries look the same (simply moving left or right on the horizontal axis).
+The difference between marginal means for two countries are always fixed by the data, so the differencing of subgroup AMCEs is merely an exercise is centering those differences at arbitrary points along the range of observed differences in marginal means.
+Differences-in-AMCEs for a given feature level are therefore necessarily sometimes positive and sometimes negative, depending on the reference category used in estimating them.
+The direction of the difference per se conveys no information about underlying preferences.
+
+Second, and more practically, because there is no category for which the preferences of the two subgroups in this example are identical, no choice of reference category will lead to inferences from differences-in-AMCEs that accurately reflect the underlying difference in preferences.
+Were there a category for which preferences were equivalent, that could be sensibly chosen as the reference category in order to be able to interpret differences-in-AMCEs as differences in preferences.
+There is never any guarantee, however, that such a reference category exists in any given experimental dataset.
+
+The choice of reference category --- while seemingly irrelevant --- has dramatic inferential consequences.
+To make this even more concrete, consider the two panels of Figure \ref{fig:hainmueller_subgroup_example}, which show the exact same analysis (comparing AMCEs for high and low ethnocentrism respondents) on the same experimental data.
+In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in preferences between the two subgroups.
+In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.
+
+<<hainmueller_subgroup_example, dependson=c("data")>>=
+# estimates benchmarked to largest difference between subgroups
+hainmueller.A <- hainmueller
+	hainmueller.A$Education <- relevel(hainmueller.A$Education, "No Formal")
+	hainmueller.A$Gender <- relevel(hainmueller.A$Gender, "Male")
+	hainmueller.A$CountryOfOrigin <- relevel(hainmueller.A$CountryOfOrigin, "Mexico")
+	hainmueller.A$ReasonForApplication <- relevel(hainmueller.A$ReasonForApplication, "Escape Persecution")
+	hainmueller.A$Job <- relevel(hainmueller.A$Job, "Doctor")
+	hainmueller.A$JobExperience <- relevel(hainmueller.A$JobExperience, "5+ Years")
+	hainmueller.A$JobPlans <- relevel(hainmueller.A$JobPlans, "No Plans to Look for Work")
+	hainmueller.A$PriorEntry <- relevel(hainmueller.A$PriorEntry, "Once w/o Authorization")
+	hainmueller.A$LanguageSkills <- relevel(hainmueller.A$LanguageSkills, "Used Interpreter")
+# estimates benchmarked to smallest difference between subgroups
+hainmueller.B <- hainmueller
+	hainmueller.B$Education <- relevel(hainmueller.B$Education, "College Degree")
+	hainmueller.B$Gender <- relevel(hainmueller.B$Gender, "Female")
+	hainmueller.B$CountryOfOrigin <- relevel(hainmueller.B$CountryOfOrigin, "Iraq")
+	hainmueller.B$ReasonForApplication <- relevel(hainmueller.B$ReasonForApplication, "Reunite with Family")
+	hainmueller.B$Job <- relevel(hainmueller.B$Job, "Child Care Provider")
+	hainmueller.B$JobExperience <- relevel(hainmueller.B$JobExperience, "None")
+	hainmueller.B$JobPlans <- relevel(hainmueller.B$JobPlans, "Interviews with Employer")
+	hainmueller.B$PriorEntry <- relevel(hainmueller.B$PriorEntry, "Never")
+	hainmueller.B$LanguageSkills <- relevel(hainmueller.B$LanguageSkills, "Broken English")
+# formula
+f <- ChosenImmigrant ~ LanguageSkills + CountryOfOrigin + Job + Education + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Gender
+# estimate
+amce_by_ethnocentrism_1 <- cj(hainmueller.A, f, id = ~ CaseID, estimate = "amce", by = ~ ethnocentrism_split)
+amce_by_ethnocentrism_2 <- cj(hainmueller.B, f, id = ~ CaseID, estimate = "amce", by = ~ ethnocentrism_split)
+# tag datasets and merge
+amce_by_ethnocentrism_1$dataset <- "A"
+amce_by_ethnocentrism_2$dataset <- "B"
+amce_ref_example_merged <- rbind(amce_by_ethnocentrism_1, amce_by_ethnocentrism_2)
+@
+
+<<hainmueller_subgroup_example_plot, dependson=c("data", "hainmueller_subgroup_example"), fig.width=10, fig.height=10>>=
+plot(amce_ref_example_merged, group = "ethnocentrism_split", feature_headers = FALSE, legend_title = "Ethnocentrism", vline = 0) + 
+  facet_wrap(feature ~ dataset, ncol = 2L, scales = "free_y", strip.position = "right", labeller = function(x) label_value(x, multi_line = FALSE)) +
+  theme(strip.text.x = element_text(size = 4))
+@
+
+In our view, the panel B is the more truthful visualization \citep{Cairo2016}.
+The differences between subgroup AMCEs more accurately convey differences in underlying preferences.
+Panel A, by contrast, leads the reader to suspect sometimes sizable difference in views along the dimensions of language skills, country of origin, job, and education, among others.
+
+% higher order margins
+
+\section{Conclusion}\label{sec:conclusion}
 
@@
 
+% Present marginal means overall and for specific subgroups of interest
+As should be clear from the above discussions, we have relatively straightforward and hopefully uncontroversial advice for how analysts of conjoint experiments should proceed:
+
+\begin{enumerate}
+\item Always report unadjusted marginal means when attempting to provide a \textit{descriptive} summary of respondent preferences in addition to or instead of AMCEs.
+Yet remain cautious about characterizing middling values as ambivalence as opposed to an unobserved pattern of heterogeneity.
+
+\item When choosing reference categories for profile features, do so systematically based upon how the resulting AMCEs will be interpreted.
+Sensible choices are setting each feature's reference category to the marginal least (marginally most) preferred level, such that all AMCEs for all features are either all positive (negative).
+
+\item Exercise extreme caution when explicitly or implicitly interpreting differences in AMCEs across subgroups given that this quantity is almost always a biased estimate (of unknown sign) of the difference in preferences.
+If differences in AMCEs are reported, the choice of reference categories should be discussed explicitly and diagnostics should be provided.
+\end{enumerate}
+
+% some big conclusion
+
 \singlespacing
 \bibliographystyle{apsa-leeper}
-\bibliography{References}
+\bibliography{references}
 \clearpage
 
+\appendix
+
+\section{Additional Results}
+
+The below figure shows full marginal means for high and low ethnocentrism respondents for all feature levels.
+
+<<hainmueller_mm_by_ethnocentrism, fig.height = 10, fig.width=10>>=
+mm_by_ethnocentrism <- cj(hainmueller, ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry, id = ~ CaseID, estimate = "mm", by = ~ ethnocentrism_split)
+plot(mm_by_ethnocentrism, group = "ethnocentrism_split", legend_title = "Ethnocentrism", vline = 0.5)
+@
+
 \end{document}

### 2018-02-22 manuscript.tex
continue working on graphs and manuscript

@@
 While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object.
+This is particularly the case when researchers engage in subgroup analyses of conjoint experiments.
+For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.\footnote{This is achieved by subsetting the data based upon the measure of ethnocentrism and performing separate regressions for high- and low-ethnocentrism respondents.} The interpretation therefore focuses not just on the arbitrarily signed AMCEs within each subgroup (what Hainmueller et al.
+term ``conditional AMCEs''; 13) but also on an implied quantity of interest: the difference between conditional AMCEs.
+The difference in AMCEs is then used to \textit{descriptively} interpret apparent differences in preferences between the two groups.
+Yet what is not obvious in such analyses is that differences-in-preferences are not directly reflected in such differences-in-AMCEs.
+Indeed, where preferences between the groups are similar, the difference in AMCEs can be large and where preferences diverge, the difference-in-AMCEs can be small.
+This is because the AMCE as a quantity of interest calculated against an arbitrarily chosen reference category for each factor level; where preferences between subgroups diverge in the reference category, the difference-in-AMCEs mislead about underlying preferences.
+
+In what follows, we formalize this problem of reference category choice and demonstrates how it is especially problematic when researchers engage in the now-common practice of comparing conditional AMCEs across respondent subgroups.
+The paper then demonstrates the problem using several example datasets and provides suggestions for improved reporting and interpretation based around a purely descriptive quantity of interest: namely, the unadjusted marginal means.
+Software for the R programming language that can be used to examine sensitivity of conjoint analysis to reference category selection and to calculate marginal means (as well as AMCEs) is also discussed.
+
+\section{Quantities of Interest}\label{sec:quantities}
+
+% AMCE
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required namespace: ggstance}}\end{kframe}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/hainmueller_immigration-1} \caption[Replication of Hainmueller et al]{Replication of Hainmueller et al. (2014) Results}\label{fig:hainmueller_immigration}
+\end{figure}
+
+\end{knitrout}
+
+A fully randomized conjoint design (without constraints between profile features) is simply a full-factorial experiment.
+The ways of analyzing this experiment are numerous, including various forms of linear model statistics such pairwise comparisons between cell or factor means, linear regression, ANOVA, and so forth.
+In this section, we describe four quantities of interest that arise when analysing conjoint designs: average marginal component effects (AMCEs), conditional AMCEs, differences in conditional AMCEs, and marginal means.
+We discuss each in turn.
+
+First, in the \citet{HainmuellerHopkinsYamamoto2014} approach, the quantity of interest is shifted from the traditional linear model statistics used in traditional analysis of factorial experiments to a statistic nearly equivalent to the average marginal effect of each profile feature level, namely the \textit{average marginal component effect} (AMCE).
+In a fully randomized design, this statistic is equivalent to the average marginal effect of each feature level for a model where each feature is converted into a matrix of indicator variables for each level with one left out as a reference category.\footnote{In designs that entail constraints between profile features, the average marginal effect is a weighted average of effects across each combination of the constrained features where the weights of the effects are the design (display) probabilities of the feature combinations.}
+
+As an example, Figure \ref{fig:hainmueller_immigration} provides a replication of Hainmueller et al.'s (2014) results, showing the AMCEs for each experiment.
+The AMCEs provide for both causal and descriptive inferences.
+Because features are randomly assigned to respondents, differences in evaluations of profiles that vary according to a given feature are causally interpretable as the effect of that randomly assigned profile variation.
+Yet while randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object.
 For example, \citet{HainmuellerHopkinsYamamoto2014} describe some of the results of their conjoint analysis of congressional candidate preferences:
@@
 
+Second, in practice, researchers do not only analyze conjoint designs using the AMCE statistic for the sample as a whole.
+They also frequently report \textit{conditional} AMCEs, wherein AMCEs are calculated separately for subgroups of respondents and those conditional estimates are directly compared.
+Table \ref{tab:papers} reports a list of recent published articles in political science that engage in this form of subgroup analysis.\footnote{\citet{RatkovicTingley2017} considered efficient methods for performing subgroup analyses in conjoint designs.
+Our focus here is on the narrower problem of interpreting subgroup analyses as traditionally performed.}
+
+Third, while analyzing subgroup preferences is in principle unproblematic, the comparison of subgroup conditional AMCEs involves an implied quantity of interest that \citet{HainmuellerHopkinsYamamoto2014} did not explicitly discuss: namely, the \textit{difference-in-AMCEs}.
+For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} eyeball the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22).
+The difference in AMCEs is thus used as a way of characterizing differences in underlying preferences between groups.
+While AMCEs do provide insight into the descriptive variation in preferences within-group and across-features, this act of interpretation is not necessarily valid between-groups.
+This is an issue we return to below.
+
 % Marginal means
+Finally, an alternative quantity of interest in any experiment (but one not discussed by \citealt{HainmuellerHopkinsYamamoto2014}) is the treatment group mean outcome.
+Comparisons of this quantity of interest across experimental conditions ultimately underlies causal inference yet it is not widely used in conjoint analysis.
+One reason for this is that the high-dimensionality of conjoint designs --- and the resulting data sparsity --- means that it is not typically possible to calculate mean outcomes for every possible combination of feature levels.
 
-\section{Challenges of Interpretation}
+Yet traditional analysis of factorial experiments provides a closely related measure that leverages the independent randomization of experimental factors to provide a useful insight into the distribution of outcomes across levels of each feature.
+This \textit{marginal mean} is, in essence, the mean outcome in each treatment condition taking factors one-at-a-time; in the case of conjoint designs, this means examining the mean outcome when a given feature level is present versus not present.
+In conjoint designs, the marginal mean outcome for a given feature level is a descriptively useful quantity that conveys the preferences of respondents toward profiles that have that feature level, averaging across co-occurrences with levels of all other features.
+In a forced-choice design, this quantity can be read as: given a profile contains level $x_i$ of feature $x$, the proportion of times respondents choose that profile is the marginal mean for that feature level.
+In forced choice designs (with two alternatives), this bounds the marginal means between 0 and 1 with the further constraint that the average of marginal means for levels of a given factor is definitionally equal to 0.5.\footnote{It is not possible for the marginal mean to ever equal zero or one if it possible for pairs of profiles shown together to both have the same level of a given feature (for example, both immigrants are from Germany).
+Instead, the marginal mean can range from the probability of co-occurrence to 1 minus that probability.
+If there are five levels of a feature, each shown with equal probability, then $Pr(Co-occurrence) = \frac{1}{5}*\frac{1}{5} = 0.04$ such that the marginal mean can take values in the range $(0.04,0.96)$.
+If the design is constrained so that features cannot be the same for both immigrants, then the marginal means fully range from zero to one.} In non-forced designs, the marginal means can vary arbitrarily along the outcome scale used.
 
-% baseline levels of features
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
 
-% subgroup analyses
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required namespace: ggstance}}\end{kframe}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_mm-1} \caption[Replication of Hainmueller et al]{Replication of Hainmueller et al.
+(2014) using Marginal Means}\label{fig:hainmueller_immigration_mm}
+\end{figure}
 
-% difference in AMCEs versus difference in marginal means
+\end{knitrout}
 
-The following figure provides a replication of Hainmueller et al.'s (2014) results:
+As an example, Figure \ref{fig:hainmueller_immigration_mm} shows marginal means for the immigration experiment from \citet{HainmuellerHopkinsYamamoto2014}.
+The results provide a close visual analogue to the AMCEs shown in Figure \ref{fig:hainmueller_immigration}.
+The differences are, however, two-fold: 1) rather than a single level of feature being set aside as a reference category, marginal means (and their variances) are estimated for all levels of every feature; and 2) the marginal means vary around the grand mean of the outcome rather than around 0.
+In the forced-choice design used by Hainmueller et al., this means all marginal means center at 0.5.
+
+\section{Challenges of Interpretation}\label{sec:challenges}
+
+With quantities of interest now defined, this section describes three issues related to the focus on average marginal component effects as the main quantity of interest in the analysis of conjoint designs.
+First, that the selection of the reference category for each feature level is arbitrary thus leading to potential failures of intuition due to the numerical equivalence but intuitive distinctions in results using different reference categories.
+Second, that subgroup analyses of conjoint designs that rely upon AMCEs analytically confuse differences in conditional AMCEs with differences-in-preferences, despite their non-equivalence.
+And finally, that unadjusted marginal means as a quantity of interest are not susceptible to either of the preceding two concerns and therefore provide a more useful measure for describing preferences in conjoint designs than analysis based upon causally interpretable AMCEs.
+
+\subsection{Arbitrary reference category choice}\label{sec:reference}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/reference_category-1} \caption[Reference Category Diagnostic for the 'Country of Origin' Feature from Hainmueller et al]{Reference Category Diagnostic for the 'Country of Origin' Feature from Hainmueller et al.
+(2014)}\label{fig:reference_category}
+\end{figure}
+
+\end{knitrout}
+
+\subsection{Subgroup Analysis}\label{sec:subgroup}
+
+A conventional presentation of subgroup analyses in a conjoint design is shown in the top panel of Figure \ref{fig:subgroup_results}.
+Note how the conditional AMCEs for several levels --- Somalia, Sudan, China, Mexico, and Philippines --- flip signs.
+While both negative, it also appears that high ethnocentrism respondents are substantially more negative toward immigrants from Iraq.
+By contrast, the AMCEs for the two groups for immigrants from Poland, France, Germany (and India, the reference category) are quite similar.
+The lower panel of Figure \ref{fig:subgroup_results} shows an alternative analysis: namely, marginal means for both subgroups.
+
+While the differences in preferences as measured by unadjusted marginal means for the two subgroups for immigrants from Somalia and Sudan do appear to differ (as reflected in the AMCEs), the differences in preferences for immigrants from Iraq, China, and the Philippines are indistinguishable from zero.
+Apparent similarity in the patterns of AMCE mask where and in what direction preferences for the two subgroups differ.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/subgroup_results-1} \caption[Subgroup Analysis for the 'Country of Origin' Feature from Hainmueller et al]{Subgroup Analysis for the 'Country of Origin' Feature from Hainmueller et al.
+(2014)}\label{fig:subgroup_results1}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\maxwidth]{figure/subgroup_results-2} \caption[Subgroup Analysis for the 'Country of Origin' Feature from Hainmueller et al]{Subgroup Analysis for the 'Country of Origin' Feature from Hainmueller et al.
+(2014)}\label{fig:subgroup_results2}
+\end{figure}
+
+\end{knitrout}
+
+Take, for example, the fact that underlying differences in preferences between the two groups are largest for immigrants from Mexico and Poland.
+While low ethnocentrism respondents are indifferent about respondents from Poland, high ethnocentrism respondents favor them substantially.
+While low ethnocentrism are slightly favorable toward immigrants from Mexico, high ethnocentrism respondents are slightly opposed to immigrants from that country.
+The difference in preferences toward immigrants from Mexico is reflected in the pattern of AMCEs but the difference in preferences toward immigrants from Poland is not.
+Why?
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/hainmueller_subgroup_differences-1} \caption[Differences in Marginal Means and AMCEs, by Ethnocentrism, from Hainmueller et al]{Differences in Marginal Means and AMCEs, by Ethnocentrism, from Hainmueller et al.
+(2014)}\label{fig:hainmueller_subgroup_differences}
+\end{figure}
+
+\end{knitrout}
+
+While the difference in marginal means conveys the fixed difference in revealed preferences between the two groups, the apparent difference in preferences between groups conveyed by a difference-in-AMCEs is sensitive to the reference category chosen when estimating the effects.
+Figure \ref{fig:fig:hainmueller_subgroup_differences} shows the results of a diagnostic procedure for examining the sensitivity of differences-in-AMCEs to the choice of reference category.
+The difference in preferences as measured by marginal means for each feature level is shown in red.
+The differences in preferences as measured by difference-in-AMCEs are shown in gray, with the difference calculated separately for each of the 10 possible reference categories.
+
+Thus, in the top-most set of bars (labelled ``Iraq''), the difference-in-AMCEs when Iraq is the reference category is definitionally fixed at zero and not estimated.
+Iterating through the other possible reference categories, the estimated difference-in-AMCEs when Somalia, Sudan, China, Poland, or the Philippines is chosen as a reference category and negative otherwise.
+In other words, when any of those five countries is chosen as the reference category, it appears that high ethnocentrism respondents are more favorable toward immigrants from Iraq than low ethnocentrism respondents; when any other country is chosen, the apparent difference in preferences toward immigrants from Germany is the opposite.
+That is deeply problematic.
+
+This sign-flipping demonstrates why the differences in subgroup preferences toward immigrants from Mexico is demonstrated in the AMCEs but the difference in preferences toward immigrants from Poland is not.
+Because India is used as the baseline level and the difference preferences of the two groups toward immigrants from India is similar to the difference in preferences of the two groups toward immigrants from Poland (i.e., the difference-in-differences is close to zero), the subgroup AMCEs are similar.
+The difference in preferences between the groups for immigrants from Mexico is opposite that of the difference in preferences for the reference category (India), so the difference in AMCEs is substantial.
+
+To generalize this problem away from the specific example at-hand, the conditional AMCEs are causal effects expressed relative to an arbitrary baseline such that the differences between AMCEs only convey a difference in preference to the extent that the reference category is equally liked by both groups.
+When the preferences toward the reference category differ substantially between groups, the difference in AMCEs is a biased estimate of the difference in preferences between the two groups.
+Similarly, even if the AMCEs are similar, it does not necessarily mean that \textit{preferences} are similar.
+
+To bring some general intuition to this problem, consider a simple two-condition experiment in which the effect of the treatment, $x \in {0,1}$, is compared across a single two-category covariate, $z \in {0,1}$.
+Subgroup regression equations might be:
+
+\begin{align*}
+\hat{y} &= \beta_0 + \beta_1 x, \quad \forall z = 0 \\
+\hat{y} &= \beta_2 + \beta_3 x, \quad \forall z = 1
+\end{align*}
+
+\noindent The effect of $x$ when $z=0$ is given by $\beta_1$.
+The effect of $x$ when $z=1$ is given by $\beta_3$.
+These are, in essence, the conditional AMCEs in a conjoint analysis.
+yet the difference in AMCEs ($\beta_3 - \beta_1$) is not equal to the differnce in preferences between the two groups, which is $\bar{y}_{z=1|x=1} - \bar{y}_{z=0|x=1}$, or estimated by $(\beta_2 + \beta_3) - (\beta_0 + \beta_1)$.
+The difference in AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$.
+Yet the standard AMCE-centric conjoint analysis does not present or characterize either of these quantities.
+And given that the reference category is arbitrary, there is never any reason to expect that an arbitrarily selected reference category satisfies that equality assumption, meaning that when one uses a difference in AMCEs to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.
+
+Worse, because conjoint analysis generates a sparse feature matrix (where there is never any guarantee that a particular combination of feature levels is observed in the data), it is also not possible to empirically select an appropriate set of reference categories using the data.
+And while it might seem possible to select a \textit{marginally} appropriate reference category (i.e., one where preferences are similar with respect to a given feaure), preferences toward that reference category may differ across other dimensions in the analysis.
+Thus, there is no way to use conditional AMCEs or differences-in-AMCEs to convey the underlying similarity or differences in preferences across sample subgroups.
+
+\subsection{Analysing Subgroup Preferences Using Marginal Means}\label{sec:marginalmeans}
+
+It is worth highlighting two important and perhaps obvious feature of the reference category diagnostic, such as that shown in Figure \ref{fig:fig:hainmueller_subgroup_differences}.
+First, the differences in AMCEs mechanically vary around the difference in marginal means, as the reference category varies.
+Thus the pattern of variation in differences in AMCEs for all of the countries look the same (simply moving left or right on the horizontal axis).
+The difference between marginal means for two countries are always fixed by the data, so the differencing of subgroup AMCEs is merely an exercise is centering those differences at arbitrary points along the range of observed differences in marginal means.
+Differences-in-AMCEs for a given feature level are therefore necessarily sometimes positive and sometimes negative, depending on the reference category used in estimating them.
+The direction of the difference per se conveys no information about underlying preferences.
+
+Second, and more practically, because there is no category for which the preferences of the two subgroups in this example are identical, no choice of reference category will lead to inferences from differences-in-AMCEs that accurately reflect the underlying difference in preferences.
+Were there a category for which preferences were equivalent, that could be sensibly chosen as the reference category in order to be able to interpret differences-in-AMCEs as differences in preferences.
+There is never any guarantee, however, that such a reference category exists in any given experimental dataset.
+
+The choice of reference category --- while seemingly irrelevant --- has dramatic inferential consequences.
+To make this even more concrete, consider the two panels of Figure \ref{fig:hainmueller_subgroup_example}, which show the exact same analysis (comparing AMCEs for high and low ethnocentrism respondents) on the same experimental data.
+In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in preferences between the two subgroups.
+In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.
 
@@
 {\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required namespace: ggstance}}\end{kframe}
-\includegraphics[width=\maxwidth]{figure/r_hainmueller_immigration-1}
+\includegraphics[width=\maxwidth]{figure/hainmueller_subgroup_example_plot-1}
 
@@
 
-\clearpage
+In our view, the panel B is the more truthful visualization \citep{Cairo2016}.
+The differences between subgroup AMCEs more accurately convey differences in underlying preferences.
+Panel A, by contrast, leads the reader to suspect sometimes sizable difference in views along the dimensions of language skills, country of origin, job, and education, among others.
 
-\section{Arbitrary reference category choice}
+% higher order margins
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/r_reference_category-1}
-
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/r_marginal_means-1}
-
-\end{knitrout}
-
-\clearpage
-
-\section{Subgroup Analysis}
-
-A conventional presentation of subgroup analyses in a conjoint design is as follows.
-Note how the conditional AMCEs for several levels - Somalia, Sudan, China, Mexico, and France - flip signs.
-Yet the largest differences in preferences between the two groups are for Germany, France, Poland, and Somalia.
-Apparently similar patterns of AMCE mask where and in what direction preferences for the two subgroups differ.
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/r_subgroup_results_amce-1}
-
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/r_subgroup_marginal_means-1}
-
-\end{knitrout}
-
-As we can see, however, while the difference in marginal means conveys the fixed difference in preferences between the two groups, the apparent difference in preferences between groups conveyed by a difference-in-AMCEs is sensitive to the reference category chosen when estimating the effects:
-
-\clearpage
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/r_subgroup_results_mm-1}
-
-\end{knitrout}
-
-Indeed, the difference in AMCEs most closely approximates the difference in marginal means (and thus the descriptive difference in preferences) when the true difference in preferences in the reference category is close to zero.
-For example, in the above figure differences in AMCEs are shown in gray and differences in marginal means are shown in red, for respondents scoring above-median (high) and below-median (low) in ethnocentrism for each possible country of origin in Hainmueller et al.'s (2014) immigration experiment.
-The difference in marginal means between high and low ethnocentrism respondents is smallest for immigrants arriving from Iraq.
-When Iraq is used as the reference category, the AMCE of Iraq is fixed at zero and the between-group difference in AMCEs is thus, by definition, also fixed at zero.
-These estimates are shown at the top of each grouping - as should be readily clear, when Iraq is used as the reference category, the difference in AMCEs for each of the other possible origin countries closely approximates (but does not exactly equal) the difference in marginal means for that origin country.
-Were there no feature level for which the two groups held similar preferences, then there would be no reference category that would generate differences in AMCES that were close to the difference in underlying marginal means.
-
-When other origin countries are used as the reference category (wherein the underlying difference in preferences between high ethnocentrism and low enthnocentrism respondents is greater), then the difference in AMCEs provides biased estimates of the difference in preferences.
-Take, for example, the difference in preferences over immigrants from China, where high ethnocentrism respondents are less favourable to these immigrants than low ethnocentrism respondents.
-The difference in marginal means is -0.033.
-Yet differences in AMCEs for Chinese immigrants vary substantially depending on which other category is chosen as the baseline.
-If China is the baseline, the apparent difference in preferences is zero (definitionally).
-While in most cases the difference in AMCEs takes the same sign as the difference in marginal means, when either Mexico or Sudan is used as the reference category the apparent difference in preferences flips signs: high ethnocentrism respondents appear to be more rather than less favorable toward Chinese immigrants when the AMCEs are estimated in that way.
-
-Yet the graph also makes clear that the differences in AMCEs all center upon the true difference in marginal means in a fixed manner.
-
-Thus the choice of reference category - while seemingly irrelevant - has dramatic inferential consequences.
-
-\section{Suggested Approaches}
-
-% Present marginal means overall and for specific subgroups of interest
-
-\section{Conclusion}
+\section{Conclusion}\label{sec:conclusion}
 
@@
 
+% Present marginal means overall and for specific subgroups of interest
+As should be clear from the above discussions, we have relatively straightforward and hopefully uncontroversial advice for how analysts of conjoint experiments should proceed:
+
+\begin{enumerate}
+\item Always report unadjusted marginal means when attempting to provide a \textit{descriptive} summary of respondent preferences in addition to or instead of AMCEs.
+Yet remain cautious about characterizing middling values as ambivalence as opposed to an unobserved pattern of heterogeneity.
+
+\item When choosing reference categories for profile features, do so systematically based upon how the resulting AMCEs will be interpreted.
+Sensible choices are setting each feature's reference category to the marginal least (marginally most) preferred level, such that all AMCEs for all features are either all positive (negative).
+
+\item Exercise extreme caution when explicitly or implicitly interpreting differences in AMCEs across subgroups given that this quantity is almost always a biased estimate (of unknown sign) of the difference in preferences.
+If differences in AMCEs are reported, the choice of reference categories should be discussed explicitly and diagnostics should be provided.
+\end{enumerate}
+
+% some big conclusion
+
 \singlespacing
 \bibliographystyle{apsa-leeper}
-\bibliography{References}
+\bibliography{references}
 \clearpage
 
+\appendix
+
+\section{Additional Results}
+
+The below figure shows full marginal means for high and low ethnocentrism respondents for all feature levels.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/hainmueller_mm_by_ethnocentrism-1}
+
+\end{knitrout}
+
 \end{document}

### 2018-07-11 manuscript.Rnw
update manuscript (almost for submission)

--- 2018-02-20 manuscript.Rnw
@@
 \usepackage[utf8]{inputenc}
-\usepackage{times}
+%\usepackage{times}
 \usepackage{booktabs}
+\usepackage{multirow}
 \usepackage{natbib}
@@
 \usepackage{setspace}
-\renewcommand{\thefigure}{S\arabic{figure}}
 \usepackage[normalem]{ulem}
@@
 \title{Measuring Subgroup Preferences in Conjoint Experiments}
-\author{Sara Hobolt, Thomas J. Leeper, and James Tilley}
+\author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}
 
@@
 
-{\abstract Conjoint analysis has experienced a recent resurgence.
-The driving force for this change has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a fully randomized conjoint design and an associated analytic approach that emphasizes a single causal quantity of interest: namely, the average marginal component effect (AMCE).
-The AMCE convey the degree to which a given value of a feature increases or decreases respondents' support for a conjoint profile, averaging across all respondents and all other profile features.
-While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses use AMCEs for descriptive purposes: that is, not map variation in preferences across attributes of a multidimensional object, such as a candidate individual or public policy.
-And many authors also engage in subgroup analyses, wherein they compare subsets of respondents to one another with respect to AMCEs.
-This paper argues that such approaches can substantially mislead researchers about the degree of agreement or disagreement between subgroups, demonstrates the problem using several example datasets, and provides several suggestions for improved reporting and interpretation.
-Most importantly, it highlights that the difference in AMCEs between groups is sensitive to the choice of reference categories of features, while the difference in the marginal means is not sensitive in this way.
-When groups substantially differ in preferences, the difference in marginal means rather than the difference better conveys the size of such disagreements.}
+{\abstract Conjoint analysis is an increasingly prominent tool for studying political preferences.
+The method powerfully disentangles the causes of preferences over complex, multidimensional objects, such as political candidates or public policies.
+Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs), which measure the degree to which a given value of a conjoint profile feature increases or decreases respondents' support for the overall profile relative to a baseline, averaging across all respondents and all other profile features.
+While the AMCE has a clear causal interpretation, most published conjoint analyses also use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object, often including comparisons between theoretically interesting subgroups of respondents.
+We demonstrate that such analyses of conditional AMCEs can substantially mislead researchers about the degree of preference agreement or disagreement between subgroups.
+Most importantly, we highlight that the difference in conditional AMCEs between subgroups is sensitive to the choice of reference categories of features, providing inferences about subgroup preferences that are biased in unpredictable ways.
+We demonstrate the problem using simple examples drawn from the published literature and provide suggestions for improved reporting and interpretation.
+Given the rapidly accelerating use of conjoint analyses, these results have critically important implications for research in nearly all areas of political science.}
 
-<<r hidden, eval=FALSE, echo=FALSE, results="hide">>=
+<<hidden, eval=FALSE, echo=FALSE, results="hide">>=
 # setwd("c:/users/thomas/dropbox/brexit identity/papers/subgroupanalysis")
-# knitr::knit2pdf("manuscript.Rnw")
+# knitr::knit2pdf("manuscript.Rnw", quiet = TRUE)
 @
 
-<<r knitr_options, echo=FALSE, results="hide">>=
-knitr::opts_chunk$set(cache = TRUE, echo=FALSE, results="hold", warning=FALSE)
+<<knitr_options, cache=FALSE, echo=FALSE, results="hide">>=
+knitr::opts_chunk$set(cache = TRUE, echo=FALSE, results="hold", warning=FALSE, error=FALSE)
 options(scipen = 10)
+@
+
+<<setup, cache=FALSE>>=
+library("rio")
+library("cregg")
+library("ggplot2")
+requireNamespace("xtable", quietly = TRUE)
+@
+
+<<data_hainmueller_candidate>>=
+# Hainmueller et al. candidate experiment
+hainmueller_candidate <- cj_df(rio::import("data/hainmueller-candidate.dta"))
+
+# levels and labels
+hainmueller_candidate$atmilitary <- rio::factorize(hainmueller_candidate$atmilitary)
+attr(hainmueller_candidate$atmilitary, "label") <- "Military Service"
+
+hainmueller_candidate$atreligion <- rio::factorize(hainmueller_candidate$atreligion)
+attr(hainmueller_candidate$atreligion, "label") <- "Religion"
+
+hainmueller_candidate$ated <- rio::factorize(hainmueller_candidate$ated)
+attr(hainmueller_candidate$ated, "label") <- "College"
+
+hainmueller_candidate$atprof <- rio::factorize(hainmueller_candidate$atprof)
+attr(hainmueller_candidate$atprof, "label") <- "Profession"
+
+hainmueller_candidate$atinc <- rio::factorize(hainmueller_candidate$atinc)
+attr(hainmueller_candidate$atinc, "label") <- "Income"
+
+hainmueller_candidate$atrace <- rio::factorize(hainmueller_candidate$atrace)
+attr(hainmueller_candidate$atrace, "label") <- "Race/Ethnicity"
+
+hainmueller_candidate$atage <- rio::factorize(hainmueller_candidate$atage)
+attr(hainmueller_candidate$atage, "label") <- "Age"
+
+hainmueller_candidate$atmale <- rio::factorize(hainmueller_candidate$atmale)
+attr(hainmueller_candidate$atmale, "label") <- "Gender"
+@
+
+<<data_hainmueller_immigration>>=
+# Hainmueller et al. immigration experiment
+hainmueller_immigration <- cj_df(rio::import("data/hainmueller-immigrant.dta"))
+
+## outcome
+hainmueller_immigration$ChosenImmigrant <- hainmueller_immigration$Chosen_Immigrant
+hainmueller_immigration$Chosen_Immigrant <- NULL
+
+## setup features
+hainmueller_immigration$Gender <- rio::factorize(hainmueller_immigration$FeatGender)
+attr(hainmueller_immigration$Gender, "label") <- "Gender"
+hainmueller_immigration$FeatGender <- NULL
+
+hainmueller_immigration$Education <- rio::factorize(hainmueller_immigration$FeatEd)
+levels(hainmueller_immigration$Education) <- sub(" in the US", "", levels(hainmueller_immigration$Education))
+attr(hainmueller_immigration$Education, "label") <- "Education"
+hainmueller_immigration$FeatEd <- NULL
+
+hainmueller_immigration$LanguageSkills <- rio::factorize(hainmueller_immigration$FeatLang)
+levels(hainmueller_immigration$LanguageSkills) <- sub("During( the)? admission interview, this applicant ", "", levels(hainmueller_immigration$LanguageSkills))
+attr(hainmueller_immigration$LanguageSkills, "label") <- "Language Skills"
+hainmueller_immigration$FeatLang <- NULL
+
+hainmueller_immigration$CountryOfOrigin <- rio::factorize(hainmueller_immigration$FeatCountry)
+hainmueller_immigration$CountryOfOrigin <- relevel(hainmueller_immigration$CountryOfOrigin, "India")
+attr(hainmueller_immigration$CountryOfOrigin, "label") <- "Country of Origin"
+hainmueller_immigration$FeatCountry <- NULL
+
+hainmueller_immigration$Job <- rio::factorize(hainmueller_immigration$FeatJob)
+attr(hainmueller_immigration$Job, "label") <- "Job"
+hainmueller_immigration$FeatJob <- NULL
+
+hainmueller_immigration$JobExperience <- rio::factorize(hainmueller_immigration$FeatExp)
+attr(hainmueller_immigration$JobExperience, "label") <- "Job Experience"
+hainmueller_immigration$FeatExp <- NULL
+
+hainmueller_immigration$JobPlans <- rio::factorize(hainmueller_immigration$FeatPlans)
+levels(hainmueller_immigration$JobPlans) <- sub(" but has done job interviews", "", levels(hainmueller_immigration$JobPlans))
+attr(hainmueller_immigration$JobPlans, "label") <- "Job Plans"
+hainmueller_immigration$FeatPlans <- NULL
+
+hainmueller_immigration$ReasonForApplication <- rio::factorize(hainmueller_immigration$FeatReason)
+attr(hainmueller_immigration$ReasonForApplication, "label") <- "Reason for Application"
+hainmueller_immigration$FeatReason <- NULL
+
+hainmueller_immigration$PriorEntry <- rio::factorize(hainmueller_immigration$FeatTrips)
+attr(hainmueller_immigration$PriorEntry, "label") <- "Prior Entry"
+hainmueller_immigration$FeatTrips <- NULL
+
+## covariates
+hainmueller_immigration$ethnocentrism_split <- ifelse(is.na(hainmueller_immigration$ethnocentrism), NA_real_, ifelse(hainmueller_immigration$ethnocentrism > 10, 1, 0))
+hainmueller_immigration$ethnocentrism_split <- factor(hainmueller_immigration$ethnocentrism_split, levels = c(0,1), labels = c("low", "high"))
+@
+
+<<data_bms>>=
+if (file.exists("data/bms.rds")) {
+    bms <- cj_df(rio::import("data/bms.rds"))
+} else {
+    bms <- cj_df(rio::import("data/ballard-rosa.dta"))
+
+    # setup terms
+    bms$taxrate1 <- factor(rio::characterize(bms$taxrate1),
+                           levels = c("0%", "5%", "15%", "25%"),
+                           labels = c("<10k: 0%", "<10k: 5%", "<10k: 15%", "<10k: 25%"))
+    bms$taxrate2 <- factor(rio::characterize(bms$taxrate2),
+                           levels = c("5%", "15%", "25%", "35%"),
+                           labels = c("10-35k: 5%", "10-35k: 15%", "10-35k: 25%", "10-35k: 35%"))
+    bms$taxrate3 <- factor(rio::characterize(bms$taxrate3),
+                           levels = c("5%", "15%", "25%", "35%"),
+                           labels = c("35-85k: 5%", "35-85k: 15%", "35-85k: 25%", "35-85k: 35%"))
+    bms$taxrate4 <- factor(rio::characterize(bms$taxrate4),
+                           levels = c("5%", "15%", "25%", "35%"),
+                           labels = c("85-175k: 5%", "85-175k: 15%", "85-175k: 25%", "85-175k: 35%"))
+    bms$taxrate5 <- factor(rio::characterize(bms$taxrate5),
+                           levels = c("5%", "15%", "25%", "35%", "45%"),
+                           labels = c("175-375k: 5%", "175-375k: 15%", "175-375k: 25%", "175-375k: 35%", "175-375k: 45%"))
+    bms$taxrate6 <- factor(rio::characterize(bms$taxrate6),
+                           levels = c("5%", "15%", "25%", "35%", "45%", "55%"),
+                           labels = c(">375k: 5%", ">375k: 15%", ">375k: 25%", ">375k: 35%", ">375k: 45%", ">375k: 55%"))
+    bms$taxrev <- factor(rio::characterize(bms$taxrev),
+                         levels = rev(c("Much more revenue (>125%)",
+                                        "More revenue (105-125%)",
+                                        "About the same revenue (95-105%)",
+                                        "Less revenue (75-95%)",
+                                        "Much less revenue (<75%)")),
+                         labels = c("<75%", "75-95%", "95-105%", "105-125%", ">125%"))
+
+    # subset variables
+    bms <- bms[c("chose_plan", "taxrate1", "taxrate2", "taxrate3", "taxrate4", "taxrate5", "taxrate6", "taxrev",
+                 "ineq_averse_dum", "hh_income", "taxes_harm_econ", "work_vs_luck", "race", "above_avg_racial_resentment",
+                 "repub_7pt", "democ_7pt", "indep_7pt", "ID", "weight", "saw_revenue")]
+
+    # subset (according to original do file)
+    bms <- bms[bms$saw_revenue == 1,]
+
+    # label
+    attr(bms$taxrate1, "label") <- "Tax rate for <$10,000"
+    attr(bms$taxrate2, "label") <- "Tax rate for $10,000-$35,000"
+    attr(bms$taxrate3, "label") <- "Tax rate for $25,000-$85,000"
+    attr(bms$taxrate4, "label") <- "Tax rate for $85,000-$175,000"
+    attr(bms$taxrate5, "label") <- "Tax rate for $175,000-$375,000"
+    attr(bms$taxrate6, "label") <- "Tax rate for >$375,000"
+    attr(bms$taxrev, "label") <- "Tax revenue"
+
+    # export
+    rio::export(bms, "data/bms.rds")
+}
+bms$taxes_harm_split <- factor(ifelse(bms$taxes_harm_econ == 1, "Help", ifelse(bms$taxes_harm_econ == 2, "Harm", NA)))
+@
+
+<<data_tkr>>=
+if (file.exists("data/tkr.rds")) {
+    tkr <- cj_df(rio::import("data/tkr.rds"))
+} else {
+    # load original data file
+    tkr <- cj_df(rio::import("data/teele.dta"))
+
+    # recode respondent characteristics
+    tkr[["sample"]] <- c("usa voter" = "Voter", "usa leg" = "Legislator")[tkr[["sample"]]]
+
+    # subset to voters
+    tkr <- tkr[tkr[["sample"]] == "Voter", ]
+
+    tkr[["Sex"]] <- factor(c("Male", "Female")[tkr[["female_respondent"]]+1L])
+
+    tkr[["PartyID"]] <- NA_integer_
+    tkr[["PartyID"]][tkr[["democrat_respondent"]] == 1] <- "Democrat"
+    tkr[["PartyID"]][tkr[["republican_respondent"]] == 1] <- "Republican"
+    tkr[["PartyID"]] <- factor(tkr[["PartyID"]])
+
+    # label features and feature levels
+    ## Sex
+    tkr[["feature_sex"]] <- factor(tkr[["orig_cand_female"]], c(0,1), c("Male", "Female"))
+    attr(tkr[["feature_sex"]], "label") <- "Candidate Sex"
+
+    ## Political experience
+    tkr[["feature_experience"]] <- NA_integer_
+    tkr[["feature_experience"]][tkr[["orig_0ys"]] == 1] <- 1L
+    tkr[["feature_experience"]][tkr[["orig_1ys"]] == 1] <- 2L
+    tkr[["feature_experience"]][tkr[["orig_3ys"]] == 1] <- 3L
+    tkr[["feature_experience"]][tkr[["orig_8ys"]] == 1] <- 4L
+    tkr[["feature_experience"]] <- factor(tkr[["feature_experience"]], 1:4, c("None", "1 year", "3 years", "8 years"))
+    attr(tkr[["feature_experience"]], "label") <- "Political Experience"
+
+    ## Martial status
+    tkr[["feature_marital"]] <- NA_integer_
+    tkr[["feature_marital"]][tkr[["orig_UN_sp"]] == 1] <- 1L
+    tkr[["feature_marital"]][tkr[["orig_FM_sp"]] == 1] <- 2L
+    tkr[["feature_marital"]][tkr[["orig_MD_sp"]] == 1] <- 3L
+    tkr[["feature_marital"]] <- factor(tkr[["feature_marital"]], 1:3, c("Unmarried", "Doctor Spouse", "Farmer Spouse"))
+    attr(tkr[["feature_marital"]], "label") <- "Martial Status"
+
+    ## Profession
+    tkr[["feature_job"]] <- NA_integer_
+    tkr[["feature_job"]][tkr[["orig_teach"]] == 1] <- 1L
+    tkr[["feature_job"]][tkr[["orig_law"]] == 1] <- 2L
+    tkr[["feature_job"]][tkr[["orig_may"]] == 1] <- 3L
+    tkr[["feature_job"]][tkr[["orig_leg"]] == 1] <- 4L
+    tkr[["feature_job"]] <- factor(tkr[["feature_job"]], 1:4, c("Teacher", "Corporate Lawyer", "Mayor", "State Legislator"))
+    attr(tkr[["feature_job"]], "label") <- "Job"
+
+    ## Children
+    tkr[["feature_children"]] <- NA_integer_
+    tkr[["feature_children"]][tkr[["orig_0ch"]] == 1] <- 1L
+    tkr[["feature_children"]][tkr[["orig_1ch"]] == 1] <- 2L
+    tkr[["feature_children"]][tkr[["orig_3ch"]] == 1] <- 3L
+    tkr[["feature_children"]] <- factor(tkr[["feature_children"]], 1:3, c("No children", "1 child", "3 children"))
+    attr(tkr[["feature_children"]], "label") <- "Children"
+
+    ## Age
+    tkr[["feature_age"]] <- NA_integer_
+    tkr[["feature_age"]][tkr[["orig_29"]] == 1] <- 1L
+    tkr[["feature_age"]][tkr[["orig_45"]] == 1] <- 2L
+    tkr[["feature_age"]][tkr[["orig_65"]] == 1] <- 3L
+    tkr[["feature_age"]] <- factor(tkr[["feature_age"]], 1:3, c("29", "45", "65"))
+    attr(tkr[["feature_age"]], "label") <- "Age"
+
+    ## Office (experimental factor not reported in paper?)
+    tkr[["feature_office"]] <- rio::factorize(tkr[["dv"]])
+    attr(tkr[["feature_office"]], "label") <- "Office"
+
+    # export
+    rio::export(tkr, "data/tkr.rds")
+}
 @
@@
 
-Conjoint analysis has experienced a recent resurgence in the social sciences and especially in political science.
-The driving force has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE).
-By capturing the multidimensionality of target objects, such as a candidate individual or public policy, the conjoint design breaks any explicit or implicit confounding between those features, thus giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' support for a packaged conjoint profile, averaging across all respondents and all other profile features.
+Amidst the dramatically increased use of experiments within political science \citep{Druckmanetal2006, Mutz2011}, conjoint experimental designs have recently become a prominent methodological tool in political science.
+While traditional survey experiments tend to examine just one or two factors that might shape outcomes \citep[see, for reviews,][]{GainesKuklinskiQuirk2007, Sniderman2011}, conjoint designs allow researchers to study the independent effects on preferences of many features of complex, multidimensional objects such as political candidates \citep{Campbelletal2016, TeeleKallaRosenbluth2018}, immigrant admissions \citep{HainmuellerHopkins2015, BansakHainmuellerHangartner2016, WrightLevyCitrin2016}, or public policies \citep{GallegoMarx2017, Hankinson2018}.
+The driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE).
+By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit or implicit confounding between features of these objects, giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' support for a packaged conjoint profile relative to a baseline, averaging across all respondents and all other profile features.
 
-While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object.
-For example, \citet{HainmuellerHopkinsYamamoto2014} describe some of the results of their conjoint analysis of congressional candidate preferences:
+While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object.
+This is particularly the case when researchers engage in subgroup analyses of conjoint experiments for heterogeneity.
+For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.
+Similarly, \citet{BansakHainmuellerHangartner2016} compare preferences toward immigrants across number of binary respondent characteristics: age, education, left-right ideology, and income.
+In a different domain, \citet{BallardRosaMartinScheve2016} compare preferences over tax policies across a number of subgroups defined by demographics and political orientations.
+\citet{TeeleKallaRosenbluth2018} compare AMCEs for features of male and female political candidates among male and female respondents.
+\citet{KirklandCoppock2017} do a similar comparison between Democrats and Republicans in hypothetical elections.
+
+In these and many other articles, interpretation of these subgroup analyses focus not just on the \textit{causal effects} of profile features within each subgroup (what Hainmueller et al.
+term ``conditional AMCEs''; 13) but also focus on an implied quantity of interest: the \textit{difference} between two conditional AMCEs across subgroups.
+Searching for causal effect heterogeneity is an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017}, yet most conjoint analyses use this difference-in-AMCEs instead to \textit{descriptively} interpret apparent differences in preferences between the two groups.
+What is not obvious in such analyses is that differences-in-preferences (that is to say, the degree of favorability toward profiles containing a given feature) are not directly reflected in differences-in-AMCEs.
+Yet authors frequently use visual or more formal comparisons of conditional AMCEs to make descriptive claims about preferences, leading themselves and readers astray.
+In this paper, we show that a difference in underlying subgroup preferences --- like a difference in willingness to support a Syrian immigrant between high and low ethnocentrism respondents --- is only reflected in the difference-in-AMCEs under particular preference configurations and analytic choices.
+
+As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well but where preferences between subgroups diverge in the reference category, the difference-in-AMCEs is a highly misleading representation of underlying preferences.
+Yet most published conjoint studies appear to report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment.
+Ultimately effects are relative, not absolute, statements about preferences.
+For example, in a comparison of subgroup effects for Democrats and Republicans, Republicans might display a smaller effect because their preferences in the reference category are already very positive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.
+There is simply no predictable inference to be drawn from subgroup causal effects to the levels of underlying subgroup preferences.
+This inferential error --- interpreting differences in the size of causal effects as descriptive differences in preferences --- appears to be widespread in published conjoint analyses.
+Thus a seemingly trivial methodological decision has the potential to substantially alter our interpretations of a rapidly growing body of evidence about political preferences over important and varied political matters, including candidate selection and public policy.
+
+In what follows, we demonstrate the challenges of conjoint analysis and show how reference category choice for profile features creates significant problems for the now-common practice of comparing conditional AMCEs across respondent subgroups.
+We show that the size and the direction of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features and that reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar, using examples drawn from the published political science literature (namely experiments by \citealt{HainmuellerHopkinsYamamoto2014, BallardRosaMartinScheve2016, TeeleKallaRosenbluth2018}).
+The paper then provides suggestions for improved reporting and interpretation based around a purely descriptive quantity of interest: unadjusted marginal means.
+Newly developed software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment --- is demonstrated throughout \citep{Leeper2018cregg}.
+We conclude with advice for best practices in the analysis and presentation of conjoint results.
+
+\section*{Quantities of Interest in Conjoint Experiments}\label{sec:quantities}
+
+Conjoint analysis serves two purposes.
+One is to assess causal effects.
+Another is preference description.
+In causal inference, conjoints provide a design and analytic approach that allows researchers to understand the causal effect of a given feature on overall support for a multidimensional object, averaging across other features of the object included in the design.
+Such inferences can be thought of as statements of the form: ``shifting an immigrant's country of origin from India to Poland increases favorability by X percentage points.'' In descriptive inference, conjoints provide information about both (a) the absolute favorability of respondents toward objects with particular features or combinations of features, and (b) the relative favorability of respondents toward an object with alternative combinations of features.
+Such inferences can be thought of as statements of the form ``Polish immigrants are preferred by X\% of respondents'' or ``Polish immigrants are more supported than Mexican immigrants, by X percentage points.'' Thus both causal and descriptive interpretations of conjoints are based upon the distribution of preferences across profile features and differences in preferences across alternative feature combinations.
+
+Importantly, a fully randomized conjoint design (without constraints between profile features) is simply a full-factorial experiment with some cells possibly, albeit randomly, left unobserved.
+All quantities of interest relevant to the analysis of conjoint designs derive from combinations of cell means, marginal means, and the grand mean, as is common in the traditional analysis of factorial experiments.
+In a forced choice design, the \textit{grand mean} is by definition 0.5 (i.e., 50\% of all profiles shown are chosen and 50\% are not chosen).
+\textit{Cell means} are the mean outcome for each particular combination of feature levels.
+In the full-factorial design discussed by \citet{HainmuellerHopkinsYamamoto2014} and now widely used in political science, many or perhaps most cell means are unobserved.
+For example, in their candidate choice experiment, there are $2*6*6*6*2*6*6*6 = 186,624$ cell means but only 3,466 observations so about 98\% of cell means are unobserved.
+While this would be problematic for attempting to infer pairwise comparisons between cells, conjoint analysts mostly focus on the marginal effects of each feature rather than more complex interactions.
+
+Average marginal component effects (AMCEs) depend only upon \textit{marginal means}: that is the column and row means for each feature level averaging across all other features.
+The marginal means describe the variation in preferences toward profiles that have a particular feature level.
+For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities: a marginal mean of 0 indicates respondents select profiles with that feature level with probability $Pr(Y=1|X=x) = 0$ while a marginal mean of 1 indicates respondents select profiles with that feature level with probability $(Pr(Y=1|X=x)=1$.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany).
+Instead, the marginal mean can range from the probability of co-occurrence to 1 minus that probability.
+If there are five levels of a feature, each shown with equal probability, then the probability of co-occurrence is $\frac{1}{5}*\frac{1}{5} = 0.04$ such that the marginal mean can take values in the range $(0.04,0.96)$.
+If the design is constrained so that features cannot be the same for both immigrants, then the marginal means fully range from zero to one.
+This constraint on the range of the marginal means also constrains the range of AMCEs.
+Notably, many conjoints provide features with only two levels, such as the male-versus-female candidate feature examined by \citet{TeeleKallaRosenbluth2018}.
+In such cases, the probability of co-occurrence is $\frac{1}{2}*\frac{1}{2} = 0.25$ bounding the AMCE for female (as opposed to male) candidates to the range $(-0.5, 0.5)$ if both candidates can have the same sex.
+Caution is therefore needed in comparing the relative size of features with few levels to features with many levels given that effects have different bounds.} With rating scale outcomes, marginal means can vary arbitrarily along the outcome scale used.
+
+<<hainmueller_candidate_replication, dependson=c("data_hainmueller_candidate"), fig.height=6, fig.width=8, fig.cap="Replication of Hainmueller et al.
+(2014) Candidate Experiment using AMCEs and MMs", fig.show="hold", message=FALSE>>=
+plot(
+  cregg::cj(
+   hainmueller_candidate, 
+   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
+   id = ~ resID,
+   estimate = "amce"
+  ), vline = 0, xlim = c(-0.4,0.4)
+)
+plot(
+  cregg::cj(
+   hainmueller_candidate, 
+   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
+   id = ~ resID,
+   estimate = "mm"
+  ), vline = 0.5, xlim = c(0.25,0.75)
+)
+@
+
+Because levels of features are randomly assigned, pairwise differences between two marginal means for a given feature (e.g., between candidates who are male versus female) have a direct causal interpretation.
+For fully randomized designs, the AMCE proposed by \citet{HainmuellerHopkinsYamamoto2014} is equivalent to the average marginal effect of each feature level for a model where each feature is converted into a matrix of indicator variables with one level left out as a reference category.\footnote{This is no different from any other regression context wherein one level of any categorical variable must be omitted from the design matrix in order to avoid perfect multicollinearity.
+In designs that entail constraints between profile features, the average marginal effect is a weighted average of effects across each combination of the constrained features where the weights on the effects are arbitrary but typically uniform.
+We ignore this distinction in the remainder of this article, as all of our results apply equally to fully randomized and to constrained designs.} This close relationship between AMCEs and marginal means is visible in Figure \ref{fig:hainmueller_candidate_replication} which presents a replication of the AMCE-based analysis of their candidate experiment (upper panel) and an analogous examination of the results using marginal means (lower panel).
+Note, in particular, how marginal means convey information about the preferences of respondents for all feature levels while AMCEs definitionally restrict the AMCE for the reference category to zero (or undefined).
+For example, the AMCE for a candidate serving in the military is 0.09 (or a 9-percentage point) increase in favorability, reflecting marginal means for serving and non-serving candidates of 0.46 and 0.54, respectively.
+
+The AMCE is often described as an estimate of the relative favorability of profiles with counterfactual levels of a feature; for example, ``male candidates are preferred to female candidates'' \citep[6]{TeeleKallaRosenbluth2018}.
+\citet{HainmuellerHopkinsYamamoto2014} similarly describe some of the results of conjoint on preferences toward Congressional candidates:
 
@@
 Support for Evangelical Protestants is also 0.04 percentage points lower (SE = 0.02) than the baseline.
-Mainline Protestants, Catholics, and Jews all receive ratings indistinguishable from those of a baseline candidate.
 (19)
@@
 
-This characterization of the results has a distinctly descriptive flavor.
-While a given religious characteristic \textit{causes} respondents to evaluate a given candidate more or less favorably, the gist of the analysis is that there are differences in the evaluations of candidates of different religious persuasions.
-\citeauthor{HainmuellerHopkinsYamamoto2014}'s phrasing highlights another feature of conjoint analysis that is not widely discussed: the baseline (or reference category) in the estimation of AMCEs significantly colors which pairwise comparisons between features are highlighted and the degree to which preferences are stated in positive or negative terms.
-By choosing a non-religious candidate as a baseline, the AMCEs are all expressed relative to this baseline; the difference (if any) between evaluations of Mormon and Evangelical candidates, for example, is not obvious and while it is likely that Mainline Protestant, Catholic, and Jewish candidates are all preferred over Mormon or Evangelical candidates, the AMCEs for these categories are indistinguishable from zero (rather than the positive values they would take if Mormon or Evangelical were the reference category).
-Similarly, by selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), some AMCEs are positive while others are negative.
-Yet because any feature level could be used as the reference cateory, the size but also \textit{direction} of AMCEs is arbitrary.
-Were the category with the lowest favorability chosen as the reference, all AMCEs would be positive; were the category with the highest favorability chosen as the reference, all AMCEs would be negative.
-The results would be \textit{numerically equivalent} --- because ultimately the choice of reference category is completely arbitrary and mathematicaly irrelevant --- but the choice as sizable consequences for the interpretation of conjoint analyses.
+\noindent These examples make clear that despite the \textit{causal} inference potentially provided by the AMCE, the quantity of interest is frequently used to provide a characterization of a preferences that has a distinctly descriptive flavor.
+Indeed, this style of description is widespread in conjoint analyses.
+\citet{BallardRosaMartinScheve2016} interpretation their tax preference conjoint:
 
-This is particularly the case when researchers engage in subgroup analyses of conjoint experiments.
-For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.\footnote{This is achieved by subsetting the data based upon the measure of ethnocentrism and performing separate regressions for high- and low-ethnocentrism respondents.} The interpretation therefore focuses not just on the arbitrarily signed AMCEs within each subgroup (what Hainmueller et al.
-term ``conditional AMCEs''; 13) but also on an implied quantity of interest: the difference between conditional AMCEs.
-This comparison seems intuitively correct but because the conditional AMCEs are causal effects expressed relative to an arbitrary baseline, the differences between AMCEs only convey a difference in preference to the extent that the reference category is equally liked by both groups.
-When the preferences toward the reference category differ substantially between groups, the difference in AMCEs is a biased estimate of the difference in preferences between the two groups.
-For example, \citet{HainmuellerHopkinsYamamoto2014} eyeball the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22).
-Yet simply because the AMCEs are similar does not necessarily mean that \textit{preferences} are similar.
+\begin{quote}
+we find strong support for progressive preferences over federal income taxes among the American public [\dots] respondents are less likely to support a given tax plan as the tax rate on the poorest three groups increases but more likely to support an income tax policy when the tax rate on the richest two groups increases, at least to a point.
+\end{quote}
 
-To bring some intuition to this problem, consider a simple two-condition experiment in which the effect of the treatment, $x \in {0,1}$, is compared across a single two-category covariate, $z \in {0,1}$.
-Subgroup regression equations might be:
+\noindent This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature.
+A positive (negative) AMCE is read as higher (lower) favorability but it is only higher (lower) relative to whatever category serves as the baseline.
+For example, in the \citeauthor{HainmuellerHopkinsYamamoto2014} candidate example, choosing a non-religious candidate as a baseline means the AMCEs in the candidate experiment are all expressed relative to this non-religious baseline; the difference (if any) between other pairs of marginal means (e.g., evaluations of Mormon and Evangelical candidates) is not obvious.
+Relatedly, the negative direction (and the size) of the AMCEs for Mormon and Evangelical candidates would be different if the least-liked category (Mormon candidates) were the reference group.
+In that case, the AMCE for Evangelicals would be small and positive and the AMCEs for all other categories (including the presented reference category, ``none'') would be large and positive.
+
+<<reference_category, dependson=c("data_hainmueller_immigration"), fig.width=8, fig.height=5, fig.cap="Reference Category Diagnostic for the 'Education' Feature from Hainmueller et al.'s (2014) Immigration Experiment">>=
+tmp <- amce_by_reference(hainmueller_immigration, ChosenImmigrant ~ Education, ~ Education, id = ~CaseID)
+ggplot(tmp, aes(x = estimate, y = level, group = BY, colour = BY)) +
+  geom_vline(xintercept = 0, colour = "gray") +
+  geom_point(position = ggstance::position_dodgev(height = 0.5)) +
+  geom_errorbarh(aes(xmin = lower, xmax = upper),  
+                 size = 0.2, height = 0,
+                 position = ggstance::position_dodgev(height = 0.5)) + 
+  scale_colour_discrete(guide = ggplot2::guide_legend(title = "Reference Category", ncol = 1)) +
+  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
+  ylab("") +
+  xlab("Estimated AMCE") + 
+  theme_minimal() + 
+      ggplot2::theme(
+        legend.position = "bottom",
+        panel.grid.major = ggplot2::element_blank(),
+        panel.grid.minor = ggplot2::element_blank()
+      )
+rm(tmp)
+@
+
+This choice of reference category for estimating AMCEs can seem trivial but is quite consequential.
+For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment, the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline.
+Figure \ref{fig:reference_category} shows how the estimated AMCEs for each level of education would have differed depending on that choice.
+Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline.\footnote{As another example, in \citeauthor{BallardRosaMartinScheve2016}'s tax preference experiment, the lowest level of taxation is chosen as the reference category for each feature for reasons of substantive interpretation, yet despite the substantive intuitiveness of this, favorability toward the lowest level of taxation is not necessarily higher or lower than preferences for alternative tax rates.} The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses.\footnote{In \textit{constrained} conjoint designs, the choice of reference category is even more important.
+Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature.
+Consequently, the AMCE for the ``Escape Persecution'' level (relative to the  ``Reunite with family'' reference category) is only defined for the subset of the design involving countries `China,' `Sudan,' `Somalia,' and `Iraq.' The AMCEs for those four countries (relative to India as a baseline) marginalize across all reasons for application, but the AMCEs for the first six countries marginalize only across the latter two reasons.
+Thus the interpretation of AMCEs --- and the basic ability to estimate them in constrained designs --- depends entirely upon the selection of a reference category where all feature levels can co-occur.
+In a design where \textit{all} features are constrained, then AMCEs are undefined for the design as a whole and only estimable for subsets of the design that are \textit{conditionally} unconstrained.}
+
+%To demonstrate this, Figure \ref{fig:reference_category} shows the estimated AMCEs for the country of origin feature from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, with the analysis repeated ten times each time using a different country as the reference category.
+For example, the top-most set of points and error bars convey the AMCE for Iraq from each of these analyses.
+When Iraq is the reference category, its AMCE is undefined.
+When any other country is chosen as a reference category, the AMCE for Iraq is negative because respondents are more negative toward Iraqi immigrants than they are toward those of other countries.
+Similarly, the bottom set of points and error bars reflects the estimated AMCEs for Germany.
+When Germany is the reference category, its AMCE is undefined but when any other country is used as the reference category, its AMCE is positive.
+
+%These cases are therefore not \textit{directionally} sensitive to the choice of reference category but of course the point estimates vary considerably.
+But the estimated AMCE of countries who are neither strongly disliked or strongly favored by respondents are highly sensitive to choice of reference category.
+Consider, for example, the estimated AMCEs for China (the four set of points from the top).
+When highly disliked countries are chosen as the reference category (like Somalia, Sudan, or Iraq), the AMCE for China is positive; when highly favored countries are chosen (like Germany, Poland, or the Philippines), the AMCE for China is negative.
+
+\section*{Consequences of Arbitrary Reference Category Choice}\label{sec:challenges}
+
+Given the need to choose a reference category for every feature in order to estimate AMCEs, an important question is: how do researchers decide which of tens of thousands of possible experimental cells should be selected as the reference category?
+Examining recently published conjoint analyses, it appears that the choice of reference category is either arbitrary or based upon substantive intuition about the meaning of feature levels.
+For example, \citet{HainmuellerHopkinsYamamoto2014} choose female immigrants as a baseline in their immigration experiment, thus providing an estimate of the AMCE of being male, while \citet{TeeleKallaRosenbluth2018} choose male candidates as a baseline in their conjoint, thus providing an estimate of the AMCE of being female.
+The choice is seemingly innocuous.
+Sometimes choices of reference category appear to be driven by substantive knowledge: on language skills of immigrants, \citet{HainmuellerHopkinsYamamoto2014} choose fluency as a baseline; on the prior trips to the US feature, ``never'' is chosen as the baseline.
+These seem sensible on face value --- it might seem less useful to define all effects relative to ``having visited many times as a tourist'' as the AMCEs then lose an immediately intuitive interpretation.
+
+% Difference in conditional AMCEs
+\begin{table}
+\caption{Uses of Subgroup Analysis Published in Political Science Journals}\label{tab:papers}
+\begin{center}
+\footnotesize
+\begin{tabular}{p{2in} p{2in} p{2in}}\toprule
+\textbf{Paper} & \textbf{Topic} & \textbf{Subgroup Comparisons} \\ \midrule
+\citet{BechtelScheve2013} & Climate agreement preferences & Environmentalism and International Reciprocity Attitudes \\ \midrule
+\citet{FranchinoZucchini2014} & Candidate preferences & Political Interest, Left-right self-placement\\ \midrule
+\citet{HainmuellerHopkinsYamamoto2014} & Immigration preferences & Ethnocentrism \\ \midrule
+\citet{HansenOlsenBech2014} & Policy preferences & Partisanship \\ \midrule
+\citet{Carlson2015} & Candidate preferences & Co-ethnicity \\ \midrule
+\citet{BansakHainmuellerHangartner2016} & Immigration preferences & Left-right self-placement, age, education, income\\ \midrule
+\citet{BallardRosaMartinScheve2016} & Tax preferences & Various\\ \midrule
+\citet{Campbelletal2016} & Candidate preferences & Partisanship \\ \midrule
+\citet{CarnesLupu2016} & Candidate preferences & Partisanship \\ \midrule
+\citet{Mummolo2016} & News selection & Various\\ \midrule
+\citet{VivyanWagner2016} & Candidate preferences & Political attitudes \\ \midrule
+\citet{MummoloNall2017} & Mobility preferences & Partisanship \\ \midrule
+\citet{BechtelGenoveseScheve2017} & Climate agreement preferences & Employment sector emissions \\ \midrule
+\citet{BechtelHainmuellerMargalit2017} & International bailout preferences & Various\\ \midrule
+\citet{GallegoMarx2017} & Labor market policy & Left-right self-placement \\ \midrule
+\citet{KirklandCoppock2017} & Candidate preferences & Partisanship \\ \midrule
+\citet{Sen2017} & Judicial candidate preferences & Partisanship \\ \midrule
+\citet{Sobolewskaetal2017} & Immigrant integration & Various \\ \midrule
+\citet{EggersVivyanWagner2018} & Candidate preferences & Sex \\ \midrule
+\citet{Hankinson2018} & Housing policy preferences & Various \\ \midrule
+\citet{OliverosSchuster2018} & Bureaucrat candidate preferences & Various \\ \midrule
+\citet{TeeleKallaRosenbluth2018} & Candidate preferences & Sex, Partisanship \\
+\bottomrule
+\end{tabular}
+\end{center}
+\end{table}
+
+Yet the choice is consequential.
+A possibly surprising consequence of the seemingly arbitrary selection of a reference category --- and the resulting arbitrariness of both the size and direction of AMCEs --- is that it can provide highly distorted descriptive interpretation of preferences among subgroups of respondents.
+This occurs when researchers examine \textit{conditional} AMCEs, wherein AMCEs are calculated separately for subgroups of respondents and those conditional estimates are directly compared \citep[13]{HainmuellerHopkinsYamamoto2014}.
+Table \ref{tab:papers} reports a list of recently published articles in political science that engage in this form of subgroup analysis.\footnote{\citet{RatkovicTingley2017} considered efficient methods for performing subgroup analyses in conjoint designs.
+Our focus here is on the narrower problem of interpreting subgroup analyses as traditionally performed using subsetting or interaction terms in a regression framework.} Given the commonly descriptive interpretations of conjoint experimental results, such subgroup analyses seem perfectly intuitive and the set of subgroups listed in the last column of Table \ref{tab:papers} contains some unsurprising covariates, such as partisanship, that are of obvious theoretical interest in almost any study of individual preferences.
+Analytically, these conditional AMCEs can be obtained either from regression estimates on respondent subgroups or through interactions between conjoint features and respondent characteristics, the details of which are unimportant for our purposes.
+
+Conditional AMCEs are not per se a problematic quantity of inference.
+Like subgroup analysis of any experiment, they convey the causal effect of an experimental factor on overall favorability among the subgroup of interest.
+Consider, for example, a two-condition party cue experiment where Democrats and Republicans are exposed to an endorsement cue from the Democratic party or no cue and opinions toward the policy serve as the outcome.
+It is sensible to imagine that effects of the cue might differ for the two groups and therefore to compare the size of cue effect among the two groups.
+Perhaps Democrats are more responsive to the Democratic party cue than are Republicans, making the causal effect larger for Democrats than Republicans.
+Discussions of conditional AMCEs in conjoint analyses often explicitly or implicitly engage in this kind of discussion comparing the size and direction of subgroup causal effects.
+If interpreted as a difference in the size of the causal effect for two groups, such comparisons are perfectly consistent with more traditional experimental analysis and a perfectly acceptable interpretation of the conjoint results.
+
+<<tkr_replication, dependson=c("data_tkr"), fig.height=5, fig.width=8, fig.cap="Replication of Teele et al. (2018) Candidate Experiment using AMCEs and MMs", fig.show="hold", message=FALSE>>=
+plot(
+  cj(
+   tkr, 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "amce",
+   by = ~ PartyID
+  ), vline = 0, group = "PartyID", xlim = c(-0.35, 0.35)
+) + scale_colour_manual("PartyID", limits = c("Democrat", "Republican"), values = c("Blue", "Red"))
+plot(
+  cj(
+   tkr, 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "mm",
+   by = ~ PartyID
+  ), vline = 0.5, group = "PartyID", xlim = c(0.3,0.7)
+) + scale_colour_manual("PartyID", limits = c("Democrat", "Republican"), values = c("Blue", "Red"))
+@
+
+Yet, just as analysis of full sample conjoint data is often descriptive in nature, so too conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally.
+For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} visually compare the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22).
+\citet{BallardRosaMartinScheve2016} make similar comparisons in their tax policy conjoint: ``While there are few strong differences in preferences for taxing the lower three income groups (the `hard work' group has slightly lower elasticities for taxing the poor), there are strong differences in preferences for taxing the rich.
+Respondents who believe luck plays a role in economic success are more strongly progressive, although preferences over taxing the \$175K--\$375K bracket are relatively flat'' (12).
+In these examples, the differences between conditional AMCEs are used as a way of descriptively characterizing differences in \textit{preferences} between the groups rather than differences in \textit{causal effects on preferences} in the groups.
+
+As a more complete example, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment separately for Democratic and Republican voters, as provided in the original paper, and the lower panel shows the results using conditional marginal means.
+Respondents' preference for female candidates is very apparent in both forms of analysis.
+Yet the discrepancy between the differences in preferences (i.e., conditional marginal means) and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature in Figure \ref{fig:tkr_replication} (the second set of estimates from the top in both panels).
+The conditional AMCEs in the upper panel correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates.
+Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates).
+In reality, however, the conditional marginal means shown in the lower panel demonstrate that actually Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience.
+Democrats are much more sensitive to experience than are Republicans and important differences in preferences are apparent for extreme categories in the visualization of conditional marginal means, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.
+The selection of a reference category is therefore hugely consequential for a descriptive reading of the AMCE results.
+
+Interpreting conjoint AMCEs as measures of preferences is an inferential error.
+In a simple experiment like the party cue example just given, this kind of interpretation would be obviously flawed.
+A larger causal effect of the party cue for Democrats than Republicans does not necessarily mean that Democrats are more supportive than Republicans on average or in either condition.
+Effects are relative, not absolute, statements about preferences.
+Republicans, for example, might experience a smaller effect because their preferences in the control group are already very supportive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.
+There is simply no predictable connection between subgroup causal effects and the levels of underlying subgroup preferences.
+This inferential error --- interpreting differences in the size of causal effects as descriptive differences in preferences --- appears to be widespread in published conjoint analyses.
+While AMCEs do provide insight into the descriptive variation in preferences within-group and across-features, and conditional AMCEs do estimate the size of causal effects of features within groups, AMCEs cannot provide direct insight into the pattern of preferences between groups because they do not provide information about \textit{absolute} levels of favorability toward profiles with each feature (or combination of features).
+
+This additional information matters.
+Consider again the simple two-condition experiment in which the effect of a cue treatment, $x \in {0,1}$, is compared across a single two-category covariate, $z \in {0,1}$ such as Democratic or Republican self-identification.
+Subgroup regression equations to estimate effects for each group are:
 
@@
 These are, in essence, the conditional AMCEs in a conjoint analysis.
-yet the difference in AMCEs ($\beta_3 - \beta_1$) is not equal to the differnce in preferences between the two groups, which is $\bar{y}_{z=1|x=1} - \bar{y}_{z=0|x=1}$, or estimated by $(\beta_2 + \beta_3) - (\beta_0 + \beta_1)$.
-The difference in AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$.
+Yet the difference in AMCEs ($\beta_3 - \beta_1$) is not equal to the difference in preferences between the two groups, which is $\bar{y}_{z=1|x=1} - \bar{y}_{z=0|x=1}$ (estimated by $(\beta_2 + \beta_3) - (\beta_0 + \beta_1)$).
+The difference-in-AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$.
 Yet the standard AMCE-centric conjoint analysis does not present or characterize either of these quantities.
-And given that the reference category is arbitrary, there is never any reason to expect that an arbitrarily selected reference category satisfies that equality assumption, meaining that when one uses a difference in AMCEs to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.
+Similarity of conditional AMCEs therefore only convey similarity of the \textit{causal effect} of the feature, but do not convey similarity of \textit{preferences} unless preferences toward profiles with the reference category are equivalent across groups.
+Given the reference category choice is typically arbitrary or driven by substantive knowledge of the levels, there is never any reason to expect that an arbitrarily selected reference category satisfies that equality assumption.
+When using a difference-in-AMCEs comparison to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.
 
-Worse, because conjoint analysis generates a sparse feature matrix (where there is never any guarantee that a particular combination of feature levels is observed in the data), it is also not possible to empirically select an appropriate set of reference categories using data.
-And while it might seem possible to select a \textit{marginally} appropriate reference category (i.e., one where preferences are similar with respect to a given feaure), preferences toward that reference category may differ across other dimensions in the analysis.
-Thus, there is no way to use conditional AMCEs or differences-in-AMCEs to convey the underlying similarity or differences in preferences across sample subgroups.
+<<bms_difference_comparison, dependson=c("data_bms"), fig.width=8, fig.height=4, fig.cap="Estimated Preferences Difference between Inequity Averse and Non-Averse Respondents from Ballard-Rosa et al.
+(2016) Tax Preference Experiment">>=
+# reported results
+main <- cj(bms[!is.na(bms$ineq_averse_dum),], chose_plan ~ taxrate6, id = ~ ID, estimate = "amce_diff", by = ~ ineq_averse_dum)
+main$statistic <- "Originally Reported Difference"
 
-In what follows, we formalize how the arbitrary selection of a reference category can mislead researchers about the pattern of preferences exposed by a conjoint experiment and demonstrates how this problem is especially problematic when researchers engage in the now-common practice of comparing conditional AMCEs across respondent subgroups.
-The paper then demonstrates the problem using several example datasets and provides suggestions for improved reporting and interpretation based around a purely descriptive quantity of interest: namely, the unadjusted marginal means.
-Software for the R programming language to easily calculate marginal means (as well as AMCEs) is also discussed.
+# AMCE differences
+amce_diffs <- do.call("rbind", lapply(levels(bms$taxrate6)[-1], function(x) {
+    tmp <- bms[!is.na(bms$ineq_averse_dum),]
+    tmp$taxrate6 <- relevel(tmp$taxrate6, x)
+    cj(tmp, chose_plan ~ taxrate6, id = ~ ID, estimate = "amce_diff", by = ~ ineq_averse_dum)
+}))
+amce_diffs$statistic <- "Difference in AMCEs"
 
-\section{Quantities of Interest}
+# Difference in Marginal Means
+mm_diff <- cj(bms, chose_plan ~ taxrate6, id = ~ ID, estimate = "mm_diff", by = ~ ineq_averse_dum)
+mm_diff$statistic <- "Difference in MMs"
 
-% AMCE
+# Merge
+diffs <- rbind(main, amce_diffs, mm_diff)
+levels(diffs$statistic) <- c("Originally Reported Difference", "Difference in AMCEs", "Difference in MMs")
+# Plot
+ggplot(diffs, aes(x = estimate, y = level, group = statistic, colour = statistic, fill = statistic, shape = statistic)) +
+  geom_vline(xintercept = 0, colour = "black") +
+  geom_point(position = ggstance::position_dodgev(height = 0.25), size=2) +
+  geom_errorbarh(aes(xmin = lower, xmax = upper),  
+                 size = 0.2, height = 0,
+                 position = ggstance::position_dodgev(height = 0.25)) + 
+  scale_colour_manual("Statistic", limits = levels(diffs$statistic),
+                      values = c("black", "gray", "black"),
+                      guide = ggplot2::guide_legend(title = "Statistic")) +
+  scale_fill_manual("Statistic",
+                    limits = levels(diffs$statistic),
+                    values = c("black", "gray", "black"),
+                    guide = ggplot2::guide_legend(title = "Statistic")) +
+  scale_shape_manual("Statistic",
+                     limits = levels(diffs$statistic),
+                     values = c(20, 16, 23),
+                     guide = ggplot2::guide_legend(title = "Statistic")) +
+  scale_x_continuous(limits = c(-.4,.4), oob = scales::rescale_none) +
+  ylab("") +
+  xlab("Estimated Difference between Inequity Averse and Non-Averse Respondents") + 
+  theme_minimal() + 
+      ggplot2::theme(
+        legend.position = "bottom",
+        panel.grid.major = ggplot2::element_blank(),
+        panel.grid.minor = ggplot2::element_blank()
+      )
 
-% Difference in conditional AMCEs
-
-\citet{RatkovicTingley2017} considered efficient methods for performing subgroup analyses in conjoint designs.
-Our focus here is on the narrower problem of interpreting subgroup analyses as traditionally performed.
-
-\begin{table}
-\caption{Uses of Subgroup Analysis in Published Work}
-\begin{center}
-\footnotesize
-\begin{tabular}{p{2.5in} p{2in} p{2in}}\toprule
-\textbf{Paper} & \textbf{Topic} & \textbf{Subgroup Comparisons} \\ \midrule
-Hainmueller, Hopkins, and Yamamoto (2014) & Immigration Preferences & Ethnocentrism \\
-Bechtel and Scheve (2013) & Climate agreement preferences & Environmentalism and International Reciprocity Attitudes \\
-Bechtel, Genovese, and Scheve (2017) & Climate agreement preferences & Employment sector emissions \\
-Hansen, Olsen, and Bech (2015) & Policy Preferences & Partisanship \\
-Carlson (2015) & Candidate Choice & Co-ethnicity \\
-Franchino and Zucchini (2015) & Candidate Choice & Political Interest, Left-right self-placement\\
-Carnes and Lupu (2016) & Candidate Choice & Partisanship \\
-Mummolo (2016) & News Selection & Various\\
-Mummolo and Nall (2016) & Mobility preferences & Partisanship \\
-Ballard-Rosa, Martin, and Scheve (2016) & Tax Preferences & Various\\
-Bechtel, Hainmueller, and Margalit (2017) & International bailout preferences & Various\\
-Sen (2017) & Judicial candidate preferences & Partisanship \\
-Campbell, Cowley, Vivyan, and Wagner (2016) & Candiate preferences & Partisanship \\
-Kirkland, Coppock (2017) & Candidate choice & Partisanship \\ \bottomrule
-\end{tabular}
-\end{center}
-\end{table}
-
-% Marginal means
-
-\section{Challenges of Interpretation}
-
-% baseline levels of features
-
-% subgroup analyses
-
-% difference in AMCEs versus difference in marginal means
-
-<<r setup>>=
-library("ggplot2")
-requireNamespace("ggstance")
-library("cregg")
+rm(main, mm_diff, amce_diffs, diffs)
 @
 
-<<r data>>=
-data(hainmueller)
-hainmueller$ethnocentrism_split <- ifelse(is.na(hainmueller$ethnocentrism), NA_real_, ifelse(hainmueller$ethnocentrism > 10, 1, 0))
-hainmueller$ethnocentrism_split <- factor(hainmueller$ethnocentrism_split, levels = c(0,1), labels = c("low", "high"))
+We can see this bias clearly in a reanalysis of \citeauthor{BallardRosaMartinScheve2016}'s tax preference experiment.
+Figure \ref{fig:bms_difference_comparison} shows an analysis for the feature capturing the tax rate for the highest earners (those over \$375,000 per year) replicating a portion of the results they present comparing inequity averse and non-averse respondents \citet[9 figure 2]{BallardRosaMartinScheve2016}.
+The original analysis was presented as conditional AMCEs for the two subgroups with inequity averse respondents having positive AMCEs for all tax levels (relative to 5\% as the reference category) and AMCEs for non-averse respondents being largely indistinguishable from zero.
+Figure \ref{fig:bms_difference_comparison} presents the implied difference-in-AMCEs from the original analysis as round black dots, demonstrating the substantial and positive \textit{apparent} differences between the two groups.
+The black diamonds show the true differences in marginal means between the two groups.
+The gray dots represent the alternative differences-in-AMCEs that could have been generated from alternative choices of reference category using the same data.
+Because respondents in the two groups actually have substantially different preferences over the reference category 5\% tax rate (inequity averse respondents are much less favorable toward this rate than non-averse respondents) differences-in-AMCEs make it seem like inequity averse respondents are much \textit{more} favorable toward 15\% and 25\% tax rates than non-averse respondents, when in actuality averse respondents are \textit{less} favorable toward the 15\% tax rate than non-averse respondents and the two groups have largely similar views of a 25\% tax rate.
+Not only does the difference-in-AMCEs overestimate group differences for very high tax rates (35\%, 45\%, 55\%) but the difference-in-AMCEs flips the true direction of group differences for lower rates.
+The authors correctly read their data as showing ``support for more progressive preferences is correlated with concern over societal inequality'' \citep[9]{BallardRosaMartinScheve2016} but for the wrong reason: inequity averse and non-averse respondents are similarly favorable toward middling tax rates and diverge in their views of very high and very low rates for high earners.
+
+It is worth highlighting two further features in Figure \ref{fig:bms_difference_comparison}.
+First, the alternative differences-in-AMCEs estimates vary mechanically around the difference in marginal means, as the reference category varies.
+The difference between marginal means for two groups are always fixed in the data, so the differencing of subgroup AMCEs is merely an exercise is centering those differences at arbitrary points along the range of observed differences in marginal means.
+Differences-in-AMCEs for a given feature level are therefore necessarily sometimes positive and sometimes negative, depending on the reference category used in estimating them.
+The direction of the difference per se conveys no information about underlying pattern of preferences in the two groups.
+Yet the choice of reference category --- likely unintentionally --- resulted in the most extreme, positive difference-in-AMCEs that could be estimated from the data but alternative reference categories could have conveyed different, equally incorrect insights.
+
+Second, and more practically, because there is no category for which the preferences of the two subgroups in this example are identical, no choice of reference category would have led to inferences from differences-in-AMCEs that accurately reflect the underlying difference in preferences.
+Even in the 25\% tax rate category, the difference between the two groups is slightly negative.
+Were there a category for which preferences were equivalent, that could be sensibly chosen as the reference category in order to be able to interpret differences-in-AMCEs as differences in preferences.
+There is never any guarantee, however, that such a reference category exists in any given experimental dataset.
+If multiple subgroup analyses are performed, it is unlikely the same reference category would work well across all analyses, making consistent interpretation difficult.
+As such, even if the AMCEs are similar, it does not necessarily mean that \textit{preferences} are similar; if AMCEs are dissimilar, it does not necessarily mean that preferences differ.
+
+Ultimately, it is important to note that because conjoint analysis generates a sparse feature matrix (where there is never any guarantee that a particular combination of feature levels is observed in the data), it is also not possible to empirically select an appropriate set of reference categories using the data.
+It is impossible to know which cell --- of the tens of thousands in the design --- is the best choice of reference.
+This is because while it might seem possible to select a \textit{marginally} appropriate reference category (i.e., one where preferences are similar with respect to a given feature), preferences toward that reference category may differ across other dimensions in the analysis.
+And it is furthermore possible that there is no such cell for which preferences are identical in the two groups; such a cell may exist, but there is no reason to expect that it should exist in any given application.
+Thus, there is no way to use conditional AMCEs or differences between those conditional AMCEs to convey the underlying similarity or differences in preferences across sample subgroups.
+
+\section*{Improved Analysis of Subgroup Preferences in Conjoint Designs}\label{sec:marginalmeans}
+
+<<hainmueller_subgroup_example, dependson=c("data_hainmueller_immigration"), fig.cap="Comparison of Alternative Reference Categories for Hainmueller et al. (2014) immigration Experiment">>=
+# estimates benchmarked to largest difference between subgroups
+hainmueller.A <- hainmueller_immigration
+    hainmueller.A$Education <- relevel(hainmueller.A$Education, "No formal education")
+    hainmueller.A$Gender <- relevel(hainmueller.A$Gender, "male")
+    hainmueller.A$CountryOfOrigin <- relevel(hainmueller.A$CountryOfOrigin, "Mexico")
+    hainmueller.A$ReasonForApplication <- relevel(hainmueller.A$ReasonForApplication, "Escape political/religious persecution")
+    hainmueller.A$Job <- relevel(hainmueller.A$Job, "Doctor")
+    hainmueller.A$JobExperience <- relevel(hainmueller.A$JobExperience, "More than five years of job training and experience")
+    hainmueller.A$JobPlans <- relevel(hainmueller.A$JobPlans, "Has no plans to look for work at this time")
+    hainmueller.A$PriorEntry <- relevel(hainmueller.A$PriorEntry, "Entered the U.S. once before without legal authorization")
+    hainmueller.A$LanguageSkills <- relevel(hainmueller.A$LanguageSkills, "spoke [language] and used an interpreter")
+# estimates benchmarked to smallest difference between subgroups
+hainmueller.B <- hainmueller_immigration
+    hainmueller.B$Education <- relevel(hainmueller.B$Education, "Equivalent to completing a college degree")
+    hainmueller.B$Gender <- relevel(hainmueller.B$Gender, "female")
+    hainmueller.B$CountryOfOrigin <- relevel(hainmueller.B$CountryOfOrigin, "Iraq")
+    hainmueller.B$ReasonForApplication <- relevel(hainmueller.B$ReasonForApplication, "Reunite with family members already in the U.S.")
+    hainmueller.B$Job <- relevel(hainmueller.B$Job, "Child care provider")
+    hainmueller.B$JobExperience <- relevel(hainmueller.B$JobExperience, "No job training or prior experience")
+    hainmueller.B$JobPlans <- relevel(hainmueller.B$JobPlans, "Does not have a contract with a U.S. employer")
+    hainmueller.B$PriorEntry <- relevel(hainmueller.B$PriorEntry, "Never been to the U.S.")
+    hainmueller.B$LanguageSkills <- relevel(hainmueller.B$LanguageSkills, "spoke broken English")
+# formula
+f1 <- ChosenImmigrant ~ LanguageSkills + CountryOfOrigin + Job + Education + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Gender  + Education:Job + CountryOfOrigin:ReasonForApplication
+# estimate
+amce_by_ethnocentrism_1 <- cj(hainmueller.A, f1, id = ~ CaseID, estimate = "amce", by = ~ ethnocentrism_split)
+amce_by_ethnocentrism_2 <- cj(hainmueller.B, f1, id = ~ CaseID, estimate = "amce", by = ~ ethnocentrism_split)
+#amce_by_ethnocentrism_3 <- cj(hainmueller_immigration, f1, id = ~ CaseID, estimate = "amce", by = ~ ethnocentrism_split)
+# tag datasets and merge
+amce_by_ethnocentrism_1$dataset <- "A"
+amce_by_ethnocentrism_2$dataset <- "B"
+#amce_by_ethnocentrism_3$dataset <- "C"
+amce_ref_example_merged <- rbind(amce_by_ethnocentrism_1, amce_by_ethnocentrism_2)
 @
 
-The following figure provides a replication of Hainmueller et al.'s (2014) results:
+<<hainmueller_subgroup_example_plot, dependson=c("data_hainmueller_immigration", "hainmueller_subgroup_example"), fig.width=8, fig.height=12, fig.cap="Alternative Reference Categories for Features in Hainmueller et al.
+(2014) Immigration Experiment", message=FALSE>>=
+plot(amce_ref_example_merged, group = "ethnocentrism_split", feature_headers = FALSE, legend_title = "Ethnocentrism", vline = 0) + 
+  scale_colour_manual("Ethnocentrism", limits = c("high", "low"), values = c("Red", "Blue")) +
+  facet_grid(rows = vars(feature), cols = vars(dataset), scales = "free_y", space = "free_y", labeller = function(x) label_value(x, multi_line = FALSE)) +
+  theme(strip.text.x = element_text(size = 8),
+        strip.text.y = element_text(size = 5))
+@
 
-<<r hainmueller_immigration, dependson=c("data"), fig.height=10, fig.width=8>>=
+We have shown that subgroup analyses of conjoint designs frequently entail the use of difference-in-AMCE comparisons and we have also shown that such analyses, counterintuitively, do not demonstrate differences in preferences between groups due the near-impossibility of selecting a non-arbitrary reference category against which to estimate AMCEs.
+Thus the choice of reference category --- while seemingly irrelevant --- has dramatic inferential consequences in conjoint analyses.
+Here we provide a more complete example, demonstrating the full extent of this problem for interpretation of conjoint results and present alternative forms of analysis that more robustly convey subgroup preferences and the differences (if any) between them.
+Consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which show the exact same analysis (comparing AMCEs for high and low ethnocentrism respondents) on the same experimental data from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment.
+In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in preferences between the two subgroups.
+In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.\footnote{The appendix contains comparable plots for experiments by \citet{BallardRosaMartinScheve2016} and \citet{TeeleKallaRosenbluth2018}.}
+
+Panel A gives the impression that there are significant differences in preferences between high and low ethnocentrism respondents toward immigrants from different countries of origin, with different careers, and with different educational attainments.
+By contrast, Panel B gives the impression that these differences --- indeed all differences --- are negligible.
+The experimental data and analytic approach in the two portrayals is identical; the only difference is the choice of reference category for the profile features.
+Given what we have shown about the relationship between differences in conditional AMCEs and differences in conditional marginal means, Panel B is the more truthful visualization \citep{Cairo2016}.
+The differences between subgroup AMCEs there more accurately convey differences in underlying preferences because the reference categories used in Panel B are the most similar between the two groups.
+Yet even this may not \textit{perfectly} convey differences because no feature generates perfect agreement between the subgroups.
+
+<<hainmueller_mm_by_ethnocentrism, dependson=c("data_hainmueller_immigration"), fig.height = 14, fig.width=10, fig.cap="Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment", message=FALSE>>=
+mm_by_ethnocentrism <- cj(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry, id = ~ CaseID, estimate = "mm", by = ~ ethnocentrism_split)
+plot(mm_by_ethnocentrism,
+     group = "ethnocentrism_split",
+     legend_title = "Ethnocentrism",
+     vline = 0.5,
+     xlim = c(0.2,0.8)) +
+  scale_colour_manual("Ethnocentrism", limits = c("high", "low"), values = c("Red", "Blue"))
+@
+
+<<hainmueller_mm_diffs, dependson=c("data_hainmueller_immigration"), fig.height = 14, fig.width=10, fig.cap="Differences in Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment", message=FALSE>>=
+mm_by_ethnocentrism <- cj(subset(hainmueller_immigration, !is.na(ethnocentrism_split)),
+                          ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
+                          id = ~ CaseID,
+                          estimate = "mm_diff",
+                          by = ~ ethnocentrism_split)
+plot(mm_by_ethnocentrism, vline = 0, xlim = c(-0.3,0.3)) +
+  scale_colour_manual("feature", values = rep("Black", 9))
+@
+
+Alternatively presenting subgroup differences using conditional marginal means (as in Figure \ref{fig:hainmueller_mm_by_ethnocentrism}) provides the intended descriptive comparison of subgroup preferences.
+Each dot and error bar represents the conditional marginal mean (and its standard error) for high ethnocentrism (in red) and low ethnocentrism (in blue) respondents.
+This display of conditional marginal means highlights just how similar the preferences are for the two groups.
+For example, in the first set of estimates, both groups of respondents display minimally positive preferences toward female immigrants and minimally negative preferences toward male immigrants, averaging across those immigrants' other profile features.
+The second set of estimates shows both group are also more favorable toward higher-educated immigrants and less favorable toward less-education immigrants with no visually apparent differences.
+The third set of estimates, related to language skills, shows again similar patterns: both groups are more favorable toward immigrants with higher English proficiency than immigrants with lower English proficiency.
+
+These estimates are less obviously identical for the two groups but look quite close.
+To test for pairwise differences between high and low ethnocentrism respondents, we can calculate differences in conditional conditional marginal means at each feature level, with associated significance tests:
+
+\begin{itemize}
+<<hainmueller_mmdiffs_by_ethnocentrism, dependson=c("data_hainmueller_immigration"), results="asis">>=
+mmdiffs_by_ethnocentrism <- cj(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry, id = ~ CaseID, estimate = "mm_diff", by = ~ ethnocentrism_split)
+mmd <- mmdiffs_by_ethnocentrism[mmdiffs_by_ethnocentrism$feature == "Language Skills", c("level", "estimate", "std.error", "z", "p")]
+cat(sprintf("\\item %s: %0.2f (%0.2f, $z_{\\text{diff}}$=%0.2f, $p\\leq %0.2f$)\n", mmd[[1]][1], mmd[[2]][1], mmd[[3]][1], mmd[[4]][1], mmd[[5]][1]))
+cat(sprintf("\\item %s: %0.2f (%0.2f, $z_{\\text{diff}}$=%0.2f, $p\\leq %0.2f$)\n", mmd[[1]][2], mmd[[2]][2], mmd[[3]][2], mmd[[4]][2], mmd[[5]][2]))
+cat(sprintf("\\item %s: %0.2f (%0.2f, $z_{\\text{diff}}$=%0.2f, $p\\leq %0.2f$)\n", mmd[[1]][3], mmd[[2]][3], mmd[[3]][3], mmd[[4]][3], mmd[[5]][3]))
+cat(sprintf("\\item %s: %0.2f (%0.2f, $z_{\\text{diff}}$=%0.2f, $p\\leq %0.2f$)\n", mmd[[1]][4], mmd[[2]][4], mmd[[3]][4], mmd[[4]][4], mmd[[5]][4]))	
+@
+\end{itemize}
+
+<<hainmueller_language_diffs, dependson=c("data_hainmueller_immigration"), eval=TRUE, echo=FALSE>>=
+hainmueller_anova_language <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ LanguageSkills, id = ~ CaseID, by = ~ ethnocentrism_split)
+@
+
+\noindent These pairwise tests show that are our eyes have not deceived us.
+None of the level-specific differences in conditional marginal means are statistically distinguishable from zero.
+Were we interested in an omnibus tests of whether any of these differences were non-zero, we could perform a nested model comparison of two equations: (a) one estimating only marginal effects of the ``Language Skills'' feature, and (b) the same model with additional interactions between the subgrouping covariate and the features.
+The resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: \Sexpr{sprintf("F(%d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_language$Df[2], hainmueller_anova_language$F[2], hainmueller_anova_language$"Pr(>F)"[2])}.
+We could repeat such pairwise comparisons or omnibus comparisons for each feature in the design.
+
+Furthermore, we could also directly visualize differences in conditional marginal means for this feature --- and all features --- as in Figure \ref{fig:hainmueller_mm_diffs}.
+This provides a more direct presentation of \textit{differences} between subgroup preferences as the vertical line indicates feature levels for which there is no difference between the two groups.
+Positive values to the right of the line indicate positive differences (high ethnocentrism respondents are more favorable toward immigrants with this feature than low ethnocentrism respondents) and negative value to the left of zero convey the opposite.
+A further advantage of this plot is that unlike displays of conditional AMCEs, differences in conditional marginal means communicate subgroup differences for all feature levels including the reference categories.
+This display makes readily clear what was only indirectly apparent in Figure \ref{fig:hainmueller_mm_by_ethnocentrism}: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.
+
+<<nested_model, dependson=c("data_hainmueller_immigration"), eval=TRUE, echo=FALSE>>=
+hainmueller_anova_all <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Gender + Job*Education + LanguageSkills + CountryOfOrigin*ReasonForApplication + JobExperience + JobPlans + PriorEntry, id = ~ CaseID, by = ~ ethnocentrism_split)
+@
+
+As before, we can perform an omnibus tests for the presence of any subgroup differences across all features, again using nested model comparison of two equations: (a) one estimating only effects of the features, and (b) the same model with additional interactions between the subgrouping covariate and all features.
+The result of that test for differences by ethnocentrism from the immigration experiment is: \Sexpr{sprintf("F(%d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_all$Df[2], hainmueller_anova_all$F[2], hainmueller_anova_all$"Pr(>F)"[2])}, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.
+This kind of test can also be used to assess heterogeneity across conjoint features.
+For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9).
+Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to an quite different conclusion.
+
+\section*{Conclusion}\label{sec:conclusion}
+
+This article has identified several challenges related to the analysis and reporting of conjoint experimental designs, particularly analyses of subgroup differences.
+We suggest that conjoint analyses should report not only average marginal component effects (AMCEs) but also descriptive quantities that better convey underlying preferences over profile features and better convey subgroup differences in those preferences.
+Our intention here is not to substantively undermine any previous set of results but instead to urge researchers moving forward to demonstrate considerable caution in how they design, analyze, and present the results of these types of experiments.
+We have relatively straightforward and hopefully uncontroversial advice for how analysts of conjoint experiments should proceed:
+
+\begin{enumerate}
+\item Always report unadjusted marginal means when attempting to provide a \textit{descriptive} summary of respondent preferences in addition to or instead of AMCEs.\footnote{Like the presentation of AMCEs, displaying marginal means in constrained conjoint designs may also distort apparent patterns given that not all features can co-occur.
+Partitioning the design into fractions such that each fraction contains a fully unconstrained design would mitigate any concern with that presentation.}
+
+\item Exercise extreme caution when explicitly or implicitly interpreting differences-in-AMCEs across subgroups.
+While that quantity conveys the difference in effects of a change in a given feature, heterogeneous effects do not necessarily mean different underlying preferences.
+Differences-in-AMCEs are almost always a biased estimate (of unknown sign and direction) of the difference in underlying preferences.
+If differences in AMCEs are reported, the choice of reference categories should be discussed explicitly and diagnostics should be provided to justify it.
+
+\item When descriptively characterizing differences in preferences between subgroups, directly estimate the subgroup difference using conditional marginal means and differences between conditional marginal means, rather than relying on difference-in-AMCEs.
+
+\item To formally test for group differences in preferences, regression with interaction terms between the subgrouping covariate and all feature levels will generate estimates of level-specific differences in preferences via the coefficients on the interaction terms.\footnote{The analysis is slightly more complicated in constrained designs.} A nested model comparison between this equation against one without such interactions provides an omnibus test of subgroup differences, which should be reported when characterizing overall patterns of subgroup differences.
+\end{enumerate}
+
+\noindent Following this advice, we hope, will allow researchers to more clearly and more accurately represent the results of conjoint experiments.
+
+The popularity of conjoint analyses in recent years highlights the power of the design and the important contributions made by \citet{HainmuellerHopkinsYamamoto2014} in providing a novel causal interpretation of these fully randomized factorial designs.
+Yet with new tools always come new challenges.
+The now-common practice of descriptively interpreting conjoints requires more caution than is immediately obvious.
+This paper has demonstrated several such challenges and hopefully provides useful advice for how researchers should proceed with the analysis of such designs.
+
+To facilitate such analysis and, especially, to provide easy-to-use tools for calculating marginal means and performing reference category selection diagnostics, we provide software called \textbf{cregg} \citep{Leeper2018cregg} that will perform these analyses and also provides the simple-to-use visualization tools used throughout this article.
+With that resource in-hand, researchers should be well-equipped to analyze conjoint designs without running into the analytic challenges discussed here.
+
+\singlespacing
+\bibliographystyle{apsa-leeper}
+\bibliography{references}
+\clearpage
+
+\appendix
+
+\section{Hainmueller et al. (2014) Immigration Experiment}
+
+\subsection{Replication using AMCEs}
+
+<<hainmueller_immigration_amce_appendix, dependson=c("data_hainmueller_immigration"), fig.height=8, fig.width=8>>=
 plot(
   cj(
-   hainmueller, 
-   ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
+   hainmueller_immigration, 
+   ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication,
    id = ~ CaseID
@@
 
-<<r functions>>=
-amces_by_reference <- function(data, variable, formula) {
-    # get levels
-    levs <- levels(data[[variable]])
-
-    # loop over levels
-    out <- list()
-    for (i in seq_along(levs)) {
-        data[[variable]] <- relevel(data[[variable]], levs[i])
-        out[[i]] <- cj(data, formula, id = ~ CaseID)
-        out[[i]][["ref_category"]] <- levs[i]
-    }
-
-    # return value
-    out <- do.call("rbind", out)
-    out[["ref_category"]] <- factor(out[["ref_category"]], levels = levs)
-    class(out) <- c("cj_amce", "data.frame")
-    out
-}
-@
-
-\section{Arbitrary reference category choice}
-
-<<r reference_category, dependson=c("data"), fig.width=8, fig.height=5>>=
-x <- amces_by_reference(hainmueller, "CountryOfOrigin", ChosenImmigrant ~ CountryOfOrigin)
-
-ggplot(x, aes(x = estimate, y = level, group = ref_category, colour = level)) +
-  geom_vline(xintercept = 0, colour = "gray") +
-  geom_point(position = ggstance::position_dodgev(height = 0.75)) +
-  geom_errorbarh(aes(xmin = lower, xmax = upper),  
-                 size = 0.2, height = 0,
-                 position = ggstance::position_dodgev(height = 0.75)) + 
-  scale_colour_discrete(guide = ggplot2::guide_legend(title = "Reference Category")) +
-  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
-  ylab("") +
-  xlab("Estimated AMCE") + 
-  theme_minimal() + 
-      ggplot2::theme(
-        legend.position = "bottom",
-        panel.grid.major = ggplot2::element_blank(),
-        panel.grid.minor = ggplot2::element_blank()
-      )
-@
-
-<<r marginal_means, fig.width=8, fig.height=5>>=
-plot(mm(hainmueller, ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID), vline = 0.5, xlim = c(0,1))
+<<hainmueller_amce_table, dependson=c("data_hainmueller_immigration"), results="asis">>=
+print(xtable::xtable(
+  cj(
+     hainmueller_immigration, 
+     ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication,
+     estimate = "amce",
+     id = ~ CaseID
+  )[c("feature", "level", "estimate", "std.error", "z")],
+    digits = 2, align = c("l", "l", "p{3in}", "r", "r", "r")
+), include.rownames = FALSE, size = "footnotesize")
 @
@@
 
-\section{Subgroup Analysis}
+\subsection{Replication using MMs}
 
-A conventional presentation of subgroup analyses in a conjoint design is as follows.
-Note how the conditional AMCEs for several levels - Somalia, Sudan, China, Mexico, and France - flip signs.
-Yet the largest differences in preferences between the two groups are for Germany, France, Poland, and Somalia.
-Apparently similar patterns of AMCE mask where and in what direction preferences for the two subgroups differ.
-
-<<r subgroup_results_amce, dependson=c("data"), fig.width=8, fig.height=5>>=
-by_split <- lapply(c("low","high"), function(x) {
-    out <- cj(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "amce")
-    out$ethnocentrism_split <- x
-    out
-})
-x <- do.call("rbind", by_split)
-
-ggplot(x, aes(x = estimate, y = level, group = ethnocentrism_split, colour = ethnocentrism_split)) +
-  geom_vline(xintercept = 0, colour = "gray") +
-  geom_point(position = ggstance::position_dodgev(height = 0.75)) +
-  geom_errorbarh(aes(xmin = lower, xmax = upper),  
-                 size = 0.2, height = 0,
-                 position = ggstance::position_dodgev(height = 0.75)) + 
-  scale_colour_discrete(guide = ggplot2::guide_legend(title = "Ethnocentrism")) +
-  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
-  ylab("") +
-  xlab("Estimated AMCE") + 
-  theme_minimal() + 
-      ggplot2::theme(
-        legend.position = "bottom",
-        panel.grid.major = ggplot2::element_blank(),
-        panel.grid.minor = ggplot2::element_blank()
+<<hainmueller_immigration_mm_appendix, dependson=c("data_hainmueller_immigration"), fig.height=8, fig.width=8>>=
+plot(
+  cj(
+   hainmueller_immigration, 
+   ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication,
+   id = ~ CaseID,
+   estimate = "mm",
+   h0 = 0.5
+  ), vline = 0.5
 )
@@
 
-<<r subgroup_marginal_means, dependson=c("data"), fig.width=8, fig.height=5>>=
-plot(cj(hainmueller, ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "mm", by = ~ethnocentrism_split), vline = 0.5, group = "ethnocentrism_split")
+\clearpage
+
+<<hainmueller_mm_table, dependson=c("data_hainmueller_immigration"), results="asis">>=
+print(xtable::xtable(
+  cj(
+     hainmueller_immigration, 
+     ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication,
+     estimate = "mm",
+     id = ~ CaseID,
+     h0 = 0.5
+  )[c("feature", "level", "estimate", "std.error", "z")],
+    digits = 2, align = c("l", "l", "p{3in}", "r", "r", "r")
+), include.rownames = FALSE, size = "footnotesize")
 @
-
-As we can see, however, while the difference in marginal means conveys the fixed difference in preferences between the two groups, the apparent difference in preferences between groups conveyed by a difference-in-AMCEs is sensitive to the reference category chosen when estimating the effects:
 
@@
 
-<<r subgroup_results_mm, dependson=c("data"), fig.width=10, fig.height=10>>=
-# difference in marginal means
-by_split_mm <- lapply(levels(hainmueller$ethnocentrism_split), function(x) {
-    out <- cj(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "mm")
-    out$ethnocentrism_split <- x
-    out
-})
-x_mm <- merge(by_split_mm[[1]], by_split_mm[[2]], by = c("level"), suffixes = c(".low", ".high"))
-## difference
-x_mm[["diff"]] <- x_mm[["estimate.high"]] - x_mm[["estimate.low"]]
-## standard error of difference
-x_mm[["diff_se"]] <- sqrt(x_mm[["std.error.high"]]^2 + x_mm[["std.error.low"]]^2)
-x_mm[["ref_category"]] <- "Marginal Mean"
+\subsection{Subgroup Analysis for Hainmueller et al. (2014) Immigration Experiment using AMCEs}
 
-# difference in AMCEs
-by_split_amce <- lapply(levels(hainmueller$ethnocentrism_split), function(x) {
-    out <- amces_by_reference(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), "CountryOfOrigin", ChosenImmigrant ~ CountryOfOrigin)
-    out$ethnocentrism_split <- x
-    out
-})
-x_amce <- merge(by_split_amce[[1]], by_split_amce[[2]], by = c("level", "ref_category"), suffixes = c(".low", ".high"))
-## difference
-x_amce[["diff"]] <- x_amce[["estimate.high"]] - x_amce[["estimate.low"]]
-## standard error of difference
-x_amce[["diff_se"]] <- sqrt(x_amce[["std.error.high"]]^2 + x_amce[["std.error.low"]]^2)
-
-x_merged <- rbind(x_mm[c("level", "diff", "diff_se", "ref_category")], x_amce[c("level", "diff", "diff_se", "ref_category")])
-x_merged[["ref_category"]] <- factor(x_merged[["ref_category"]], levels = c("Marginal Mean", levels(x_amce[["ref_category"]])))
-x_merged[["is_mm"]] <- ifelse(x_merged[["ref_category"]] == "Marginal Mean", "Difference in MMs", "Difference in AMCEs")
-
-ggplot(x_merged, aes(x = diff, y = level, group = ref_category, colour = is_mm, shape = is_mm)) +
-  geom_vline(xintercept = 0, colour = "gray") +
-  geom_point(aes(shape = is_mm), position = ggstance::position_dodgev(height = 0.75)) +
-  scale_shape_manual(values = c(16,15), guide = FALSE) + 
-  geom_errorbarh(aes(xmin = diff - diff_se, xmax = diff + diff_se),  
-                 size = 0.2, height = 0,
-                 position = ggstance::position_dodgev(height = 0.75)) + 
-  #scale_colour_discrete(guide = ggplot2::guide_legend(title = "Reference Category")) +
-  scale_colour_manual(values = c("gray", "red"), guide = ggplot2::guide_legend(title = "Estimate Type")) +
-  scale_x_continuous(oob = scales::rescale_none) +
-  ylab("") +
-  xlab("Estimated Difference") + 
-  theme_minimal() + 
-      ggplot2::theme(
-        legend.position = "right",
-        panel.grid.major = ggplot2::element_blank(),
-        panel.grid.minor = ggplot2::element_blank()
+<<hainmueller_immigration_subgroup_amce_appendix, dependson=c("data_hainmueller_immigration"), fig.height=8, fig.width=8>>=
+plot(
+  cj(
+   na.omit(hainmueller_immigration), 
+   ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication,
+   id = ~ CaseID,
+   by = ~ethnocentrism_split
+  ), group = "ethnocentrism_split"
 )
@@
 
-Indeed, the difference in AMCEs most closely approximates the difference in marginal means (and thus the descriptive difference in preferences) when the true difference in preferences in the reference category is close to zero.
-For example, in the above figure differences in AMCEs are shown in gray and differences in marginal means are shown in red, for respondents scoring above-median (high) and below-median (low) in ethnocentrism for each possible country of origin in Hainmueller et al.'s (2014) immigration experiment.
-The difference in marginal means between high and low ethnocentrism respondents is smallest for immigrants arriving from Iraq.
-When Iraq is used as the reference category, the AMCE of Iraq is fixed at zero and the between-group difference in AMCEs is thus, by definition, also fixed at zero.
-These estimates are shown at the top of each grouping - as should be readily clear, when Iraq is used as the reference category, the difference in AMCEs for each of the other possible origin countries closely approximates (but does not exactly equal) the difference in marginal means for that origin country.
-Were there no feature level for which the two groups held similar preferences, then there would be no reference category that would generate differences in AMCES that were close to the difference in underlying marginal means.
-
-When other origin countries are used as the reference category (wherein the underlying difference in preferences between high ethnocentrism and low enthnocentrism respondents is greater), then the difference in AMCEs provides biased estimates of the difference in preferences.
-Take, for example, the difference in preferences over immigrants from China, where high ethnocentrism respondents are less favourable to these immigrants than low ethnocentrism respondents.
-The difference in marginal means is -0.033.
-Yet differences in AMCEs for Chinese immigrants vary substantially depending on which other category is chosen as the baseline.
-If China is the baseline, the apparent difference in preferences is zero (definitionally).
-While in most cases the difference in AMCEs takes the same sign as the difference in marginal means, when either Mexico or Sudan is used as the reference category the apparent difference in preferences flips signs: high ethnocentrism respondents appear to be more rather than less favorable toward Chinese immigrants when the AMCEs are estimated in that way.
-
-Yet the graph also makes clear that the differences in AMCEs all center upon the true difference in marginal means in a fixed manner.
-
-Thus the choice of reference category - while seemingly irrelevant - has dramatic inferential consequences.
-
-\section{Suggested Approaches}
-
-% Present marginal means overall and for specific subgroups of interest
-
-\section{Conclusion}
-
-This paper has several identified challenges related to the analysis and reporting of conjoint experimental designs, particularly analyses of subgroup differences.
-It suggests that authors should report not only average marginal component effects (AMCEs) but also descriptive quantities that better convey subgroup differences.
-
-\singlespacing
-\bibliographystyle{apsa-leeper}
-\bibliography{References}
 \clearpage
 
+\subsection{Subgroup Analysis for Hainmueller et al. (2014) Immigration Experiment using MMs}
+
+<<hainmueller_immigration_subgroup_mm_appendix, dependson=c("data_hainmueller_immigration"), fig.height=8, fig.width=8>>=
+plot(
+  cj(
+   na.omit(hainmueller_immigration), 
+   ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication,
+   id = ~ CaseID,
+   estimate = "mm",
+   h0 = 0.5,
+   by = ~ethnocentrism_split
+  ), vline = 0.5, group = "ethnocentrism_split"
+)
+@
+
+\clearpage
+
+\section{Hainmueller et al. (2014) Candidate Experiment}
+
+\subsection{Replication using AMCEs}
+
+<<hainmueller_candidate_amce_appendix, dependson=c("data_hainmueller_candidate"), fig.height=8, fig.width=8>>=
+plot(
+  cj(
+   hainmueller_candidate, 
+   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
+   id = ~ resID,
+   estimate = "amce"
+  )
+)
+@
+
+\clearpage
+
+<<hainmueller_candidate_amce_table, dependson=c("data_hainmueller_candidate"), results="asis">>=
+print(xtable::xtable(
+  cj(
+     hainmueller_candidate, 
+     selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
+     id = ~ resID,
+     estimate = "amce"
+  )[c("feature", "level", "estimate", "std.error", "z")],
+    digits = 2, align = c("l", "l", "p{3in}", "r", "r", "r")
+), include.rownames = FALSE, size = "footnotesize")
+@
+
+\clearpage
+
+\subsection{Replication using MMs}
+
+<<hainmueller_candidate_mm_appendix, dependson=c("data_hainmueller_candidate"), fig.height=8, fig.width=8>>=
+plot(
+  cj(
+   hainmueller_candidate, 
+   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
+   id = ~ resID,
+   estimate = "mm",
+   h0 = 0.5
+  ), vline = 0.5
+)
+@
+
+\clearpage
+
+<<hainmueller_candidate_mm_table, dependson=c("data_hainmueller_candidate"), results="asis">>=
+print(xtable::xtable(
+  cj(
+     hainmueller_candidate, 
+     selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
+     id = ~ resID,
+     estimate = "mm",
+     h0 = 0.5
+  )[c("feature", "level", "estimate", "std.error", "z")],
+    digits = 2, align = c("l", "l", "p{3in}", "r", "r", "r")
+), include.rownames = FALSE, size = "footnotesize")
+@
+
+\clearpage
+
+\section{Ballard-Rosa et al. (2016) Tax Preference Experiment}
+
+\subsection{Replication using AMCEs}
+
+<<bms_amce_appendix, dependson=c("data_bms"), fig.height=8, fig.width=8>>=
+plot(
+  cj(bms, chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev, weights = ~ weight, id = ~ ID, estimate = "amce")
+)
+@
+
+\clearpage
+
+<<bms_amce_table, dependson=c("data_bms"), results="asis">>=
+print(xtable::xtable(
+  cj(
+    bms,
+    chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev,
+    weights = ~ weight,
+    id = ~ ID,
+    estimate = "amce"
+   )[c("feature", "level", "estimate", "std.error", "z")],
+     digits = 2, align = c("l", "l", "p{1.5in}", "r", "r", "r")
+), include.rownames = FALSE)
+@
+
+\clearpage
+
+\subsection{Replication using MMs}
+
+<<bms_mm_appendix, dependson=c("data_bms"), fig.height=8, fig.width=8>>=
+plot(
+  cj(bms, chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev, weights = ~ weight, id = ~ ID, estimate = "mm", h0 = 0.5),
+  vline = 0.5
+)
+@
+
+\clearpage
+
+<<bms_mm_table, dependson=c("data_bms"), results="asis">>=
+print(xtable::xtable(
+  cj(
+    bms,
+    chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev,
+    weights = ~ weight,
+    id = ~ ID,
+    estimate = "mm",
+    h0 = 0.5)[c("feature", "level", "estimate", "std.error", "z")],
+  digits = 2, align = c("l", "l", "p{1.5in}", "r", "r", "r")
+), include.rownames = FALSE)
+@
+
+\clearpage
+
+\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by ``Taxes Harm Economy'' Split using AMCEs}
+
+<<bms_subgroup_amce_appendix1, dependson=c("data_bms"), fig.width=8, fig.height=8>>=
+plot(cj(subset(bms, taxes_harm_split %in% c("Help", "Harm")),
+        chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev,
+        id = ~ID,
+        weights = ~weight,
+        estimate = "amce",
+        by = ~ taxes_harm_econ),
+     vline = 0,
+     group = "taxes_harm_econ",
+     legend_title = "Taxes Help/Harm Economy")
+@
+
+\clearpage
+
+\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by ``Taxes Harm Economy'' Split using MMs}
+
+<<bms_subgroup_mm_appendix1, dependson=c("data_bms"), fig.width=8, fig.height=8>>=
+plot(cj(subset(bms, taxes_harm_split %in% c("Help", "Harm")),
+        chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev,
+        id = ~ID,
+        weights = ~weight,
+        estimate = "mm",
+        h0 = 0.5,
+        by = ~ taxes_harm_econ),
+     vline = 0.5,
+     group = "taxes_harm_econ",
+     legend_title = "Taxes Help/Harm Economy")
+@
+
+\clearpage
+
+\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by Inequity Aversion using AMCEs}
+
+<<bms_subgroup_amce_appendix2, dependson=c("data_bms"), fig.width=8, fig.height=8>>=
+plot(cj(subset(bms, !is.na(ineq_averse_dum)),
+        chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev,
+        id = ~ID,
+        weights = ~weight,
+        estimate = "amce",
+        by = ~ ineq_averse_dum),
+     vline = 0,
+     group = "ineq_averse_dum",
+     legend_title = "Inequity Aversion")
+@
+
+\clearpage
+
+\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by Inequity Aversion using MMs}
+
+<<bms_subgroup_mm_appendix2, dependson=c("data_bms"), fig.width=8, fig.height=8>>=
+plot(cj(subset(bms, !is.na(ineq_averse_dum)),
+        chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev,
+        id = ~ID,
+        weights = ~weight,
+        estimate = "mm",
+        h0 = 0.5,
+        by = ~ ineq_averse_dum),
+     vline = 0.5,
+     group = "ineq_averse_dum",
+     legend_title = "Inequity Aversion")
+@
+
+\clearpage
+
+\subsection{Comparison of Alternative Reference Categories for Ballard-Rosa et al. (2016) Tax Preference Experiment, by ``Taxes Harm Economy'' Split}
+
+<<bms_subgroup_example1, dependson=c("data_bms")>>=
+# estimates benchmarked to largest difference between subgroups
+bms.A <- bms
+    bms.A$taxrate1 <- relevel(bms.A$taxrate1, "<10k: 15%")
+    bms.A$taxrate2 <- relevel(bms.A$taxrate2, "10-35k: 35%")
+    bms.A$taxrate3 <- relevel(bms.A$taxrate3, "35-85k: 35%")
+    bms.A$taxrate4 <- relevel(bms.A$taxrate4, "85-175k: 5%")
+    bms.A$taxrate5 <- relevel(bms.A$taxrate5, "175-375k: 45%")
+    bms.A$taxrate6 <- relevel(bms.A$taxrate6, ">375k: 45%")
+    bms.A$taxrev <- relevel(bms.A$taxrev, "<75%")
+# estimates benchmarked to smallest difference between subgroups
+bms.B <- bms
+    bms.B$taxrate1 <- relevel(bms.A$taxrate1, "<10k: 5%")
+    bms.B$taxrate2 <- relevel(bms.A$taxrate2, "10-35k: 25%")
+    bms.B$taxrate3 <- relevel(bms.A$taxrate3, "35-85k: 25%")
+    bms.B$taxrate4 <- relevel(bms.A$taxrate4, "85-175k: 25%")
+    bms.B$taxrate5 <- relevel(bms.A$taxrate5, "175-375k: 25%")
+    bms.B$taxrate6 <- relevel(bms.A$taxrate6, ">375k: 35%")
+    bms.B$taxrev <- relevel(bms.A$taxrev, "95-105%")
+# formula
+f1 <- chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev
+# estimate
+amce_by_harm_1 <- cj(bms.A, f1, id = ~ ID, weights = ~ weight, estimate = "amce", by = ~ taxes_harm_split)
+amce_by_harm_2 <- cj(bms.B, f1, id = ~ ID, weights = ~ weight, estimate = "amce", by = ~ taxes_harm_split)
+# tag datasets and merge
+amce_by_harm_1$dataset <- "A"
+amce_by_harm_2$dataset <- "B"
+amce_ref_bms_merged1 <- rbind(amce_by_harm_1, amce_by_harm_2)
+amce_ref_bms_merged1$level <- factor(amce_ref_bms_merged1$level, levels = with(bms, c(levels(taxrate1), levels(taxrate2), levels(taxrate3), levels(taxrate4), levels(taxrate5), levels(taxrate6), levels(taxrev))))
+@
+
+<<bms_subgroup_example_plot1, dependson=c("data_bms", "bms_subgroup_example1"), fig.width=10, fig.height=10, fig.caption="Alternative Reference Categories Features in Ballard-Rosa et al.
+(2016) Tax Preference Experiment, by ``Taxes Harm Economy'' Split">>=
+plot(amce_ref_bms_merged1, group = "taxes_harm_split", feature_headers = FALSE, legend_title = "Taxes Help/Harm Economy", vline = 0) + 
+  facet_grid(rows = vars(feature), cols = vars(dataset), scales = "free_y", space = "free_y", labeller = function(x) label_value(x, multi_line = FALSE)) +
+  theme(strip.text.x = element_text(size = 8),
+        strip.text.y = element_text(size = 5))
+@
+
+\clearpage
+
+\subsection{Comparison of Alternative Reference Categories for Ballard-Rosa et al. (2016) Tax Preference Experiment, by Inequity Aversion}
+
+<<bms_subgroup_example2, dependson=c("data_bms")>>=
+# estimates benchmarked to largest difference between subgroups
+bms.A <- bms
+    bms.A$taxrate1 <- relevel(bms.A$taxrate1, "<10k: 25%")
+    bms.A$taxrate2 <- relevel(bms.A$taxrate2, "10-35k: 35%")
+    bms.A$taxrate3 <- relevel(bms.A$taxrate3, "35-85k: 35%")
+    bms.A$taxrate4 <- relevel(bms.A$taxrate4, "85-175k: 35%")
+    bms.A$taxrate5 <- relevel(bms.A$taxrate5, "175-375k: 45%")
+    bms.A$taxrate6 <- relevel(bms.A$taxrate6, ">375k: 5%")
+    bms.A$taxrev <- relevel(bms.A$taxrev, "105-125%")
+# estimates benchmarked to smallest difference between subgroups
+bms.B <- bms
+    bms.B$taxrate1 <- relevel(bms.A$taxrate1, "<10k: 5%")
+    bms.B$taxrate2 <- relevel(bms.A$taxrate2, "10-35k: 5%")
+    bms.B$taxrate3 <- relevel(bms.A$taxrate3, "35-85k: 5%")
+    bms.B$taxrate4 <- relevel(bms.A$taxrate4, "85-175k: 15%")
+    bms.B$taxrate5 <- relevel(bms.A$taxrate5, "175-375k: 25%")
+    bms.B$taxrate6 <- relevel(bms.A$taxrate6, ">375k: 25%")
+    bms.B$taxrev <- relevel(bms.A$taxrev, "95-105%")
+# formula
+f1 <- chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev
+# estimate
+amce_by_harm_1 <- cj(subset(bms.A, !is.na(ineq_averse_dum)), f1, id = ~ ID, weights = ~ weight, estimate = "amce", by = ~ ineq_averse_dum)
+amce_by_harm_2 <- cj(subset(bms.B, !is.na(ineq_averse_dum)), f1, id = ~ ID, weights = ~ weight, estimate = "amce", by = ~ ineq_averse_dum)
+# tag datasets and merge
+amce_by_harm_1$dataset <- "A"
+amce_by_harm_2$dataset <- "B"
+amce_ref_bms_merged2 <- rbind(amce_by_harm_1, amce_by_harm_2)
+amce_ref_bms_merged2$level <- factor(amce_ref_bms_merged2$level, levels = with(bms, c(levels(taxrate1), levels(taxrate2), levels(taxrate3), levels(taxrate4), levels(taxrate5), levels(taxrate6), levels(taxrev))))
+@
+
+<<bms_subgroup_example_plot2, dependson=c("data_bms", "bms_subgroup_example2"), fig.width=10, fig.height=10, fig.caption="Alternative Reference Categories Features in Ballard-Rosa et al.
+(2016) Tax Preference Experiment, by Inequity Aversion">>=
+plot(amce_ref_bms_merged2, group = "ineq_averse_dum", feature_headers = FALSE, legend_title = "Inequity Aversion", vline = 0) + 
+  facet_grid(rows = vars(feature), cols = vars(dataset), scales = "free_y", space = "free_y", labeller = function(x) label_value(x, multi_line = FALSE)) +
+  theme(strip.text.x = element_text(size = 8),
+        strip.text.y = element_text(size = 5))
+@
+
+\clearpage
+
+\section{Teele et al. (2018) Candidate Experiment}
+
+\subsection{Replication using AMCEs}
+
+<<tkr_amce_appendix, dependson=c("data_tkr"), fig.height=5, fig.width=8>>=
+plot(
+  cj(
+   tkr, 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "amce"
+  ),
+)
+@
+
+\clearpage
+
+<<tkr_amce_table, dependson=c("data_tkr"), results="asis">>=
+print(xtable::xtable(
+  cj(
+   tkr, 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "amce"
+  )[c("feature", "level", "estimate", "std.error", "z")],
+  digits = 2, align = c("l", "l", "p{1.5in}", "r", "r", "r")
+), include.rownames = FALSE)
+@
+
+\clearpage
+
+\subsection{Replication using MMs}
+
+<<tkr_mm_appendix, dependson=c("data_tkr"), fig.height=5, fig.width=8>>=
+plot(
+  cj(
+   tkr, 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "mm",
+   h0 = 0.5
+  ), vline = 0.5
+)
+@
+
+\clearpage
+
+<<tkr_mm_table, dependson=c("data_tkr"), results="asis">>=
+print(xtable::xtable(
+  cj(
+   tkr, 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "mm",
+   h0 = 0.5
+  )[c("feature", "level", "estimate", "std.error", "z")],
+  digits = 2, align = c("l", "l", "p{1.5in}", "r", "r", "r")
+), include.rownames = FALSE)
+@
+
+\clearpage
+
+\subsection{Subgroup Analysis for Teele et al. (2018) Candidate Experiment using AMCEs}
+
+<<tkr_subgroup_amce_appendix, dependson=c("data_tkr"), fig.height=5, fig.width=8>>=
+plot(
+  cj(
+   subset(tkr, !is.na(PartyID)), 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "amce",
+   by = ~ PartyID
+  ), group = "PartyID"
+)
+@
+
+\subsection{Subgroup Analysis for Teele et al. (2018) Candidate Experiment using MMs}
+
+<<tkr_subgroup_mm_appendix, dependson=c("data_tkr"), fig.height=5, fig.width=8>>=
+plot(
+  cj(
+   subset(tkr, !is.na(PartyID)), 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "mm",
+   by = ~ PartyID,
+   h0 = 0.5
+  ), vline = 0.5, group = "PartyID"
+)
+@
+
+\clearpage
+
+\subsection{Comparison of Alternative Reference Categories for Teele et al. (2018) Candidate Experiment}
+
+<<tkr_subgroup_example, dependson=c("data_tkr")>>=
+# estimates benchmarked to largest difference between subgroups
+tkr.A <- tkr
+    tkr.A$feature_sex <- relevel(tkr.A$feature_sex, "Male")
+    tkr.A$feature_experience <- relevel(tkr.A$feature_experience, "None")
+    tkr.A$feature_marital <- relevel(tkr.A$feature_marital, "Doctor Spouse")
+    tkr.A$feature_job <- relevel(tkr.A$feature_job, "Corporate Lawyer")
+    tkr.A$feature_children <- relevel(tkr.A$feature_children, "1 child")
+    tkr.A$feature_age <- relevel(tkr.A$feature_age, "65")
+# estimates benchmarked to smallest difference between subgroups
+tkr.B <- tkr
+    tkr.B$feature_sex <- relevel(tkr.B$feature_sex, "Male")
+    tkr.B$feature_experience <- relevel(tkr.B$feature_experience, "1 year")
+    tkr.B$feature_marital <- relevel(tkr.B$feature_marital, "Farmer Spouse")
+    tkr.B$feature_job <- relevel(tkr.B$feature_job, "Mayor")
+    tkr.B$feature_children <- relevel(tkr.B$feature_children, "No children")
+    tkr.B$feature_age <- relevel(tkr.B$feature_age, "45")
+# formula
+f1 <- winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age
+# estimate
+amce_by_pid_1 <- cj(subset(tkr.A, !is.na(PartyID)), f1, id = ~ responseid, estimate = "amce", by = ~ PartyID)
+amce_by_pid_2 <- cj(subset(tkr.B, !is.na(PartyID)), f1, id = ~ responseid, estimate = "amce", by = ~ PartyID)
+# tag datasets and merge
+amce_by_pid_1$dataset <- "A"
+amce_by_pid_2$dataset <- "B"
+amce_ref_tkr_merged <- rbind(amce_by_pid_1, amce_by_pid_2)
+amce_ref_tkr_merged$level <- factor(amce_ref_tkr_merged$level, levels = with(tkr, c(levels(feature_sex), levels(feature_experience), levels(feature_marital), levels(feature_job), levels(feature_children), levels(feature_age))))
+@
+
+<<tkr_subgroup_example_plot, dependson=c("data_tkr", "tkr_subgroup_example"), fig.width=10, fig.height=10, fig.caption="Alternative Reference Categories Features in Teele et al.
+(2018) Candidate Experiment">>=
+plot(amce_ref_tkr_merged, group = "PartyID", feature_headers = FALSE, legend_title = "Party Identification", vline = 0) + 
+  facet_grid(rows = vars(feature), cols = vars(dataset), scales = "free_y", space = "free_y", labeller = function(x) label_value(x, multi_line = FALSE)) +
+  theme(strip.text.x = element_text(size = 8),
+        strip.text.y = element_text(size = 5))
+@
+
+\clearpage
+
+\section*{}
+
+\noindent This paper was built using \texttt{knitr::knit2pdf()} under the following environment:
+
+<<session_info, cache=FALSE>>=
+sessionInfo()
+@
+
 \end{document}

### 2018-07-11 manuscript.tex
update manuscript (almost for submission)

--- 2018-02-20 manuscript.tex
@@
 \title{Measuring Subgroup Preferences in Conjoint Experiments}
-\author{Sara Hobolt, Thomas J. Leeper, and James Tilley}
+\author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
@@
 
-{\abstract Conjoint analysis has experienced a recent resurgence.
-The driving force for this change has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a fully randomized conjoint design and an associated analytic approach that emphasizes a single causal quantity of interest: namely, the average marginal component effect (AMCE).
-The AMCE convey the degree to which a given value of a feature increases or decreases respondents' support for a conjoint profile, averaging across all respondents and all other profile features.
-While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses use AMCEs for descriptive purposes: that is, not map variation in preferences across attributes of a multidimensional object, such as a candidate individual or public policy.
-And many authors also engage in subgroup analyses, wherein they compare subsets of respondents to one another with respect to AMCEs.
-This paper argues that such approaches can substantially mislead researchers about the degree of agreement or disagreement between subgroups, demonstrates the problem using several example datasets, and provides several suggestions for improved reporting and interpretation.
-Most importantly, it highlights that the difference in AMCEs between groups is sensitive to the choice of reference categories of features, while the difference in the marginal means is not sensitive in this way.
-When groups substantially differ in preferences, the difference in marginal means rather than the difference better conveys the size of such disagreements.}
+{\abstract Conjoint analysis is an increasingly prominent tool for studying political preferences.
+The method powerfully disentangles the causes of preferences over complex, multidimensional objects, such as political candidates or public policies.
+Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs), which measure the degree to which a given value of a conjoint profile feature increases or decreases respondents' support for the overall profile relative to a baseline, averaging across all respondents and all other profile features.
+While the AMCE has a clear causal interpretation, most published conjoint analyses also use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object, often including comparisons between theoretically interesting subgroups of respondents.
+We demonstrate that such analyses of conditional AMCEs can substantially mislead researchers about the degree of preference agreement or disagreement between subgroups.
+Most importantly, we highlight that the difference in conditional AMCEs between subgroups is sensitive to the choice of reference categories of features, providing inferences about subgroup preferences that are biased in unpredictable ways.
+We demonstrate the problem using simple examples drawn from the published literature and provide suggestions for improved reporting and interpretation.
+Given the rapidly accelerating use of conjoint analyses, these results have critically important implications for research in nearly all areas of political science.}
 
@@
 
-Conjoint analysis has experienced a recent resurgence in the social sciences and especially in political science.
-The driving force has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE).
-By capturing the multidimensionality of target objects, such as a candidate individual or public policy, the conjoint design breaks any explicit or implicit confounding between those features, thus giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' support for a packaged conjoint profile, averaging across all respondents and all other profile features.
+Amidst the dramatically increased use of experiments within political science \citep{Druckmanetal2006, Mutz2011}, conjoint experimental designs have recently become a prominent methodological tool in political science.
+While traditional survey experiments tend to examine just one or two factors that might shape outcomes \citep[see, for reviews,][]{GainesKuklinskiQuirk2007, Sniderman2011}, conjoint designs allow researchers to study the independent effects on preferences of many features of complex, multidimensional objects such as political candidates \citep{Campbelletal2016, TeeleKallaRosenbluth2018}, immigrant admissions \citep{HainmuellerHopkins2015, BansakHainmuellerHangartner2016, WrightLevyCitrin2016}, or public policies \citep{GallegoMarx2017, Hankinson2018}.
+The driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE).
+By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit or implicit confounding between features of these objects, giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' support for a packaged conjoint profile relative to a baseline, averaging across all respondents and all other profile features.
 
-While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object.
-For example, \citet{HainmuellerHopkinsYamamoto2014} describe some of the results of their conjoint analysis of congressional candidate preferences:
+While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object.
+This is particularly the case when researchers engage in subgroup analyses of conjoint experiments for heterogeneity.
+For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.
+Similarly, \citet{BansakHainmuellerHangartner2016} compare preferences toward immigrants across number of binary respondent characteristics: age, education, left-right ideology, and income.
+In a different domain, \citet{BallardRosaMartinScheve2016} compare preferences over tax policies across a number of subgroups defined by demographics and political orientations.
+\citet{TeeleKallaRosenbluth2018} compare AMCEs for features of male and female political candidates among male and female respondents.
+\citet{KirklandCoppock2017} do a similar comparison between Democrats and Republicans in hypothetical elections.
+
+In these and many other articles, interpretation of these subgroup analyses focus not just on the \textit{causal effects} of profile features within each subgroup (what Hainmueller et al.
+term ``conditional AMCEs''; 13) but also focus on an implied quantity of interest: the \textit{difference} between two conditional AMCEs across subgroups.
+Searching for causal effect heterogeneity is an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017}, yet most conjoint analyses use this difference-in-AMCEs instead to \textit{descriptively} interpret apparent differences in preferences between the two groups.
+What is not obvious in such analyses is that differences-in-preferences (that is to say, the degree of favorability toward profiles containing a given feature) are not directly reflected in differences-in-AMCEs.
+Yet authors frequently use visual or more formal comparisons of conditional AMCEs to make descriptive claims about preferences, leading themselves and readers astray.
+In this paper, we show that a difference in underlying subgroup preferences --- like a difference in willingness to support a Syrian immigrant between high and low ethnocentrism respondents --- is only reflected in the difference-in-AMCEs under particular preference configurations and analytic choices.
+
+As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well but where preferences between subgroups diverge in the reference category, the difference-in-AMCEs is a highly misleading representation of underlying preferences.
+Yet most published conjoint studies appear to report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment.
+Ultimately effects are relative, not absolute, statements about preferences.
+For example, in a comparison of subgroup effects for Democrats and Republicans, Republicans might display a smaller effect because their preferences in the reference category are already very positive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.
+There is simply no predictable inference to be drawn from subgroup causal effects to the levels of underlying subgroup preferences.
+This inferential error --- interpreting differences in the size of causal effects as descriptive differences in preferences --- appears to be widespread in published conjoint analyses.
+Thus a seemingly trivial methodological decision has the potential to substantially alter our interpretations of a rapidly growing body of evidence about political preferences over important and varied political matters, including candidate selection and public policy.
+
+In what follows, we demonstrate the challenges of conjoint analysis and show how reference category choice for profile features creates significant problems for the now-common practice of comparing conditional AMCEs across respondent subgroups.
+We show that the size and the direction of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features and that reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar, using examples drawn from the published political science literature (namely experiments by \citealt{HainmuellerHopkinsYamamoto2014, BallardRosaMartinScheve2016, TeeleKallaRosenbluth2018}).
+The paper then provides suggestions for improved reporting and interpretation based around a purely descriptive quantity of interest: unadjusted marginal means.
+Newly developed software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment --- is demonstrated throughout \citep{Leeper2018cregg}.
+We conclude with advice for best practices in the analysis and presentation of conjoint results.
+
+\section*{Quantities of Interest in Conjoint Experiments}\label{sec:quantities}
+
+Conjoint analysis serves two purposes.
+One is to assess causal effects.
+Another is preference description.
+In causal inference, conjoints provide a design and analytic approach that allows researchers to understand the causal effect of a given feature on overall support for a multidimensional object, averaging across other features of the object included in the design.
+Such inferences can be thought of as statements of the form: ``shifting an immigrant's country of origin from India to Poland increases favorability by X percentage points.'' In descriptive inference, conjoints provide information about both (a) the absolute favorability of respondents toward objects with particular features or combinations of features, and (b) the relative favorability of respondents toward an object with alternative combinations of features.
+Such inferences can be thought of as statements of the form ``Polish immigrants are preferred by X\% of respondents'' or ``Polish immigrants are more supported than Mexican immigrants, by X percentage points.'' Thus both causal and descriptive interpretations of conjoints are based upon the distribution of preferences across profile features and differences in preferences across alternative feature combinations.
+
+Importantly, a fully randomized conjoint design (without constraints between profile features) is simply a full-factorial experiment with some cells possibly, albeit randomly, left unobserved.
+All quantities of interest relevant to the analysis of conjoint designs derive from combinations of cell means, marginal means, and the grand mean, as is common in the traditional analysis of factorial experiments.
+In a forced choice design, the \textit{grand mean} is by definition 0.5 (i.e., 50\% of all profiles shown are chosen and 50\% are not chosen).
+\textit{Cell means} are the mean outcome for each particular combination of feature levels.
+In the full-factorial design discussed by \citet{HainmuellerHopkinsYamamoto2014} and now widely used in political science, many or perhaps most cell means are unobserved.
+For example, in their candidate choice experiment, there are $2*6*6*6*2*6*6*6 = 186,624$ cell means but only 3,466 observations so about 98\% of cell means are unobserved.
+While this would be problematic for attempting to infer pairwise comparisons between cells, conjoint analysts mostly focus on the marginal effects of each feature rather than more complex interactions.
+
+Average marginal component effects (AMCEs) depend only upon \textit{marginal means}: that is the column and row means for each feature level averaging across all other features.
+The marginal means describe the variation in preferences toward profiles that have a particular feature level.
+For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities: a marginal mean of 0 indicates respondents select profiles with that feature level with probability $Pr(Y=1|X=x) = 0$ while a marginal mean of 1 indicates respondents select profiles with that feature level with probability $(Pr(Y=1|X=x)=1$.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany).
+Instead, the marginal mean can range from the probability of co-occurrence to 1 minus that probability.
+If there are five levels of a feature, each shown with equal probability, then the probability of co-occurrence is $\frac{1}{5}*\frac{1}{5} = 0.04$ such that the marginal mean can take values in the range $(0.04,0.96)$.
+If the design is constrained so that features cannot be the same for both immigrants, then the marginal means fully range from zero to one.
+This constraint on the range of the marginal means also constrains the range of AMCEs.
+Notably, many conjoints provide features with only two levels, such as the male-versus-female candidate feature examined by \citet{TeeleKallaRosenbluth2018}.
+In such cases, the probability of co-occurrence is $\frac{1}{2}*\frac{1}{2} = 0.25$ bounding the AMCE for female (as opposed to male) candidates to the range $(-0.5, 0.5)$ if both candidates can have the same sex.
+Caution is therefore needed in comparing the relative size of features with few levels to features with many levels given that effects have different bounds.} With rating scale outcomes, marginal means can vary arbitrarily along the outcome scale used.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_replication-1} 
+\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_replication-2} \caption[Replication of Hainmueller et al]{Replication of Hainmueller et al.
+(2014) Candidate Experiment using AMCEs and MMs}\label{fig:hainmueller_candidate_replication}
+\end{figure}
+
+\end{knitrout}
+
+Because levels of features are randomly assigned, pairwise differences between two marginal means for a given feature (e.g., between candidates who are male versus female) have a direct causal interpretation.
+For fully randomized designs, the AMCE proposed by \citet{HainmuellerHopkinsYamamoto2014} is equivalent to the average marginal effect of each feature level for a model where each feature is converted into a matrix of indicator variables with one level left out as a reference category.\footnote{This is no different from any other regression context wherein one level of any categorical variable must be omitted from the design matrix in order to avoid perfect multicollinearity.
+In designs that entail constraints between profile features, the average marginal effect is a weighted average of effects across each combination of the constrained features where the weights on the effects are arbitrary but typically uniform.
+We ignore this distinction in the remainder of this article, as all of our results apply equally to fully randomized and to constrained designs.} This close relationship between AMCEs and marginal means is visible in Figure \ref{fig:hainmueller_candidate_replication} which presents a replication of the AMCE-based analysis of their candidate experiment (upper panel) and an analogous examination of the results using marginal means (lower panel).
+Note, in particular, how marginal means convey information about the preferences of respondents for all feature levels while AMCEs definitionally restrict the AMCE for the reference category to zero (or undefined).
+For example, the AMCE for a candidate serving in the military is 0.09 (or a 9-percentage point) increase in favorability, reflecting marginal means for serving and non-serving candidates of 0.46 and 0.54, respectively.
+
+The AMCE is often described as an estimate of the relative favorability of profiles with counterfactual levels of a feature; for example, ``male candidates are preferred to female candidates'' \citep[6]{TeeleKallaRosenbluth2018}.
+\citet{HainmuellerHopkinsYamamoto2014} similarly describe some of the results of conjoint on preferences toward Congressional candidates:
 
@@
 
-This characterization of the results has a distinctly descriptive flavor.
-While a given religious characteristic \textit{causes} respondents to evaluate a given candidate more or less favorably, the gist of the analysis is that there are differences in the evaluations of candidates of different religious persuasions.
-\citeauthor{HainmuellerHopkinsYamamoto2014}'s phrasing highlights another feature of conjoint analysis that is not widely discussed: the baseline (or reference category) in the estimation of AMCEs significantly colors which pairwise comparisons between features are highlighted and the degree to which preferences are stated in positive or negative terms.
-By choosing a non-religious candidate as a baseline, the AMCEs are all expressed relative to this baseline; the difference (if any) between evaluations of Mormon and Evangelical candidates, for example, is not obvious and while it is likely that Mainline Protestant, Catholic, and Jewish candidates are all preferred over Mormon or Evangelical candidates, the AMCEs for these categories are indistinguishable from zero (rather than the positive values they would take if Mormon or Evangelical were the reference category).
-Similarly, by selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), some AMCEs are positive while others are negative.
-Yet because any feature level could be used as the reference cateory, the size but also \textit{direction} of AMCEs is arbitrary.
-Were the category with the lowest favorability chosen as the reference, all AMCEs would be positive; were the category with the highest favorability chosen as the reference, all AMCEs would be negative.
-The results would be \textit{numerically equivalent} --- because ultimately the choice of reference category is completely arbitrary and mathematicaly irrelevant --- but the choice as sizable consequences for the interpretation of conjoint analyses.
+\noindent These examples make clear that despite the \textit{causal} inference potentially provided by the AMCE, the quantity of interest is frequently used to provide a characterization of a preferences that has a distinctly descriptive flavor.
+Indeed, this style of description is widespread in conjoint analyses.
+\citet{BallardRosaMartinScheve2016} interpretation their tax preference conjoint:
 
-This is particularly the case when researchers engage in subgroup analyses of conjoint experiments.
-For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.\footnote{This is achieved by subsetting the data based upon the measure of ethnocentrism and performing separate regressions for high- and low-ethnocentrism respondents.} The interpretation therefore focuses not just on the arbitrarily signed AMCEs within each subgroup (what Hainmueller et al.
-term ``conditional AMCEs''; 13) but also on an implied quantity of interest: the difference between conditional AMCEs.
-This comparison seems intuitively correct but because the conditional AMCEs are causal effects expressed relative to an arbitrary baseline, the differences between AMCEs only convey a difference in preference to the extent that the reference category is equally liked by both groups.
-When the preferences toward the reference category differ substantially between groups, the difference in AMCEs is a biased estimate of the difference in preferences between the two groups.
-For example, \citet{HainmuellerHopkinsYamamoto2014} eyeball the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22).
-Yet simply because the AMCEs are similar does not necessarily mean that \textit{preferences} are similar.
+\begin{quote}
+we find strong support for progressive preferences over federal income taxes among the American public [\dots] respondents are less likely to support a given tax plan as the tax rate on the poorest three groups increases but more likely to support an income tax policy when the tax rate on the richest two groups increases, at least to a point.
+\end{quote}
 
-To bring some intuition to this problem, consider a simple two-condition experiment in which the effect of the treatment, $x \in {0,1}$, is compared across a single two-category covariate, $z \in {0,1}$.
-Subgroup regression equations might be:
+\noindent This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature.
+A positive (negative) AMCE is read as higher (lower) favorability but it is only higher (lower) relative to whatever category serves as the baseline.
+For example, in the \citeauthor{HainmuellerHopkinsYamamoto2014} candidate example, choosing a non-religious candidate as a baseline means the AMCEs in the candidate experiment are all expressed relative to this non-religious baseline; the difference (if any) between other pairs of marginal means (e.g., evaluations of Mormon and Evangelical candidates) is not obvious.
+Relatedly, the negative direction (and the size) of the AMCEs for Mormon and Evangelical candidates would be different if the least-liked category (Mormon candidates) were the reference group.
+In that case, the AMCE for Evangelicals would be small and positive and the AMCEs for all other categories (including the presented reference category, ``none'') would be large and positive.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/reference_category-1} \caption[Reference Category Diagnostic for the 'Education' Feature from Hainmueller et al.'s (2014) Immigration Experiment]{Reference Category Diagnostic for the 'Education' Feature from Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:reference_category}
+\end{figure}
+
+\end{knitrout}
+
+This choice of reference category for estimating AMCEs can seem trivial but is quite consequential.
+For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment, the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline.
+Figure \ref{fig:reference_category} shows how the estimated AMCEs for each level of education would have differed depending on that choice.
+Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline.\footnote{As another example, in \citeauthor{BallardRosaMartinScheve2016}'s tax preference experiment, the lowest level of taxation is chosen as the reference category for each feature for reasons of substantive interpretation, yet despite the substantive intuitiveness of this, favorability toward the lowest level of taxation is not necessarily higher or lower than preferences for alternative tax rates.} The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses.\footnote{In \textit{constrained} conjoint designs, the choice of reference category is even more important.
+Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature.
+Consequently, the AMCE for the ``Escape Persecution'' level (relative to the  ``Reunite with family'' reference category) is only defined for the subset of the design involving countries `China,' `Sudan,' `Somalia,' and `Iraq.' The AMCEs for those four countries (relative to India as a baseline) marginalize across all reasons for application, but the AMCEs for the first six countries marginalize only across the latter two reasons.
+Thus the interpretation of AMCEs --- and the basic ability to estimate them in constrained designs --- depends entirely upon the selection of a reference category where all feature levels can co-occur.
+In a design where \textit{all} features are constrained, then AMCEs are undefined for the design as a whole and only estimable for subsets of the design that are \textit{conditionally} unconstrained.}
+
+%To demonstrate this, Figure \ref{fig:reference_category} shows the estimated AMCEs for the country of origin feature from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, with the analysis repeated ten times each time using a different country as the reference category.
+For example, the top-most set of points and error bars convey the AMCE for Iraq from each of these analyses.
+When Iraq is the reference category, its AMCE is undefined.
+When any other country is chosen as a reference category, the AMCE for Iraq is negative because respondents are more negative toward Iraqi immigrants than they are toward those of other countries.
+Similarly, the bottom set of points and error bars reflects the estimated AMCEs for Germany.
+When Germany is the reference category, its AMCE is undefined but when any other country is used as the reference category, its AMCE is positive.
+
+%These cases are therefore not \textit{directionally} sensitive to the choice of reference category but of course the point estimates vary considerably.
+But the estimated AMCE of countries who are neither strongly disliked or strongly favored by respondents are highly sensitive to choice of reference category.
+Consider, for example, the estimated AMCEs for China (the four set of points from the top).
+When highly disliked countries are chosen as the reference category (like Somalia, Sudan, or Iraq), the AMCE for China is positive; when highly favored countries are chosen (like Germany, Poland, or the Philippines), the AMCE for China is negative.
+
+\section*{Consequences of Arbitrary Reference Category Choice}\label{sec:challenges}
+
+Given the need to choose a reference category for every feature in order to estimate AMCEs, an important question is: how do researchers decide which of tens of thousands of possible experimental cells should be selected as the reference category?
+Examining recently published conjoint analyses, it appears that the choice of reference category is either arbitrary or based upon substantive intuition about the meaning of feature levels.
+For example, \citet{HainmuellerHopkinsYamamoto2014} choose female immigrants as a baseline in their immigration experiment, thus providing an estimate of the AMCE of being male, while \citet{TeeleKallaRosenbluth2018} choose male candidates as a baseline in their conjoint, thus providing an estimate of the AMCE of being female.
+The choice is seemingly innocuous.
+Sometimes choices of reference category appear to be driven by substantive knowledge: on language skills of immigrants, \citet{HainmuellerHopkinsYamamoto2014} choose fluency as a baseline; on the prior trips to the US feature, ``never'' is chosen as the baseline.
+These seem sensible on face value --- it might seem less useful to define all effects relative to ``having visited many times as a tourist'' as the AMCEs then lose an immediately intuitive interpretation.
+
+% Difference in conditional AMCEs
+\begin{table}
+\caption{Uses of Subgroup Analysis Published in Political Science Journals}\label{tab:papers}
+\begin{center}
+\footnotesize
+\begin{tabular}{p{2in} p{2in} p{2in}}\toprule
+\textbf{Paper} & \textbf{Topic} & \textbf{Subgroup Comparisons} \\ \midrule
+\citet{BechtelScheve2013} & Climate agreement preferences & Environmentalism and International Reciprocity Attitudes \\ \midrule
+\citet{FranchinoZucchini2014} & Candidate preferences & Political Interest, Left-right self-placement\\ \midrule
+\citet{HainmuellerHopkinsYamamoto2014} & Immigration preferences & Ethnocentrism \\ \midrule
+\citet{HansenOlsenBech2014} & Policy preferences & Partisanship \\ \midrule
+\citet{Carlson2015} & Candidate preferences & Co-ethnicity \\ \midrule
+\citet{BansakHainmuellerHangartner2016} & Immigration preferences & Left-right self-placement, age, education, income\\ \midrule
+\citet{BallardRosaMartinScheve2016} & Tax preferences & Various\\ \midrule
+\citet{Campbelletal2016} & Candidate preferences & Partisanship \\ \midrule
+\citet{CarnesLupu2016} & Candidate preferences & Partisanship \\ \midrule
+\citet{Mummolo2016} & News selection & Various\\ \midrule
+\citet{VivyanWagner2016} & Candidate preferences & Political attitudes \\ \midrule
+\citet{MummoloNall2017} & Mobility preferences & Partisanship \\ \midrule
+\citet{BechtelGenoveseScheve2017} & Climate agreement preferences & Employment sector emissions \\ \midrule
+\citet{BechtelHainmuellerMargalit2017} & International bailout preferences & Various\\ \midrule
+\citet{GallegoMarx2017} & Labor market policy & Left-right self-placement \\ \midrule
+\citet{KirklandCoppock2017} & Candidate preferences & Partisanship \\ \midrule
+\citet{Sen2017} & Judicial candidate preferences & Partisanship \\ \midrule
+\citet{Sobolewskaetal2017} & Immigrant integration & Various \\ \midrule
+\citet{EggersVivyanWagner2018} & Candidate preferences & Sex \\ \midrule
+\citet{Hankinson2018} & Housing policy preferences & Various \\ \midrule
+\citet{OliverosSchuster2018} & Bureaucrat candidate preferences & Various \\ \midrule
+\citet{TeeleKallaRosenbluth2018} & Candidate preferences & Sex, Partisanship \\
+\bottomrule
+\end{tabular}
+\end{center}
+\end{table}
+
+Yet the choice is consequential.
+A possibly surprising consequence of the seemingly arbitrary selection of a reference category --- and the resulting arbitrariness of both the size and direction of AMCEs --- is that it can provide highly distorted descriptive interpretation of preferences among subgroups of respondents.
+This occurs when researchers examine \textit{conditional} AMCEs, wherein AMCEs are calculated separately for subgroups of respondents and those conditional estimates are directly compared \citep[13]{HainmuellerHopkinsYamamoto2014}.
+Table \ref{tab:papers} reports a list of recently published articles in political science that engage in this form of subgroup analysis.\footnote{\citet{RatkovicTingley2017} considered efficient methods for performing subgroup analyses in conjoint designs.
+Our focus here is on the narrower problem of interpreting subgroup analyses as traditionally performed using subsetting or interaction terms in a regression framework.} Given the commonly descriptive interpretations of conjoint experimental results, such subgroup analyses seem perfectly intuitive and the set of subgroups listed in the last column of Table \ref{tab:papers} contains some unsurprising covariates, such as partisanship, that are of obvious theoretical interest in almost any study of individual preferences.
+Analytically, these conditional AMCEs can be obtained either from regression estimates on respondent subgroups or through interactions between conjoint features and respondent characteristics, the details of which are unimportant for our purposes.
+
+Conditional AMCEs are not per se a problematic quantity of inference.
+Like subgroup analysis of any experiment, they convey the causal effect of an experimental factor on overall favorability among the subgroup of interest.
+Consider, for example, a two-condition party cue experiment where Democrats and Republicans are exposed to an endorsement cue from the Democratic party or no cue and opinions toward the policy serve as the outcome.
+It is sensible to imagine that effects of the cue might differ for the two groups and therefore to compare the size of cue effect among the two groups.
+Perhaps Democrats are more responsive to the Democratic party cue than are Republicans, making the causal effect larger for Democrats than Republicans.
+Discussions of conditional AMCEs in conjoint analyses often explicitly or implicitly engage in this kind of discussion comparing the size and direction of subgroup causal effects.
+If interpreted as a difference in the size of the causal effect for two groups, such comparisons are perfectly consistent with more traditional experimental analysis and a perfectly acceptable interpretation of the conjoint results.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/tkr_replication-1} 
+\includegraphics[width=\maxwidth]{figure/tkr_replication-2} \caption[Replication of Teele et al]{Replication of Teele et al. (2018) Candidate Experiment using AMCEs and MMs}\label{fig:tkr_replication}
+\end{figure}
+
+\end{knitrout}
+
+Yet, just as analysis of full sample conjoint data is often descriptive in nature, so too conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally.
+For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} visually compare the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22).
+\citet{BallardRosaMartinScheve2016} make similar comparisons in their tax policy conjoint: ``While there are few strong differences in preferences for taxing the lower three income groups (the `hard work' group has slightly lower elasticities for taxing the poor), there are strong differences in preferences for taxing the rich.
+Respondents who believe luck plays a role in economic success are more strongly progressive, although preferences over taxing the \$175K--\$375K bracket are relatively flat'' (12).
+In these examples, the differences between conditional AMCEs are used as a way of descriptively characterizing differences in \textit{preferences} between the groups rather than differences in \textit{causal effects on preferences} in the groups.
+
+As a more complete example, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment separately for Democratic and Republican voters, as provided in the original paper, and the lower panel shows the results using conditional marginal means.
+Respondents' preference for female candidates is very apparent in both forms of analysis.
+Yet the discrepancy between the differences in preferences (i.e., conditional marginal means) and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature in Figure \ref{fig:tkr_replication} (the second set of estimates from the top in both panels).
+The conditional AMCEs in the upper panel correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates.
+Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates).
+In reality, however, the conditional marginal means shown in the lower panel demonstrate that actually Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience.
+Democrats are much more sensitive to experience than are Republicans and important differences in preferences are apparent for extreme categories in the visualization of conditional marginal means, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.
+The selection of a reference category is therefore hugely consequential for a descriptive reading of the AMCE results.
+
+Interpreting conjoint AMCEs as measures of preferences is an inferential error.
+In a simple experiment like the party cue example just given, this kind of interpretation would be obviously flawed.
+A larger causal effect of the party cue for Democrats than Republicans does not necessarily mean that Democrats are more supportive than Republicans on average or in either condition.
+Effects are relative, not absolute, statements about preferences.
+Republicans, for example, might experience a smaller effect because their preferences in the control group are already very supportive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.
+There is simply no predictable connection between subgroup causal effects and the levels of underlying subgroup preferences.
+This inferential error --- interpreting differences in the size of causal effects as descriptive differences in preferences --- appears to be widespread in published conjoint analyses.
+While AMCEs do provide insight into the descriptive variation in preferences within-group and across-features, and conditional AMCEs do estimate the size of causal effects of features within groups, AMCEs cannot provide direct insight into the pattern of preferences between groups because they do not provide information about \textit{absolute} levels of favorability toward profiles with each feature (or combination of features).
+
+This additional information matters.
+Consider again the simple two-condition experiment in which the effect of a cue treatment, $x \in {0,1}$, is compared across a single two-category covariate, $z \in {0,1}$ such as Democratic or Republican self-identification.
+Subgroup regression equations to estimate effects for each group are:
 
@@
 These are, in essence, the conditional AMCEs in a conjoint analysis.
-yet the difference in AMCEs ($\beta_3 - \beta_1$) is not equal to the differnce in preferences between the two groups, which is $\bar{y}_{z=1|x=1} - \bar{y}_{z=0|x=1}$, or estimated by $(\beta_2 + \beta_3) - (\beta_0 + \beta_1)$.
-The difference in AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$.
+Yet the difference in AMCEs ($\beta_3 - \beta_1$) is not equal to the difference in preferences between the two groups, which is $\bar{y}_{z=1|x=1} - \bar{y}_{z=0|x=1}$ (estimated by $(\beta_2 + \beta_3) - (\beta_0 + \beta_1)$).
+The difference-in-AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$.
 Yet the standard AMCE-centric conjoint analysis does not present or characterize either of these quantities.
-And given that the reference category is arbitrary, there is never any reason to expect that an arbitrarily selected reference category satisfies that equality assumption, meaining that when one uses a difference in AMCEs to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.
-
-Worse, because conjoint analysis generates a sparse feature matrix (where there is never any guarantee that a particular combination of feature levels is observed in the data), it is also not possible to empirically select an appropriate set of reference categories using data.
-And while it might seem possible to select a \textit{marginally} appropriate reference category (i.e., one where preferences are similar with respect to a given feaure), preferences toward that reference category may differ across other dimensions in the analysis.
-Thus, there is no way to use conditional AMCEs or differences-in-AMCEs to convey the underlying similarity or differences in preferences across sample subgroups.
-
-In what follows, we formalize how the arbitrary selection of a reference category can mislead researchers about the pattern of preferences exposed by a conjoint experiment and demonstrates how this problem is especially problematic when researchers engage in the now-common practice of comparing conditional AMCEs across respondent subgroups.
-The paper then demonstrates the problem using several example datasets and provides suggestions for improved reporting and interpretation based around a purely descriptive quantity of interest: namely, the unadjusted marginal means.
-Software for the R programming language to easily calculate marginal means (as well as AMCEs) is also discussed.
-
-\section{Quantities of Interest}
-
-% AMCE
-
-% Difference in conditional AMCEs
-
-\citet{RatkovicTingley2017} considered efficient methods for performing subgroup analyses in conjoint designs.
-Our focus here is on the narrower problem of interpreting subgroup analyses as traditionally performed.
-
-\begin{table}
-\caption{Uses of Subgroup Analysis in Published Work}
-\begin{center}
-\footnotesize
-\begin{tabular}{p{2.5in} p{2in} p{2in}}\toprule
-\textbf{Paper} & \textbf{Topic} & \textbf{Subgroup Comparisons} \\ \midrule
-Hainmueller, Hopkins, and Yamamoto (2014) & Immigration Preferences & Ethnocentrism \\
-Bechtel and Scheve (2013) & Climate agreement preferences & Environmentalism and International Reciprocity Attitudes \\
-Bechtel, Genovese, and Scheve (2017) & Climate agreement preferences & Employment sector emissions \\
-Hansen, Olsen, and Bech (2015) & Policy Preferences & Partisanship \\
-Carlson (2015) & Candidate Choice & Co-ethnicity \\
-Franchino and Zucchini (2015) & Candidate Choice & Political Interest, Left-right self-placement\\
-Carnes and Lupu (2016) & Candidate Choice & Partisanship \\
-Mummolo (2016) & News Selection & Various\\
-Mummolo and Nall (2016) & Mobility preferences & Partisanship \\
-Ballard-Rosa, Martin, and Scheve (2016) & Tax Preferences & Various\\
-Bechtel, Hainmueller, and Margalit (2017) & International bailout preferences & Various\\
-Sen (2017) & Judicial candidate preferences & Partisanship \\
-Campbell, Cowley, Vivyan, and Wagner (2016) & Candiate preferences & Partisanship \\
-Kirkland, Coppock (2017) & Candidate choice & Partisanship \\ \bottomrule
-\end{tabular}
-\end{center}
-\end{table}
-
-% Marginal means
-
-\section{Challenges of Interpretation}
-
-% baseline levels of features
-
-% subgroup analyses
-
-% difference in AMCEs versus difference in marginal means
-
-The following figure provides a replication of Hainmueller et al.'s (2014) results:
+Similarity of conditional AMCEs therefore only convey similarity of the \textit{causal effect} of the feature, but do not convey similarity of \textit{preferences} unless preferences toward profiles with the reference category are equivalent across groups.
+Given the reference category choice is typically arbitrary or driven by substantive knowledge of the levels, there is never any reason to expect that an arbitrarily selected reference category satisfies that equality assumption.
+When using a difference-in-AMCEs comparison to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.
 
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bms_difference_comparison-1} \caption[Estimated Preferences Difference between Inequity Averse and Non-Averse Respondents from Ballard-Rosa et al]{Estimated Preferences Difference between Inequity Averse and Non-Averse Respondents from Ballard-Rosa et al.
+(2016) Tax Preference Experiment}\label{fig:bms_difference_comparison}
+\end{figure}
 
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required namespace: ggstance}}\end{kframe}
-\includegraphics[width=\maxwidth]{figure/r_hainmueller_immigration-1}
+\end{knitrout}
+
+We can see this bias clearly in a reanalysis of \citeauthor{BallardRosaMartinScheve2016}'s tax preference experiment.
+Figure \ref{fig:bms_difference_comparison} shows an analysis for the feature capturing the tax rate for the highest earners (those over \$375,000 per year) replicating a portion of the results they present comparing inequity averse and non-averse respondents \citet[9 figure 2]{BallardRosaMartinScheve2016}.
+The original analysis was presented as conditional AMCEs for the two subgroups with inequity averse respondents having positive AMCEs for all tax levels (relative to 5\% as the reference category) and AMCEs for non-averse respondents being largely indistinguishable from zero.
+Figure \ref{fig:bms_difference_comparison} presents the implied difference-in-AMCEs from the original analysis as round black dots, demonstrating the substantial and positive \textit{apparent} differences between the two groups.
+The black diamonds show the true differences in marginal means between the two groups.
+The gray dots represent the alternative differences-in-AMCEs that could have been generated from alternative choices of reference category using the same data.
+Because respondents in the two groups actually have substantially different preferences over the reference category 5\% tax rate (inequity averse respondents are much less favorable toward this rate than non-averse respondents) differences-in-AMCEs make it seem like inequity averse respondents are much \textit{more} favorable toward 15\% and 25\% tax rates than non-averse respondents, when in actuality averse respondents are \textit{less} favorable toward the 15\% tax rate than non-averse respondents and the two groups have largely similar views of a 25\% tax rate.
+Not only does the difference-in-AMCEs overestimate group differences for very high tax rates (35\%, 45\%, 55\%) but the difference-in-AMCEs flips the true direction of group differences for lower rates.
+The authors correctly read their data as showing ``support for more progressive preferences is correlated with concern over societal inequality'' \citep[9]{BallardRosaMartinScheve2016} but for the wrong reason: inequity averse and non-averse respondents are similarly favorable toward middling tax rates and diverge in their views of very high and very low rates for high earners.
+
+It is worth highlighting two further features in Figure \ref{fig:bms_difference_comparison}.
+First, the alternative differences-in-AMCEs estimates vary mechanically around the difference in marginal means, as the reference category varies.
+The difference between marginal means for two groups are always fixed in the data, so the differencing of subgroup AMCEs is merely an exercise is centering those differences at arbitrary points along the range of observed differences in marginal means.
+Differences-in-AMCEs for a given feature level are therefore necessarily sometimes positive and sometimes negative, depending on the reference category used in estimating them.
+The direction of the difference per se conveys no information about underlying pattern of preferences in the two groups.
+Yet the choice of reference category --- likely unintentionally --- resulted in the most extreme, positive difference-in-AMCEs that could be estimated from the data but alternative reference categories could have conveyed different, equally incorrect insights.
+
+Second, and more practically, because there is no category for which the preferences of the two subgroups in this example are identical, no choice of reference category would have led to inferences from differences-in-AMCEs that accurately reflect the underlying difference in preferences.
+Even in the 25\% tax rate category, the difference between the two groups is slightly negative.
+Were there a category for which preferences were equivalent, that could be sensibly chosen as the reference category in order to be able to interpret differences-in-AMCEs as differences in preferences.
+There is never any guarantee, however, that such a reference category exists in any given experimental dataset.
+If multiple subgroup analyses are performed, it is unlikely the same reference category would work well across all analyses, making consistent interpretation difficult.
+As such, even if the AMCEs are similar, it does not necessarily mean that \textit{preferences} are similar; if AMCEs are dissimilar, it does not necessarily mean that preferences differ.
+
+Ultimately, it is important to note that because conjoint analysis generates a sparse feature matrix (where there is never any guarantee that a particular combination of feature levels is observed in the data), it is also not possible to empirically select an appropriate set of reference categories using the data.
+It is impossible to know which cell --- of the tens of thousands in the design --- is the best choice of reference.
+This is because while it might seem possible to select a \textit{marginally} appropriate reference category (i.e., one where preferences are similar with respect to a given feature), preferences toward that reference category may differ across other dimensions in the analysis.
+And it is furthermore possible that there is no such cell for which preferences are identical in the two groups; such a cell may exist, but there is no reason to expect that it should exist in any given application.
+Thus, there is no way to use conditional AMCEs or differences between those conditional AMCEs to convey the underlying similarity or differences in preferences across sample subgroups.
+
+\section*{Improved Analysis of Subgroup Preferences in Conjoint Designs}\label{sec:marginalmeans}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/hainmueller_subgroup_example_plot-1} \caption[Alternative Reference Categories for Features in Hainmueller et al]{Alternative Reference Categories for Features in Hainmueller et al.
+(2014) Immigration Experiment}\label{fig:hainmueller_subgroup_example_plot}
+\end{figure}
+
+\end{knitrout}
+
+We have shown that subgroup analyses of conjoint designs frequently entail the use of difference-in-AMCE comparisons and we have also shown that such analyses, counterintuitively, do not demonstrate differences in preferences between groups due the near-impossibility of selecting a non-arbitrary reference category against which to estimate AMCEs.
+Thus the choice of reference category --- while seemingly irrelevant --- has dramatic inferential consequences in conjoint analyses.
+Here we provide a more complete example, demonstrating the full extent of this problem for interpretation of conjoint results and present alternative forms of analysis that more robustly convey subgroup preferences and the differences (if any) between them.
+Consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which show the exact same analysis (comparing AMCEs for high and low ethnocentrism respondents) on the same experimental data from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment.
+In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in preferences between the two subgroups.
+In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.\footnote{The appendix contains comparable plots for experiments by \citet{BallardRosaMartinScheve2016} and \citet{TeeleKallaRosenbluth2018}.}
+
+Panel A gives the impression that there are significant differences in preferences between high and low ethnocentrism respondents toward immigrants from different countries of origin, with different careers, and with different educational attainments.
+By contrast, Panel B gives the impression that these differences --- indeed all differences --- are negligible.
+The experimental data and analytic approach in the two portrayals is identical; the only difference is the choice of reference category for the profile features.
+Given what we have shown about the relationship between differences in conditional AMCEs and differences in conditional marginal means, Panel B is the more truthful visualization \citep{Cairo2016}.
+The differences between subgroup AMCEs there more accurately convey differences in underlying preferences because the reference categories used in Panel B are the most similar between the two groups.
+Yet even this may not \textit{perfectly} convey differences because no feature generates perfect agreement between the subgroups.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/hainmueller_mm_by_ethnocentrism-1} \caption[Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment]{Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:hainmueller_mm_by_ethnocentrism}
+\end{figure}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/hainmueller_mm_diffs-1} \caption[Differences in Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment]{Differences in Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:hainmueller_mm_diffs}
+\end{figure}
+
+\end{knitrout}
+
+Alternatively presenting subgroup differences using conditional marginal means (as in Figure \ref{fig:hainmueller_mm_by_ethnocentrism}) provides the intended descriptive comparison of subgroup preferences.
+Each dot and error bar represents the conditional marginal mean (and its standard error) for high ethnocentrism (in red) and low ethnocentrism (in blue) respondents.
+This display of conditional marginal means highlights just how similar the preferences are for the two groups.
+For example, in the first set of estimates, both groups of respondents display minimally positive preferences toward female immigrants and minimally negative preferences toward male immigrants, averaging across those immigrants' other profile features.
+The second set of estimates shows both group are also more favorable toward higher-educated immigrants and less favorable toward less-education immigrants with no visually apparent differences.
+The third set of estimates, related to language skills, shows again similar patterns: both groups are more favorable toward immigrants with higher English proficiency than immigrants with lower English proficiency.
+
+These estimates are less obviously identical for the two groups but look quite close.
+To test for pairwise differences between high and low ethnocentrism respondents, we can calculate differences in conditional conditional marginal means at each feature level, with associated significance tests:
+
+\begin{itemize}
+\item spoke fluent English: 0.02 (0.02, $z_{\text{diff}}$=1.30, $p\leq 0.20$)
+\item spoke broken English: 0.01 (0.02, $z_{\text{diff}}$=0.71, $p\leq 0.48$)
+\item tried to speak English but was unable: -0.01 (0.02, $z_{\text{diff}}$=-0.78, $p\leq 0.43$)
+\item spoke [language] and used an interpreter: -0.02 (0.02, $z_{\text{diff}}$=-1.22, $p\leq 0.22$)
+
+\end{itemize}
+
+\noindent These pairwise tests show that are our eyes have not deceived us.
+None of the level-specific differences in conditional marginal means are statistically distinguishable from zero.
+Were we interested in an omnibus tests of whether any of these differences were non-zero, we could perform a nested model comparison of two equations: (a) one estimating only marginal effects of the ``Language Skills'' feature, and (b) the same model with additional interactions between the subgrouping covariate and the features.
+The resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: F(4)=1.06, $p\leq0.37$.
+We could repeat such pairwise comparisons or omnibus comparisons for each feature in the design.
+
+Furthermore, we could also directly visualize differences in conditional marginal means for this feature --- and all features --- as in Figure \ref{fig:hainmueller_mm_diffs}.
+This provides a more direct presentation of \textit{differences} between subgroup preferences as the vertical line indicates feature levels for which there is no difference between the two groups.
+Positive values to the right of the line indicate positive differences (high ethnocentrism respondents are more favorable toward immigrants with this feature than low ethnocentrism respondents) and negative value to the left of zero convey the opposite.
+A further advantage of this plot is that unlike displays of conditional AMCEs, differences in conditional marginal means communicate subgroup differences for all feature levels including the reference categories.
+This display makes readily clear what was only indirectly apparent in Figure \ref{fig:hainmueller_mm_by_ethnocentrism}: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.
+
+As before, we can perform an omnibus tests for the presence of any subgroup differences across all features, again using nested model comparison of two equations: (a) one estimating only effects of the features, and (b) the same model with additional interactions between the subgrouping covariate and all features.
+The result of that test for differences by ethnocentrism from the immigration experiment is: F(98)=1.16, $p\leq0.14$, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.
+This kind of test can also be used to assess heterogeneity across conjoint features.
+For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9).
+Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to an quite different conclusion.
+
+\section*{Conclusion}\label{sec:conclusion}
+
+This article has identified several challenges related to the analysis and reporting of conjoint experimental designs, particularly analyses of subgroup differences.
+We suggest that conjoint analyses should report not only average marginal component effects (AMCEs) but also descriptive quantities that better convey underlying preferences over profile features and better convey subgroup differences in those preferences.
+Our intention here is not to substantively undermine any previous set of results but instead to urge researchers moving forward to demonstrate considerable caution in how they design, analyze, and present the results of these types of experiments.
+We have relatively straightforward and hopefully uncontroversial advice for how analysts of conjoint experiments should proceed:
+
+\begin{enumerate}
+\item Always report unadjusted marginal means when attempting to provide a \textit{descriptive} summary of respondent preferences in addition to or instead of AMCEs.\footnote{Like the presentation of AMCEs, displaying marginal means in constrained conjoint designs may also distort apparent patterns given that not all features can co-occur.
+Partitioning the design into fractions such that each fraction contains a fully unconstrained design would mitigate any concern with that presentation.}
+
+\item Exercise extreme caution when explicitly or implicitly interpreting differences-in-AMCEs across subgroups.
+While that quantity conveys the difference in effects of a change in a given feature, heterogeneous effects do not necessarily mean different underlying preferences.
+Differences-in-AMCEs are almost always a biased estimate (of unknown sign and direction) of the difference in underlying preferences.
+If differences in AMCEs are reported, the choice of reference categories should be discussed explicitly and diagnostics should be provided to justify it.
+
+\item When descriptively characterizing differences in preferences between subgroups, directly estimate the subgroup difference using conditional marginal means and differences between conditional marginal means, rather than relying on difference-in-AMCEs.
+
+\item To formally test for group differences in preferences, regression with interaction terms between the subgrouping covariate and all feature levels will generate estimates of level-specific differences in preferences via the coefficients on the interaction terms.\footnote{The analysis is slightly more complicated in constrained designs.} A nested model comparison between this equation against one without such interactions provides an omnibus test of subgroup differences, which should be reported when characterizing overall patterns of subgroup differences.
+\end{enumerate}
+
+\noindent Following this advice, we hope, will allow researchers to more clearly and more accurately represent the results of conjoint experiments.
+
+The popularity of conjoint analyses in recent years highlights the power of the design and the important contributions made by \citet{HainmuellerHopkinsYamamoto2014} in providing a novel causal interpretation of these fully randomized factorial designs.
+Yet with new tools always come new challenges.
+The now-common practice of descriptively interpreting conjoints requires more caution than is immediately obvious.
+This paper has demonstrated several such challenges and hopefully provides useful advice for how researchers should proceed with the analysis of such designs.
+
+To facilitate such analysis and, especially, to provide easy-to-use tools for calculating marginal means and performing reference category selection diagnostics, we provide software called \textbf{cregg} \citep{Leeper2018cregg} that will perform these analyses and also provides the simple-to-use visualization tools used throughout this article.
+With that resource in-hand, researchers should be well-equipped to analyze conjoint designs without running into the analytic challenges discussed here.
+
+\singlespacing
+\bibliographystyle{apsa-leeper}
+\bibliography{references}
+\clearpage
+
+\appendix
+
+\section{Hainmueller et al. (2014) Immigration Experiment}
+
+\subsection{Replication using AMCEs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_amce_appendix-1}
 
@@
 
-\section{Arbitrary reference category choice}
+% latex table generated in R 3.5.1 by xtable 1.8-2 package
+% Wed Jul 11 09:37:48 2018
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lp{3in}rrr}
+  \hline
+feature & level & estimate & std.error & z \\ 
+  \hline
+Gender & female & 0.00 &  &  \\ 
+  Gender & male & -0.03 & 0.01 & -3.25 \\ 
+  Education & No formal education & 0.00 &  &  \\ 
+  Education & Equivalent to completing fourth grade & 0.03 & 0.01 & 2.22 \\ 
+  Education & Equivalent to completing eighth grade & 0.06 & 0.01 & 3.86 \\ 
+  Education & Equivalent to completing high school & 0.12 & 0.01 & 7.98 \\ 
+  Education & Equivalent to completing two years of college & 0.16 & 0.02 & 7.12 \\ 
+  Education & Equivalent to completing a college degree & 0.19 & 0.02 & 8.26 \\ 
+  Education & Equivalent to completing a graduate degree & 0.18 & 0.02 & 10.41 \\ 
+  Language Skills & spoke fluent English & 0.00 &  &  \\ 
+  Language Skills & spoke broken English & -0.06 & 0.01 & -4.98 \\ 
+  Language Skills & tried to speak English but was unable & -0.13 & 0.01 & -11.11 \\ 
+  Language Skills & spoke [language] and used an interpreter & -0.16 & 0.01 & -13.78 \\ 
+  Country of Origin & India & 0.00 &  &  \\ 
+  Country of Origin & Germany & 0.05 & 0.02 & 2.66 \\ 
+  Country of Origin & France & 0.03 & 0.02 & 1.53 \\ 
+  Country of Origin & Mexico & 0.01 & 0.02 & 0.59 \\ 
+  Country of Origin & Philippines & 0.03 & 0.02 & 1.91 \\ 
+  Country of Origin & Poland & 0.03 & 0.02 & 1.83 \\ 
+  Country of Origin & China & -0.02 & 0.02 & -0.81 \\ 
+  Country of Origin & Sudan & -0.04 & 0.02 & -2.01 \\ 
+  Country of Origin & Somalia & -0.05 & 0.02 & -2.29 \\ 
+  Country of Origin & Iraq & -0.11 & 0.02 & -5.56 \\ 
+  Job & Janitor & 0.00 &  &  \\ 
+  Job & Waiter & -0.01 & 0.02 & -0.41 \\ 
+  Job & Child care provider & 0.01 & 0.02 & 0.89 \\ 
+  Job & Gardener & 0.01 & 0.02 & 0.78 \\ 
+  Job & Financial analyst & 0.06 & 0.03 & 2.17 \\ 
+  Job & Construction worker & 0.04 & 0.02 & 2.26 \\ 
+  Job & Teacher & 0.07 & 0.02 & 4.39 \\ 
+  Job & Computer programmer & 0.08 & 0.03 & 2.76 \\ 
+  Job & Nurse & 0.08 & 0.02 & 5.08 \\ 
+  Job & Research scientist & 0.13 & 0.03 & 4.44 \\ 
+  Job & Doctor & 0.16 & 0.03 & 5.49 \\ 
+  Job Experience & No job training or prior experience & 0.00 &  &  \\ 
+  Job Experience & One or two years of job training and experience & 0.07 & 0.01 & 5.92 \\ 
+  Job Experience & Three to five years of job training and experience & 0.11 & 0.01 & 9.32 \\ 
+  Job Experience & More than five years of job training and experience & 0.11 & 0.01 & 9.96 \\ 
+  Job Plans & Has a contract with a U.S. employer & 0.00 &  &  \\ 
+  Job Plans & Does not have a contract with a U.S. employer & -0.10 & 0.01 & -8.50 \\ 
+  Job Plans & Will look for work after arriving in the U.S. & -0.12 & 0.01 & -10.69 \\ 
+  Job Plans & Has no plans to look for work at this time & -0.28 & 0.01 & -23.91 \\ 
+  Reason for Application & Reunite with family members already in the U.S. & 0.00 &  &  \\ 
+  Reason for Application & Seek better job in U.S. & -0.04 & 0.01 & -4.37 \\ 
+  Reason for Application & Escape political/religious persecution & 0.06 & 0.02 & 3.58 \\ 
+  Prior Entry & Never been to the U.S. & 0.00 &  &  \\ 
+  Prior Entry & Entered U.S. once before on a tourist visa & 0.06 & 0.01 & 4.49 \\ 
+  Prior Entry & Has visited the U.S. many times before on tourist visas & 0.05 & 0.01 & 4.24 \\ 
+  Prior Entry & Spent six months with family members in the U.S & 0.08 & 0.01 & 5.98 \\ 
+  Prior Entry & Entered the U.S. once before without legal authorization & -0.11 & 0.01 & -8.45 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\end{table}
+
+\clearpage
+
+\subsection{Replication using MMs}
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/r_reference_category-1}
-
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/r_marginal_means-1}
+\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_mm_appendix-1}
 
@@
 
-\section{Subgroup Analysis}
+% latex table generated in R 3.5.1 by xtable 1.8-2 package
+% Wed Jul 11 09:37:55 2018
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lp{3in}rrr}
+  \hline
+feature & level & estimate & std.error & z \\ 
+  \hline
+Gender & female & 0.51 & 0.01 & 1.99 \\ 
+  Gender & male & 0.49 & 0.01 & -2.03 \\ 
+  Education & No formal education & 0.39 & 0.01 & -10.04 \\ 
+  Education & Equivalent to completing fourth grade & 0.42 & 0.01 & -7.08 \\ 
+  Education & Equivalent to completing eighth grade & 0.44 & 0.01 & -5.00 \\ 
+  Education & Equivalent to completing high school & 0.51 & 0.01 & 0.67 \\ 
+  Education & Equivalent to completing two years of college & 0.57 & 0.01 & 5.92 \\ 
+  Education & Equivalent to completing a college degree & 0.59 & 0.01 & 8.00 \\ 
+  Education & Equivalent to completing a graduate degree & 0.58 & 0.01 & 7.40 \\ 
+  Language Skills & spoke fluent English & 0.59 & 0.01 & 10.63 \\ 
+  Language Skills & spoke broken English & 0.53 & 0.01 & 3.07 \\ 
+  Language Skills & tried to speak English but was unable & 0.46 & 0.01 & -4.83 \\ 
+  Language Skills & spoke [language] and used an interpreter & 0.42 & 0.01 & -8.98 \\ 
+  Country of Origin & India & 0.50 & 0.01 & 0.13 \\ 
+  Country of Origin & Germany & 0.54 & 0.01 & 3.22 \\ 
+  Country of Origin & France & 0.52 & 0.01 & 1.26 \\ 
+  Country of Origin & Mexico & 0.51 & 0.01 & 0.92 \\ 
+  Country of Origin & Philippines & 0.53 & 0.01 & 2.36 \\ 
+  Country of Origin & Poland & 0.53 & 0.01 & 2.01 \\ 
+  Country of Origin & China & 0.50 & 0.01 & -0.03 \\ 
+  Country of Origin & Sudan & 0.48 & 0.01 & -1.42 \\ 
+  Country of Origin & Somalia & 0.47 & 0.01 & -2.01 \\ 
+  Country of Origin & Iraq & 0.41 & 0.01 & -6.76 \\ 
+  Job & Janitor & 0.45 & 0.01 & -4.20 \\ 
+  Job & Waiter & 0.45 & 0.01 & -4.56 \\ 
+  Job & Child care provider & 0.46 & 0.01 & -3.50 \\ 
+  Job & Gardener & 0.46 & 0.01 & -3.11 \\ 
+  Job & Financial analyst & 0.57 & 0.02 & 3.16 \\ 
+  Job & Construction worker & 0.48 & 0.01 & -1.23 \\ 
+  Job & Teacher & 0.52 & 0.01 & 1.49 \\ 
+  Job & Computer programmer & 0.58 & 0.02 & 4.01 \\ 
+  Job & Nurse & 0.53 & 0.01 & 2.82 \\ 
+  Job & Research scientist & 0.64 & 0.02 & 6.82 \\ 
+  Job & Doctor & 0.67 & 0.02 & 8.53 \\ 
+  Job Experience & No job training or prior experience & 0.43 & 0.01 & -8.27 \\ 
+  Job Experience & One or two years of job training and experience & 0.49 & 0.01 & -1.05 \\ 
+  Job Experience & Three to five years of job training and experience & 0.54 & 0.01 & 4.33 \\ 
+  Job Experience & More than five years of job training and experience & 0.54 & 0.01 & 4.92 \\ 
+  Job Plans & Has a contract with a U.S. employer & 0.63 & 0.01 & 15.40 \\ 
+  Job Plans & Does not have a contract with a U.S. employer & 0.53 & 0.01 & 3.47 \\ 
+  Job Plans & Will look for work after arriving in the U.S. & 0.51 & 0.01 & 0.78 \\ 
+  Job Plans & Has no plans to look for work at this time & 0.34 & 0.01 & -19.86 \\ 
+  Reason for Application & Reunite with family members already in the U.S. & 0.52 & 0.01 & 3.00 \\ 
+  Reason for Application & Seek better job in U.S. & 0.48 & 0.01 & -3.76 \\ 
+  Reason for Application & Escape political/religious persecution & 0.52 & 0.01 & 1.40 \\ 
+  Prior Entry & Never been to the U.S. & 0.49 & 0.01 & -1.47 \\ 
+  Prior Entry & Entered U.S. once before on a tourist visa & 0.54 & 0.01 & 4.37 \\ 
+  Prior Entry & Has visited the U.S. many times before on tourist visas & 0.54 & 0.01 & 4.50 \\ 
+  Prior Entry & Spent six months with family members in the U.S & 0.56 & 0.01 & 6.24 \\ 
+  Prior Entry & Entered the U.S. once before without legal authorization & 0.37 & 0.01 & -13.96 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\end{table}
 
-A conventional presentation of subgroup analyses in a conjoint design is as follows.
-Note how the conditional AMCEs for several levels - Somalia, Sudan, China, Mexico, and France - flip signs.
-Yet the largest differences in preferences between the two groups are for Germany, France, Poland, and Somalia.
-Apparently similar patterns of AMCE mask where and in what direction preferences for the two subgroups differ.
+\clearpage
+
+\subsection{Subgroup Analysis for Hainmueller et al. (2014) Immigration Experiment using AMCEs}
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/r_subgroup_results_amce-1}
+\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_subgroup_amce_appendix-1}
 
@@
 
+\clearpage
+
+\subsection{Subgroup Analysis for Hainmueller et al. (2014) Immigration Experiment using MMs}
+
 \begin{knitrout}
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/r_subgroup_marginal_means-1}
+\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_subgroup_mm_appendix-1}
 
@@
 
-As we can see, however, while the difference in marginal means conveys the fixed difference in preferences between the two groups, the apparent difference in preferences between groups conveyed by a difference-in-AMCEs is sensitive to the reference category chosen when estimating the effects:
+\clearpage
+
+\section{Hainmueller et al. (2014) Candidate Experiment}
+
+\subsection{Replication using AMCEs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_amce_appendix-1}
+
+\end{knitrout}
 
@@
 
+% latex table generated in R 3.5.1 by xtable 1.8-2 package
+% Wed Jul 11 09:38:07 2018
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lp{3in}rrr}
+  \hline
+feature & level & estimate & std.error & z \\ 
+  \hline
+Military Service & Did Not Serve & 0.00 &  &  \\ 
+  Military Service & Served & 0.09 & 0.02 & 4.95 \\ 
+  Religion & None & 0.00 &  &  \\ 
+  Religion & Jewish & -0.04 & 0.03 & -1.42 \\ 
+  Religion & Catholic & -0.02 & 0.03 & -0.56 \\ 
+  Religion & Mainline protestant & -0.01 & 0.03 & -0.48 \\ 
+  Religion & Evangelical protestant & -0.12 & 0.03 & -3.78 \\ 
+  Religion & Mormon & -0.14 & 0.03 & -4.46 \\ 
+  College & No BA & 0.00 &  &  \\ 
+  College & Baptist college & 0.14 & 0.03 & 4.82 \\ 
+  College & Community college & 0.15 & 0.03 & 5.17 \\ 
+  College & State university & 0.19 & 0.03 & 6.77 \\ 
+  College & Small college & 0.18 & 0.03 & 6.50 \\ 
+  College & Ivy League university & 0.27 & 0.03 & 9.26 \\ 
+  Profession & Business owner & 0.00 &  &  \\ 
+  Profession & Lawyer & -0.02 & 0.03 & -0.71 \\ 
+  Profession & Doctor & -0.02 & 0.03 & -0.53 \\ 
+  Profession & High school teacher & -0.04 & 0.03 & -1.42 \\ 
+  Profession & Farmer & -0.09 & 0.03 & -2.94 \\ 
+  Profession & Car dealer & -0.23 & 0.03 & -7.24 \\ 
+  Income & 32K & 0.00 &  &  \\ 
+  Income & 54K & 0.02 & 0.03 & 0.82 \\ 
+  Income & 65K & 0.06 & 0.03 & 2.26 \\ 
+  Income & 92K & 0.03 & 0.03 & 1.12 \\ 
+  Income & 210K & 0.07 & 0.03 & 2.41 \\ 
+  Income & 5.1M & 0.01 & 0.03 & 0.25 \\ 
+  Race/Ethnicity & White & 0.00 &  &  \\ 
+  Race/Ethnicity & Native American & 0.02 & 0.03 & 0.85 \\ 
+  Race/Ethnicity & Black & 0.03 & 0.03 & 1.22 \\ 
+  Race/Ethnicity & Hispanic & -0.02 & 0.03 & -0.84 \\ 
+  Race/Ethnicity & Caucasian & 0.00 & 0.03 & 0.18 \\ 
+  Race/Ethnicity & Asian American & 0.04 & 0.03 & 1.51 \\ 
+  Age & 36 & 0.00 &  &  \\ 
+  Age & 45 & 0.03 & 0.03 & 0.88 \\ 
+  Age & 52 & 0.02 & 0.03 & 0.78 \\ 
+  Age & 60 & 0.00 & 0.03 & 0.14 \\ 
+  Age & 68 & -0.06 & 0.03 & -2.17 \\ 
+  Age & 75 & -0.15 & 0.03 & -5.06 \\ 
+  Gender & Male & 0.00 &  &  \\ 
+  Gender & Female & 0.00 & 0.02 & 0.09 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\end{table}
+
+\clearpage
+
+\subsection{Replication using MMs}
+
 \begin{knitrout}
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/r_subgroup_results_mm-1}
+\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_mm_appendix-1}
 
@@
 
-Indeed, the difference in AMCEs most closely approximates the difference in marginal means (and thus the descriptive difference in preferences) when the true difference in preferences in the reference category is close to zero.
-For example, in the above figure differences in AMCEs are shown in gray and differences in marginal means are shown in red, for respondents scoring above-median (high) and below-median (low) in ethnocentrism for each possible country of origin in Hainmueller et al.'s (2014) immigration experiment.
-The difference in marginal means between high and low ethnocentrism respondents is smallest for immigrants arriving from Iraq.
-When Iraq is used as the reference category, the AMCE of Iraq is fixed at zero and the between-group difference in AMCEs is thus, by definition, also fixed at zero.
-These estimates are shown at the top of each grouping - as should be readily clear, when Iraq is used as the reference category, the difference in AMCEs for each of the other possible origin countries closely approximates (but does not exactly equal) the difference in marginal means for that origin country.
-Were there no feature level for which the two groups held similar preferences, then there would be no reference category that would generate differences in AMCES that were close to the difference in underlying marginal means.
-
-When other origin countries are used as the reference category (wherein the underlying difference in preferences between high ethnocentrism and low enthnocentrism respondents is greater), then the difference in AMCEs provides biased estimates of the difference in preferences.
-Take, for example, the difference in preferences over immigrants from China, where high ethnocentrism respondents are less favourable to these immigrants than low ethnocentrism respondents.
-The difference in marginal means is -0.033.
-Yet differences in AMCEs for Chinese immigrants vary substantially depending on which other category is chosen as the baseline.
-If China is the baseline, the apparent difference in preferences is zero (definitionally).
-While in most cases the difference in AMCEs takes the same sign as the difference in marginal means, when either Mexico or Sudan is used as the reference category the apparent difference in preferences flips signs: high ethnocentrism respondents appear to be more rather than less favorable toward Chinese immigrants when the AMCEs are estimated in that way.
-
-Yet the graph also makes clear that the differences in AMCEs all center upon the true difference in marginal means in a fixed manner.
-
-Thus the choice of reference category - while seemingly irrelevant - has dramatic inferential consequences.
-
-\section{Suggested Approaches}
-
-% Present marginal means overall and for specific subgroups of interest
-
-\section{Conclusion}
-
-This paper has several identified challenges related to the analysis and reporting of conjoint experimental designs, particularly analyses of subgroup differences.
-It suggests that authors should report not only average marginal component effects (AMCEs) but also descriptive quantities that better convey subgroup differences.
-
-\singlespacing
-\bibliographystyle{apsa-leeper}
-\bibliography{References}
 \clearpage
 
+% latex table generated in R 3.5.1 by xtable 1.8-2 package
+% Wed Jul 11 09:38:11 2018
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lp{3in}rrr}
+  \hline
+feature & level & estimate & std.error & z \\ 
+  \hline
+Military Service & Did Not Serve & 0.46 & 0.01 & -3.54 \\ 
+  Military Service & Served & 0.54 & 0.01 & 3.55 \\ 
+  Religion & None & 0.56 & 0.02 & 2.73 \\ 
+  Religion & Jewish & 0.52 & 0.02 & 0.96 \\ 
+  Religion & Catholic & 0.53 & 0.02 & 1.24 \\ 
+  Religion & Mainline protestant & 0.54 & 0.02 & 2.06 \\ 
+  Religion & Evangelical protestant & 0.44 & 0.02 & -3.05 \\ 
+  Religion & Mormon & 0.42 & 0.02 & -4.04 \\ 
+  College & No BA & 0.34 & 0.02 & -8.11 \\ 
+  College & Baptist college & 0.48 & 0.02 & -0.83 \\ 
+  College & Community college & 0.49 & 0.02 & -0.39 \\ 
+  College & State university & 0.53 & 0.02 & 1.39 \\ 
+  College & Small college & 0.52 & 0.02 & 0.99 \\ 
+  College & Ivy League university & 0.62 & 0.02 & 6.27 \\ 
+  Profession & Business owner & 0.57 & 0.02 & 3.35 \\ 
+  Profession & Lawyer & 0.55 & 0.02 & 2.20 \\ 
+  Profession & Doctor & 0.54 & 0.02 & 2.08 \\ 
+  Profession & High school teacher & 0.53 & 0.02 & 1.44 \\ 
+  Profession & Farmer & 0.48 & 0.02 & -0.98 \\ 
+  Profession & Car dealer & 0.33 & 0.02 & -8.64 \\ 
+  Income & 32K & 0.46 & 0.02 & -1.89 \\ 
+  Income & 54K & 0.49 & 0.02 & -0.65 \\ 
+  Income & 65K & 0.53 & 0.02 & 1.33 \\ 
+  Income & 92K & 0.51 & 0.02 & 0.46 \\ 
+  Income & 210K & 0.54 & 0.02 & 1.94 \\ 
+  Income & 5.1M & 0.47 & 0.02 & -1.26 \\ 
+  Race/Ethnicity & White & 0.48 & 0.02 & -0.88 \\ 
+  Race/Ethnicity & Native American & 0.52 & 0.02 & 0.96 \\ 
+  Race/Ethnicity & Black & 0.52 & 0.02 & 0.85 \\ 
+  Race/Ethnicity & Hispanic & 0.47 & 0.02 & -1.59 \\ 
+  Race/Ethnicity & Caucasian & 0.49 & 0.02 & -0.53 \\ 
+  Race/Ethnicity & Asian American & 0.52 & 0.02 & 1.14 \\ 
+  Age & 36 & 0.53 & 0.02 & 1.43 \\ 
+  Age & 45 & 0.55 & 0.02 & 2.21 \\ 
+  Age & 52 & 0.56 & 0.02 & 3.18 \\ 
+  Age & 60 & 0.53 & 0.02 & 1.40 \\ 
+  Age & 68 & 0.45 & 0.02 & -2.31 \\ 
+  Age & 75 & 0.38 & 0.02 & -5.99 \\ 
+  Gender & Male & 0.50 & 0.01 & -0.07 \\ 
+  Gender & Female & 0.50 & 0.01 & 0.07 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\end{table}
+
+\clearpage
+
+\section{Ballard-Rosa et al. (2016) Tax Preference Experiment}
+
+\subsection{Replication using AMCEs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bms_amce_appendix-1}
+
+\end{knitrout}
+
+\clearpage
+
+% latex table generated in R 3.5.1 by xtable 1.8-2 package
+% Wed Jul 11 10:11:31 2018
+\begin{table}[ht]
+\centering
+\begin{tabular}{lp{1.5in}rrr}
+  \hline
+feature & level & estimate & std.error & z \\ 
+  \hline
+Tax rate for $<$\$10,000 & $<$10k: 0\% & 0.00 &  &  \\ 
+  Tax rate for $<$\$10,000 & $<$10k: 5\% & -0.02 & 0.01 & -3.81 \\ 
+  Tax rate for $<$\$10,000 & $<$10k: 15\% & -0.11 & 0.01 & -15.97 \\ 
+  Tax rate for $<$\$10,000 & $<$10k: 25\% & -0.24 & 0.01 & -28.33 \\ 
+  Tax rate for \$10,000-\$35,000 & 10-35k: 5\% & 0.00 &  &  \\ 
+  Tax rate for \$10,000-\$35,000 & 10-35k: 15\% & -0.02 & 0.01 & -2.94 \\ 
+  Tax rate for \$10,000-\$35,000 & 10-35k: 25\% & -0.10 & 0.01 & -9.42 \\ 
+  Tax rate for \$10,000-\$35,000 & 10-35k: 35\% & -0.22 & 0.01 & -15.96 \\ 
+  Tax rate for \$25,000-\$85,000 & 35-85k: 5\% & 0.00 &  &  \\ 
+  Tax rate for \$25,000-\$85,000 & 35-85k: 15\% & 0.00 & 0.01 & 0.03 \\ 
+  Tax rate for \$25,000-\$85,000 & 35-85k: 25\% & -0.07 & 0.01 & -9.18 \\ 
+  Tax rate for \$25,000-\$85,000 & 35-85k: 35\% & -0.13 & 0.01 & -14.55 \\ 
+  Tax rate for \$85,000-\$175,000 & 85-175k: 5\% & 0.00 &  &  \\ 
+  Tax rate for \$85,000-\$175,000 & 85-175k: 15\% & 0.01 & 0.01 & 2.06 \\ 
+  Tax rate for \$85,000-\$175,000 & 85-175k: 25\% & -0.02 & 0.01 & -2.80 \\ 
+  Tax rate for \$85,000-\$175,000 & 85-175k: 35\% & -0.01 & 0.01 & -2.19 \\ 
+  Tax rate for \$175,000-\$375,000 & 175-375k: 5\% & 0.00 &  &  \\ 
+  Tax rate for \$175,000-\$375,000 & 175-375k: 15\% & 0.03 & 0.01 & 5.97 \\ 
+  Tax rate for \$175,000-\$375,000 & 175-375k: 25\% & 0.04 & 0.01 & 6.53 \\ 
+  Tax rate for \$175,000-\$375,000 & 175-375k: 35\% & 0.06 & 0.01 & 9.77 \\ 
+  Tax rate for \$175,000-\$375,000 & 175-375k: 45\% & 0.03 & 0.01 & 4.80 \\ 
+  Tax rate for $>$\$375,000 & $>$375k: 5\% & 0.00 &  &  \\ 
+  Tax rate for $>$\$375,000 & $>$375k: 15\% & 0.06 & 0.01 & 8.22 \\ 
+  Tax rate for $>$\$375,000 & $>$375k: 25\% & 0.09 & 0.01 & 12.18 \\ 
+  Tax rate for $>$\$375,000 & $>$375k: 35\% & 0.11 & 0.01 & 15.44 \\ 
+  Tax rate for $>$\$375,000 & $>$375k: 45\% & 0.11 & 0.01 & 13.23 \\ 
+  Tax rate for $>$\$375,000 & $>$375k: 55\% & 0.08 & 0.01 & 9.55 \\ 
+  Tax revenue & $<$75\% & 0.00 &  &  \\ 
+  Tax revenue & 75-95\% & 0.03 & 0.01 & 3.56 \\ 
+  Tax revenue & 95-105\% & 0.07 & 0.01 & 6.11 \\ 
+  Tax revenue & 105-125\% & 0.09 & 0.01 & 6.33 \\ 
+  Tax revenue & $>$125\% & 0.14 & 0.02 & 7.22 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\clearpage
+
+\subsection{Replication using MMs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bms_mm_appendix-1}
+
+\end{knitrout}
+
+\clearpage
+
+% latex table generated in R 3.5.1 by xtable 1.8-2 package
+% Wed Jul 11 10:11:43 2018
+\begin{table}[ht]
+\centering
+\begin{tabular}{lp{1.5in}rrr}
+  \hline
+feature & level & estimate & std.error & z \\ 
+  \hline
+Tax rate for $<$\$10,000 & $<$10k: 0\% & 0.57 & 0.01 & 9.37 \\ 
+  Tax rate for $<$\$10,000 & $<$10k: 5\% & 0.56 & 0.01 & 8.06 \\ 
+  Tax rate for $<$\$10,000 & $<$10k: 15\% & 0.49 & 0.01 & -1.11 \\ 
+  Tax rate for $<$\$10,000 & $<$10k: 25\% & 0.37 & 0.01 & -16.07 \\ 
+  Tax rate for \$10,000-\$35,000 & 10-35k: 5\% & 0.54 & 0.01 & 4.75 \\ 
+  Tax rate for \$10,000-\$35,000 & 10-35k: 15\% & 0.54 & 0.01 & 5.55 \\ 
+  Tax rate for \$10,000-\$35,000 & 10-35k: 25\% & 0.50 & 0.01 & 0.39 \\ 
+  Tax rate for \$10,000-\$35,000 & 10-35k: 35\% & 0.42 & 0.01 & -10.62 \\ 
+  Tax rate for \$25,000-\$85,000 & 35-85k: 5\% & 0.53 & 0.01 & 3.45 \\ 
+  Tax rate for \$25,000-\$85,000 & 35-85k: 15\% & 0.54 & 0.01 & 5.37 \\ 
+  Tax rate for \$25,000-\$85,000 & 35-85k: 25\% & 0.49 & 0.01 & -1.27 \\ 
+  Tax rate for \$25,000-\$85,000 & 35-85k: 35\% & 0.44 & 0.01 & -7.50 \\ 
+  Tax rate for \$85,000-\$175,000 & 85-175k: 5\% & 0.50 & 0.01 & 0.00 \\ 
+  Tax rate for \$85,000-\$175,000 & 85-175k: 15\% & 0.51 & 0.01 & 1.42 \\ 
+  Tax rate for \$85,000-\$175,000 & 85-175k: 25\% & 0.49 & 0.01 & -1.00 \\ 
+  Tax rate for \$85,000-\$175,000 & 85-175k: 35\% & 0.50 & 0.01 & -0.46 \\ 
+  Tax rate for \$175,000-\$375,000 & 175-375k: 5\% & 0.46 & 0.01 & -4.37 \\ 
+  Tax rate for \$175,000-\$375,000 & 175-375k: 15\% & 0.50 & 0.01 & -0.47 \\ 
+  Tax rate for \$175,000-\$375,000 & 175-375k: 25\% & 0.51 & 0.01 & 0.84 \\ 
+  Tax rate for \$175,000-\$375,000 & 175-375k: 35\% & 0.53 & 0.01 & 3.11 \\ 
+  Tax rate for \$175,000-\$375,000 & 175-375k: 45\% & 0.51 & 0.01 & 0.80 \\ 
+  Tax rate for $>$\$375,000 & $>$375k: 5\% & 0.41 & 0.01 & -9.57 \\ 
+  Tax rate for $>$\$375,000 & $>$375k: 15\% & 0.47 & 0.01 & -3.30 \\ 
+  Tax rate for $>$\$375,000 & $>$375k: 25\% & 0.51 & 0.01 & 0.97 \\ 
+  Tax rate for $>$\$375,000 & $>$375k: 35\% & 0.54 & 0.01 & 4.48 \\ 
+  Tax rate for $>$\$375,000 & $>$375k: 45\% & 0.55 & 0.01 & 4.75 \\ 
+  Tax rate for $>$\$375,000 & $>$375k: 55\% & 0.53 & 0.01 & 3.12 \\ 
+  Tax revenue & $<$75\% & 0.57 & 0.01 & 8.22 \\ 
+  Tax revenue & 75-95\% & 0.53 & 0.01 & 3.47 \\ 
+  Tax revenue & 95-105\% & 0.51 & 0.01 & 1.18 \\ 
+  Tax revenue & 105-125\% & 0.48 & 0.01 & -2.21 \\ 
+  Tax revenue & $>$125\% & 0.41 & 0.01 & -10.54 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\clearpage
+
+\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by ``Taxes Harm Economy'' Split using AMCEs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bms_subgroup_amce_appendix1-1}
+
+\end{knitrout}
+
+\clearpage
+
+\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by ``Taxes Harm Economy'' Split using MMs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bms_subgroup_mm_appendix1-1}
+
+\end{knitrout}
+
+\clearpage
+
+\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by Inequity Aversion using AMCEs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bms_subgroup_amce_appendix2-1}
+
+\end{knitrout}
+
+\clearpage
+
+\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by Inequity Aversion using MMs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bms_subgroup_mm_appendix2-1}
+
+\end{knitrout}
+
+\clearpage
+
+\subsection{Comparison of Alternative Reference Categories for Ballard-Rosa et al. (2016) Tax Preference Experiment, by ``Taxes Harm Economy'' Split}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bms_subgroup_example_plot1-1}
+
+\end{knitrout}
+
+\clearpage
+
+\subsection{Comparison of Alternative Reference Categories for Ballard-Rosa et al. (2016) Tax Preference Experiment, by Inequity Aversion}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bms_subgroup_example_plot2-1}
+
+\end{knitrout}
+
+\clearpage
+
+\section{Teele et al. (2018) Candidate Experiment}
+
+\subsection{Replication using AMCEs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/tkr_amce_appendix-1}
+
+\end{knitrout}
+
+\clearpage
+
+% latex table generated in R 3.5.1 by xtable 1.8-2 package
+% Wed Jul 11 10:12:23 2018
+\begin{table}[ht]
+\centering
+\begin{tabular}{lp{1.5in}rrr}
+  \hline
+feature & level & estimate & std.error & z \\ 
+  \hline
+Candidate Sex & Male & 0.00 &  &  \\ 
+  Candidate Sex & Female & 0.04 & 0.01 & 4.74 \\ 
+  Political Experience & None & 0.00 &  &  \\ 
+  Political Experience & 1 year & 0.05 & 0.01 & 4.06 \\ 
+  Political Experience & 3 years & 0.11 & 0.01 & 8.47 \\ 
+  Political Experience & 8 years & 0.15 & 0.01 & 10.83 \\ 
+  Martial Status & Unmarried & 0.00 &  &  \\ 
+  Martial Status & Doctor Spouse & 0.08 & 0.01 & 7.25 \\ 
+  Martial Status & Farmer Spouse & 0.06 & 0.01 & 5.26 \\ 
+  Job & Teacher & 0.00 &  &  \\ 
+  Job & Corporate Lawyer & -0.07 & 0.01 & -5.29 \\ 
+  Job & Mayor & 0.05 & 0.01 & 3.74 \\ 
+  Job & State Legislator & 0.05 & 0.01 & 3.59 \\ 
+  Children & No children & 0.00 &  &  \\ 
+  Children & 1 child & 0.05 & 0.01 & 4.84 \\ 
+  Children & 3 children & 0.05 & 0.01 & 4.77 \\ 
+  Age & 29 & 0.00 &  &  \\ 
+  Age & 45 & 0.08 & 0.01 & 7.07 \\ 
+  Age & 65 & -0.01 & 0.01 & -1.24 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\clearpage
+
+\subsection{Replication using MMs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/tkr_mm_appendix-1}
+
+\end{knitrout}
+
+\clearpage
+
+% latex table generated in R 3.5.1 by xtable 1.8-2 package
+% Wed Jul 11 10:12:27 2018
+\begin{table}[ht]
+\centering
+\begin{tabular}{lp{1.5in}rrr}
+  \hline
+feature & level & estimate & std.error & z \\ 
+  \hline
+Candidate Sex & Male & 0.48 & 0.01 & -3.22 \\ 
+  Candidate Sex & Female & 0.52 & 0.01 & 3.20 \\ 
+  Political Experience & None & 0.42 & 0.01 & -8.81 \\ 
+  Political Experience & 1 year & 0.48 & 0.01 & -2.56 \\ 
+  Political Experience & 3 years & 0.53 & 0.01 & 3.58 \\ 
+  Political Experience & 8 years & 0.57 & 0.01 & 7.99 \\ 
+  Martial Status & Unmarried & 0.45 & 0.01 & -6.05 \\ 
+  Martial Status & Doctor Spouse & 0.54 & 0.01 & 4.66 \\ 
+  Martial Status & Farmer Spouse & 0.51 & 0.01 & 1.37 \\ 
+  Job & Teacher & 0.49 & 0.01 & -1.01 \\ 
+  Job & Corporate Lawyer & 0.42 & 0.01 & -8.44 \\ 
+  Job & Mayor & 0.54 & 0.01 & 4.77 \\ 
+  Job & State Legislator & 0.54 & 0.01 & 4.55 \\ 
+  Children & No children & 0.47 & 0.01 & -4.47 \\ 
+  Children & 1 child & 0.52 & 0.01 & 2.07 \\ 
+  Children & 3 children & 0.52 & 0.01 & 2.34 \\ 
+  Age & 29 & 0.48 & 0.01 & -2.65 \\ 
+  Age & 45 & 0.56 & 0.01 & 7.28 \\ 
+  Age & 65 & 0.46 & 0.01 & -4.66 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\clearpage
+
+\subsection{Subgroup Analysis for Teele et al. (2018) Candidate Experiment using AMCEs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/tkr_subgroup_amce_appendix-1}
+
+\end{knitrout}
+
+\subsection{Subgroup Analysis for Teele et al. (2018) Candidate Experiment using MMs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/tkr_subgroup_mm_appendix-1}
+
+\end{knitrout}
+
+\clearpage
+
+\subsection{Comparison of Alternative Reference Categories for Teele et al. (2018) Candidate Experiment}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/tkr_subgroup_example_plot-1}
+
+\end{knitrout}
+
+\clearpage
+
+\section*{}
+
+\noindent This paper was built using \texttt{knitr::knit2pdf()} under the following environment:
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## R version 3.5.1 (2018-07-02)
+## Platform: x86_64-w64-mingw32/x64 (64-bit)
+## Running under: Windows 7 x64 (build 7601) Service Pack 1
+## 
+## Matrix products: default
+## 
+## locale:
+## [1] LC_COLLATE=English_United Kingdom.1252 
+## [2] LC_CTYPE=English_United Kingdom.1252   
+## [3] LC_MONETARY=English_United Kingdom.1252
+## [4] LC_NUMERIC=C                           
+## [5] LC_TIME=English_United Kingdom.1252    
+## 
+## attached base packages:
+## [1] stats     graphics  grDevices utils     datasets  methods   base     
+## 
+## other attached packages:
+## [1] ggplot2_3.0.0 cregg_0.2.3   rio_0.5.11   
+## 
+## loaded via a namespace (and not attached):
+##  [1] zip_1.0.0         Rcpp_0.12.17      cellranger_1.1.0 
+##  [4] pillar_1.2.3      compiler_3.5.1    plyr_1.8.4       
+##  [7] bindr_0.1.1       forcats_0.3.0     tools_3.5.1      
+## [10] digest_0.6.15     lattice_0.20-35   ggstance_0.3     
+## [13] evaluate_0.10.1   tibble_1.4.2      gtable_0.2.0     
+## [16] pkgconfig_2.0.1   rlang_0.2.1       Matrix_1.2-14    
+## [19] openxlsx_4.1.0    curl_3.2          haven_1.1.2      
+## [22] bindrcpp_0.2.2    withr_2.1.2       stringr_1.3.1    
+## [25] dplyr_0.7.6       knitr_1.20        hms_0.4.2        
+## [28] lmtest_0.9-36     grid_3.5.1        tidyselect_0.2.4 
+## [31] glue_1.2.0        data.table_1.11.4 R6_2.2.2         
+## [34] survival_2.42-4   readxl_1.1.0      foreign_0.8-70   
+## [37] reshape2_1.4.3    readr_1.1.1       purrr_0.2.5      
+## [40] magrittr_1.5      codetools_0.2-15  splines_3.5.1    
+## [43] scales_0.5.0      assertthat_0.2.0  xtable_1.8-2     
+## [46] colorspace_1.3-2  labeling_0.3      sandwich_2.4-0   
+## [49] survey_3.33-2     stringi_1.1.7     lazyeval_0.2.1   
+## [52] munsell_0.5.0     zoo_1.8-2
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
 \end{document}

### 2018-11-03 manuscript.tex
add edits from James (2018-10-29)

@@
 ## other attached packages:
-## [1] ggplot2_3.0.0 cregg_0.2.3   rio_0.5.11   
+## [1] ggplot2_3.0.0 cregg_0.3.0   rio_0.5.11   
 ## 
 ## loaded via a namespace (and not attached):
-##  [1] zip_1.0.0         Rcpp_0.12.17      cellranger_1.1.0 
-##  [4] pillar_1.2.3      compiler_3.5.1    plyr_1.8.4       
+##  [1] zip_1.0.0         Rcpp_0.12.18      cellranger_1.1.0 
+##  [4] pillar_1.3.0.9000 compiler_3.5.1    plyr_1.8.4       
 ##  [7] bindr_0.1.1       forcats_0.3.0     tools_3.5.1      
-## [10] digest_0.6.15     lattice_0.20-35   ggstance_0.3     
-## [13] evaluate_0.10.1   tibble_1.4.2      gtable_0.2.0     
-## [16] pkgconfig_2.0.1   rlang_0.2.1       Matrix_1.2-14    
-## [19] openxlsx_4.1.0    curl_3.2          haven_1.1.2      
+## [10] digest_0.6.16     lattice_0.20-35   ggstance_0.3.1   
+## [13] evaluate_0.11     tibble_1.4.2      gtable_0.2.0     
+## [16] pkgconfig_2.0.2   rlang_0.2.2       Matrix_1.2-14    
+## [19] openxlsx_4.1.0    curl_3.2          haven_1.1.2.9000 
 ## [22] bindrcpp_0.2.2    withr_2.1.2       stringr_1.3.1    
 ## [25] dplyr_0.7.6       knitr_1.20        hms_0.4.2        
-## [28] lmtest_0.9-36     grid_3.5.1        tidyselect_0.2.4 
-## [31] glue_1.2.0        data.table_1.11.4 R6_2.2.2         
-## [34] survival_2.42-4   readxl_1.1.0      foreign_0.8-70   
-## [37] reshape2_1.4.3    readr_1.1.1       purrr_0.2.5      
-## [40] magrittr_1.5      codetools_0.2-15  splines_3.5.1    
-## [43] scales_0.5.0      assertthat_0.2.0  xtable_1.8-2     
-## [46] colorspace_1.3-2  labeling_0.3      sandwich_2.4-0   
-## [49] survey_3.33-2     stringi_1.1.7     lazyeval_0.2.1   
-## [52] munsell_0.5.0     zoo_1.8-2
+## [28] lmtest_0.9-36     tidyselect_0.2.4  grid_3.5.1       
+## [31] glue_1.3.0        data.table_1.11.4 R6_2.2.2         
+## [34] survival_2.42-6   readxl_1.1.0      foreign_0.8-71   
+## [37] purrr_0.2.5       magrittr_1.5      splines_3.5.1    
+## [40] scales_1.0.0      assertthat_0.2.0  xtable_1.8-2     
+## [43] colorspace_1.3-2  sandwich_2.5-0    survey_3.33-2    
+## [46] stringi_1.1.7     lazyeval_0.2.1    munsell_0.5.0    
+## [49] crayon_1.3.4      zoo_1.8-3
 \end{verbatim}

### 2018-11-17 manuscript.Rnw
update quantities of interest discussion

@@
 \subsectionfont{\normalfont\large\underline}
+\usepackage{floatrow}
+\floatsetup[figure]{capposition=top}
+\floatsetup[table]{capposition=top}
 
@@
 {\abstract Conjoint analysis is an increasingly prominent tool for studying political preferences.
-The method powerfully disentangles the causes of preferences over complex, multidimensional objects, such as political candidates or public policies.
+The method powerfully disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as political candidates or public policies.
 Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs), which measure the degree to which a given value of a conjoint profile feature increases or decreases respondents' support for the overall profile relative to a baseline, averaging across all respondents and all other profile features.
-While the AMCE has a clear causal interpretation, most published conjoint analyses also use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object, often including comparisons between theoretically interesting subgroups of respondents.
-We demonstrate that such analyses of conditional AMCEs can substantially mislead researchers about the degree of preference agreement or disagreement between subgroups.
-Most importantly, we highlight that the difference in conditional AMCEs between subgroups is sensitive to the choice of reference categories of features, providing inferences about subgroup preferences that are biased in unpredictable ways.
-We demonstrate the problem using simple examples drawn from the published literature and provide suggestions for improved reporting and interpretation.
+While the AMCE has a clear causal interpretation, most published conjoint analyses also use AMCEs for descriptive purposes: that is, to simply describe differences in levels of favorability toward objects, often including comparisons between subgroups of respondents.
+We demonstrate that such descriptive use of conditional AMCEs can substantially mislead researchers about the degree of agreement or disagreement between subgroups due the simple, familiar, but oft-forgotten property that interactions are sensitive to the reference category used in regression analysis.
+We show how researchers can be misled by differences in conditional AMCEs between subgroups, generating descriptive inferences from conjoints about subgroup differences in favorability that have arbitary sign, size, and significance.
+We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation.
 Given the rapidly accelerating use of conjoint analyses, these results have critically important implications for research in nearly all areas of political science.}
@@
 The driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE).
-By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit or implicit confounding between features of these objects, giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' support for a packaged conjoint profile relative to a baseline, averaging across all respondents and all other profile features.
-
-While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs for descriptive purposes: that is, to map variation in preferences across attributes of a multidimensional object.
-This is particularly the case when researchers engage in subgroup analyses of conjoint experiments for heterogeneity.
-For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.
+By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit or implicit confounding between features of these objects, giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' favorability toward a packaged conjoint profile relative to a baseline, averaging across all respondents and all other profile features.
+
+While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs for descriptive purposes: that is, to map variation in favorability toward a multidimensional object across its various features.
+This is particularly the case when researchers engage in subgroup analyses of conjoint experiments in search of preference heterogeneity.
+For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their original immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.
 Similarly, \citet{BansakHainmuellerHangartner2016} compare preferences toward immigrants across number of binary respondent characteristics: age, education, left-right ideology, and income.
@@
 term ``conditional AMCEs''; 13) but also focus on an implied quantity of interest: the \textit{difference} between two conditional AMCEs across subgroups.
-Searching for causal effect heterogeneity is an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017}, yet most conjoint analyses use this difference-in-AMCEs instead to \textit{descriptively} interpret apparent differences in preferences between the two groups.
-What is not obvious in such analyses is that differences-in-preferences (that is to say, the degree of favorability toward profiles containing a given feature) are not directly reflected in differences-in-AMCEs.
-Yet authors frequently use visual or more formal comparisons of conditional AMCEs to make descriptive claims about preferences, leading themselves and readers astray.
+Searching for causal effect heterogeneity is an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017}, yet most conjoint analyses use this difference-in-AMCEs instead to \textit{descriptively} interpret apparent differences in favorability toward objects with a given feature (e.g., immigrants from Syria) between the two groups (e.g., low and high ethnocentrism respondents).
+
+What is not necessarily obvious in such analyses is that differences-in-preferences (that is to say, the difference in degree of favorability toward profiles containing a given feature) are not directly reflected in differences-in-AMCEs.
+Yet authors frequently use visual or more formal comparisons of conditional AMCEs to make descriptive claims about such differences, leading themselves and readers astray.
+Differences in AMCEs do not provide inference into difference between subgroups' favorability toward a conjoint feature.
 In this paper, we show that a difference in underlying subgroup preferences --- like a difference in willingness to support a Syrian immigrant between high and low ethnocentrism respondents --- is only reflected in the difference-in-AMCEs under particular preference configurations and analytic choices.
-
-As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well but where preferences between subgroups diverge in the reference category, the difference-in-AMCEs is a highly misleading representation of underlying preferences.
+The underlying cause of this error is simple and familiar to any applied researcher but appears to be forgotten in most applied conjoint work.
+
+As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well but where preferences between subgroups diverge in the reference category, the difference-in-AMCEs is a highly misleading representation of underlying patterns of favorability.
 Yet most published conjoint studies appear to report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment.
-Ultimately effects are relative, not absolute, statements about preferences.
-For example, in a comparison of subgroup effects for Democrats and Republicans, Republicans might display a smaller effect because their preferences in the reference category are already very positive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.
-There is simply no predictable inference to be drawn from subgroup causal effects to the levels of underlying subgroup preferences.
+Ultimately AMCEs are relative, not absolute, statements about preferences so subgroup differences are also relative not absolute statements about preference heterogeneity.\footnote{For example, in a comparison of subgroup effects for Democrats and Republicans, Republicans might display a smaller effect because their preferences in the reference category are already very positive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.} There is simply no predictable inference to be drawn from subgroup causal effects to the levels of underlying subgroup opinion.
 This inferential error --- interpreting differences in the size of causal effects as descriptive differences in preferences --- appears to be widespread in published conjoint analyses.
@@
 In what follows, we demonstrate the challenges of conjoint analysis and show how reference category choice for profile features creates significant problems for the now-common practice of comparing conditional AMCEs across respondent subgroups.
-We show that the size and the direction of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features and that reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar, using examples drawn from the published political science literature (namely experiments by \citealt{HainmuellerHopkinsYamamoto2014, BallardRosaMartinScheve2016, TeeleKallaRosenbluth2018}).
+We show how the use of an arbitrary reference category means the size and the direction of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features and that reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar, using examples drawn from the published political science literature (namely experiments by \citealt{HainmuellerHopkinsYamamoto2014, BallardRosaMartinScheve2016, TeeleKallaRosenbluth2018}).
 The paper then provides suggestions for improved reporting and interpretation based around a purely descriptive quantity of interest: unadjusted marginal means.
@@
 One is to assess causal effects.
-Another is preference description.
-In causal inference, conjoints provide a design and analytic approach that allows researchers to understand the causal effect of a given feature on overall support for a multidimensional object, averaging across other features of the object included in the design.
-Such inferences can be thought of as statements of the form: ``shifting an immigrant's country of origin from India to Poland increases favorability by X percentage points.'' In descriptive inference, conjoints provide information about both (a) the absolute favorability of respondents toward objects with particular features or combinations of features, and (b) the relative favorability of respondents toward an object with alternative combinations of features.
+Another is preference description.\footnote{Here we use ``preference'' as \citet{HainmuellerHopkinsYamamoto2014} do: that is, as a statement of \textit{favorability} or \textit{support} for a profile.} In causal inference, conjoints provide a design and analytic approach that allows researchers to understand the causal effect of a given feature on overall support for a multidimensional object, averaging across other features of the object included in the design.
+Such inferences can be thought of as statements of the form: ``shifting an immigrant's country of origin from India to Poland increases favorability by X percentage points.'' In descriptive inference, conjoints provide information about both (a) the \textit{absolute} favorability of respondents toward objects with particular features or combinations of features, and (b) the \textit{relative} favorability of respondents toward an object with alternative combinations of features.
 Such inferences can be thought of as statements of the form ``Polish immigrants are preferred by X\% of respondents'' or ``Polish immigrants are more supported than Mexican immigrants, by X percentage points.'' Thus both causal and descriptive interpretations of conjoints are based upon the distribution of preferences across profile features and differences in preferences across alternative feature combinations.
 
-Importantly, a fully randomized conjoint design (without constraints between profile features) is simply a full-factorial experiment with some cells possibly, albeit randomly, left unobserved.
+Importantly, a fully randomized conjoint design without constraints between profile features is simply a full-factorial experiment (with some cells possibly, albeit randomly, left unobserved).
 All quantities of interest relevant to the analysis of conjoint designs derive from combinations of cell means, marginal means, and the grand mean, as is common in the traditional analysis of factorial experiments.
@@
 
-Average marginal component effects (AMCEs) depend only upon \textit{marginal means}: that is the column and row means for each feature level averaging across all other features.
-The marginal means describe the variation in preferences toward profiles that have a particular feature level.
+Average marginal component effects (AMCEs) depend only upon \textit{marginal means}: that is the column and row mean outcomes for each feature level averaging across all other features.
+A marginal mean describes the level of favorability toward profiles that have a particular feature level, marginalizing across all other features.
 For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities: a marginal mean of 0 indicates respondents select profiles with that feature level with probability $Pr(Y=1|X=x) = 0$ while a marginal mean of 1 indicates respondents select profiles with that feature level with probability $(Pr(Y=1|X=x)=1$.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany).
@@
 Because levels of features are randomly assigned, pairwise differences between two marginal means for a given feature (e.g., between candidates who are male versus female) have a direct causal interpretation.
-For fully randomized designs, the AMCE proposed by \citet{HainmuellerHopkinsYamamoto2014} is equivalent to the average marginal effect of each feature level for a model where each feature is converted into a matrix of indicator variables with one level left out as a reference category.\footnote{This is no different from any other regression context wherein one level of any categorical variable must be omitted from the design matrix in order to avoid perfect multicollinearity.
-In designs that entail constraints between profile features, the average marginal effect is a weighted average of effects across each combination of the constrained features where the weights on the effects are arbitrary but typically uniform.
+For fully randomized designs, the AMCE proposed by \citet{HainmuellerHopkinsYamamoto2014} is equivalent to the average marginal effect of each feature level for a model where each feature is converted into a matrix of indicator variables with one level left out as a reference category.
+This is no different from any other regression context wherein one level of any categorical variable must be omitted from the design matrix in order to avoid perfect multicollinearity.\footnote{In designs that entail constraints between profile features, the average marginal effect is a weighted average of effects across each combination of the constrained features where the weights on the effects are arbitrary but typically uniform.
 We ignore this distinction in the remainder of this article, as all of our results apply equally to fully randomized and to constrained designs.} This close relationship between AMCEs and marginal means is visible in Figure \ref{fig:hainmueller_candidate_replication} which presents a replication of the AMCE-based analysis of their candidate experiment (upper panel) and an analogous examination of the results using marginal means (lower panel).
@@
 
-This choice of reference category for estimating AMCEs can seem trivial but is quite consequential.
+Being a familiar analytic problem in any regression context, this choice of reference category for estimating AMCEs can seem trivial but is quite consequential.
 For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment, the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline.
@@
 \citet{OliverosSchuster2018} & Bureaucrat candidate preferences & Various \\ \midrule
-\citet{TeeleKallaRosenbluth2018} & Candidate preferences & Sex, Partisanship \\
+\citet{TeeleKallaRosenbluth2018} & Candidate preferences & Sex, Partisanship \\ \midrule
+\citet{Careyetal2018} & Hiring preferences & Various \\ \midrule
 \bottomrule
@@
 \end{center}
+All articles in this table use subgroup conditional AMCEs to make inferences about differences in preferences between subgroups.
 \end{table}
@@
 As a more complete example, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment separately for Democratic and Republican voters, as provided in the original paper, and the lower panel shows the results using conditional marginal means.
+Here and throughout we opt for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.
 Respondents' preference for female candidates is very apparent in both forms of analysis.
@@
 
-<<bms_difference_comparison, dependson=c("data_bms"), fig.width=8, fig.height=4, fig.cap="Estimated Preferences Difference between Inequity Averse and Non-Averse Respondents from Ballard-Rosa et al.
-(2016) Tax Preference Experiment">>=
+<<bms_difference_comparison, dependson=c("data_bms"), fig.width=8, fig.height=4, fig.cap="Estimated Preference Differences between Inequity Averse and Non-Averse Respondents from Ballard-Rosa et al.
+(2016) Tax Preference Experiment for Each Possible Reference Category">>=
 # reported results
@@
 
-<<hainmueller_subgroup_example, dependson=c("data_hainmueller_immigration"), fig.cap="Comparison of Alternative Reference Categories for Hainmueller et al. (2014) immigration Experiment">>=
+<<hainmueller_subgroup_example, dependson=c("data_hainmueller_immigration"), fig.cap="Comparison of Subgroup AMCEs Using Alternative Reference Categories for Hainmueller et al.
+(2014) Immigration Experiment">>=
 # estimates benchmarked to largest difference between subgroups
@@
 \appendix
+\tableofcontents
+
+\clearpage
+
+\section{Definition of Quantities of Interest}
+
+A conjoint experiment serves two purposes: (1) description of the conditional distribution of favorability over variations in multiple features, and (2) leveraging the random observation of combinations of features (so-called ``profiles'') to infer that any differences in favorability over features are causally attributable to the features as opposed to something else.
+The quantities of interest are therefore functions of the features being randomized as in any factorial experiment.
+But additionally, conjoints typically involve within-subjects research designs (i.e., multiple, different profile observations per participant) thus necessitating some additional notation to account for the \textit{survey implementation} of the conjoint in addition to the definition of the descriptive and causal parameters of interest.
+
+Ultimately, a conjoint since \citet{HainmuellerHopkinsYamamoto2014} is a complex survey-experimental design involving multiple observations across a high-dimension factorial experimental space.
+Specifically, $I$ respondents ($i \in \{1, \dots, I\}$) are presented with $K$ rating or forced choice decision tasks, each involving $J$ (typically 2) alternative profiles of, for example, candidates or policies.
+Each profile consists of a vector of $F$ (typically discrete) features or attributes that describe the profile (e.g., age, sex), each composed of $D_f$ alternative levels, a number which can vary across features.
+The experiment thus generates a dataset with $N = I \times J \times K$ observations of some rating scale or discrete choice outcome, $Y$, from a random sample of profiles drawn from the $C = \prod_{f = 1}^{F} D_f$ population of experimental \textit{cells} in the $F$-dimension feature space.
+
+The survey implementation of the conjoint therefore generates $N$ observations that can be indexed by $i,j,k$, forming an $N \times(L+4)$ dimensional data matrix $\mathbf{M}$ with each row representing the vector of feature levels $\vec{F}$ in each profile $j$ of respondent $i$'s task $k$, with indicators for $i$, $j$, $k$, and the corresponding outcome $Y_{i,j,k}$.\footnote{In typical paired designs (where $J=2$), this means each task generates two data points: $Y_{i,1,k}$ and $Y_{i,2,k}$.
+Note, too, that in fully randomized designs, these two profiles can be identical.
+Furthermore in fully randomized, forced-choice designs this can yield the additional curiosity that $Y_{i,\mathbf{c}} \neq Y_{i,\mathbf{c}}$ for a given respondent, $i$, and profile, $\mathbf{c}$.}
+
+With no loss of information, we can think of each row in this matrix equivalently as an observation of $Y_{i,\vec{F}}$.
+This is because \citet{HainmuellerHopkinsYamamoto2014} make several important assumptions that allow us to interpret these data in a different way than the survey implementation implies.
+First, they assume no carryover effects (Assumption 1), such that multiple observations from the same respondent can be treated as independent of one another.
+Second, they assume no profile order effects within-task (Assumption 2), such that profiles within a task can be treated as independent of each other.
+Assumptions 1 and 2 imply that the survey implementation indices for task, $k$, and profile-within-task, $j$, can be ignored.
+They have no bearing on any quantity of interest, by assumption.
+
+The analyst is therefore left with a dataset of $N$ observations, grouped into $i$ participants, each providing into $Y_{\vec{F}}$.
+All quantities of interest must therefore be specified over as features of the distribution of $Y$ over the $F$-dimensional feature space.
+In what follows, we therefore focus on the experimental features being randomized rather than the survey design factors being assumed away.
+\citet{HainmuellerHopkinsYamamoto2014} make a third assumption that profiles are randomly constituted (Assumption 3), which in a fully randomized design, has the effect of meaning that features and feature combinations are randomly sampled for observation.
+If this randomization is uniform (which it almost always is in applied examples) this means we can additionally ignore the probability of observing any given combination (as all profiles are equally likely to be observed).
+This is a point we return to in a moment.
+
+The most basic thing that can be learned about the distribution of $Y$ is the expected value, $E[Y]$, or \textit{grand mean} (in the parlance of factorial experiments).
+We can think of this quantity in terms of the survey implementation process (namely, respondents, tasks, and profiles) or as a simple function of the resulting data:
+
+\begin{equation}
+\bar{Y} = \dfrac{1}{I \times J \times K} \sum_{i=1}^{I} \sum_{j=1}^{J} \sum_{k=1}^{K} Y_{i,j,k} = \dfrac{1}{N} \sum_{n=1}^{N} Y_n
+\end{equation}
+
+\noindent The nested summation over $i,j,k$ could be stated explicitly but is unnecessary as the grand mean is simply the mean of all observed $Y$.
+A useful check on intuition is that in a forced choice design, where a respondent must choose only one profile, $j$, of all those presented in each task $k$, then by design $\bar{Y} = \frac{1}{J}$.
+For common, two-alternative, forced choice designs, $\bar{Y}$ therefore always equals $0.5$.
+By contrast, in rating scale designs, $\bar{Y}$ can take any value between the lower and upper bounds of the rating scale.
+
+In an experiment where $N > C$ (the number of observations is large than the number of cells) due to a large sample, or few factors, or levels of each factor, or both (or both of these design characteristic), a sensible next quantity of interest is the \textit{cell mean}: $E[Y|\vec{X} = \vec{x}]$, which in a conjoint simply measures the mean favorability toward a particular profile, $\vec{x}$.
+An effort to actually estimate this quantity will, however, become obviously intractable when one recognizes that the number of observations in a typical conjoint is much lower the number of feasible profiles ($N \ll C$).
+The cell mean can be unobserved for many or perhaps most experimental cells.
+
+Therefore quantities of interest that derive from it --- such as pairwise differences of means between cells --- cannot be estimated for any of the arbitrary $\binom{C}{2}$ pairs of cells.
+As an example, in the \cite{HainmuellerHopkinsYamamoto2014} candidate experiment, $C = 6^6 * 2^2 = 186,624$ and $N = 3466$, so less than 2\% of experimental cells were observable and a minuscule fraction of the 17.4 billion pairwise cell combinations could have generated estimable effects.
+
+It is at this point that the quantities of interest in a conjoint can become confusing.
+In a typical experiment where $N > C$, these pairwise differences of means are the standard estimator for a causal effect.
+For example, we might be interested in the effect on $Y$ of changing the value of one feature to another theoretically interesting value of that feature, holding all other feature values in the profile constant:
+
+\begin{equation}
+\tau = E[Y|X_1=x_1,X_2=x_2,\dots,X_f=x_f] - E[Y|X_1= \neg x_1,X_2=x_2,\dots,X_f=x_f]
+\end{equation}
+
+\noindent but we have no guarantee that both or, in fact, either of those particular cells are observed.
+If even this minimal causal quantity cannot be guaranteed to be estimable by design, questions about higher-order interactions across features are even more difficult to estimate as they require observing four or more specific cells, any of which may be missing.
+Even if we were interested in such quantities, we would be unlikely to be able to estimate them.
+
+Conjoint designs therefore ask us to think about completely different quantities of interest from typical sentiment measurement or experimentation.
+Consequently, what quantities might we care about that can be estimated from an $L$-dimension factorial experimental with considerable sparsity other than the grand mean?
+
+Even though $N \ll C$ in most applied conjoints, $N > F$.
+This means that even if we probably cannot learn about particular high-dimensional \textit{combinations of features}, we can learn about favorability toward particular features alone.
+That is, we can learn about conditional expectations over each feature dimension, $E[Y|X_f=x_f]$.
+In the factorial experiments literature, this conditional mean is called the \textit{marginal mean} (as it lies at the margins of a tabular presentation cell means for the complete design).
+The uniform sampling of cells in the design means that this is quantity can be estimated by the simple mean of $Y \forall X_f = x_f$.
+Were a constrained conjoint design used where some feature combinations were impossible, the marginal means would only be intelligible in the fractions of the design where all cells are observed.\footnote{Practically, the random sampling of cells does not need to be uniform; over- and under-representation of cells is possible.
+We focus here on fully randomized designs that draw profiles from the full space with equal probability.
+A nuance in \citeauthor{HainmuellerHopkinsYamamoto2014}'s notation is that their quantities of interest are conditioned on an arbitrary joint distribution of features rather than the particular joint distribution of features that was used to construct design or the joint distribution of features that happens to emerge empirically.
+In other words, they weight cells by an arbitrary joint probability mass function.}
+
+To clarify this point, consider the constrained 2x3 design below where one cell is unobserved by design:
+
+\begin{center}
+\begin{tabular}{lccc}\toprule
+ & $A = 1$ & $A = 2$ & \\ \midrule
+$B = 1$ & $Y_{A=1, B=1}$ & $Y_{A=2, B=1}$ & $E[Y|B=1]$ \\
+$B = 2$ & $Y_{A=1, B=2}$ & $Y_{A=2, B=1}$ & $E[Y|B=2]$ \\
+$B = 3$ & $Y_{A=1, B=3}$ & -- & $E[Y|B=3]$ \\ \midrule
+ & $E[Y|A=1]$ & $E[Y|A=2]$ & $E[Y]$ \\ \bottomrule
+\end{tabular}
+\end{center}
+
+\noindent Were the lower-right cell ($A=2, B=3$) observable by design, then a direct comparison of the marginal means, $E[Y|A=1]$ and $E[Y|A=2]$, in the lower table margin would provide direct insight into the relative favorability of respondents to profiles with features $A=1$ and $A=2$, marginalized over $B$.
+But because this cell is unobserved, these marginal means marginalize over different subsets of the possible values of $B$ making them not obviously comparable.
+By contrast, the first and second marginal means at the top-right of the table --- $E[Y|B=1]$ and $E[Y|B=2]$ --- provide insight into the favorability of participants toward profiles with features $B=1$ and with feature $B=2$ marginalizing over the two possible values of $A$.
+A researcher could safely conclude that participants are more (less) favorable toward profiles with feature $B=1$ than $B=2$ from this information alone.
+But they would not be able to so for feature $A$ without either (a) an explicit caveat that the comparison is of dissimilar subsets of profiles along dimension $B$ or (b) calculating marginal means over only the completely observable\footnote{Note that what matters here is \textit{observability}, not whether any given cell is actually observed.
+We know from above that most cells will be unobserved even in a uniformly sampled, unconstrained design.} portion of the feature space.
+
+For the common \textit{descriptive} use of conjoint designs to measure preferences over multi-dimensional objects, these marginal means alone are of direct interest.
+They express favorability on the scale of the outcome over alternative values of each feature.
+
+For the \textit{causal} interpretation of conjoint designs, comparisons of these marginal means is required.
+Comparisons between them provide causal inferences about the effect of changing a focal feature, marginalizing across the distribution of other features.
+Because feature combinations (i.e., the profiles) are randomly constructed and randomly observed from all possible combinations, the distribution of other non-focal features is, in expectation, is independent of the focal feature, thus identical across all levels of the focal feature, and therefore ignorable.
+A typical causal effect of interest is therefore the difference in marginal means across two levels of a feature.
+For an unconstrained design, this difference is the \textit{average marginal component effect} (AMCE) defined by \citet{HainmuellerHopkinsYamamoto2014}.
+In this way, an AMCE is simply a marginal effect of the factorial design: the difference of two marginal means.
+
+Unfortunately, this is not a perfectly complete definition, but it covers the vast majority of applied cases.
+The exceptions are few.
+First, \citeauthor{HainmuellerHopkinsYamamoto2014} allow the joint distribution of features used in calculating the difference of marginal means to be arbitrary.
+This is meant to accommodate the weighting of effects to reflect the real-world distribution of feature combinations (e.g., down-weighting African American Republican political candidates given their rarity in real-world politics) but in practice this is uncommon.
+
+Second, in constrained designs where some cells are unobservable, care needs to be taken in both defining and estimating AMCEs.
+Take, for example, the trivial example just above.
+The difference $E[Y|B=2]-E[Y|B=1]$ marginalizes over the full set of levels of $A$ but $E[Y|B=3]-E[Y|B=1]$ marginalizes only over case where $A=1$.
+\citeauthor{HainmuellerHopkinsYamamoto2014} allow for these two differences to be presented as the AMCE despite the fact that the quantities marginalize over distinct subsets of the design.
+For example, if feature $A$ is race ${Caucasian, African American}$ and feature $B$ is religion ${Evangelical, Catholic, Jewish}$.
+In \citeauthor{HainmuellerHopkinsYamamoto2014}'s notation, the AMCE of a candidate being Jewish relative to being Evangelical Christian is defined only for Caucasian candidates, while the AMCE of being Catholic is defined for both African American and Caucasian candidates.
+There is nothing inherently problematic about that but, as noted earlier, it requires either being clear about what features are being marginalized over or an analysis of only the complete and comparable subset of the design.
+So, researchers using such designs may prefer to not present the AMCE of being Jewish together with the other results as it does not draw upon the complete set of feature combinations used in other portions of the analysis.
+
+\clearpage
 

### 2018-11-17 manuscript.tex
update quantities of interest discussion

@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/bms_difference_comparison-1} \caption[Estimated Preferences Difference between Inequity Averse and Non-Averse Respondents from Ballard-Rosa et al]{Estimated Preferences Difference between Inequity Averse and Non-Averse Respondents from Ballard-Rosa et al.
-(2016) Tax Preference Experiment}\label{fig:bms_difference_comparison}
+\includegraphics[width=\maxwidth]{figure/bms_difference_comparison-1} \caption[Estimated Preference Differences between Inequity Averse and Non-Averse Respondents from Ballard-Rosa et al]{Estimated Preference Differences between Inequity Averse and Non-Averse Respondents from Ballard-Rosa et al.
+(2016) Tax Preference Experiment for Each Possible Reference Category}\label{fig:bms_difference_comparison}
 \end{figure}
@@
 ## other attached packages:
-## [1] ggplot2_3.0.0 cregg_0.3.0   rio_0.5.11   
+## [1] ggplot2_3.1.0 cregg_0.3.0   rio_0.5.11   
 ## 
 ## loaded via a namespace (and not attached):
-##  [1] zip_1.0.0         Rcpp_0.12.18      cellranger_1.1.0 
+##  [1] zip_1.0.0         Rcpp_0.12.19      cellranger_1.1.0 
 ##  [4] pillar_1.3.0.9000 compiler_3.5.1    plyr_1.8.4       
 ##  [7] bindr_0.1.1       forcats_0.3.0     tools_3.5.1      
-## [10] digest_0.6.16     lattice_0.20-35   ggstance_0.3.1   
-## [13] evaluate_0.11     tibble_1.4.2      gtable_0.2.0     
-## [16] pkgconfig_2.0.2   rlang_0.2.2       Matrix_1.2-14    
+## [10] digest_0.6.18     lattice_0.20-35   ggstance_0.3.1   
+## [13] evaluate_0.12     tibble_1.4.2      gtable_0.2.0     
+## [16] pkgconfig_2.0.2   rlang_0.3.0.1     Matrix_1.2-15    
 ## [19] openxlsx_4.1.0    curl_3.2          haven_1.1.2.9000 
 ## [22] bindrcpp_0.2.2    withr_2.1.2       stringr_1.3.1    
-## [25] dplyr_0.7.6       knitr_1.20        hms_0.4.2        
-## [28] lmtest_0.9-36     tidyselect_0.2.4  grid_3.5.1       
-## [31] glue_1.3.0        data.table_1.11.4 R6_2.2.2         
-## [34] survival_2.42-6   readxl_1.1.0      foreign_0.8-71   
+## [25] dplyr_0.7.7       knitr_1.20        hms_0.4.2        
+## [28] lmtest_0.9-36     tidyselect_0.2.5  grid_3.5.1       
+## [31] glue_1.3.0        data.table_1.11.8 R6_2.3.0         
+## [34] survival_2.43-1   readxl_1.1.0      foreign_0.8-71   
 ## [37] purrr_0.2.5       magrittr_1.5      splines_3.5.1    
-## [40] scales_1.0.0      assertthat_0.2.0  xtable_1.8-2     
-## [43] colorspace_1.3-2  sandwich_2.5-0    survey_3.33-2    
-## [46] stringi_1.1.7     lazyeval_0.2.1    munsell_0.5.0    
-## [49] crayon_1.3.4      zoo_1.8-3
+## [40] scales_1.0.0      assertthat_0.2.0  xtable_1.8-3     
+## [43] colorspace_1.3-2  sandwich_2.5-0    survey_3.34      
+## [46] stringi_1.2.4     lazyeval_0.2.1    munsell_0.5.0    
+## [49] crayon_1.3.4      zoo_1.8-4
 \end{verbatim}

### 2018-11-25 manuscript.Rnw
rebuild manuscript w/ some small changes

@@
 Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs), which measure the degree to which a given value of a conjoint profile feature increases or decreases respondents' support for the overall profile relative to a baseline, averaging across all respondents and all other profile features.
-While the AMCE has a clear causal interpretation, most published conjoint analyses also use AMCEs for descriptive purposes: that is, to simply describe differences in levels of favorability toward objects, often including comparisons between subgroups of respondents.
-We demonstrate that such descriptive use of conditional AMCEs can substantially mislead researchers about the degree of agreement or disagreement between subgroups due the simple, familiar, but oft-forgotten property that interactions are sensitive to the reference category used in regression analysis.
-We show how researchers can be misled by differences in conditional AMCEs between subgroups, generating descriptive inferences from conjoints about subgroup differences in favorability that have arbitary sign, size, and significance.
-We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation.
+While the AMCE has a clear causal interpretation, most published conjoint analyses also use AMCEs to simply describe preferences (i.e., levels of favorability toward objects), often including comparisons of AMCEs between subgroups of respondents.
+We show how this descriptive use of these conditional AMCEs can substantially mislead researchers about the degree of agreement or disagreement between subgroups due the simple, familiar, but seemingly forgotten property that interactions are sensitive to the reference category used in regression analysis.
+We show how researchers can be misled by differences in conditional AMCEs between subgroups, generating inferences about subgroup differences in favorability that have arbitrary sign, size, and significance.
+We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation using two quantities of interest: the marginal mean and the omnibus F-test.
 Given the rapidly accelerating use of conjoint analyses, these results have critically important implications for research in nearly all areas of political science.}
@@
 
-While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs for descriptive purposes: that is, to map variation in favorability toward a multidimensional object across its various features.
+While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs for \textit{descriptive} purposes: that is, to map variation in favorability toward a multidimensional object across its various features.
 This is particularly the case when researchers engage in subgroup analyses of conjoint experiments in search of preference heterogeneity.
@@
 
-As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well but where preferences between subgroups diverge in the reference category, the difference-in-AMCEs is a highly misleading representation of underlying patterns of favorability.
+As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well but where preferences between subgroups diverge in the reference category, the difference-in-AMCEs is a misleading representation of underlying patterns of favorability.
 Yet most published conjoint studies appear to report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment.
@@
 This inferential error --- interpreting differences in the size of causal effects as descriptive differences in preferences --- appears to be widespread in published conjoint analyses.
-Thus a seemingly trivial methodological decision has the potential to substantially alter our interpretations of a rapidly growing body of evidence about political preferences over important and varied political matters, including candidate selection and public policy.
-
-In what follows, we demonstrate the challenges of conjoint analysis and show how reference category choice for profile features creates significant problems for the now-common practice of comparing conditional AMCEs across respondent subgroups.
+The root of this error is likely familiar to many researchers: it is simply a matter of regression specification for models involving interactions between categorical regressors.
+\citet{EgamiImai2018}, for example, provide an extensive discussion of the implications of this property for interpreting causal interactions between features of conjoint profiles.
+The state of the published literature would suggest the problem remains non-obvious when applied to descriptive analysis of subgroups in conjoint designs.
+
+In what follows, we demonstrate the challenges of conjoint analysis and reminder readers of how reference category choice for profile features creates significant problems for comparing conditional AMCEs across respondent subgroups.
 We show how the use of an arbitrary reference category means the size and the direction of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features and that reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar, using examples drawn from the published political science literature (namely experiments by \citealt{HainmuellerHopkinsYamamoto2014, BallardRosaMartinScheve2016, TeeleKallaRosenbluth2018}).
-The paper then provides suggestions for improved reporting and interpretation based around a purely descriptive quantity of interest: unadjusted marginal means.
+The paper then provides suggestions for improved conjoint reporting and interpretation based around two quantities of interest drawn from the factorial experimentation literature: (1) unadjusted marginal means, a quantity measuring favorability toward a given feature, and (b) an omnibus F-test, measuring differences therein.
 Newly developed software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment --- is demonstrated throughout \citep{Leeper2018cregg}.
@@
 One is to assess causal effects.
-Another is preference description.\footnote{Here we use ``preference'' as \citet{HainmuellerHopkinsYamamoto2014} do: that is, as a statement of \textit{favorability} or \textit{support} for a profile.} In causal inference, conjoints provide a design and analytic approach that allows researchers to understand the causal effect of a given feature on overall support for a multidimensional object, averaging across other features of the object included in the design.
+Another is preference description.\footnote{Here we use ``preference'' as \citet{HainmuellerHopkinsYamamoto2014} do: that is, as a statement of \textit{favorability} or \textit{support} for a profile, not the more narrow economic definition of a strict rank ordering of objects by favorability.} In causal inference, conjoints provide a design and analytic approach that allows researchers to understand the causal effect of a given feature on overall support for a multidimensional object, averaging across other features of the object included in the design.
 Such inferences can be thought of as statements of the form: ``shifting an immigrant's country of origin from India to Poland increases favorability by X percentage points.'' In descriptive inference, conjoints provide information about both (a) the \textit{absolute} favorability of respondents toward objects with particular features or combinations of features, and (b) the \textit{relative} favorability of respondents toward an object with alternative combinations of features.
@@
 While this would be problematic for attempting to infer pairwise comparisons between cells, conjoint analysts mostly focus on the marginal effects of each feature rather than more complex interactions.
+Appendix \ref{app:quantities} provides detailed notation and elaborations of these definitions of quantities of interest.
 
@@
 We ignore this distinction in the remainder of this article, as all of our results apply equally to fully randomized and to constrained designs.} This close relationship between AMCEs and marginal means is visible in Figure \ref{fig:hainmueller_candidate_replication} which presents a replication of the AMCE-based analysis of their candidate experiment (upper panel) and an analogous examination of the results using marginal means (lower panel).
+Here and throughout we use visual presentation of results, but full numerical estimates including appropriate standard errors are presented in the Appendix.
 Note, in particular, how marginal means convey information about the preferences of respondents for all feature levels while AMCEs definitionally restrict the AMCE for the reference category to zero (or undefined).
@@
 As a more complete example, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment separately for Democratic and Republican voters, as provided in the original paper, and the lower panel shows the results using conditional marginal means.
-Here and throughout we opt for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.
+Again, we opt for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.
 Respondents' preference for female candidates is very apparent in both forms of analysis.
@@
 }))
-amce_diffs$statistic <- "Difference in AMCEs"
+amce_diffs$statistic <- "Potential Differences in AMCEs"
 
@@
 diffs <- rbind(main, amce_diffs, mm_diff)
-levels(diffs$statistic) <- c("Originally Reported Difference", "Difference in AMCEs", "Difference in MMs")
+levels(diffs$statistic) <- c("Originally Reported Difference", "Potential Differences in AMCEs", "Difference in MMs")
 # Plot
@@
 
-<<hainmueller_subgroup_example, dependson=c("data_hainmueller_immigration"), fig.cap="Comparison of Subgroup AMCEs Using Alternative Reference Categories for Hainmueller et al.
-(2014) Immigration Experiment">>=
+<<hainmueller_subgroup_example, dependson=c("data_hainmueller_immigration")>>=
 # estimates benchmarked to largest difference between subgroups
@@
 
-<<hainmueller_subgroup_example_plot, dependson=c("data_hainmueller_immigration", "hainmueller_subgroup_example"), fig.width=8, fig.height=12, fig.cap="Alternative Reference Categories for Features in Hainmueller et al.
+<<hainmueller_subgroup_example_plot, dependson=c("data_hainmueller_immigration", "hainmueller_subgroup_example"), fig.width=8, fig.height=12, fig.cap="Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Hainmueller et al.
 (2014) Immigration Experiment", message=FALSE>>=
@@
 
-\section{Definition of Quantities of Interest}
+\section{Definition of Quantities of Interest}\label{app:quantities}
 

### 2018-11-25 manuscript.tex
rebuild manuscript w/ some small changes

@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/hainmueller_subgroup_example_plot-1} \caption[Alternative Reference Categories for Features in Hainmueller et al]{Alternative Reference Categories for Features in Hainmueller et al.
+\includegraphics[width=\maxwidth]{figure/hainmueller_subgroup_example_plot-1} \caption[Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Hainmueller et al]{Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Hainmueller et al.
 (2014) Immigration Experiment}\label{fig:hainmueller_subgroup_example_plot}
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-2 package
-% Wed Jul 11 09:37:48 2018
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Nov 25 10:42:30 2018
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-2 package
-% Wed Jul 11 09:37:55 2018
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Nov 25 10:42:36 2018
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-2 package
-% Wed Jul 11 09:38:07 2018
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Nov 25 10:42:42 2018
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-2 package
-% Wed Jul 11 09:38:11 2018
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Nov 25 10:42:44 2018
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-2 package
-% Wed Jul 11 10:11:31 2018
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Nov 25 10:42:47 2018
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-2 package
-% Wed Jul 11 10:11:43 2018
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Nov 25 10:42:56 2018
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-2 package
-% Wed Jul 11 10:12:23 2018
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Nov 25 10:43:16 2018
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-2 package
-% Wed Jul 11 10:12:27 2018
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Nov 25 10:43:19 2018
 \begin{table}[ht]
@@
 ## loaded via a namespace (and not attached):
-##  [1] zip_1.0.0         Rcpp_0.12.19      cellranger_1.1.0 
+##  [1] zip_1.0.0         Rcpp_1.0.0        cellranger_1.1.0 
 ##  [4] pillar_1.3.0.9000 compiler_3.5.1    plyr_1.8.4       
 ##  [7] bindr_0.1.1       forcats_0.3.0     tools_3.5.1      
-## [10] digest_0.6.18     lattice_0.20-35   ggstance_0.3.1   
+## [10] digest_0.6.18     lattice_0.20-38   ggstance_0.3.1   
 ## [13] evaluate_0.12     tibble_1.4.2      gtable_0.2.0     
@@
 ## [22] bindrcpp_0.2.2    withr_2.1.2       stringr_1.3.1    
-## [25] dplyr_0.7.7       knitr_1.20        hms_0.4.2        
+## [25] dplyr_0.7.8       knitr_1.20        hms_0.4.2        
 ## [28] lmtest_0.9-36     tidyselect_0.2.5  grid_3.5.1       

### 2018-12-12 manuscript.Rnw
incorporate changes from Sara 2018-12-12

@@
 Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs), which measure the degree to which a given value of a conjoint profile feature increases or decreases respondents' support for the overall profile relative to a baseline, averaging across all respondents and all other profile features.
-While the AMCE has a clear causal interpretation, most published conjoint analyses also use AMCEs to simply describe preferences (i.e., levels of favorability toward objects), often including comparisons of AMCEs between subgroups of respondents.
-We show how this descriptive use of these conditional AMCEs can substantially mislead researchers about the degree of agreement or disagreement between subgroups due the simple, familiar, but seemingly forgotten property that interactions are sensitive to the reference category used in regression analysis.
-We show how researchers can be misled by differences in conditional AMCEs between subgroups, generating inferences about subgroup differences in favorability that have arbitrary sign, size, and significance.
+While the AMCE has a clear causal interpretation, most published conjoint analyses also use AMCEs to simply describe preferences, often including comparisons of AMCEs between subgroups of respondents.
+We show how this descriptive use of conditional AMCEs can be substantially misleading about the degree of agreement or disagreement between subgroups due the simple, but often forgotten, property that interactions are sensitive to the reference category used in regression analysis.
+This leads to inferences about subgroup differences in preferences that have arbitrary sign, size, and significance.
 We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation using two quantities of interest: the marginal mean and the omnibus F-test.
-Given the rapidly accelerating use of conjoint analyses, these results have critically important implications for research in nearly all areas of political science.}
+Given the rapidly accelerating use of conjoint analyses, this paper makes an important contribution by highlighting pitfalls and presenting advice for best practice in the analysis and presentation of conjoint experiments.}
 
@@
 In these and many other articles, interpretation of these subgroup analyses focus not just on the \textit{causal effects} of profile features within each subgroup (what Hainmueller et al.
-term ``conditional AMCEs''; 13) but also focus on an implied quantity of interest: the \textit{difference} between two conditional AMCEs across subgroups.
+term ``conditional AMCEs''; 13) but also on an implied quantity of interest: the \textit{difference} between two conditional AMCEs across subgroups.
 Searching for causal effect heterogeneity is an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017}, yet most conjoint analyses use this difference-in-AMCEs instead to \textit{descriptively} interpret apparent differences in favorability toward objects with a given feature (e.g., immigrants from Syria) between the two groups (e.g., low and high ethnocentrism respondents).
@@
 The paper then provides suggestions for improved conjoint reporting and interpretation based around two quantities of interest drawn from the factorial experimentation literature: (1) unadjusted marginal means, a quantity measuring favorability toward a given feature, and (b) an omnibus F-test, measuring differences therein.
-Newly developed software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment --- is demonstrated throughout \citep{Leeper2018cregg}.
+Newly developed software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment --- is demonstrated throughout.
 We conclude with advice for best practices in the analysis and presentation of conjoint results.
@@
 This is no different from any other regression context wherein one level of any categorical variable must be omitted from the design matrix in order to avoid perfect multicollinearity.\footnote{In designs that entail constraints between profile features, the average marginal effect is a weighted average of effects across each combination of the constrained features where the weights on the effects are arbitrary but typically uniform.
-We ignore this distinction in the remainder of this article, as all of our results apply equally to fully randomized and to constrained designs.} This close relationship between AMCEs and marginal means is visible in Figure \ref{fig:hainmueller_candidate_replication} which presents a replication of the AMCE-based analysis of their candidate experiment (upper panel) and an analogous examination of the results using marginal means (lower panel).
+We ignore this distinction in the remainder of this article, as all of our results apply equally to fully randomized and to constrained designs.} This close relationship between AMCEs and marginal means is visible in Figure \ref{fig:hainmueller_candidate_replication} which presents a replication of the AMCE-based analysis of the Hainmueller et al.
+candidate experiment (upper panel) and an analogous examination of the results using marginal means (lower panel).
 Here and throughout we use visual presentation of results, but full numerical estimates including appropriate standard errors are presented in the Appendix.
@@
 Figure \ref{fig:reference_category} shows how the estimated AMCEs for each level of education would have differed depending on that choice.
-Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline.\footnote{As another example, in \citeauthor{BallardRosaMartinScheve2016}'s tax preference experiment, the lowest level of taxation is chosen as the reference category for each feature for reasons of substantive interpretation, yet despite the substantive intuitiveness of this, favorability toward the lowest level of taxation is not necessarily higher or lower than preferences for alternative tax rates.} The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses.\footnote{In \textit{constrained} conjoint designs, the choice of reference category is even more important.
+Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline.\footnote{As another example, in \citeauthor{BallardRosaMartinScheve2016}'s tax preference experiment, the lowest level of taxation is chosen as the reference category for each feature for reasons of substantive interpretation, yet despite the substantive intuitiveness of this, favorability toward the lowest level of taxation is not necessarily higher or lower than preferences for alternative tax rates.} The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.\footnote{In \textit{constrained} conjoint designs, the choice of reference category is even more important.
 Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature.
@@
 
-Yet, just as analysis of full sample conjoint data is often descriptive in nature, so too conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally.
+Yet, just as analysis of full sample conjoint data is often descriptive in nature, so too do conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally.
 For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} visually compare the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22).
@@
 
-\item Exercise extreme caution when explicitly or implicitly interpreting differences-in-AMCEs across subgroups.
+\item Exercise caution when explicitly or implicitly interpreting differences-in-AMCEs across subgroups.
 While that quantity conveys the difference in effects of a change in a given feature, heterogeneous effects do not necessarily mean different underlying preferences.
@@
 
-\item When descriptively characterizing differences in preferences between subgroups, directly estimate the subgroup difference using conditional marginal means and differences between conditional marginal means, rather than relying on difference-in-AMCEs.
+\item When descriptively characterizing differences in preferences between subgroups, directly estimate the subgroup difference using conditional marginal means and differences between conditional marginal means, rather than relying on the difference-in-AMCEs.
 
@@
 
-\noindent Following this advice, we hope, will allow researchers to more clearly and more accurately represent the results of conjoint experiments.
+\noindent Following this advice, we hope, will allow researchers to more clearly and more accurately represent descriptive results of conjoint experiments.
 
@@
 
-In an experiment where $N > C$ (the number of observations is large than the number of cells) due to a large sample, or few factors, or levels of each factor, or both (or both of these design characteristic), a sensible next quantity of interest is the \textit{cell mean}: $E[Y|\vec{X} = \vec{x}]$, which in a conjoint simply measures the mean favorability toward a particular profile, $\vec{x}$.
+In an experiment where $N > C$ (the number of observations is larger than the number of cells) due to a large sample, or few factors, or levels of each factor, or both (or both of these design characteristic), a sensible next quantity of interest is the \textit{cell mean}: $E[Y|\vec{X} = \vec{x}]$, which in a conjoint simply measures the mean favorability toward a particular profile, $\vec{x}$.
 An effort to actually estimate this quantity will, however, become obviously intractable when one recognizes that the number of observations in a typical conjoint is much lower the number of feasible profiles ($N \ll C$).

### 2018-12-12 manuscript.tex
incorporate changes from Sara 2018-12-12

@@
 ## other attached packages:
-## [1] ggplot2_3.1.0 cregg_0.3.0   rio_0.5.11   
+## [1] ggplot2_3.1.0 cregg_0.3.0   rio_0.5.16   
 ## 
@@
 ## [16] pkgconfig_2.0.2   rlang_0.3.0.1     Matrix_1.2-15    
-## [19] openxlsx_4.1.0    curl_3.2          haven_1.1.2.9000 
+## [19] openxlsx_4.1.0    curl_3.2          haven_2.0.0      
 ## [22] bindrcpp_0.2.2    withr_2.1.2       stringr_1.3.1    
@@
 ## [31] glue_1.3.0        data.table_1.11.8 R6_2.3.0         
-## [34] survival_2.43-1   readxl_1.1.0      foreign_0.8-71   
+## [34] survival_2.43-3   readxl_1.1.0      foreign_0.8-71   
 ## [37] purrr_0.2.5       magrittr_1.5      splines_3.5.1    

### 2019-04-11 manuscript.Rnw
add in Bechtel and Scheve example; update figures; edit

@@
 \usepackage[utf8]{inputenc}
+\usepackage{mathpazo}
 %\usepackage{times}
@@
 
-\title{Measuring Subgroup Preferences in Conjoint Experiments}
+\title{Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}}
 \author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}
@@
 Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs), which measure the degree to which a given value of a conjoint profile feature increases or decreases respondents' support for the overall profile relative to a baseline, averaging across all respondents and all other profile features.
-While the AMCE has a clear causal interpretation, most published conjoint analyses also use AMCEs to simply describe preferences, often including comparisons of AMCEs between subgroups of respondents.
-We show how this descriptive use of conditional AMCEs can be substantially misleading about the degree of agreement or disagreement between subgroups due the simple, but often forgotten, property that interactions are sensitive to the reference category used in regression analysis.
+While the AMCE has a clear causal interpretation (about the \textit{effect} of features), most published conjoint analyses also use AMCEs to simply describe \textit{levels} of preferences or favorability, often including comparisons of AMCEs between subgroups of respondents.
+We show how this descriptive use of conditional AMCEs can be substantially misleading about the degree of agreement or disagreement between subgroups due the simple property that regression interactions are sensitive to the reference category used in the analysis.
 This leads to inferences about subgroup differences in preferences that have arbitrary sign, size, and significance.
 We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation using two quantities of interest: the marginal mean and the omnibus F-test.
-Given the rapidly accelerating use of conjoint analyses, this paper makes an important contribution by highlighting pitfalls and presenting advice for best practice in the analysis and presentation of conjoint experiments.}
+Amidst the rapidly accelerating use of conjoint analyses, we highlight common pitfalls and offer advice for best practice in the analysis and presentation of conjoint experiments.}
 
@@
 library("ggplot2")
+library("gridExtra")
 requireNamespace("xtable", quietly = TRUE)
@@
 hainmueller_immigration$ethnocentrism_split <- factor(hainmueller_immigration$ethnocentrism_split, levels = c(0,1), labels = c("low", "high"))
+
+## constraints
+hainmueller_immigration$constraint1constrained <- ifelse(
+  (hainmueller_immigration$CountryOfOrigin %in% c("India", "Germany", "France", "Mexico", "Philippines", "Poland")) & (hainmueller_immigration$ReasonForApplication %in% c("Seek better job in U.S.", "Reunite with family members already in the U.S."))
+, TRUE, FALSE)
+hainmueller_immigration$constraint1unconstrained <- ifelse(
+  hainmueller_immigration$CountryOfOrigin %in% c("China", "Sudan", "Somalia", "France")
+, TRUE, FALSE)
+hainmueller_immigration$constraint2constrained <- ifelse(
+  (hainmueller_immigration$Job %in% c("Financial analyst", "Computer programmer", "Research scientist", "Doctor")) & (!hainmueller_immigration$Education %in% c("No formal education", "Equivalent to completing fourth grade", "Equivalent to completing eighth grade", "Equivalent to completing high school"))
+, TRUE, FALSE)
+hainmueller_immigration$constraint2unconstrained <- ifelse(
+  hainmueller_immigration$Job %in% c("Janitor", "Waiter", "Child care provider", "Gardener", "Construction worker", "Teacher", "Nurse")
+, TRUE, FALSE)
 @
@@
 
+<<data_bechtel>>=
+if (file.exists("data/bms.rds")) {
+    bechtel <- cj_df(rio::import("data/bechtel.rds"))
+} else {
+	# load original data file
+	bechtel <- cj_df(rio::import("data/bechtel_scheve_pnas.dta"))
+
+	# conjoint features
+	tmp <- attr(bechtel[["cost_cj"]], "label")
+	bechtel[["cost_cj"]] <- rio::factorize(bechtel[["cost_cj"]])
+	levels(bechtel[["cost_cj"]]) <- gsub("^.{1}", "€", levels(bechtel$cost_cj))
+	attr(bechtel[["cost_cj"]], "label") <- tmp
+	rm(tmp)
+
+	tmp <- attr(bechtel[["distrib_cj"]], "label")
+	bechtel[["distrib_cj"]] <- rio::factorize(bechtel[["distrib_cj"]])
+	attr(bechtel[["distrib_cj"]], "label") <- tmp
+	rm(tmp)
+
+	tmp <- attr(bechtel[["ctries_cj"]], "label")
+	bechtel[["ctries_cj"]] <- rio::factorize(bechtel[["ctries_cj"]])
+	attr(bechtel[["ctries_cj"]], "label") <- tmp
+	rm(tmp)
+
+	tmp <- attr(bechtel[["emissions_cj"]], "label")
+	bechtel[["emissions_cj"]] <- rio::factorize(bechtel[["emissions_cj"]])
+	attr(bechtel[["emissions_cj"]], "label") <- tmp
+	rm(tmp)
+
+	tmp <- attr(bechtel[["sanctions_cj"]], "label")
+	bechtel[["sanctions_cj"]] <- rio::factorize(bechtel[["sanctions_cj"]])
+	levels(bechtel[["sanctions_cj"]])[2:4] <- gsub("^.{1}", "€", levels(bechtel$sanctions_cj)[2:4])
+	attr(bechtel[["sanctions_cj"]], "label") <- tmp
+	rm(tmp)
+
+	tmp <- attr(bechtel[["monitoring_cj"]], "label")
+	bechtel[["monitoring_cj"]] <- rio::factorize(bechtel[["monitoring_cj"]])
+	attr(bechtel[["monitoring_cj"]], "label") <- tmp
+	rm(tmp)
+
+	tmp <- attr(bechtel[["country"]], "label")
+	bechtel[["country"]] <- rio::factorize(bechtel[["country"]])
+	attr(bechtel[["country"]], "label") <- tmp
+	rm(tmp)
+
+	# covariates
+	## environmentalism
+	tmp <- attr(bechtel[["support_iec_high_group"]], "label")
+	bechtel[["environmentalism"]] <- rio::factorize(bechtel[["support_iec_high_group"]])
+	levels(bechtel[["environmentalism"]]) <- paste0("Environmentalism: ", levels(bechtel[["environmentalism"]]))
+	attr(bechtel[["environmentalism"]], "label") <- tmp
+	rm(tmp)
+
+	## reciprocity
+	tmp <- attr(bechtel[["recip_s_high_group"]], "label")
+	bechtel[["reciprocity"]] <- rio::factorize(bechtel[["recip_s_high_group"]])
+	levels(bechtel[["reciprocity"]]) <- paste0("Reciprocity: ", levels(bechtel[["reciprocity"]]))
+	attr(bechtel[["reciprocity"]], "label") <- tmp
+	rm(tmp)
+
+    # export
+    rio::export(bechtel, "data/bechtel.rds")    
+}
+@
+
 <<data_tkr>>=
@@
 Amidst the dramatically increased use of experiments within political science \citep{Druckmanetal2006, Mutz2011}, conjoint experimental designs have recently become a prominent methodological tool in political science.
-While traditional survey experiments tend to examine just one or two factors that might shape outcomes \citep[see, for reviews,][]{GainesKuklinskiQuirk2007, Sniderman2011}, conjoint designs allow researchers to study the independent effects on preferences of many features of complex, multidimensional objects such as political candidates \citep{Campbelletal2016, TeeleKallaRosenbluth2018}, immigrant admissions \citep{HainmuellerHopkins2015, BansakHainmuellerHangartner2016, WrightLevyCitrin2016}, or public policies \citep{GallegoMarx2017, Hankinson2018}.
-The driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE).
-By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit or implicit confounding between features of these objects, giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' favorability toward a packaged conjoint profile relative to a baseline, averaging across all respondents and all other profile features.
-
-While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs for \textit{descriptive} purposes: that is, to map variation in favorability toward a multidimensional object across its various features.
+While survey experiments have traditionally examined just one or two factors that might shape outcomes \citep[see, for reviews,][]{GainesKuklinskiQuirk2007, Sniderman2011}, conjoint designs allow researchers to study the independent effects on preferences of many features of complex, multidimensional objects such as political candidates \citep{Campbelletal2016, TeeleKallaRosenbluth2018}, immigrant admissions \citep{HainmuellerHopkins2015, BansakHainmuellerHangartner2016, WrightLevyCitrin2016}, or public policies \citep{GallegoMarx2017, Hankinson2018}.
+Factorial designs of this sort have a long history but the driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a small-sample, fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE).
+By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit or implicit confounding between features of these objects, giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' favorability toward a packaged conjoint profile relative to a baseline.
+
+While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs not only for \textit{causal} purposes (interpreting AMCEs as effect sizes), but also for \textit{descriptive} purposes: that is, to map levels of favorability toward a multidimensional object across its various features.\footnote{See \citet{Shmueli2010} for an elaboration on the distinctions between explanatory (causal) modelling, descriptive modelling, and predictive modelling.} In this sense, conjoints are often applied like list experiments, using randomization to measure a sample's preferences over something difficult to measure with direct questioning.
+A positive (negative) AMCE for a given feature can be read as a descriptive measure of high (low) favorability toward profiles with that feature.
+Though the quantity is causal, it is often read descriptively.
+
 This is particularly the case when researchers engage in subgroup analyses of conjoint experiments in search of preference heterogeneity.
+Such exercises are an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017, EgamiImai2018}.
 For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their original immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.
@@
 In a different domain, \citet{BallardRosaMartinScheve2016} compare preferences over tax policies across a number of subgroups defined by demographics and political orientations.
+\citet{BechtelScheve2013} compare AMCEs on climate agreements across four different countries, and across subgroups of respondents.
 \citet{TeeleKallaRosenbluth2018} compare AMCEs for features of male and female political candidates among male and female respondents.
-\citet{KirklandCoppock2017} do a similar comparison between Democrats and Republicans in hypothetical elections.
-
-In these and many other articles, interpretation of these subgroup analyses focus not just on the \textit{causal effects} of profile features within each subgroup (what Hainmueller et al.
-term ``conditional AMCEs''; 13) but also on an implied quantity of interest: the \textit{difference} between two conditional AMCEs across subgroups.
-Searching for causal effect heterogeneity is an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017}, yet most conjoint analyses use this difference-in-AMCEs instead to \textit{descriptively} interpret apparent differences in favorability toward objects with a given feature (e.g., immigrants from Syria) between the two groups (e.g., low and high ethnocentrism respondents).
-
-What is not necessarily obvious in such analyses is that differences-in-preferences (that is to say, the difference in degree of favorability toward profiles containing a given feature) are not directly reflected in differences-in-AMCEs.
-Yet authors frequently use visual or more formal comparisons of conditional AMCEs to make descriptive claims about such differences, leading themselves and readers astray.
-Differences in AMCEs do not provide inference into difference between subgroups' favorability toward a conjoint feature.
-In this paper, we show that a difference in underlying subgroup preferences --- like a difference in willingness to support a Syrian immigrant between high and low ethnocentrism respondents --- is only reflected in the difference-in-AMCEs under particular preference configurations and analytic choices.
-The underlying cause of this error is simple and familiar to any applied researcher but appears to be forgotten in most applied conjoint work.
+Most of these comparisons are visual or informal.
+But some involve explicit estimation of the subgroup difference, such as when \citet{KirklandCoppock2017} compare conditional AMCEs across hypothetical partisan and nonpartisan elections.
+Interpretation of subgroup AMCEs thus involves an implied quantity of interest: the \textit{difference} between two conditional AMCEs.
+
+What is not necessarily obvious in such analyses is that differences-in-preferences (that is to say, the difference in degree of favorability toward profiles containing a given feature) are not directly reflected in subgroup differences-in-AMCEs.
+A difference in effect sizes is distinct from a difference in the preferences so affected.
+We show that a difference in two (or more) subgroups' favorability toward a conojoint feature --- like a difference in willingness to support a Syrian immigrant between high and low ethnocentrism respondents --- is only reflected in the difference-in-AMCEs in very rare circumstances.
+As such, no information about the similarity of the subgroups' preferences is provided by comparisons of subgroup AMCEs, yet such comparisons are commonly made in practice.
 
 As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well but where preferences between subgroups diverge in the reference category, the difference-in-AMCEs is a misleading representation of underlying patterns of favorability.
-Yet most published conjoint studies appear to report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment.
-Ultimately AMCEs are relative, not absolute, statements about preferences so subgroup differences are also relative not absolute statements about preference heterogeneity.\footnote{For example, in a comparison of subgroup effects for Democrats and Republicans, Republicans might display a smaller effect because their preferences in the reference category are already very positive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.} There is simply no predictable inference to be drawn from subgroup causal effects to the levels of underlying subgroup opinion.
-This inferential error --- interpreting differences in the size of causal effects as descriptive differences in preferences --- appears to be widespread in published conjoint analyses.
-The root of this error is likely familiar to many researchers: it is simply a matter of regression specification for models involving interactions between categorical regressors.
-\citet{EgamiImai2018}, for example, provide an extensive discussion of the implications of this property for interpreting causal interactions between features of conjoint profiles.
+Given most published conjoint studies appear to report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment, difference-in-AMCEs should not be assumed to be interpretable as differences in subgroup preferences.\footnote{For example, in a comparison of subgroup effects for Democrats and Republicans, Republicans might display a smaller effect because their preferences in the reference category are already very positive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.} The root of this error is likely familiar to many researchers: it is simply a matter of regression specification for models involving interactions between categorical regressors.
+\citet{EgamiImai2018}, for example, provide an extensive discussion of the implications of this property for interpreting causal interactions between randomized features of conjoint profiles.
 The state of the published literature would suggest the problem remains non-obvious when applied to descriptive analysis of subgroups in conjoint designs.
 
-In what follows, we demonstrate the challenges of conjoint analysis and reminder readers of how reference category choice for profile features creates significant problems for comparing conditional AMCEs across respondent subgroups.
-We show how the use of an arbitrary reference category means the size and the direction of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features and that reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar, using examples drawn from the published political science literature (namely experiments by \citealt{HainmuellerHopkinsYamamoto2014, BallardRosaMartinScheve2016, TeeleKallaRosenbluth2018}).
-The paper then provides suggestions for improved conjoint reporting and interpretation based around two quantities of interest drawn from the factorial experimentation literature: (1) unadjusted marginal means, a quantity measuring favorability toward a given feature, and (b) an omnibus F-test, measuring differences therein.
-Newly developed software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment --- is demonstrated throughout.
+In what follows, we demonstrate the challenges of conjoint analysis and remind readers of how reference category choice for profile features creates problems for comparing conditional AMCEs across respondent subgroups.
+We show how the use of an arbitrary reference category means the size, direction, and statistical significance of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features; reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar.
+We demonstrate this with examples drawn from the published political science literature (namely experiments by \citealt{HainmuellerHopkinsYamamoto2014, BechtelScheve2013, TeeleKallaRosenbluth2018}).
+The paper then provides suggestions for improved conjoint reporting and interpretation based around two quantities of interest drawn from the factorial experimentation literature: (a) unadjusted marginal means, a quantity measuring favorability toward a given feature, and (b) an omnibus F-test, measuring differences therein.
+Software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment --- is demonstrated throughout.
 We conclude with advice for best practices in the analysis and presentation of conjoint results.
@@
 One is to assess causal effects.
-Another is preference description.\footnote{Here we use ``preference'' as \citet{HainmuellerHopkinsYamamoto2014} do: that is, as a statement of \textit{favorability} or \textit{support} for a profile, not the more narrow economic definition of a strict rank ordering of objects by favorability.} In causal inference, conjoints provide a design and analytic approach that allows researchers to understand the causal effect of a given feature on overall support for a multidimensional object, averaging across other features of the object included in the design.
+Another is preference description.\footnote{Here we use ``preference'' as \citet{HainmuellerHopkinsYamamoto2014} do: that is, as a statement of \textit{favorability} or \textit{support} for a profile, not the more narrow economic definition of a strict rank ordering of objects by favorability.} In causal inference, fully randomized conjoints provide a design and analytic approach that allows researchers to understand the causal effect of a given feature on overall support for a multidimensional object, averaging across other features of the object included in the design.
 Such inferences can be thought of as statements of the form: ``shifting an immigrant's country of origin from India to Poland increases favorability by X percentage points.'' In descriptive inference, conjoints provide information about both (a) the \textit{absolute} favorability of respondents toward objects with particular features or combinations of features, and (b) the \textit{relative} favorability of respondents toward an object with alternative combinations of features.
@@
 
-Importantly, a fully randomized conjoint design without constraints between profile features is simply a full-factorial experiment (with some cells possibly, albeit randomly, left unobserved).
-All quantities of interest relevant to the analysis of conjoint designs derive from combinations of cell means, marginal means, and the grand mean, as is common in the traditional analysis of factorial experiments.
-In a forced choice design, the \textit{grand mean} is by definition 0.5 (i.e., 50\% of all profiles shown are chosen and 50\% are not chosen).
+Analytically, a fully randomized conjoint design without constraints between profile features is simply a full-factorial experiment (with some cells possibly, albeit randomly, left unobserved).
+All quantities of interest relevant to the analysis of conjoint designs therefore derive from combinations of cell means, marginal means, and the grand mean, as in the traditional analysis of factorial experiments.
+In a forced choice conjoint design, the \textit{grand mean} is by definition 0.5 (i.e., 50\% of all profiles shown are chosen and 50\% are not chosen).
 \textit{Cell means} are the mean outcome for each particular combination of feature levels.
@@
 
-Average marginal component effects (AMCEs) depend only upon \textit{marginal means}: that is the column and row mean outcomes for each feature level averaging across all other features.
-A marginal mean describes the level of favorability toward profiles that have a particular feature level, marginalizing across all other features.
-For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities: a marginal mean of 0 indicates respondents select profiles with that feature level with probability $Pr(Y=1|X=x) = 0$ while a marginal mean of 1 indicates respondents select profiles with that feature level with probability $(Pr(Y=1|X=x)=1$.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany).
+In fully randomized designs, the average marginal component effects (AMCEs) are simply marginal effects of changing one feature level to another, all else constant.
+AMCEs therefore depend only upon \textit{marginal means}: that is the column and row mean outcomes for each feature level averaging across all other features.
+A marginal mean describes the level of favorability toward profiles that have a particular feature level, ignoring all other features.
+For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities: a marginal mean of 0 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x) = 0$ while a marginal mean of 1 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x)=1$, where $Y$ is a binary outcome and $X$ is a vector of profile features.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany).
 Instead, the marginal mean can range from the probability of co-occurrence to 1 minus that probability.
@@
 This constraint on the range of the marginal means also constrains the range of AMCEs.
-Notably, many conjoints provide features with only two levels, such as the male-versus-female candidate feature examined by \citet{TeeleKallaRosenbluth2018}.
+Notably, many conjoints provide features with only two levels, such as the male-versus-female candidate feature examined by \citet{TeeleKallaRosenbluth2018} or \citet{HainmuellerHopkinsYamamoto2014} in their conjoints on candidate choice.
 In such cases, the probability of co-occurrence is $\frac{1}{2}*\frac{1}{2} = 0.25$ bounding the AMCE for female (as opposed to male) candidates to the range $(-0.5, 0.5)$ if both candidates can have the same sex.
@@
 
-<<hainmueller_candidate_replication, dependson=c("data_hainmueller_candidate"), fig.height=6, fig.width=8, fig.cap="Replication of Hainmueller et al.
+<<hainmueller_candidate_replication, dependson=c("data_hainmueller_candidate"), fig.height=8, fig.width=10, fig.cap="Replication of Hainmueller et al.
 (2014) Candidate Experiment using AMCEs and MMs", fig.show="hold", message=FALSE>>=
-plot(
+p1 <- plot(
   cregg::cj(
@@
    estimate = "amce"
-  ), vline = 0, xlim = c(-0.4,0.4)
-)
-plot(
+  ), vline = 0
+) + 
+  ggplot2::scale_x_continuous(
+    limits = c(-0.4, 0.4), 
+    breaks = c(-0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4)
+  ) + 
+  ggplot2::geom_text(
+    aes(label = ifelse(is.na(std.error), "", sprintf("%0.2f (%0.2f)", estimate, std.error))),
+    colour = "black", 
+    size = 2,
+    position = position_nudge(y = .5)
+ ) + 
+ theme(legend.position="none")
+p2 <- plot(
   cregg::cj(
@@
    estimate = "mm"
-  ), vline = 0.5, xlim = c(0.25,0.75)
-)
+  ), vline = 0.5
+) + 
+  ggplot2::scale_x_continuous(
+    limits = c(0.1, 0.9), 
+    breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
+  ) + 
+  ggplot2::geom_text(
+    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
+    colour = "black", 
+    size = 2,
+    position = position_nudge(y = .5)
+  ) + 
+  theme(legend.position="none")
+gridExtra::grid.arrange(p1, p2, ncol=2)
 @
@@
 We ignore this distinction in the remainder of this article, as all of our results apply equally to fully randomized and to constrained designs.} This close relationship between AMCEs and marginal means is visible in Figure \ref{fig:hainmueller_candidate_replication} which presents a replication of the AMCE-based analysis of the Hainmueller et al.
-candidate experiment (upper panel) and an analogous examination of the results using marginal means (lower panel).
-Here and throughout we use visual presentation of results, but full numerical estimates including appropriate standard errors are presented in the Appendix.
+candidate experiment (left panel) and an analogous examination of the results using marginal means (right panel).
 Note, in particular, how marginal means convey information about the preferences of respondents for all feature levels while AMCEs definitionally restrict the AMCE for the reference category to zero (or undefined).
 For example, the AMCE for a candidate serving in the military is 0.09 (or a 9-percentage point) increase in favorability, reflecting marginal means for serving and non-serving candidates of 0.46 and 0.54, respectively.
-
-The AMCE is often described as an estimate of the relative favorability of profiles with counterfactual levels of a feature; for example, ``male candidates are preferred to female candidates'' \citep[6]{TeeleKallaRosenbluth2018}.
-\citet{HainmuellerHopkinsYamamoto2014} similarly describe some of the results of conjoint on preferences toward Congressional candidates:
+Similarly, the zero effect size for candidate gender reflects identical marginal means for male and female candidates (0.50 in each case).
+AMCEs in fully randomized designs are simply differences between marginal means at each feature level and the marginal mean in the reference category, ignoring other features.
+
+The AMCE is often described as an estimate of the relative favorability of profiles with counterfactual levels of a feature.
+For example, \citet{TeeleKallaRosenbluth2018} summarize their conjoint on public support ``female candidates are favored [over men] by 7.3 percentage points'' (6).
+Similarly, \citet{HainmuellerHopkinsYamamoto2014} describe some of the results of conjoint on preferences toward political candidates:
 
@@
 
-\noindent These examples make clear that despite the \textit{causal} inference potentially provided by the AMCE, the quantity of interest is frequently used to provide a characterization of a preferences that has a distinctly descriptive flavor.
+\noindent These examples make clear that despite the \textit{causal} inference potentially provided by the AMCE, the quantity of interest is frequently used to provide a characterization of a preferences that has a distinctly descriptive flavor about the relative \textit{levels} of support across profiles and also across subgroups of respondents.
 Indeed, this style of description is widespread in conjoint analyses.
-\citet{BallardRosaMartinScheve2016} interpretation their tax preference conjoint:
-
-\begin{quote}
-we find strong support for progressive preferences over federal income taxes among the American public [\dots] respondents are less likely to support a given tax plan as the tax rate on the poorest three groups increases but more likely to support an income tax policy when the tax rate on the richest two groups increases, at least to a point.
-\end{quote}
-
-\noindent This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature.
+This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature.
 A positive (negative) AMCE is read as higher (lower) favorability but it is only higher (lower) relative to whatever category serves as the baseline.
@@
 In that case, the AMCE for Evangelicals would be small and positive and the AMCEs for all other categories (including the presented reference category, ``none'') would be large and positive.
-
-<<reference_category, dependson=c("data_hainmueller_immigration"), fig.width=8, fig.height=5, fig.cap="Reference Category Diagnostic for the 'Education' Feature from Hainmueller et al.'s (2014) Immigration Experiment">>=
+More trivially, \citet{TeeleKallaRosenbluth2018} describe their comparisons about public preferences for female candidates relative to male candidates, but could have equivalent described patterns of equal size but opposite sign comparing preferences over male relative to female candidates.
+
+<<reference_category, dependson=c("data_hainmueller_immigration"), fig.width=8, fig.height=4, fig.cap="Estimated AMCEs for Levels of the `Education' Feature for Each Possible Reference Category from Hainmueller et al.'s (2014) Immigration Experiment">>=
 tmp <- amce_by_reference(hainmueller_immigration, ChosenImmigrant ~ Education, ~ Education, id = ~CaseID)
@@
   geom_vline(xintercept = 0, colour = "gray") +
-  geom_point(position = ggstance::position_dodgev(height = 0.5)) +
+  geom_point(position = ggstance::position_dodgev(height = 1)) +
   geom_errorbarh(aes(xmin = lower, xmax = upper),  
                  size = 0.2, height = 0,
-                 position = ggstance::position_dodgev(height = 0.5)) + 
-  scale_colour_discrete(guide = ggplot2::guide_legend(title = "Reference Category", ncol = 1)) +
+                 position = ggstance::position_dodgev(height = 1)) + 
+  scale_colour_discrete(
+    guide = ggplot2::guide_legend(
+      title = "Reference Category",
+      title.position = "top",
+      ncol = 2
+    )
+  ) +
   scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
@@
 
-Being a familiar analytic problem in any regression context, this choice of reference category for estimating AMCEs can seem trivial but is quite consequential.
-For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment, the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline.
-Figure \ref{fig:reference_category} shows how the estimated AMCEs for each level of education would have differed depending on that choice.
-Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline.\footnote{As another example, in \citeauthor{BallardRosaMartinScheve2016}'s tax preference experiment, the lowest level of taxation is chosen as the reference category for each feature for reasons of substantive interpretation, yet despite the substantive intuitiveness of this, favorability toward the lowest level of taxation is not necessarily higher or lower than preferences for alternative tax rates.} The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.\footnote{In \textit{constrained} conjoint designs, the choice of reference category is even more important.
+Though seemingly arbitrary, the choice of reference category for estimating AMCEs can be quite consequential.\footnote{Since this manuscript has been under review, we have been made aware of one working paper by \citet{ClaytonFerwerdaHoriuchi2018}, on the topic of immigration preferences, that correctly notes the need to address the arbitrary reference category in order to compare subgroup preferences.} For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment (again, see \ref{fig:hainmueller_candidate_replication}), the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline.
+Figure \ref{fig:reference_category} shows how the estimated AMCEs for each level of the education feature would have differed depending on that choice.
+Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline.
+The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.\footnote{In \textit{constrained} conjoint designs, the choice of reference category is even more important.
 Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature.
@@
 The choice is seemingly innocuous.
-Sometimes choices of reference category appear to be driven by substantive knowledge: on language skills of immigrants, \citet{HainmuellerHopkinsYamamoto2014} choose fluency as a baseline; on the prior trips to the US feature, ``never'' is chosen as the baseline.
-These seem sensible on face value --- it might seem less useful to define all effects relative to ``having visited many times as a tourist'' as the AMCEs then lose an immediately intuitive interpretation.
+Sometimes choices of reference category appear to be driven by substantive knowledge: on language skills of immigrants in their immigration experiment, \citet{HainmuellerHopkinsYamamoto2014} choose fluency as a baseline; on the prior trips to the US feature, ``never'' is chosen as the baseline.
 
@@
 \begin{center}
-\footnotesize
-\begin{tabular}{p{2in} p{2in} p{2in}}\toprule
-\textbf{Paper} & \textbf{Topic} & \textbf{Subgroup Comparisons} \\ \midrule
-\citet{BechtelScheve2013} & Climate agreement preferences & Environmentalism and International Reciprocity Attitudes \\ \midrule
-\citet{FranchinoZucchini2014} & Candidate preferences & Political Interest, Left-right self-placement\\ \midrule
-\citet{HainmuellerHopkinsYamamoto2014} & Immigration preferences & Ethnocentrism \\ \midrule
-\citet{HansenOlsenBech2014} & Policy preferences & Partisanship \\ \midrule
-\citet{Carlson2015} & Candidate preferences & Co-ethnicity \\ \midrule
-\citet{BansakHainmuellerHangartner2016} & Immigration preferences & Left-right self-placement, age, education, income\\ \midrule
-\citet{BallardRosaMartinScheve2016} & Tax preferences & Various\\ \midrule
-\citet{Campbelletal2016} & Candidate preferences & Partisanship \\ \midrule
-\citet{CarnesLupu2016} & Candidate preferences & Partisanship \\ \midrule
-\citet{Mummolo2016} & News selection & Various\\ \midrule
-\citet{VivyanWagner2016} & Candidate preferences & Political attitudes \\ \midrule
-\citet{MummoloNall2017} & Mobility preferences & Partisanship \\ \midrule
-\citet{BechtelGenoveseScheve2017} & Climate agreement preferences & Employment sector emissions \\ \midrule
-\citet{BechtelHainmuellerMargalit2017} & International bailout preferences & Various\\ \midrule
-\citet{GallegoMarx2017} & Labor market policy & Left-right self-placement \\ \midrule
-\citet{KirklandCoppock2017} & Candidate preferences & Partisanship \\ \midrule
-\citet{Sen2017} & Judicial candidate preferences & Partisanship \\ \midrule
-\citet{Sobolewskaetal2017} & Immigrant integration & Various \\ \midrule
-\citet{EggersVivyanWagner2018} & Candidate preferences & Sex \\ \midrule
-\citet{Hankinson2018} & Housing policy preferences & Various \\ \midrule
-\citet{OliverosSchuster2018} & Bureaucrat candidate preferences & Various \\ \midrule
-\citet{TeeleKallaRosenbluth2018} & Candidate preferences & Sex, Partisanship \\ \midrule
-\citet{Careyetal2018} & Hiring preferences & Various \\ \midrule
+\scriptsize
+\begin{tabular}{p{1.5in} p{1.5in} p{1.5in} p{1.5in}}\toprule
+\textbf{Paper} & \textbf{Journal} & \textbf{Topic} & \textbf{Subgroup Comparisons} \\ \midrule
+\citet{BechtelScheve2013} & PNAS & Climate agreement preferences & Environmentalism and International Reciprocity Attitudes \\ \midrule
+\citet{FranchinoZucchini2014} & PSRM & Candidate preferences & Political Interest, Left-right self-placement\\ \midrule
+\citet{HainmuellerHopkinsYamamoto2014} & Political Analysis & Immigration preferences & Ethnocentrism \\ \midrule
+\citet{HansenOlsenBech2014} & Politcal Behavior & Policy preferences & Partisanship \\ \midrule
+\citet{Carlson2015} & World Politics & Candidate preferences & Co-ethnicity \\ \midrule
+\citet{BansakHainmuellerHangartner2016} & Science & Immigration preferences & Left-right self-placement, age, education, income\\ \midrule
+\citet{BallardRosaMartinScheve2016} & JOP & Tax preferences & Various\\ \midrule
+\citet{Campbelletal2016} & BJPS & Candidate preferences & Partisanship \\ \midrule
+\citet{CarnesLupu2016} & APSR & Candidate preferences & Partisanship \\ \midrule
+\citet{Mummolo2016} & JOP & News selection & Various\\ \midrule
+\citet{VivyanWagner2016} & EJPR & Candidate preferences & Political attitudes \\ \midrule
+\citet{MummoloNall2017} & JOP & Mobility preferences & Partisanship \\ \midrule
+\citet{BechtelGenoveseScheve2017} & BJPS & Climate agreement preferences & Employment sector emissions \\ \midrule
+\citet{BechtelHainmuellerMargalit2017} & EJPR & International bailout preferences & Various\\ \midrule
+\citet{GallegoMarx2017} & J. European Public Policy & Labor market policy & Left-right self-placement \\ \midrule
+\citet{KirklandCoppock2017} & Political Behavior & Candidate preferences & Partisanship \\ \midrule
+\citet{Sen2017} & PRQ & Judicial candidate preferences & Partisanship \\ \midrule
+\citet{Sobolewskaetal2017} & J. Ethnic \& Migration Studies & Immigrant integration & Various \\ \midrule
+\citet{EggersVivyanWagner2018} & JOP & Candidate preferences & Sex \\ \midrule
+\citet{Hankinson2018} & APSR & Housing policy preferences & Various \\ \midrule
+\citet{OliverosSchuster2018} & CPS & Bureaucrat candidate preferences & Various \\ \midrule
+\citet{TeeleKallaRosenbluth2018} & APSR & Candidate preferences & Sex, Partisanship \\ \midrule
+\citet{Careyetal2018} & Politics, Groups, and Identities & Hiring preferences & Various \\ \midrule
 \bottomrule
@@
 \end{center}
+
 All articles in this table use subgroup conditional AMCEs to make inferences about differences in preferences between subgroups.
@@
 
-Yet the choice is consequential.
-A possibly surprising consequence of the seemingly arbitrary selection of a reference category --- and the resulting arbitrariness of both the size and direction of AMCEs --- is that it can provide highly distorted descriptive interpretation of preferences among subgroups of respondents.
+While seemingly arbitrary and innocuous, the choice of reference category can provide highly distorted descriptive interpretations of preferences among subgroups of respondents.
 This occurs when researchers examine \textit{conditional} AMCEs, wherein AMCEs are calculated separately for subgroups of respondents and those conditional estimates are directly compared \citep[13]{HainmuellerHopkinsYamamoto2014}.
-Table \ref{tab:papers} reports a list of recently published articles in political science that engage in this form of subgroup analysis.\footnote{\citet{RatkovicTingley2017} considered efficient methods for performing subgroup analyses in conjoint designs.
-Our focus here is on the narrower problem of interpreting subgroup analyses as traditionally performed using subsetting or interaction terms in a regression framework.} Given the commonly descriptive interpretations of conjoint experimental results, such subgroup analyses seem perfectly intuitive and the set of subgroups listed in the last column of Table \ref{tab:papers} contains some unsurprising covariates, such as partisanship, that are of obvious theoretical interest in almost any study of individual preferences.
-Analytically, these conditional AMCEs can be obtained either from regression estimates on respondent subgroups or through interactions between conjoint features and respondent characteristics, the details of which are unimportant for our purposes.
-
-Conditional AMCEs are not per se a problematic quantity of inference.
-Like subgroup analysis of any experiment, they convey the causal effect of an experimental factor on overall favorability among the subgroup of interest.
-Consider, for example, a two-condition party cue experiment where Democrats and Republicans are exposed to an endorsement cue from the Democratic party or no cue and opinions toward the policy serve as the outcome.
-It is sensible to imagine that effects of the cue might differ for the two groups and therefore to compare the size of cue effect among the two groups.
-Perhaps Democrats are more responsive to the Democratic party cue than are Republicans, making the causal effect larger for Democrats than Republicans.
+Conditional AMCEs convey the causal effect of an experimental factor on overall favorability among the subgroup of interest.
+Consider, for example, a two-condition candidate choice experiment where Democratic and Republican respondents are exposed to either a male or female candidate and opinions toward the candidate serve as the outcome.
+It is sensible to imagine that effects of candidate sex might differ for the two groups and therefore to compare the size of treatment between the two groups.
+Perhaps Democrats are more responsive to candidate sex than are Republicans, making the causal effect larger for Democrats than Republicans.
+When conjoint analysts engage in subgroup comparisons, they are engaging in this kind of search for heterogeneous treatment effects across subgroups, but across a much larger number of experimental factors.
+
 Discussions of conditional AMCEs in conjoint analyses often explicitly or implicitly engage in this kind of discussion comparing the size and direction of subgroup causal effects.
-If interpreted as a difference in the size of the causal effect for two groups, such comparisons are perfectly consistent with more traditional experimental analysis and a perfectly acceptable interpretation of the conjoint results.
-
-<<tkr_replication, dependson=c("data_tkr"), fig.height=5, fig.width=8, fig.cap="Replication of Teele et al. (2018) Candidate Experiment using AMCEs and MMs", fig.show="hold", message=FALSE>>=
-plot(
-  cj(
+Indeed, Table \ref{tab:papers} reports a list of recently published articles in political science that engage in this form of subgroup analysis.
+Given the common practice of descriptively interpreting conjoint experimental results, such subgroup analyses seem perfectly intuitive and the set of subgroups listed in the last column of Table \ref{tab:papers} contains some unsurprising covariates, such as partisanship, that are of obvious theoretical interest in almost any study of individual preferences.
+If interpreted as a difference in the size of the \textit{causal effect} for two groups, such comparisons are perfectly consistent with more traditional experimental analysis and a perfectly acceptable interpretation of the conjoint results.
+
+<<tkr_replication, dependson=c("data_tkr"), fig.height=4.5, fig.width=5, fig.cap="Replication of Results for `Candidate Sex' Feature from Teele et al.
+(2018) Candidate Experiment using Full Sample and Subgroup AMCEs and MMs", fig.show="hold", message=FALSE>>=
+a <- plot(
+  subset(cj(
+   tkr, 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "amce",
+  ), feature == "Candidate Sex"), 
+  xlab = NULL, feature_headers = FALSE, vline = 0, xlim = c(-0.11, 0.11), size = 2
+) + 
+  ggtitle(NULL, "Full Sample AMCEs") + 
+  scale_colour_manual("Feature", limits = "Candidate Sex", values = "black") +
+  theme(
+  	legend.position = "none",
+  	panel.border = element_blank(),
+  	axis.line.x = element_blank(),
+	axis.line.y = element_blank()
+  )
+
+b <- plot(
+  subset(cj(
+   tkr, 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "mm",
+  ), feature == "Candidate Sex"),
+  xlab = NULL, feature_headers = FALSE, vline = 0.5, xlim = c(0.39,0.61), size = 2
+) + 
+  ggtitle(NULL, "Full Sample MMs") + 
+  scale_colour_manual("Feature", limits = "Candidate Sex", values = "black") +
+  theme(
+   	legend.position = "none",
+   	panel.border = element_blank(),
+   	axis.line.x = element_blank(),
+	axis.line.y = element_blank()
+  )
+
+c <- plot(
+  subset(cj(
    tkr, 
@@
    by = ~ PartyID
-  ), vline = 0, group = "PartyID", xlim = c(-0.35, 0.35)
-) + scale_colour_manual("PartyID", limits = c("Democrat", "Republican"), values = c("Blue", "Red"))
-plot(
-  cj(
+  ), feature == "Candidate Sex"), 
+  xlab = NULL, feature_headers = FALSE, vline = 0, group = "PartyID", xlim = c(-0.11, 0.11), size = 2
+) + 
+ annotate("text", y = 1.65, x = -0.04, label = "Republicans", size = 3) + 
+ annotate("text", y = 1.3, x = 0.05, label = "Democrats", size = 3) + 
+ ggtitle(NULL, "Subgroup AMCEs") + 
+ scale_colour_manual(values=rep("black", 2)) +
+ aes(shape = PartyID) + 
+ scale_shape_manual("PartyID", limits = c("Democrat", "Republican"), values = c(15,17)) +
+ theme(
+   legend.position = "none",
+   panel.border = element_blank(),
+   axis.line.x = element_blank(),
+   axis.line.y = element_blank()
+ )
+
+d <- plot(
+  subset(cj(
    tkr, 
@@
    by = ~ PartyID
-  ), vline = 0.5, group = "PartyID", xlim = c(0.3,0.7)
-) + scale_colour_manual("PartyID", limits = c("Democrat", "Republican"), values = c("Blue", "Red"))
+  ), feature == "Candidate Sex"),
+  xlab = NULL, feature_headers = FALSE, vline = 0.5, group = "PartyID", xlim = c(0.39,0.61), size = 2
+) + 
+ ggtitle(NULL, "Subgroup MMs") + 
+ scale_colour_manual(values=rep("black", 2)) +
+ aes(shape = PartyID) + 
+ scale_shape_manual("PartyID", limits = c("Democrat", "Republican"), values = c(15,17)) +
+ theme(
+  legend.position = "none",
+  panel.border = element_blank(),
+  axis.line.x = element_blank(),
+  axis.line.y = element_blank()
+ )
+
+# combine
+gA = ggplotGrob(a)
+gB = ggplotGrob(b)
+gC = ggplotGrob(c)
+gD = ggplotGrob(d)
+gridExtra::grid.arrange(gA, gB, gC, gD, ncol = 1)
 @
@@
 For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} visually compare the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22).
-\citet{BallardRosaMartinScheve2016} make similar comparisons in their tax policy conjoint: ``While there are few strong differences in preferences for taxing the lower three income groups (the `hard work' group has slightly lower elasticities for taxing the poor), there are strong differences in preferences for taxing the rich.
-Respondents who believe luck plays a role in economic success are more strongly progressive, although preferences over taxing the \$175K--\$375K bracket are relatively flat'' (12).
-In these examples, the differences between conditional AMCEs are used as a way of descriptively characterizing differences in \textit{preferences} between the groups rather than differences in \textit{causal effects on preferences} in the groups.
-
-As a more complete example, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment separately for Democratic and Republican voters, as provided in the original paper, and the lower panel shows the results using conditional marginal means.
-Again, we opt for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.
-Respondents' preference for female candidates is very apparent in both forms of analysis.
-Yet the discrepancy between the differences in preferences (i.e., conditional marginal means) and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature in Figure \ref{fig:tkr_replication} (the second set of estimates from the top in both panels).
-The conditional AMCEs in the upper panel correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates.
-Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates).
-In reality, however, the conditional marginal means shown in the lower panel demonstrate that actually Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience.
-Democrats are much more sensitive to experience than are Republicans and important differences in preferences are apparent for extreme categories in the visualization of conditional marginal means, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.
-The selection of a reference category is therefore hugely consequential for a descriptive reading of the AMCE results.
-
-Interpreting conjoint AMCEs as measures of preferences is an inferential error.
-In a simple experiment like the party cue example just given, this kind of interpretation would be obviously flawed.
-A larger causal effect of the party cue for Democrats than Republicans does not necessarily mean that Democrats are more supportive than Republicans on average or in either condition.
-Effects are relative, not absolute, statements about preferences.
-Republicans, for example, might experience a smaller effect because their preferences in the control group are already very supportive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.
-There is simply no predictable connection between subgroup causal effects and the levels of underlying subgroup preferences.
-This inferential error --- interpreting differences in the size of causal effects as descriptive differences in preferences --- appears to be widespread in published conjoint analyses.
+\citet{BallardRosaMartinScheve2016} make similar comparisons in their tax policy conjoint: ``While there are few strong differences in preferences for taxing the lower three income groups (the `hard work' group has slightly lower elasticities for taxing the poor), there are strong differences in preferences for taxing the rich'' (12).
+In \citet{BechtelScheve2013} conjoint on support for international climate change agreements in the United States, United Kingdom, Germany, and France, they summarize their results as ``We find that individuals in all four countries largely agree on which dimensions are important and to what extent'' (13765).
+In these examples, the differences between conditional AMCEs are used as a way of descriptively characterizing differences in \textit{preferences} (i.e.
+levels of support) between the groups rather than differences in \textit{causal effects on preferences} in the groups.
+
+The selection of a reference category, while earlier an innocuous analytic decisions, becomes substantially consequential for this kind descriptive reading of conditional AMCEs.
+Most obviously, using AMCEs descriptively prevents analysts from describing levels of favorability in the reference category but also can lead to misinterpretations of patterns in preferences.
+AMCEs are relative, not absolute, statements about preferences.
+As such, there is simply no predictable connection between subgroup causal effects and the levels of underlying subgroup preferences.
+Yet analysts and their readers frequently interpret differences in conditional AMCEs as differences in underlying preferences.
 While AMCEs do provide insight into the descriptive variation in preferences within-group and across-features, and conditional AMCEs do estimate the size of causal effects of features within groups, AMCEs cannot provide direct insight into the pattern of preferences between groups because they do not provide information about \textit{absolute} levels of favorability toward profiles with each feature (or combination of features).
@@
 This additional information matters.
-Consider again the simple two-condition experiment in which the effect of a cue treatment, $x \in {0,1}$, is compared across a single two-category covariate, $z \in {0,1}$ such as Democratic or Republican self-identification.
+Consider again the simple two-condition experiment in which the effect of a male as opposed to female candidate, $x \in {0,1}$, is compared across a single two-category covariate, $z \in {0,1}$ such as Democratic or Republican self-identification.
 Subgroup regression equations to estimate effects for each group are:
@@
 \begin{align*}
-\hat{y} &= \beta_0 + \beta_1 x, \quad \forall z = 0 \\
-\hat{y} &= \beta_2 + \beta_3 x, \quad \forall z = 1
+\hat{y} &= \beta_0 + \beta_1 x + \epsilon, \quad \forall z = 0 \\
+\hat{y} &= \beta_2 + \beta_3 x + \epsilon, \quad \forall z = 1
 \end{align*}
@@
 The difference-in-AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$.
-Yet the standard AMCE-centric conjoint analysis does not present or characterize either of these quantities.
-Similarity of conditional AMCEs therefore only convey similarity of the \textit{causal effect} of the feature, but do not convey similarity of \textit{preferences} unless preferences toward profiles with the reference category are equivalent across groups.
-Given the reference category choice is typically arbitrary or driven by substantive knowledge of the levels, there is never any reason to expect that an arbitrarily selected reference category satisfies that equality assumption.
+Yet the standard AMCE-centric conjoint analysis does not present or characterize absolute favorability in the reference category.
+Similarity of conditional AMCEs only means similarity of the \textit{causal effect} of the feature across groups, not similarity of \textit{preferences} unless preferences toward profiles with the reference category are equivalent in both groups.
+Given the reference category choice is typically arbitrary or driven by substantive knowledge of the levels, there is never any reason to expect that an arbitrarily selected reference category satisfies this equality requirement.
 When using a difference-in-AMCEs comparison to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.
 
-<<bms_difference_comparison, dependson=c("data_bms"), fig.width=8, fig.height=4, fig.cap="Estimated Preference Differences between Inequity Averse and Non-Averse Respondents from Ballard-Rosa et al.
-(2016) Tax Preference Experiment for Each Possible Reference Category">>=
+To draw this example out more fully, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment for the full sample of respondents.
+The second panel shows full sample marginal means.
+The third panel shows conditional AMCEs separately for Democratic and Republican voters, as provided in the original paper and the lower panel shows the results using conditional marginal means for Democratic and Republican voters.\footnote{We opt here for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.} Respondents' preference for female candidates is very apparent in both forms of analysis in the upper two panels because the AMCE definitionally equals the difference in marginal means.
+But how do Republicans and Democrats differ in their preferences over male and female candidates?
+By requiring a reference category fixed to zero, the conditional AMCE results in the third panel suggest that there is a very large difference in favorability toward female candidates between Republican and Democratic respondents.
+In reality, however, the difference in these conditional AMCEs (0.086) reflects the true difference in favorability toward female candidates (difference: 0.045; Democrats: 0.537, Republicans: 0.492) \textit{plus} the difference in favorability toward male candidates (difference: 0.045; Democrats: 0.463, Republicans: 0.508).
+Because Democrats and Republicans actually differ in their views of profiles containing the reference (male) category, AMCEs sum the true differences in preferences for a given feature level with the difference in preferences toward the reference category.\footnote{Another example that clearly demonstrates the discrepancy between the differences in preferences and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature of this experiment (see Supporting Materials).
+The conditional AMCEs correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates.
+Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates).
+In reality, however, the conditional marginal means reveal that actually Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience.
+Democrats are much more sensitive to experience than are Republicans and important differences in preferences between the groups are apparent for very high and very low experience, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.}
+
+<<bechtel_difference_comparison, dependson=c("data_bms"), fig.width=8, fig.height=3, fig.cap="True Difference in Favorability and Implied Preference Differences between High and Low Environmentalism Respondents for `Monthly Cost' Feature from Bechtel and Scheve (2013) Climate Agreement Experiment for Each Possible Reference Category">>=
 # reported results
-main <- cj(bms[!is.na(bms$ineq_averse_dum),], chose_plan ~ taxrate6, id = ~ ID, estimate = "amce_diff", by = ~ ineq_averse_dum)
+main <- cj(bechtel[!is.na(bechtel$environmentalism),], choice_cj ~ cost_cj, id = ~ ID, weights = ~weight, estimate = "amce_diff", by = ~ environmentalism)
 main$statistic <- "Originally Reported Difference"
+## fill in baseline difference
+main[5L, ] <-  main[4L, ]
+main[5L, "level"] <- levels(bechtel$cost_cj)[1L]
+main[5L, c("estimate", "std.error", "z", "p", "lower", "upper")] <- c(0, rep(NA, 5))
 
 # AMCE differences
-amce_diffs <- do.call("rbind", lapply(levels(bms$taxrate6)[-1], function(x) {
-    tmp <- bms[!is.na(bms$ineq_averse_dum),]
-    tmp$taxrate6 <- relevel(tmp$taxrate6, x)
-    cj(tmp, chose_plan ~ taxrate6, id = ~ ID, estimate = "amce_diff", by = ~ ineq_averse_dum)
+amce_diffs <- do.call("rbind", lapply(levels(bechtel$cost_cj), function(x) {
+    tmp <- bechtel[!is.na(bechtel$environmentalism),]
+    tmp$cost_cj <- relevel(tmp$cost_cj, x)
+    cj(tmp, choice_cj ~ cost_cj, id = ~ ID, weights = ~weight, estimate = "amce_diff", by = ~ environmentalism)
 }))
@@
 # Difference in Marginal Means
-mm_diff <- cj(bms, chose_plan ~ taxrate6, id = ~ ID, estimate = "mm_diff", by = ~ ineq_averse_dum)
+mm_diff <- cj(bechtel, choice_cj ~ cost_cj, id = ~ ID, weights = ~weight, estimate = "mm_diff", by = ~ environmentalism)
 mm_diff$statistic <- "Difference in MMs"
@@
 ggplot(diffs, aes(x = estimate, y = level, group = statistic, colour = statistic, fill = statistic, shape = statistic)) +
-  geom_vline(xintercept = 0, colour = "black") +
+  geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
   geom_point(position = ggstance::position_dodgev(height = 0.25), size=2) +
@@
                      guide = ggplot2::guide_legend(title = "Statistic")) +
-  scale_x_continuous(limits = c(-.4,.4), oob = scales::rescale_none) +
+  scale_x_continuous(limits = c(-0.1,0.1), oob = scales::rescale_none) +
   ylab("") +
-  xlab("Estimated Difference between Inequity Averse and Non-Averse Respondents") + 
+  xlab("Estimated Preference Difference between High and Low Environmentalism Respondents") + 
   theme_minimal() + 
@@
 
-We can see this bias clearly in a reanalysis of \citeauthor{BallardRosaMartinScheve2016}'s tax preference experiment.
-Figure \ref{fig:bms_difference_comparison} shows an analysis for the feature capturing the tax rate for the highest earners (those over \$375,000 per year) replicating a portion of the results they present comparing inequity averse and non-averse respondents \citet[9 figure 2]{BallardRosaMartinScheve2016}.
-The original analysis was presented as conditional AMCEs for the two subgroups with inequity averse respondents having positive AMCEs for all tax levels (relative to 5\% as the reference category) and AMCEs for non-averse respondents being largely indistinguishable from zero.
-Figure \ref{fig:bms_difference_comparison} presents the implied difference-in-AMCEs from the original analysis as round black dots, demonstrating the substantial and positive \textit{apparent} differences between the two groups.
-The black diamonds show the true differences in marginal means between the two groups.
-The gray dots represent the alternative differences-in-AMCEs that could have been generated from alternative choices of reference category using the same data.
-Because respondents in the two groups actually have substantially different preferences over the reference category 5\% tax rate (inequity averse respondents are much less favorable toward this rate than non-averse respondents) differences-in-AMCEs make it seem like inequity averse respondents are much \textit{more} favorable toward 15\% and 25\% tax rates than non-averse respondents, when in actuality averse respondents are \textit{less} favorable toward the 15\% tax rate than non-averse respondents and the two groups have largely similar views of a 25\% tax rate.
-Not only does the difference-in-AMCEs overestimate group differences for very high tax rates (35\%, 45\%, 55\%) but the difference-in-AMCEs flips the true direction of group differences for lower rates.
-The authors correctly read their data as showing ``support for more progressive preferences is correlated with concern over societal inequality'' \citep[9]{BallardRosaMartinScheve2016} but for the wrong reason: inequity averse and non-averse respondents are similarly favorable toward middling tax rates and diverge in their views of very high and very low rates for high earners.
-
-It is worth highlighting two further features in Figure \ref{fig:bms_difference_comparison}.
-First, the alternative differences-in-AMCEs estimates vary mechanically around the difference in marginal means, as the reference category varies.
+We can also see this bias clearly in a reanalysis of \citeauthor{BechtelScheve2013}'s four-country climate change agreement experiment.
+Figure \ref{fig:bechtel_difference_comparison} shows an analysis for the feature capturing the monthly household cost for a potential international climate agreement, replicating a portion of the results they present comparing high- and low-environmentalism respondents (pooling across countries) \citet[13767 figure 4]{BechtelScheve2013}.
+The original analysis was presented as conditional AMCEs for the two subgroups with 28 Euro per month as the reference category.
+Conditional AMCEs for both groups were presented as negative with conditional AMCEs for low-environmentalism respondents being more negative than the conditional AMCEs for high-environmentalism respondents at every feaure level.
+This implies positive differences in favorability toward each monthly cost between high- and low-environmentalism respondents.
+Figure \ref{fig:bechtel_difference_comparison} presents the implied difference-in-AMCEs from the original analysis as black circles, demonstrating the substantial and positive \textit{apparent} differences between the two groups.
+For example, the difference-in-AMCEs for the 56 Euro per month level (incorrectly) implies that high-environmentalism respondents are \textit{more} favorable toward a 56 Euro per month household cost of an agreement than are low-environmentalism respondents.
+Yet the opposite is actually true: high environmentalism respondents are less favorable toward this option than low environmentalism respondents.
+By using the 28 Euro per month level as the reference category, the original analysis implies that preferences are identical between the two groups when in reality high-environmentalism respondents are much less favorable toward a 28 Euro per month cost than low-environmentalism respondents.
+The black diamonds in Figure \ref{fig:bechtel_difference_comparison} show these true differences in favorability as marginal means for the two groups.
+
+Furthermore, the gray dots in Figure \ref{fig:bechtel_difference_comparison} represent the alternative differences-in-AMCEs that \textit{could have been generated} from alternative choices of reference category using the same data.
+Not only is it possible for reference categories choice to significantly color the apparent size of differences between subgroup, that choice can also impact the direction and statistical significance of subgroup differences.
+An analyst could easily choose a reference category that presents differences between these two group as large and positive, small and positive, small and negative, large and negative, or negligible.
+The original analysis (again, black circles) happens to show large and positive differences between the groups.
+
+It is worth highlighting two further features in Figure \ref{fig:bechtel_difference_comparison}.
+First, the alternative differences-in-AMCEs estimates vary mechanically around the difference in marginal means, as the reference category varies (just as the AMCE estimates did in Figure \ref{fig:reference_category}).
 The difference between marginal means for two groups are always fixed in the data, so the differencing of subgroup AMCEs is merely an exercise is centering those differences at arbitrary points along the range of observed differences in marginal means.
-Differences-in-AMCEs for a given feature level are therefore necessarily sometimes positive and sometimes negative, depending on the reference category used in estimating them.
+Differences-in-AMCEs for a given feature level must therefore necessarily sometimes be positive and sometimes be negative, depending on the reference category used in estimating them.
 The direction of the difference per se conveys no information about underlying pattern of preferences in the two groups.
-Yet the choice of reference category --- likely unintentionally --- resulted in the most extreme, positive difference-in-AMCEs that could be estimated from the data but alternative reference categories could have conveyed different, equally incorrect insights.
 
 Second, and more practically, because there is no category for which the preferences of the two subgroups in this example are identical, no choice of reference category would have led to inferences from differences-in-AMCEs that accurately reflect the underlying difference in preferences.
-Even in the 25\% tax rate category, the difference between the two groups is slightly negative.
-Were there a category for which preferences were equivalent, that could be sensibly chosen as the reference category in order to be able to interpret differences-in-AMCEs as differences in preferences.
-There is never any guarantee, however, that such a reference category exists in any given experimental dataset.
+Even in the 84 Euro per month level, the difference between the two groups is slightly positive.
+Were there a category for which subgroup preferences were exactly equal, that could be sensibly chosen as the reference category in order to be able to interpret differences-in-AMCEs as differences in preferences.
+But there is never any guarantee, however, that such a reference category exists in any given experimental dataset.
 If multiple subgroup analyses are performed, it is unlikely the same reference category would work well across all analyses, making consistent interpretation difficult.
-As such, even if the AMCEs are similar, it does not necessarily mean that \textit{preferences} are similar; if AMCEs are dissimilar, it does not necessarily mean that preferences differ.
-
-Ultimately, it is important to note that because conjoint analysis generates a sparse feature matrix (where there is never any guarantee that a particular combination of feature levels is observed in the data), it is also not possible to empirically select an appropriate set of reference categories using the data.
+And because conjoint analysis generates a sparse feature matrix (where there is never any guarantee that a particular combination of feature levels is observed in the data), it is also not possible to empirically select an appropriate set of reference categories using the observed data.
 It is impossible to know which cell --- of the tens of thousands in the design --- is the best choice of reference.
-This is because while it might seem possible to select a \textit{marginally} appropriate reference category (i.e., one where preferences are similar with respect to a given feature), preferences toward that reference category may differ across other dimensions in the analysis.
-And it is furthermore possible that there is no such cell for which preferences are identical in the two groups; such a cell may exist, but there is no reason to expect that it should exist in any given application.
+Indeed it is possible that there is no such cell for which preferences are identical in the two groups; such a cell may exist, but there is no reason to expect that it should exist in any given application or that it would happen to be observed.
 Thus, there is no way to use conditional AMCEs or differences between those conditional AMCEs to convey the underlying similarity or differences in preferences across sample subgroups.
@@
 
-We have shown that subgroup analyses of conjoint designs frequently entail the use of difference-in-AMCE comparisons and we have also shown that such analyses, counterintuitively, do not demonstrate differences in preferences between groups due the near-impossibility of selecting a non-arbitrary reference category against which to estimate AMCEs.
+We have shown that subgroup analyses of conjoint designs frequently entail the use of difference-in-AMCE comparisons and we have also shown that such analyses, perhaps counterintuitively, do not demonstrate differences in preferences between groups due the near-impossibility of selecting a non-arbitrary reference category against which to estimate AMCEs.
 Thus the choice of reference category --- while seemingly irrelevant --- has dramatic inferential consequences in conjoint analyses.
 Here we provide a more complete example, demonstrating the full extent of this problem for interpretation of conjoint results and present alternative forms of analysis that more robustly convey subgroup preferences and the differences (if any) between them.
+Specifically, we show how reference category changes can lead to visual patterns of differences-in-AMCEs that provide strikingly different interpretations.
+We then show how to visualize and formally compare subgroup marginal means using simple means comparisons tests to avoid this problem.
+Finally, we demonstrate how to use nested model comparison tests to formally test for omnibus differences between groups.
+
 Consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which show the exact same analysis (comparing AMCEs for high and low ethnocentrism respondents) on the same experimental data from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment.
@@
 
-<<hainmueller_mm_by_ethnocentrism, dependson=c("data_hainmueller_immigration"), fig.height = 14, fig.width=10, fig.cap="Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment", message=FALSE>>=
-mm_by_ethnocentrism <- cj(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry, id = ~ CaseID, estimate = "mm", by = ~ ethnocentrism_split)
-plot(mm_by_ethnocentrism,
-     group = "ethnocentrism_split",
-     legend_title = "Ethnocentrism",
-     vline = 0.5,
-     xlim = c(0.2,0.8)) +
-  scale_colour_manual("Ethnocentrism", limits = c("high", "low"), values = c("Red", "Blue"))
-@
-
 <<hainmueller_mm_diffs, dependson=c("data_hainmueller_immigration"), fig.height = 14, fig.width=10, fig.cap="Differences in Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment", message=FALSE>>=
@@
                           by = ~ ethnocentrism_split)
-plot(mm_by_ethnocentrism, vline = 0, xlim = c(-0.3,0.3)) +
-  scale_colour_manual("feature", values = rep("Black", 9))
-@
-
-Alternatively presenting subgroup differences using conditional marginal means (as in Figure \ref{fig:hainmueller_mm_by_ethnocentrism}) provides the intended descriptive comparison of subgroup preferences.
+plot(mm_by_ethnocentrism, vline = 0, xlim = c(-0.3,0.3), xlab = "Estimated Difference in Marginal Means") +
+  scale_colour_manual("feature", values = rep("Black", 9)) +
+  ggplot2::theme(legend.position = "none")
+@
+
+Alternatively presenting subgroup differences using conditional marginal means (as in Figure \ref{fig:hainmueller_mm_diffs}) provides the intended descriptive comparison of subgroup preferences.
 Each dot and error bar represents the conditional marginal mean (and its standard error) for high ethnocentrism (in red) and low ethnocentrism (in blue) respondents.
@@
 None of the level-specific differences in conditional marginal means are statistically distinguishable from zero.
-Were we interested in an omnibus tests of whether any of these differences were non-zero, we could perform a nested model comparison of two equations: (a) one estimating only marginal effects of the ``Language Skills'' feature, and (b) the same model with additional interactions between the subgrouping covariate and the features.
-The resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: \Sexpr{sprintf("F(%d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_language$Df[2], hainmueller_anova_language$F[2], hainmueller_anova_language$"Pr(>F)"[2])}.
+Were we interested in an omnibus tests of whether any of these differences were non-zero, we could perform a nested model comparison of two equations: (a) one estimating only marginal effects of the ``Language Skills'' feature levels, and (b) the same model with additional interactions between the subgrouping covariate and the feature levels.
+The test compares the sum of squared residuals for the two equations.
+
+To make this concrete, for a feature with four levels (one treated as a reference category), the first (restricted) equation would be:
+
+\begin{equation}\label{eq:restricted}
+Y = \beta_0 + \beta_1 Level_1 + \beta_2 Level_2 + \beta_3 Level_3 + u
+\end{equation}
+
+\noindent The second (unrestricted) equation would allow for interactions between feature levels and the subgroup identifier:
+
+\begin{equation}\label{eq:unrestricted}
+\begin{split}
+Y = & \beta_0 + \beta_1 Level_1 + \beta_2 Level_2 + \beta_3 Level_3 + \beta_4 Group + \\
+& \beta_5 Level_1 * Group + \beta_6 Level_2 * Group + \beta_7 Level_3 * Group + u
+\end{split}
+\end{equation}
+
+\noindent While Equation \ref{eq:restricted} imposes the constraint that $\beta_4 = \beta_5 = \beta_6 = \beta_7 = 0$, Equation \ref{eq:unrestricted} allows for subgroup differences in favorability.
+The nested model comparison allows us to test the joint null hypothesis that there are no differences between the subgroups in any of the feature levels.
+This entails computing an F-statistic:
+
+\begin{equation}
+F = \dfrac{\dfrac{SSR_{Restricted} - SSR_{Unrestricted}}{r}}{\dfrac{SSR_{Unrestricted}}{n - k - 1}}
+\end{equation}
+
+\noindent where $SSR_{Restricted}$ is the sum of squared residuals for Equation \ref{eq:restricted}, $SSR_{Unrestricted}$ is the sum of squared residuals for Equation \ref{eq:unrestricted}, where $r$ is the number of restrictions (in the above example, 4), $n$ is the number of cases, and $k$ is the number of feature levels in the unrestricted model.
+Note that this test is not sensitive to reference category used in the regression
+
+For the \citeauthor{HainmuellerHopkinsYamamoto2014} language feature, the resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_language$Df[2], hainmueller_anova_language[["Resid.
+Df"]][1], hainmueller_anova_language$F[2], hainmueller_anova_language$"Pr(>F)"[2])}.
 We could repeat such pairwise comparisons or omnibus comparisons for each feature in the design.
@@
 A further advantage of this plot is that unlike displays of conditional AMCEs, differences in conditional marginal means communicate subgroup differences for all feature levels including the reference categories.
-This display makes readily clear what was only indirectly apparent in Figure \ref{fig:hainmueller_mm_by_ethnocentrism}: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.
-
-<<nested_model, dependson=c("data_hainmueller_immigration"), eval=TRUE, echo=FALSE>>=
+This display makes readily clear what was only indirectly apparent in Figure \ref{fig:hainmueller_mm_diffs}: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.
+
+<<hainmueller_all_diffs, dependson=c("data_hainmueller_immigration"), eval=TRUE, echo=FALSE>>=
 hainmueller_anova_all <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Gender + Job*Education + LanguageSkills + CountryOfOrigin*ReasonForApplication + JobExperience + JobPlans + PriorEntry, id = ~ CaseID, by = ~ ethnocentrism_split)
@@
 
+<<bechtel_anova, dependson=c("data_bechtel"), eval=TRUE, echo=FALSE>>=
+#bechtel_anova_environmentalism <- cj_anova(subset(bechtel, !is.na(environmentalism)), choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, id = ~ ID, by = ~ environmentalism)
+#bechtel_anova_reciprocity <- cj_anova(subset(bechtel, !is.na(reciprocity)), choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, id = ~ ID, by = ~ reciprocity)
+bechtel_anova_country <- cj_anova(subset(bechtel, !is.na(country)), choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, id = ~ ID, by = ~ country)
+bechtel_anova_country_cost <- cj_anova(subset(bechtel, !is.na(country)), choice_cj ~ cost_cj, id = ~ ID, by = ~ country)
+@
+
 As before, we can perform an omnibus tests for the presence of any subgroup differences across all features, again using nested model comparison of two equations: (a) one estimating only effects of the features, and (b) the same model with additional interactions between the subgrouping covariate and all features.
-The result of that test for differences by ethnocentrism from the immigration experiment is: \Sexpr{sprintf("F(%d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_all$Df[2], hainmueller_anova_all$F[2], hainmueller_anova_all$"Pr(>F)"[2])}, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.
-This kind of test can also be used to assess heterogeneity across conjoint features.
+The result of that test for differences by ethnocentrism from the immigration experiment is: \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_all$Df[2], hainmueller_anova_all[["Resid.
+Df"]][1], hainmueller_anova_all$F[2], hainmueller_anova_all$"Pr(>F)"[2])}, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.
+By contrast, \citet{BechtelScheve2013} argue in their cross-country conjoint examining climate change agreements ``that individuals in all four countries largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}.
+Yet a nested model comparisons shows the countries do differ in their preferences \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country$Df[2], bechtel_anova_country[["Resid.
+Df"]][1], bechtel_anova_country$F[2], bechtel_anova_country$"Pr(>F)"[2])}.
+This cross-country variation is largely driven by differences in sensitivity to monthly household costs feature, \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country_cost$Df[2], bechtel_anova_country_cost[["Resid.
+Df"]][1], bechtel_anova_country_cost$F[2], bechtel_anova_country_cost$"Pr(>F)"[2])}, with the United Kingdom and United States being more cost sensitive than Germany and France as is plainly visible in a plot of marginal means by country (see SI).
+
+This kind of nested model comparison test can also be used to assess heterogeneity across conjoint features \citep[see also][]{EgamiImai2018}.
 For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9).
@@
 We suggest that conjoint analyses should report not only average marginal component effects (AMCEs) but also descriptive quantities that better convey underlying preferences over profile features and better convey subgroup differences in those preferences.
-Our intention here is not to substantively undermine any previous set of results but instead to urge researchers moving forward to demonstrate considerable caution in how they design, analyze, and present the results of these types of experiments.
+Our intention here is not to substantively undermine any previous set of results but instead to urge researchers moving forward to demonstrate considerable caution in how they design, analyze, and present the results of these types of descriptive experiments.
 We have relatively straightforward and hopefully uncontroversial advice for how analysts of conjoint experiments should proceed:
@@
 \item Exercise caution when explicitly or implicitly interpreting differences-in-AMCEs across subgroups.
-While that quantity conveys the difference in effects of a change in a given feature, heterogeneous effects do not necessarily mean different underlying preferences.
-Differences-in-AMCEs are almost always a biased estimate (of unknown sign and direction) of the difference in underlying preferences.
+Differences-in-AMCEs are differences in effect sizes for subgroups, not statments about the relative favorability of the subgroups toward profiles with a feature.
+Heterogeneous effects do not necessarily mean different underlying preferences.
 If differences in AMCEs are reported, the choice of reference categories should be discussed explicitly and diagnostics should be provided to justify it.
@@
 
-The most basic thing that can be learned about the distribution of $Y$ is the expected value, $E[Y]$, or \textit{grand mean} (in the parlance of factorial experiments).
+The most basic thing that can be estimated about the distribution of $Y$ is the expected value, $E[Y]$, or \textit{grand mean} (in the parlance of factorial experiments).
 We can think of this quantity in terms of the survey implementation process (namely, respondents, tasks, and profiles) or as a simple function of the resulting data:
@@
 
-In an experiment where $N > C$ (the number of observations is larger than the number of cells) due to a large sample, or few factors, or levels of each factor, or both (or both of these design characteristic), a sensible next quantity of interest is the \textit{cell mean}: $E[Y|\vec{X} = \vec{x}]$, which in a conjoint simply measures the mean favorability toward a particular profile, $\vec{x}$.
+In a \textit{full factorial} experiment where $N > C$ (the number of observations is larger than the number of cells) due to a large sample, or few factors, or levels of each factor, or both (or both of these design characteristics), a sensible next quantity of interest is the \textit{cell mean}: $E[Y|\vec{X} = \vec{x}]$, which in a conjoint simply measures the mean favorability toward a particular profile, $\vec{x}$.
 An effort to actually estimate this quantity will, however, become obviously intractable when one recognizes that the number of observations in a typical conjoint is much lower the number of feasible profiles ($N \ll C$).
@@
 It is at this point that the quantities of interest in a conjoint can become confusing.
-In a typical experiment where $N > C$, these pairwise differences of means are the standard estimator for a causal effect.
+In a typical experiment where $N > C$, these pairwise differences of means are the standard estimator for a causal effect (the estimand being the causal effect on favorability of changing from one profile to another).
 For example, we might be interested in the effect on $Y$ of changing the value of one feature to another theoretically interesting value of that feature, holding all other feature values in the profile constant:
@@
 In the factorial experiments literature, this conditional mean is called the \textit{marginal mean} (as it lies at the margins of a tabular presentation cell means for the complete design).
-The uniform sampling of cells in the design means that this is quantity can be estimated by the simple mean of $Y \forall X_f = x_f$.
+For example, the following 2x3 factorial design contains 6 cell means ($2*3$), 1 grand mean, and five marginal means ($2+3$, one for each level of each factor):
+
+\begin{center}
+\begin{tabular}{lccc}\toprule
+ & $A = 1$ & $A = 2$ & \\ \midrule
+$B = 1$ & $\bar{Y}_{A=1, B=1}$ & $\bar{Y}_{A=2, B=1}$ & $E[Y|B=1]$ \\
+$B = 2$ & $\bar{Y}_{A=1, B=2}$ & $\bar{Y}_{A=2, B=2}$ & $E[Y|B=2]$ \\
+$B = 3$ & $\bar{Y}_{A=1, B=3}$ & $\bar{Y}_{A=2, B=3}$ & $E[Y|B=3]$ \\ \midrule
+ & $E[Y|A=1]$ & $E[Y|A=2]$ & $E[Y]$ \\ \bottomrule
+\end{tabular}
+\end{center}
+
+The uniform sampling of cells in the design means that this is quantity can be estimated by the simple mean of $Y \forall X_f = x_f$.\footnote{In unbalanced designs where the probability of being in a given cell is not uniform across cells, there is sometimes a distinction made between \textit{descriptive} marginal means that equally weight observations and \textit{design} marginal means that equally weight cells in the design.
+Given conjoint designs generally do not allow for the observation of cell means, the distinction is not relevant and we refer to \textit{descriptive} marginal means simply as ``marginal means.''}
+
 Were a constrained conjoint design used where some feature combinations were impossible, the marginal means would only be intelligible in the fractions of the design where all cells are observed.\footnote{Practically, the random sampling of cells does not need to be uniform; over- and under-representation of cells is possible.
@@
  & $A = 1$ & $A = 2$ & \\ \midrule
-$B = 1$ & $Y_{A=1, B=1}$ & $Y_{A=2, B=1}$ & $E[Y|B=1]$ \\
-$B = 2$ & $Y_{A=1, B=2}$ & $Y_{A=2, B=1}$ & $E[Y|B=2]$ \\
-$B = 3$ & $Y_{A=1, B=3}$ & -- & $E[Y|B=3]$ \\ \midrule
+$B = 1$ & $\bar{Y}_{A=1, B=1}$ & $\bar{Y}_{A=2, B=1}$ & $E[Y|B=1]$ \\
+$B = 2$ & $\bar{Y}_{A=1, B=2}$ & $\bar{Y}_{A=2, B=2}$ & $E[Y|B=2]$ \\
+$B = 3$ & $\bar{Y}_{A=1, B=3}$ & -- & $E[Y|B=3]$ \\ \midrule
  & $E[Y|A=1]$ & $E[Y|A=2]$ & $E[Y]$ \\ \bottomrule
@@
 But they would not be able to so for feature $A$ without either (a) an explicit caveat that the comparison is of dissimilar subsets of profiles along dimension $B$ or (b) calculating marginal means over only the completely observable\footnote{Note that what matters here is \textit{observability}, not whether any given cell is actually observed.
-We know from above that most cells will be unobserved even in a uniformly sampled, unconstrained design.} portion of the feature space.
+We know from above that most cells will be unobserved even in a uniformly sampled, unconstrained design.} portion of the feature space due to the curse of dimensionality.
 
 For the common \textit{descriptive} use of conjoint designs to measure preferences over multi-dimensional objects, these marginal means alone are of direct interest.
-They express favorability on the scale of the outcome over alternative values of each feature.
+They express favorability on the scale of the outcome over alternative values of each feature independent of the features in the design.\footnote{They do not necessarily convey favorability in an absolute sense.
+A high marginal mean for a given feature does not imply that the sample prefers that feature in an absolute sense.
+Instead, favorability has to be understood in light of the features presented to respondents.
+This is the innovation in conjoints; rather than asking respondents whether they will support a Mormon candidate (for example), we can infer their favorability toward a Mormon candidate in light of other candidate characteristics they may consider.
+Still our design may not contain all such features, so caution is needed in drawing typical public opinion inferences from these marginal means.}
 
@@
 Because feature combinations (i.e., the profiles) are randomly constructed and randomly observed from all possible combinations, the distribution of other non-focal features is, in expectation, is independent of the focal feature, thus identical across all levels of the focal feature, and therefore ignorable.
-A typical causal effect of interest is therefore the difference in marginal means across two levels of a feature.
+
+A typical causal effect of interest is therefore the difference in marginal means across two levels of a feature (i.e., the marginal effect of a change in a feature's levels).
 For an unconstrained design, this difference is the \textit{average marginal component effect} (AMCE) defined by \citet{HainmuellerHopkinsYamamoto2014}.
@@
 First, \citeauthor{HainmuellerHopkinsYamamoto2014} allow the joint distribution of features used in calculating the difference of marginal means to be arbitrary.
-This is meant to accommodate the weighting of effects to reflect the real-world distribution of feature combinations (e.g., down-weighting African American Republican political candidates given their rarity in real-world politics) but in practice this is uncommon.
+This is meant to accommodate the weighting of marginal means to reflect the real-world distribution of feature combinations (e.g., down-weighting African American Republican political candidates given their rarity in real-world politics).
+Their definition of an AMCE allows for arbitrary weighting, but in practice this is uncommon.
 
@@
 The difference $E[Y|B=2]-E[Y|B=1]$ marginalizes over the full set of levels of $A$ but $E[Y|B=3]-E[Y|B=1]$ marginalizes only over case where $A=1$.
+Thus these two marginal effects reflect different subsets of the data and different combinations of values of $A$.
+
 \citeauthor{HainmuellerHopkinsYamamoto2014} allow for these two differences to be presented as the AMCE despite the fact that the quantities marginalize over distinct subsets of the design.
+Indeed, their definition of AMCE for constrained designs diverges from the intuitive marginal effect to instead define the AMCEs for levels of $B$ as an average of marginal effects of $B$ over subsets of $A$ and the AMCEs for levels of $A$ as averages of the marginal effects of $A$ over subsets of $B$ (again, weighting these marginal effects arbitrarily).
 For example, if feature $A$ is race ${Caucasian, African American}$ and feature $B$ is religion ${Evangelical, Catholic, Jewish}$.
 In \citeauthor{HainmuellerHopkinsYamamoto2014}'s notation, the AMCE of a candidate being Jewish relative to being Evangelical Christian is defined only for Caucasian candidates, while the AMCE of being Catholic is defined for both African American and Caucasian candidates.
-There is nothing inherently problematic about that but, as noted earlier, it requires either being clear about what features are being marginalized over or an analysis of only the complete and comparable subset of the design.
-So, researchers using such designs may prefer to not present the AMCE of being Jewish together with the other results as it does not draw upon the complete set of feature combinations used in other portions of the analysis.
+They present these subset marginal effects as the sample AMCEs even though they are not defined for the whole sample.
+There is nothing inherently problematic about that but, as noted earlier, it requires either being clear about what features are being marginalized over for each AMCE or an analysis of only the complete and comparable subset of the design (i.e., partitioning the design to form two complete, overlapping experimental designs).
+So, the researcher in this example may prefer to not present the AMCE of being Jewish together with the other results as it does not draw upon the complete set of feature combinations used in other portions of the analysis.
 
@@
 )
+@
+
+\clearpage
+
+<<hainmueller_immigration_amce_appendix_split, dependson=c("data_hainmueller_immigration"), fig.height=4, fig.width=8>>=
+plot(
+  rbind(
+    within(cj(
+      subset(hainmueller_immigration, constraint1constrained), 
+      ChosenImmigrant ~ CountryOfOrigin + ReasonForApplication,
+      id = ~ CaseID,
+      estimate = "mm"
+    ), Constraint <- "Constrained"),
+    within(cj(
+      subset(hainmueller_immigration, constraint1unconstrained), 
+      ChosenImmigrant ~ CountryOfOrigin + ReasonForApplication,
+      id = ~ CaseID,
+      estimate = "mm"
+    ), Constraint <- "Unconstrained")
+  ), vline = 0.5
+) + facet_wrap(~Constraint)
+
+plot(
+  rbind(
+    within(cj(
+      subset(hainmueller_immigration, constraint2constrained), 
+      ChosenImmigrant ~ Job + Education,
+      id = ~ CaseID,
+      estimate = "mm"
+    ), Constraint <- "Constrained"),
+    within(cj(
+      subset(hainmueller_immigration, constraint2unconstrained), 
+      ChosenImmigrant ~ Job + Education,
+      id = ~ CaseID,
+      estimate = "mm"
+    ), Constraint <- "Unconstrained")
+  ), vline = 0.5
+) + facet_wrap(~Constraint)
 @
@@
   cj(
-   na.omit(hainmueller_immigration), 
+   subset(hainmueller_immigration, !is.na(ethnocentrism_split)), 
    ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication,
@@
    h0 = 0.5,
-   by = ~ethnocentrism_split
+   by = ~ ethnocentrism_split
   ), vline = 0.5, group = "ethnocentrism_split"
@@
 
+\section{Bechtel and Scheve (2013) Climate Agreement Experiment}
+
+<<bechtel_amce>>=
+cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "amce")
+@
+
+<<bechtel_mm>>=
+cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "mm")
+@
+
+<<bechtel_subgroup_mm>>=
+cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, by = ~ country, estimate = "mm")
+plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, by = ~ country, estimate = "mm"), group = "BY", vline = 0.5)
+@
+
+<<bechtel_subgroup_amce>>=
+cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, by = ~ country, estimate = "amce")
+plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, by = ~ country, estimate = "amce"), group = "BY", vline = 0)
+@
+
+<<bechtel_subgroup_amce_country_anova>>=
+cj_anova(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, id = ~ ID, by = ~ country)
+@
+
+<<bechtel_subgroup_amce_environmentalism>>=
+plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "amce", by = ~ environmentalism), group = "BY", vline = 0)
+plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "mm", by = ~ environmentalism), group = "BY", vline = 0.5)
+@
+
+<<bechtel_reciprocity_reference>>=
+# ``Individuals who pretreatment exhibit reciprocal behavior [...] are almost twice as sensitive to both the number of countries participating and the proportion of emissions represented than individuals who do not'' (13768).
+This sensitivity is accurately stated but the use of conditional AMCEs implies that the subgroup difference is due to differences in favorability toward agreements involving 20 countries and differing opinions over agreements with 80 or 160 countries, while in reality the differences lie in 20-country and 160-country agreements and the groups do not differ in their favorability toward 80-country agreements at all.
+plot(cj(bechtel, choice_cj ~ ctries_cj + emissions_cj, weights = ~ weight, id = ~ ID, estimate = "mm", by = ~ reciprocity), group = "BY", vline = 0.5)
+@
+
+<<bechtel_subgroup_amce_reciprocity>>=
+plot(
+  cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, 
+	 weights = ~ weight, id = ~ ID, estimate = "amce", by = ~ reciprocity
+  ), 
+group = "BY", vline = 0)
+
+plot(
+  cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj,
+     weights = ~ weight, id = ~ ID, estimate = "mm", by = ~ reciprocity
+  ),
+group = "BY", vline = 0.5)
+@
+
+\clearpage
+
 \section{Teele et al. (2018) Candidate Experiment}

### 2019-04-11 manuscript.tex
add in Bechtel and Scheve example; update figures; edit

@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_replication-1} 
-\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_replication-2} \caption[Replication of Hainmueller et al]{Replication of Hainmueller et al.
+\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_replication-1} \caption[Replication of Hainmueller et al]{Replication of Hainmueller et al.
 (2014) Candidate Experiment using AMCEs and MMs}\label{fig:hainmueller_candidate_replication}
@@
 In that case, the AMCE for Evangelicals would be small and positive and the AMCEs for all other categories (including the presented reference category, ``none'') would be large and positive.
+More trivially, \citet{TeeleKallaRosenbluth2018} describe their comparisons about public preferences for female candidates relative to male candidates, but could have equivalent described patterns of equal size but opposite sign comparing preferences over male relative to female candidates.
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/reference_category-1} \caption[Reference Category Diagnostic for the 'Education' Feature from Hainmueller et al.'s (2014) Immigration Experiment]{Reference Category Diagnostic for the 'Education' Feature from Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:reference_category}
+\includegraphics[width=\maxwidth]{figure/reference_category-1} \caption[Estimated AMCEs for Levels of the `Education' Feature for Each Possible Reference Category from Hainmueller et al.'s (2014) Immigration Experiment]{Estimated AMCEs for Levels of the `Education' Feature for Each Possible Reference Category from Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:reference_category}
 \end{figure}
@@
 
-Yet the choice is consequential.
-A possibly surprising consequence of the seemingly arbitrary selection of a reference category --- and the resulting arbitrariness of both the size and direction of AMCEs --- is that it can provide highly distorted descriptive interpretation of preferences among subgroups of respondents.
+While seemingly arbitrary and innocuous, the choice of reference category can provide highly distorted descriptive interpretations of preferences among subgroups of respondents.
 This occurs when researchers examine \textit{conditional} AMCEs, wherein AMCEs are calculated separately for subgroups of respondents and those conditional estimates are directly compared \citep[13]{HainmuellerHopkinsYamamoto2014}.
-Table \ref{tab:papers} reports a list of recently published articles in political science that engage in this form of subgroup analysis.\footnote{\citet{RatkovicTingley2017} considered efficient methods for performing subgroup analyses in conjoint designs.
-Our focus here is on the narrower problem of interpreting subgroup analyses as traditionally performed using subsetting or interaction terms in a regression framework.} Given the commonly descriptive interpretations of conjoint experimental results, such subgroup analyses seem perfectly intuitive and the set of subgroups listed in the last column of Table \ref{tab:papers} contains some unsurprising covariates, such as partisanship, that are of obvious theoretical interest in almost any study of individual preferences.
-Analytically, these conditional AMCEs can be obtained either from regression estimates on respondent subgroups or through interactions between conjoint features and respondent characteristics, the details of which are unimportant for our purposes.
-
-Conditional AMCEs are not per se a problematic quantity of inference.
-Like subgroup analysis of any experiment, they convey the causal effect of an experimental factor on overall favorability among the subgroup of interest.
-Consider, for example, a two-condition party cue experiment where Democrats and Republicans are exposed to an endorsement cue from the Democratic party or no cue and opinions toward the policy serve as the outcome.
-It is sensible to imagine that effects of the cue might differ for the two groups and therefore to compare the size of cue effect among the two groups.
-Perhaps Democrats are more responsive to the Democratic party cue than are Republicans, making the causal effect larger for Democrats than Republicans.
+Conditional AMCEs convey the causal effect of an experimental factor on overall favorability among the subgroup of interest.
+Consider, for example, a two-condition candidate choice experiment where Democratic and Republican respondents are exposed to either a male or female candidate and opinions toward the candidate serve as the outcome.
+It is sensible to imagine that effects of candidate sex might differ for the two groups and therefore to compare the size of treatment between the two groups.
+Perhaps Democrats are more responsive to candidate sex than are Republicans, making the causal effect larger for Democrats than Republicans.
+When conjoint analysts engage in subgroup comparisons, they are engaging in this kind of search for heterogeneous treatment effects across subgroups, but across a much larger number of experimental factors.
+
 Discussions of conditional AMCEs in conjoint analyses often explicitly or implicitly engage in this kind of discussion comparing the size and direction of subgroup causal effects.
-If interpreted as a difference in the size of the causal effect for two groups, such comparisons are perfectly consistent with more traditional experimental analysis and a perfectly acceptable interpretation of the conjoint results.
+Indeed, Table \ref{tab:papers} reports a list of recently published articles in political science that engage in this form of subgroup analysis.
+Given the common practice of descriptively interpreting conjoint experimental results, such subgroup analyses seem perfectly intuitive and the set of subgroups listed in the last column of Table \ref{tab:papers} contains some unsurprising covariates, such as partisanship, that are of obvious theoretical interest in almost any study of individual preferences.
+If interpreted as a difference in the size of the \textit{causal effect} for two groups, such comparisons are perfectly consistent with more traditional experimental analysis and a perfectly acceptable interpretation of the conjoint results.
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/tkr_replication-1} 
-\includegraphics[width=\maxwidth]{figure/tkr_replication-2} \caption[Replication of Teele et al]{Replication of Teele et al. (2018) Candidate Experiment using AMCEs and MMs}\label{fig:tkr_replication}
+\includegraphics[width=\maxwidth]{figure/tkr_replication-1} \caption[Replication of Results for `Candidate Sex' Feature from Teele et al]{Replication of Results for `Candidate Sex' Feature from Teele et al.
+(2018) Candidate Experiment using Full Sample and Subgroup AMCEs and MMs}\label{fig:tkr_replication}
 \end{figure}
@@
 The difference-in-AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$.
-Yet the standard AMCE-centric conjoint analysis does not present or characterize either of these quantities.
-Similarity of conditional AMCEs therefore only convey similarity of the \textit{causal effect} of the feature, but do not convey similarity of \textit{preferences} unless preferences toward profiles with the reference category are equivalent across groups.
-Given the reference category choice is typically arbitrary or driven by substantive knowledge of the levels, there is never any reason to expect that an arbitrarily selected reference category satisfies that equality assumption.
+Yet the standard AMCE-centric conjoint analysis does not present or characterize absolute favorability in the reference category.
+Similarity of conditional AMCEs only means similarity of the \textit{causal effect} of the feature across groups, not similarity of \textit{preferences} unless preferences toward profiles with the reference category are equivalent in both groups.
+Given the reference category choice is typically arbitrary or driven by substantive knowledge of the levels, there is never any reason to expect that an arbitrarily selected reference category satisfies this equality requirement.
 When using a difference-in-AMCEs comparison to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.
 
+To draw this example out more fully, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment for the full sample of respondents.
+The second panel shows full sample marginal means.
+The third panel shows conditional AMCEs separately for Democratic and Republican voters, as provided in the original paper and the lower panel shows the results using conditional marginal means for Democratic and Republican voters.\footnote{We opt here for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.} Respondents' preference for female candidates is very apparent in both forms of analysis in the upper two panels because the AMCE definitionally equals the difference in marginal means.
+But how do Republicans and Democrats differ in their preferences over male and female candidates?
+By requiring a reference category fixed to zero, the conditional AMCE results in the third panel suggest that there is a very large difference in favorability toward female candidates between Republican and Democratic respondents.
+In reality, however, the difference in these conditional AMCEs (0.086) reflects the true difference in favorability toward female candidates (difference: 0.045; Democrats: 0.537, Republicans: 0.492) \textit{plus} the difference in favorability toward male candidates (difference: 0.045; Democrats: 0.463, Republicans: 0.508).
+Because Democrats and Republicans actually differ in their views of profiles containing the reference (male) category, AMCEs sum the true differences in preferences for a given feature level with the difference in preferences toward the reference category.\footnote{Another example that clearly demonstrates the discrepancy between the differences in preferences and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature of this experiment (see Supporting Materials).
+The conditional AMCEs correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates.
+Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates).
+In reality, however, the conditional marginal means reveal that actually Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience.
+Democrats are much more sensitive to experience than are Republicans and important differences in preferences between the groups are apparent for very high and very low experience, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.}
+
 \begin{knitrout}
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/bms_difference_comparison-1} \caption[Estimated Preference Differences between Inequity Averse and Non-Averse Respondents from Ballard-Rosa et al]{Estimated Preference Differences between Inequity Averse and Non-Averse Respondents from Ballard-Rosa et al.
-(2016) Tax Preference Experiment for Each Possible Reference Category}\label{fig:bms_difference_comparison}
+\includegraphics[width=\maxwidth]{figure/bechtel_difference_comparison-1} \caption[True Difference in Favorability and Implied Preference Differences between High and Low Environmentalism Respondents for `Monthly Cost' Feature from Bechtel and Scheve (2013) Climate Agreement Experiment for Each Possible Reference Category]{True Difference in Favorability and Implied Preference Differences between High and Low Environmentalism Respondents for `Monthly Cost' Feature from Bechtel and Scheve (2013) Climate Agreement Experiment for Each Possible Reference Category}\label{fig:bechtel_difference_comparison}
 \end{figure}
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/hainmueller_mm_by_ethnocentrism-1} \caption[Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment]{Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:hainmueller_mm_by_ethnocentrism}
-\end{figure}
-
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
 \includegraphics[width=\maxwidth]{figure/hainmueller_mm_diffs-1} \caption[Differences in Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment]{Differences in Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:hainmueller_mm_diffs}
@@
 
-Alternatively presenting subgroup differences using conditional marginal means (as in Figure \ref{fig:hainmueller_mm_by_ethnocentrism}) provides the intended descriptive comparison of subgroup preferences.
+Alternatively presenting subgroup differences using conditional marginal means (as in Figure \ref{fig:hainmueller_mm_diffs}) provides the intended descriptive comparison of subgroup preferences.
 Each dot and error bar represents the conditional marginal mean (and its standard error) for high ethnocentrism (in red) and low ethnocentrism (in blue) respondents.
@@
 None of the level-specific differences in conditional marginal means are statistically distinguishable from zero.
-Were we interested in an omnibus tests of whether any of these differences were non-zero, we could perform a nested model comparison of two equations: (a) one estimating only marginal effects of the ``Language Skills'' feature, and (b) the same model with additional interactions between the subgrouping covariate and the features.
-The resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: F(4)=1.06, $p\leq0.37$.
+Were we interested in an omnibus tests of whether any of these differences were non-zero, we could perform a nested model comparison of two equations: (a) one estimating only marginal effects of the ``Language Skills'' feature levels, and (b) the same model with additional interactions between the subgrouping covariate and the feature levels.
+The test compares the sum of squared residuals for the two equations.
+
+To make this concrete, for a feature with four levels (one treated as a reference category), the first (restricted) equation would be:
+
+\begin{equation}\label{eq:restricted}
+Y = \beta_0 + \beta_1 Level_1 + \beta_2 Level_2 + \beta_3 Level_3 + u
+\end{equation}
+
+\noindent The second (unrestricted) equation would allow for interactions between feature levels and the subgroup identifier:
+
+\begin{equation}\label{eq:unrestricted}
+\begin{split}
+Y = & \beta_0 + \beta_1 Level_1 + \beta_2 Level_2 + \beta_3 Level_3 + \beta_4 Group + \\
+& \beta_5 Level_1 * Group + \beta_6 Level_2 * Group + \beta_7 Level_3 * Group + u
+\end{split}
+\end{equation}
+
+\noindent While Equation \ref{eq:restricted} imposes the constraint that $\beta_4 = \beta_5 = \beta_6 = \beta_7 = 0$, Equation \ref{eq:unrestricted} allows for subgroup differences in favorability.
+The nested model comparison allows us to test the joint null hypothesis that there are no differences between the subgroups in any of the feature levels.
+This entails computing an F-statistic:
+
+\begin{equation}
+F = \dfrac{\dfrac{SSR_{Restricted} - SSR_{Unrestricted}}{r}}{\dfrac{SSR_{Unrestricted}}{n - k - 1}}
+\end{equation}
+
+\noindent where $SSR_{Restricted}$ is the sum of squared residuals for Equation \ref{eq:restricted}, $SSR_{Unrestricted}$ is the sum of squared residuals for Equation \ref{eq:unrestricted}, where $r$ is the number of restrictions (in the above example, 4), $n$ is the number of cases, and $k$ is the number of feature levels in the unrestricted model.
+Note that this test is not sensitive to reference category used in the regression
+
+For the \citeauthor{HainmuellerHopkinsYamamoto2014} language feature, the resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: F(4, 11496)=1.06, $p\leq0.37$.
 We could repeat such pairwise comparisons or omnibus comparisons for each feature in the design.
@@
 A further advantage of this plot is that unlike displays of conditional AMCEs, differences in conditional marginal means communicate subgroup differences for all feature levels including the reference categories.
-This display makes readily clear what was only indirectly apparent in Figure \ref{fig:hainmueller_mm_by_ethnocentrism}: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.
+This display makes readily clear what was only indirectly apparent in Figure \ref{fig:hainmueller_mm_diffs}: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.
 
 As before, we can perform an omnibus tests for the presence of any subgroup differences across all features, again using nested model comparison of two equations: (a) one estimating only effects of the features, and (b) the same model with additional interactions between the subgrouping covariate and all features.
-The result of that test for differences by ethnocentrism from the immigration experiment is: F(98)=1.16, $p\leq0.14$, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.
-This kind of test can also be used to assess heterogeneity across conjoint features.
+The result of that test for differences by ethnocentrism from the immigration experiment is: F(98, 11402)=1.16, $p\leq0.14$, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.
+By contrast, \citet{BechtelScheve2013} argue in their cross-country conjoint examining climate change agreements ``that individuals in all four countries largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}.
+Yet a nested model comparisons shows the countries do differ in their preferences F(54, 67982)=3.72, $p\leq0.00$.
+This cross-country variation is largely driven by differences in sensitivity to monthly household costs feature, F(15, 67995)=3.80, $p\leq0.00$, with the United Kingdom and United States being more cost sensitive than Germany and France as is plainly visible in a plot of marginal means by country (see SI).
+
+This kind of nested model comparison test can also be used to assess heterogeneity across conjoint features \citep[see also][]{EgamiImai2018}.
 For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9).
@@
 
-In an experiment where $N > C$ (the number of observations is large than the number of cells) due to a large sample, or few factors, or levels of each factor, or both (or both of these design characteristic), a sensible next quantity of interest is the \textit{cell mean}: $E[Y|\vec{X} = \vec{x}]$, which in a conjoint simply measures the mean favorability toward a particular profile, $\vec{x}$.
+In a \textit{full factorial} experiment where $N > C$ (the number of observations is larger than the number of cells) due to a large sample, or few factors, or levels of each factor, or both (or both of these design characteristics), a sensible next quantity of interest is the \textit{cell mean}: $E[Y|\vec{X} = \vec{x}]$, which in a conjoint simply measures the mean favorability toward a particular profile, $\vec{x}$.
 An effort to actually estimate this quantity will, however, become obviously intractable when one recognizes that the number of observations in a typical conjoint is much lower the number of feasible profiles ($N \ll C$).
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Nov 25 10:42:30 2018
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_amce_appendix_split-1}
+
+\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_amce_appendix_split-2}
+
+\end{knitrout}
+
+\clearpage
+
+% latex table generated in R 3.5.2 by xtable 1.8-3 package
+% Fri Mar 15 15:56:01 2019
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Nov 25 10:42:36 2018
+% latex table generated in R 3.5.2 by xtable 1.8-3 package
+% Fri Mar 15 15:56:08 2019
 \begin{table}[ht]
@@
 
+\section{Bechtel and Scheve (2013) Climate Agreement Experiment}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+##      outcome statistic                                 feature
+## 1  choice_cj      amce    Costs to average household per month
+## 2  choice_cj      amce    Costs to average household per month
+## 3  choice_cj      amce    Costs to average household per month
+## 4  choice_cj      amce    Costs to average household per month
+## 5  choice_cj      amce    Costs to average household per month
+## 6  choice_cj      amce                   Distribution of costs
+## 7  choice_cj      amce                   Distribution of costs
+## 8  choice_cj      amce                   Distribution of costs
+## 9  choice_cj      amce                   Distribution of costs
+## 10 choice_cj      amce       Number of participating countries
+## 11 choice_cj      amce       Number of participating countries
+## 12 choice_cj      amce       Number of participating countries
+## 13 choice_cj      amce   Share of global emissions represented
+## 14 choice_cj      amce   Share of global emissions represented
+## 15 choice_cj      amce   Share of global emissions represented
+## 16 choice_cj      amce Sanctions for missing reduction targets
+## 17 choice_cj      amce Sanctions for missing reduction targets
+## 18 choice_cj      amce Sanctions for missing reduction targets
+## 19 choice_cj      amce Sanctions for missing reduction targets
+## 20 choice_cj      amce                           Monitoring by
+## 21 choice_cj      amce                           Monitoring by
+## 22 choice_cj      amce                           Monitoring by
+## 23 choice_cj      amce                           Monitoring by
+##                                level     estimate   std.error           z
+## 1                      \20028 per month  0.000000000          NA          NA
+## 2                      \20056 per month -0.097845284 0.001402351  -69.772319
+## 3                      \20084 per month -0.170008434 0.001468627 -115.760108
+## 4                     \200113 per month -0.263769273 0.001471840 -179.210616
+## 5                     \200141 per month -0.332856845 0.001422455 -234.001744
+## 6                          Only rich  0.000000000          NA          NA
+## 7         Prop. to current emissions  0.065924582 0.001340698   49.171839
+## 8      Prop. to history of emissions  0.052479783 0.001345106   39.015350
+## 9  Rich pay more than poor countries  0.057280714 0.001327647   43.144545
+## 10                         20 of 192  0.000000000          NA          NA
+## 11                         80 of 192  0.092728950 0.001141542   81.231296
+## 12                        160 of 192  0.156435103 0.001175080  133.127175
+## 13          40% of current emissions  0.000000000          NA          NA
+## 14          60% of current emissions  0.022498908 0.001117762   20.128532
+## 15          80% of current emissions  0.045174103 0.001125637   40.132047
+## 16                              None  0.000000000          NA          NA
+## 17               \2006 per hh and month  0.028464249 0.001308130   21.759490
+## 18              \20017 per hh and month -0.018533001 0.001326110  -13.975465
+## 19              \20023 per hh and month -0.053180963 0.001312140  -40.529947
+## 20                   Your government  0.000000000          NA          NA
+## 21                 Indep. commission  0.061714854 0.001323261   46.638460
+## 22                    United Nations  0.024280174 0.001356516   17.898921
+## 23                        Greenpeace -0.006573634 0.001377372   -4.772591
+##                p        lower        upper
+## 1             NA           NA           NA
+## 2   0.000000e+00 -0.100593842 -0.095096727
+## 3   0.000000e+00 -0.172886890 -0.167129978
+## 4   0.000000e+00 -0.266654026 -0.260884521
+## 5   0.000000e+00 -0.335644805 -0.330068886
+## 6             NA           NA           NA
+## 7   0.000000e+00  0.063296862  0.068552302
+## 8   0.000000e+00  0.049843423  0.055116142
+## 9   0.000000e+00  0.054678574  0.059882854
+## 10            NA           NA           NA
+## 11  0.000000e+00  0.090491569  0.094966332
+## 12  0.000000e+00  0.154131988  0.158738218
+## 13            NA           NA           NA
+## 14  4.151128e-90  0.020308135  0.024689682
+## 15  0.000000e+00  0.042967896  0.047380310
+## 16            NA           NA           NA
+## 17 5.616961e-105  0.025900360  0.031028137
+## 18  2.200727e-44 -0.021132129 -0.015933874
+## 19  0.000000e+00 -0.055752710 -0.050609216
+## 20            NA           NA           NA
+## 21  0.000000e+00  0.059121310  0.064308398
+## 22  1.202281e-71  0.021621451  0.026938896
+## 23  1.818711e-06 -0.009273234 -0.003874034
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+##      outcome statistic                                 feature
+## 1  choice_cj        mm    Costs to average household per month
+## 2  choice_cj        mm    Costs to average household per month
+## 3  choice_cj        mm    Costs to average household per month
+## 4  choice_cj        mm    Costs to average household per month
+## 5  choice_cj        mm    Costs to average household per month
+## 6  choice_cj        mm                   Distribution of costs
+## 7  choice_cj        mm                   Distribution of costs
+## 8  choice_cj        mm                   Distribution of costs
+## 9  choice_cj        mm                   Distribution of costs
+## 10 choice_cj        mm       Number of participating countries
+## 11 choice_cj        mm       Number of participating countries
+## 12 choice_cj        mm       Number of participating countries
+## 13 choice_cj        mm   Share of global emissions represented
+## 14 choice_cj        mm   Share of global emissions represented
+## 15 choice_cj        mm   Share of global emissions represented
+## 16 choice_cj        mm Sanctions for missing reduction targets
+## 17 choice_cj        mm Sanctions for missing reduction targets
+## 18 choice_cj        mm Sanctions for missing reduction targets
+## 19 choice_cj        mm Sanctions for missing reduction targets
+## 20 choice_cj        mm                           Monitoring by
+## 21 choice_cj        mm                           Monitoring by
+## 22 choice_cj        mm                           Monitoring by
+## 23 choice_cj        mm                           Monitoring by
+##                                level  estimate   std.error         z p
+## 1                      \20028 per month 0.6729737 0.004126308 163.09342 0
+## 2                      \20056 per month 0.5753704 0.004309124 133.52375 0
+## 3                      \20084 per month 0.5028766 0.004395792 114.39955 0
+## 4                     \200113 per month 0.4085284 0.004325220  94.45264 0
+## 5                     \200141 per month 0.3394765 0.004148381  81.83349 0
+## 6                          Only rich 0.4570055 0.003911228 116.84452 0
+## 7         Prop. to current emissions 0.5216566 0.003926015 132.87176 0
+## 8      Prop. to history of emissions 0.5087938 0.003917689 129.87090 0
+## 9  Rich pay more than poor countries 0.5127165 0.003924942 130.63032 0
+## 10                         20 of 192 0.4182276 0.003341616 125.15729 0
+## 11                         80 of 192 0.5089863 0.003399306 149.73245 0
+## 12                        160 of 192 0.5737857 0.003373566 170.08288 0
+## 13          40% of current emissions 0.4781113 0.003380328 141.43933 0
+## 14          60% of current emissions 0.4999291 0.003407780 146.70227 0
+## 15          80% of current emissions 0.5222143 0.003402419 153.48325 0
+## 16                              None 0.5106586 0.003932951 129.84109 0
+## 17               \2006 per hh and month 0.5412417 0.003913371 138.30573 0
+## 18              \20017 per hh and month 0.4928567 0.003908225 126.10754 0
+## 19              \20023 per hh and month 0.4552868 0.003914718 116.30129 0
+## 20                   Your government 0.4813399 0.003912654 123.02130 0
+## 21                 Indep. commission 0.5426752 0.003901770 139.08437 0
+## 22                    United Nations 0.5032115 0.003941043 127.68486 0
+## 23                        Greenpeace 0.4725424 0.003920333 120.53630 0
+##        lower     upper
+## 1  0.6648863 0.6810611
+## 2  0.5669247 0.5838161
+## 3  0.4942610 0.5114922
+## 4  0.4000512 0.4170057
+## 5  0.3313459 0.3476072
+## 6  0.4493397 0.4646714
+## 7  0.5139617 0.5293514
+## 8  0.5011153 0.5164723
+## 9  0.5050237 0.5204092
+## 10 0.4116781 0.4247770
+## 11 0.5023238 0.5156488
+## 12 0.5671737 0.5803978
+## 13 0.4714860 0.4847366
+## 14 0.4932500 0.5066083
+## 15 0.5155456 0.5288829
+## 16 0.5029502 0.5183671
+## 17 0.5335716 0.5489118
+## 18 0.4851967 0.5005167
+## 19 0.4476140 0.4629595
+## 20 0.4736712 0.4890085
+## 21 0.5350279 0.5503225
+## 22 0.4954872 0.5109358
+## 23 0.4648587 0.4802262
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_mm-1} 
+\begin{kframe}\begin{verbatim}
+##                BY   outcome statistic
+## 1          France choice_cj        mm
+## 2          France choice_cj        mm
+## 3          France choice_cj        mm
+## 4          France choice_cj        mm
+## 5          France choice_cj        mm
+## 6          France choice_cj        mm
+## 7          France choice_cj        mm
+## 8          France choice_cj        mm
+## 9          France choice_cj        mm
+## 10         France choice_cj        mm
+## 11         France choice_cj        mm
+## 12         France choice_cj        mm
+## 13         France choice_cj        mm
+## 14         France choice_cj        mm
+## 15         France choice_cj        mm
+## 16         France choice_cj        mm
+## 17         France choice_cj        mm
+## 18         France choice_cj        mm
+## 19         France choice_cj        mm
+## 20         France choice_cj        mm
+## 21         France choice_cj        mm
+## 22         France choice_cj        mm
+## 23         France choice_cj        mm
+## 24        Germany choice_cj        mm
+## 25        Germany choice_cj        mm
+## 26        Germany choice_cj        mm
+## 27        Germany choice_cj        mm
+## 28        Germany choice_cj        mm
+## 29        Germany choice_cj        mm
+## 30        Germany choice_cj        mm
+## 31        Germany choice_cj        mm
+## 32        Germany choice_cj        mm
+## 33        Germany choice_cj        mm
+## 34        Germany choice_cj        mm
+## 35        Germany choice_cj        mm
+## 36        Germany choice_cj        mm
+## 37        Germany choice_cj        mm
+## 38        Germany choice_cj        mm
+## 39        Germany choice_cj        mm
+## 40        Germany choice_cj        mm
+## 41        Germany choice_cj        mm
+## 42        Germany choice_cj        mm
+## 43        Germany choice_cj        mm
+## 44        Germany choice_cj        mm
+## 45        Germany choice_cj        mm
+## 46        Germany choice_cj        mm
+## 47 United Kingdom choice_cj        mm
+## 48 United Kingdom choice_cj        mm
+## 49 United Kingdom choice_cj        mm
+## 50 United Kingdom choice_cj        mm
+## 51 United Kingdom choice_cj        mm
+## 52 United Kingdom choice_cj        mm
+## 53 United Kingdom choice_cj        mm
+## 54 United Kingdom choice_cj        mm
+## 55 United Kingdom choice_cj        mm
+## 56 United Kingdom choice_cj        mm
+## 57 United Kingdom choice_cj        mm
+## 58 United Kingdom choice_cj        mm
+## 59 United Kingdom choice_cj        mm
+## 60 United Kingdom choice_cj        mm
+## 61 United Kingdom choice_cj        mm
+## 62 United Kingdom choice_cj        mm
+## 63 United Kingdom choice_cj        mm
+## 64 United Kingdom choice_cj        mm
+## 65 United Kingdom choice_cj        mm
+## 66 United Kingdom choice_cj        mm
+## 67 United Kingdom choice_cj        mm
+## 68 United Kingdom choice_cj        mm
+## 69 United Kingdom choice_cj        mm
+## 70  United States choice_cj        mm
+## 71  United States choice_cj        mm
+## 72  United States choice_cj        mm
+## 73  United States choice_cj        mm
+## 74  United States choice_cj        mm
+## 75  United States choice_cj        mm
+## 76  United States choice_cj        mm
+## 77  United States choice_cj        mm
+## 78  United States choice_cj        mm
+## 79  United States choice_cj        mm
+## 80  United States choice_cj        mm
+## 81  United States choice_cj        mm
+## 82  United States choice_cj        mm
+## 83  United States choice_cj        mm
+## 84  United States choice_cj        mm
+## 85  United States choice_cj        mm
+## 86  United States choice_cj        mm
+## 87  United States choice_cj        mm
+## 88  United States choice_cj        mm
+## 89  United States choice_cj        mm
+## 90  United States choice_cj        mm
+## 91  United States choice_cj        mm
+## 92  United States choice_cj        mm
+##                                    feature
+## 1     Costs to average household per month
+## 2     Costs to average household per month
+## 3     Costs to average household per month
+## 4     Costs to average household per month
+## 5     Costs to average household per month
+## 6                    Distribution of costs
+## 7                    Distribution of costs
+## 8                    Distribution of costs
+## 9                    Distribution of costs
+## 10       Number of participating countries
+## 11       Number of participating countries
+## 12       Number of participating countries
+## 13   Share of global emissions represented
+## 14   Share of global emissions represented
+## 15   Share of global emissions represented
+## 16 Sanctions for missing reduction targets
+## 17 Sanctions for missing reduction targets
+## 18 Sanctions for missing reduction targets
+## 19 Sanctions for missing reduction targets
+## 20                           Monitoring by
+## 21                           Monitoring by
+## 22                           Monitoring by
+## 23                           Monitoring by
+## 24    Costs to average household per month
+## 25    Costs to average household per month
+## 26    Costs to average household per month
+## 27    Costs to average household per month
+## 28    Costs to average household per month
+## 29                   Distribution of costs
+## 30                   Distribution of costs
+## 31                   Distribution of costs
+## 32                   Distribution of costs
+## 33       Number of participating countries
+## 34       Number of participating countries
+## 35       Number of participating countries
+## 36   Share of global emissions represented
+## 37   Share of global emissions represented
+## 38   Share of global emissions represented
+## 39 Sanctions for missing reduction targets
+## 40 Sanctions for missing reduction targets
+## 41 Sanctions for missing reduction targets
+## 42 Sanctions for missing reduction targets
+## 43                           Monitoring by
+## 44                           Monitoring by
+## 45                           Monitoring by
+## 46                           Monitoring by
+## 47    Costs to average household per month
+## 48    Costs to average household per month
+## 49    Costs to average household per month
+## 50    Costs to average household per month
+## 51    Costs to average household per month
+## 52                   Distribution of costs
+## 53                   Distribution of costs
+## 54                   Distribution of costs
+## 55                   Distribution of costs
+## 56       Number of participating countries
+## 57       Number of participating countries
+## 58       Number of participating countries
+## 59   Share of global emissions represented
+## 60   Share of global emissions represented
+## 61   Share of global emissions represented
+## 62 Sanctions for missing reduction targets
+## 63 Sanctions for missing reduction targets
+## 64 Sanctions for missing reduction targets
+## 65 Sanctions for missing reduction targets
+## 66                           Monitoring by
+## 67                           Monitoring by
+## 68                           Monitoring by
+## 69                           Monitoring by
+## 70    Costs to average household per month
+## 71    Costs to average household per month
+## 72    Costs to average household per month
+## 73    Costs to average household per month
+## 74    Costs to average household per month
+## 75                   Distribution of costs
+## 76                   Distribution of costs
+## 77                   Distribution of costs
+## 78                   Distribution of costs
+## 79       Number of participating countries
+## 80       Number of participating countries
+## 81       Number of participating countries
+## 82   Share of global emissions represented
+## 83   Share of global emissions represented
+## 84   Share of global emissions represented
+## 85 Sanctions for missing reduction targets
+## 86 Sanctions for missing reduction targets
+## 87 Sanctions for missing reduction targets
+## 88 Sanctions for missing reduction targets
+## 89                           Monitoring by
+## 90                           Monitoring by
+## 91                           Monitoring by
+## 92                           Monitoring by
+##                                level  estimate   std.error        z
+## 1                      \20028 per month 0.6613316 0.008322408 79.46397
+## 2                      \20056 per month 0.5693159 0.008660576 65.73649
+## 3                      \20084 per month 0.4989851 0.008884067 56.16629
+## 4                     \200113 per month 0.3970867 0.008722819 45.52275
+## 5                     \200141 per month 0.3667680 0.008567482 42.80931
+## 6                          Only rich 0.4694590 0.007936306 59.15334
+## 7         Prop. to current emissions 0.5234480 0.007931229 65.99834
+## 8      Prop. to history of emissions 0.5070668 0.007869017 64.43840
+## 9  Rich pay more than poor countries 0.4998164 0.007880458 63.42479
+## 10                         20 of 192 0.4280902 0.006737716 63.53639
+## 11                         80 of 192 0.5079278 0.006874025 73.89089
+## 12                        160 of 192 0.5652797 0.006810168 83.00524
+## 13          40% of current emissions 0.4714751 0.006806164 69.27178
+## 14          60% of current emissions 0.4972686 0.006865214 72.43307
+## 15          80% of current emissions 0.5316843 0.006854741 77.56447
+## 16                              None 0.4925810 0.007922009 62.17879
+## 17               \2006 per hh and month 0.5433092 0.007813932 69.53084
+## 18              \20017 per hh and month 0.5026263 0.007925773 63.41668
+## 19              \20023 per hh and month 0.4603338 0.007923589 58.09663
+## 20                   Your government 0.4707127 0.007932301 59.34126
+## 21                 Indep. commission 0.5410998 0.007756003 69.76529
+## 22                    United Nations 0.5079832 0.007952899 63.87396
+## 23                        Greenpeace 0.4783606 0.007954893 60.13414
+## 24                     \20028 per month 0.6520203 0.008538989 76.35801
+## 25                     \20056 per month 0.5667114 0.008678489 65.30070
+## 26                     \20084 per month 0.4912437 0.008871631 55.37242
+## 27                    \200113 per month 0.4301405 0.008828618 48.72116
+## 28                    \200141 per month 0.3582373 0.008565178 41.82486
+## 29                         Only rich 0.4600371 0.007930387 58.00941
+## 30        Prop. to current emissions 0.5153914 0.007901516 65.22689
+## 31     Prop. to history of emissions 0.4940093 0.007884299 62.65736
+## 32 Rich pay more than poor countries 0.5312310 0.008045629 66.02727
+## 33                         20 of 192 0.4098216 0.006744866 60.76052
+## 34                         80 of 192 0.5134710 0.006855305 74.90126
+## 35                        160 of 192 0.5787895 0.006863767 84.32534
+## 36          40% of current emissions 0.4723114 0.006837992 69.07165
+## 37          60% of current emissions 0.5007192 0.006884860 72.72757
+## 38          80% of current emissions 0.5275701 0.006914689 76.29700
+## 39                              None 0.4940875 0.007989972 61.83845
+## 40               \2006 per hh and month 0.5402615 0.007912846 68.27651
+## 41              \20017 per hh and month 0.5021986 0.007968977 63.01920
+## 42              \20023 per hh and month 0.4636031 0.007886215 58.78651
+## 43                   Your government 0.4691111 0.007850099 59.75862
+## 44                 Indep. commission 0.5483852 0.007959662 68.89553
+## 45                    United Nations 0.5011726 0.007951130 63.03162
+## 46                        Greenpeace 0.4823303 0.007989396 60.37131
+## 47                     \20028 per month 0.6934878 0.008424386 82.31909
+## 48                     \20056 per month 0.5859726 0.009034648 64.85838
+## 49                     \20084 per month 0.5048116 0.009338115 54.05926
+## 50                    \200113 per month 0.4024743 0.008986324 44.78743
+## 51                    \200141 per month 0.3132586 0.008508073 36.81898
+## 52                         Only rich 0.4661502 0.008199944 56.84798
+## 53        Prop. to current emissions 0.5221721 0.008206555 63.62865
+## 54     Prop. to history of emissions 0.5024308 0.008263298 60.80270
+## 55 Rich pay more than poor countries 0.5095266 0.008245511 61.79443
+## 56                         20 of 192 0.4025534 0.006980412 57.66899
+## 57                         80 of 192 0.5079030 0.007155688 70.97892
+## 58                        160 of 192 0.5899041 0.007002721 84.23928
+## 59          40% of current emissions 0.4795459 0.007060046 67.92391
+## 60          60% of current emissions 0.5032446 0.007215347 69.74642
+## 61          80% of current emissions 0.5176103 0.007113186 72.76772
+## 62                              None 0.5270756 0.008192395 64.33718
+## 63               \2006 per hh and month 0.5405720 0.008214268 65.80890
+## 64              \20017 per hh and month 0.4769717 0.008165885 58.41029
+## 65              \20023 per hh and month 0.4544697 0.008288953 54.82836
+## 66                   Your government 0.4768185 0.008212548 58.05975
+## 67                 Indep. commission 0.5392912 0.008128128 66.34876
+## 68                    United Nations 0.5147711 0.008330945 61.79024
+## 69                        Greenpeace 0.4686105 0.008208476 57.08861
+## 70                     \20028 per month 0.6824518 0.007763555 87.90454
+## 71                     \20056 per month 0.5789579 0.008147606 71.05866
+## 72                     \20084 per month 0.5136585 0.008166584 62.89760
+## 73                    \200113 per month 0.4051599 0.008111491 49.94888
+## 74                    \200141 per month 0.3244207 0.007630904 42.51406
+## 75                         Only rich 0.4375458 0.007282486 60.08192
+## 76        Prop. to current emissions 0.5249692 0.007413118 70.81625
+## 77     Prop. to history of emissions 0.5272909 0.007370877 71.53706
+## 78 Rich pay more than poor countries 0.5112713 0.007298410 70.05243
+## 79                         20 of 192 0.4296274 0.006300652 68.18777
+## 80                         80 of 192 0.5070832 0.006363026 79.69215
+## 81                        160 of 192 0.5636379 0.006344643 88.83682
+## 82          40% of current emissions 0.4870124 0.006373185 76.41585
+## 83          60% of current emissions 0.4988350 0.006362123 78.40701
+## 84          80% of current emissions 0.5141367 0.006379806 80.58813
+## 85                              None 0.5251766 0.007391775 71.04878
+## 86               \2006 per hh and month 0.5408734 0.007408935 73.00285
+## 87              \20017 per hh and month 0.4906273 0.007267688 67.50804
+## 88              \20023 per hh and month 0.4452759 0.007296972 61.02201
+## 89                   Your government 0.5033382 0.007350454 68.47716
+## 90                 Indep. commission 0.5422171 0.007403558 73.23736
+## 91                    United Nations 0.4920508 0.007361504 66.84108
+## 92                        Greenpeace 0.4634591 0.007284021 63.62682
+##                p     lower     upper        country
+## 1   0.000000e+00 0.6450199 0.6776432         France
+## 2   0.000000e+00 0.5523415 0.5862903         France
+## 3   0.000000e+00 0.4815727 0.5163976         France
+## 4   0.000000e+00 0.3799903 0.4141831         France
+## 5   0.000000e+00 0.3499761 0.3835600         France
+## 6   0.000000e+00 0.4539041 0.4850139         France
+## 7   0.000000e+00 0.5079031 0.5389929         France
+## 8   0.000000e+00 0.4916438 0.5224898         France
+## 9   0.000000e+00 0.4843710 0.5152619         France
+## 10  0.000000e+00 0.4148845 0.4412958         France
+## 11  0.000000e+00 0.4944550 0.5214007         France
+## 12  0.000000e+00 0.5519320 0.5786274         France
+## 13  0.000000e+00 0.4581352 0.4848149         France
+## 14  0.000000e+00 0.4838130 0.5107242         France
+## 15  0.000000e+00 0.5182493 0.5451194         France
+## 16  0.000000e+00 0.4770541 0.5081078         France
+## 17  0.000000e+00 0.5279942 0.5586243         France
+## 18  0.000000e+00 0.4870920 0.5181605         France
+## 19  0.000000e+00 0.4448038 0.4758637         France
+## 20  0.000000e+00 0.4551657 0.4862597         France
+## 21  0.000000e+00 0.5258983 0.5563013         France
+## 22  0.000000e+00 0.4923958 0.5235706         France
+## 23  0.000000e+00 0.4627693 0.4939519         France
+## 24  0.000000e+00 0.6352841 0.6687564        Germany
+## 25  0.000000e+00 0.5497018 0.5837209        Germany
+## 26  0.000000e+00 0.4738556 0.5086317        Germany
+## 27  0.000000e+00 0.4128368 0.4474443        Germany
+## 28  0.000000e+00 0.3414499 0.3750248        Germany
+## 29  0.000000e+00 0.4444938 0.4755803        Germany
+## 30  0.000000e+00 0.4999047 0.5308781        Germany
+## 31  0.000000e+00 0.4785564 0.5094622        Germany
+## 32  0.000000e+00 0.5154618 0.5470001        Germany
+## 33  0.000000e+00 0.3966019 0.4230413        Germany
+## 34  0.000000e+00 0.5000348 0.5269071        Germany
+## 35  0.000000e+00 0.5653368 0.5922422        Germany
+## 36  0.000000e+00 0.4589092 0.4857136        Germany
+## 37  0.000000e+00 0.4872251 0.5142132        Germany
+## 38  0.000000e+00 0.5140175 0.5411226        Germany
+## 39  0.000000e+00 0.4784274 0.5097476        Germany
+## 40  0.000000e+00 0.5247526 0.5557704        Germany
+## 41  0.000000e+00 0.4865797 0.5178175        Germany
+## 42  0.000000e+00 0.4481464 0.4790598        Germany
+## 43  0.000000e+00 0.4537252 0.4844970        Germany
+## 44  0.000000e+00 0.5327845 0.5639858        Germany
+## 45  0.000000e+00 0.4855887 0.5167566        Germany
+## 46  0.000000e+00 0.4666714 0.4979892        Germany
+## 47  0.000000e+00 0.6769763 0.7099993 United Kingdom
+## 48  0.000000e+00 0.5682650 0.6036802 United Kingdom
+## 49  0.000000e+00 0.4865092 0.5231140 United Kingdom
+## 50  0.000000e+00 0.3848615 0.4200872 United Kingdom
+## 51 9.175209e-297 0.2965831 0.3299341 United Kingdom
+## 52  0.000000e+00 0.4500786 0.4822218 United Kingdom
+## 53  0.000000e+00 0.5060875 0.5382566 United Kingdom
+## 54  0.000000e+00 0.4862350 0.5186266 United Kingdom
+## 55  0.000000e+00 0.4933657 0.5256875 United Kingdom
+## 56  0.000000e+00 0.3888720 0.4162347 United Kingdom
+## 57  0.000000e+00 0.4938781 0.5219279 United Kingdom
+## 58  0.000000e+00 0.5761791 0.6036292 United Kingdom
+## 59  0.000000e+00 0.4657085 0.4933834 United Kingdom
+## 60  0.000000e+00 0.4891028 0.5173864 United Kingdom
+## 61  0.000000e+00 0.5036687 0.5315519 United Kingdom
+## 62  0.000000e+00 0.5110188 0.5431324 United Kingdom
+## 63  0.000000e+00 0.5244723 0.5566716 United Kingdom
+## 64  0.000000e+00 0.4609668 0.4929765 United Kingdom
+## 65  0.000000e+00 0.4382236 0.4707157 United Kingdom
+## 66  0.000000e+00 0.4607222 0.4929148 United Kingdom
+## 67  0.000000e+00 0.5233604 0.5552221 United Kingdom
+## 68  0.000000e+00 0.4984427 0.5310994 United Kingdom
+## 69  0.000000e+00 0.4525221 0.4846988 United Kingdom
+## 70  0.000000e+00 0.6672355 0.6976681  United States
+## 71  0.000000e+00 0.5629889 0.5949270  United States
+## 72  0.000000e+00 0.4976523 0.5296647  United States
+## 73  0.000000e+00 0.3892617 0.4210581  United States
+## 74  0.000000e+00 0.3094644 0.3393770  United States
+## 75  0.000000e+00 0.4232724 0.4518192  United States
+## 76  0.000000e+00 0.5104398 0.5394987  United States
+## 77  0.000000e+00 0.5128442 0.5417375  United States
+## 78  0.000000e+00 0.4969667 0.5255759  United States
+## 79  0.000000e+00 0.4172784 0.4419765  United States
+## 80  0.000000e+00 0.4946119 0.5195545  United States
+## 81  0.000000e+00 0.5512027 0.5760732  United States
+## 82  0.000000e+00 0.4745211 0.4995036  United States
+## 83  0.000000e+00 0.4863655 0.5113045  United States
+## 84  0.000000e+00 0.5016325 0.5266409  United States
+## 85  0.000000e+00 0.5106890 0.5396642  United States
+## 86  0.000000e+00 0.5263521 0.5553946  United States
+## 87  0.000000e+00 0.4763829 0.5048717  United States
+## 88  0.000000e+00 0.4309741 0.4595777  United States
+## 89  0.000000e+00 0.4889316 0.5177448  United States
+## 90  0.000000e+00 0.5277064 0.5567278  United States
+## 91  0.000000e+00 0.4776225 0.5064791  United States
+## 92  0.000000e+00 0.4491827 0.4777355  United States
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce-1} 
+\begin{kframe}\begin{verbatim}
+##                BY   outcome statistic
+## 1          France choice_cj      amce
+## 2          France choice_cj      amce
+## 3          France choice_cj      amce
+## 4          France choice_cj      amce
+## 5          France choice_cj      amce
+## 6          France choice_cj      amce
+## 7          France choice_cj      amce
+## 8          France choice_cj      amce
+## 9          France choice_cj      amce
+## 10         France choice_cj      amce
+## 11         France choice_cj      amce
+## 12         France choice_cj      amce
+## 13         France choice_cj      amce
+## 14         France choice_cj      amce
+## 15         France choice_cj      amce
+## 16         France choice_cj      amce
+## 17         France choice_cj      amce
+## 18         France choice_cj      amce
+## 19         France choice_cj      amce
+## 20         France choice_cj      amce
+## 21         France choice_cj      amce
+## 22         France choice_cj      amce
+## 23         France choice_cj      amce
+## 24        Germany choice_cj      amce
+## 25        Germany choice_cj      amce
+## 26        Germany choice_cj      amce
+## 27        Germany choice_cj      amce
+## 28        Germany choice_cj      amce
+## 29        Germany choice_cj      amce
+## 30        Germany choice_cj      amce
+## 31        Germany choice_cj      amce
+## 32        Germany choice_cj      amce
+## 33        Germany choice_cj      amce
+## 34        Germany choice_cj      amce
+## 35        Germany choice_cj      amce
+## 36        Germany choice_cj      amce
+## 37        Germany choice_cj      amce
+## 38        Germany choice_cj      amce
+## 39        Germany choice_cj      amce
+## 40        Germany choice_cj      amce
+## 41        Germany choice_cj      amce
+## 42        Germany choice_cj      amce
+## 43        Germany choice_cj      amce
+## 44        Germany choice_cj      amce
+## 45        Germany choice_cj      amce
+## 46        Germany choice_cj      amce
+## 47 United Kingdom choice_cj      amce
+## 48 United Kingdom choice_cj      amce
+## 49 United Kingdom choice_cj      amce
+## 50 United Kingdom choice_cj      amce
+## 51 United Kingdom choice_cj      amce
+## 52 United Kingdom choice_cj      amce
+## 53 United Kingdom choice_cj      amce
+## 54 United Kingdom choice_cj      amce
+## 55 United Kingdom choice_cj      amce
+## 56 United Kingdom choice_cj      amce
+## 57 United Kingdom choice_cj      amce
+## 58 United Kingdom choice_cj      amce
+## 59 United Kingdom choice_cj      amce
+## 60 United Kingdom choice_cj      amce
+## 61 United Kingdom choice_cj      amce
+## 62 United Kingdom choice_cj      amce
+## 63 United Kingdom choice_cj      amce
+## 64 United Kingdom choice_cj      amce
+## 65 United Kingdom choice_cj      amce
+## 66 United Kingdom choice_cj      amce
+## 67 United Kingdom choice_cj      amce
+## 68 United Kingdom choice_cj      amce
+## 69 United Kingdom choice_cj      amce
+## 70  United States choice_cj      amce
+## 71  United States choice_cj      amce
+## 72  United States choice_cj      amce
+## 73  United States choice_cj      amce
+## 74  United States choice_cj      amce
+## 75  United States choice_cj      amce
+## 76  United States choice_cj      amce
+## 77  United States choice_cj      amce
+## 78  United States choice_cj      amce
+## 79  United States choice_cj      amce
+## 80  United States choice_cj      amce
+## 81  United States choice_cj      amce
+## 82  United States choice_cj      amce
+## 83  United States choice_cj      amce
+## 84  United States choice_cj      amce
+## 85  United States choice_cj      amce
+## 86  United States choice_cj      amce
+## 87  United States choice_cj      amce
+## 88  United States choice_cj      amce
+## 89  United States choice_cj      amce
+## 90  United States choice_cj      amce
+## 91  United States choice_cj      amce
+## 92  United States choice_cj      amce
+##                                    feature
+## 1     Costs to average household per month
+## 2     Costs to average household per month
+## 3     Costs to average household per month
+## 4     Costs to average household per month
+## 5     Costs to average household per month
+## 6                    Distribution of costs
+## 7                    Distribution of costs
+## 8                    Distribution of costs
+## 9                    Distribution of costs
+## 10       Number of participating countries
+## 11       Number of participating countries
+## 12       Number of participating countries
+## 13   Share of global emissions represented
+## 14   Share of global emissions represented
+## 15   Share of global emissions represented
+## 16 Sanctions for missing reduction targets
+## 17 Sanctions for missing reduction targets
+## 18 Sanctions for missing reduction targets
+## 19 Sanctions for missing reduction targets
+## 20                           Monitoring by
+## 21                           Monitoring by
+## 22                           Monitoring by
+## 23                           Monitoring by
+## 24    Costs to average household per month
+## 25    Costs to average household per month
+## 26    Costs to average household per month
+## 27    Costs to average household per month
+## 28    Costs to average household per month
+## 29                   Distribution of costs
+## 30                   Distribution of costs
+## 31                   Distribution of costs
+## 32                   Distribution of costs
+## 33       Number of participating countries
+## 34       Number of participating countries
+## 35       Number of participating countries
+## 36   Share of global emissions represented
+## 37   Share of global emissions represented
+## 38   Share of global emissions represented
+## 39 Sanctions for missing reduction targets
+## 40 Sanctions for missing reduction targets
+## 41 Sanctions for missing reduction targets
+## 42 Sanctions for missing reduction targets
+## 43                           Monitoring by
+## 44                           Monitoring by
+## 45                           Monitoring by
+## 46                           Monitoring by
+## 47    Costs to average household per month
+## 48    Costs to average household per month
+## 49    Costs to average household per month
+## 50    Costs to average household per month
+## 51    Costs to average household per month
+## 52                   Distribution of costs
+## 53                   Distribution of costs
+## 54                   Distribution of costs
+## 55                   Distribution of costs
+## 56       Number of participating countries
+## 57       Number of participating countries
+## 58       Number of participating countries
+## 59   Share of global emissions represented
+## 60   Share of global emissions represented
+## 61   Share of global emissions represented
+## 62 Sanctions for missing reduction targets
+## 63 Sanctions for missing reduction targets
+## 64 Sanctions for missing reduction targets
+## 65 Sanctions for missing reduction targets
+## 66                           Monitoring by
+## 67                           Monitoring by
+## 68                           Monitoring by
+## 69                           Monitoring by
+## 70    Costs to average household per month
+## 71    Costs to average household per month
+## 72    Costs to average household per month
+## 73    Costs to average household per month
+## 74    Costs to average household per month
+## 75                   Distribution of costs
+## 76                   Distribution of costs
+## 77                   Distribution of costs
+## 78                   Distribution of costs
+## 79       Number of participating countries
+## 80       Number of participating countries
+## 81       Number of participating countries
+## 82   Share of global emissions represented
+## 83   Share of global emissions represented
+## 84   Share of global emissions represented
+## 85 Sanctions for missing reduction targets
+## 86 Sanctions for missing reduction targets
+## 87 Sanctions for missing reduction targets
+## 88 Sanctions for missing reduction targets
+## 89                           Monitoring by
+## 90                           Monitoring by
+## 91                           Monitoring by
+## 92                           Monitoring by
+##                                level     estimate   std.error           z
+## 1                      \20028 per month  0.000000000          NA          NA
+## 2                      \20056 per month -0.089860961 0.002813351  -31.940905
+## 3                      \20084 per month -0.162436163 0.002934504  -55.353875
+## 4                     \200113 per month -0.261547555 0.002918526  -89.616324
+## 5                     \200141 per month -0.291645421 0.002902892 -100.467203
+## 6                          Only rich  0.000000000          NA          NA
+## 7         Prop. to current emissions  0.054200226 0.002607077   20.789650
+## 8      Prop. to history of emissions  0.038328103 0.002658713   14.416038
+## 9  Rich pay more than poor countries  0.028519774 0.002646147   10.777849
+## 10                         20 of 192  0.000000000          NA          NA
+## 11                         80 of 192  0.082106285 0.002229365   36.829446
+## 12                        160 of 192  0.136730466 0.002294899   59.580169
+## 13          40% of current emissions  0.000000000          NA          NA
+## 14          60% of current emissions  0.026854567 0.002215284   12.122401
+## 15          80% of current emissions  0.058282940 0.002221222   26.239130
+## 16                              None  0.000000000          NA          NA
+## 17               \2006 per hh and month  0.045613729 0.002581015   17.672790
+## 18              \20017 per hh and month  0.007229382 0.002610090    2.769783
+## 19              \20023 per hh and month -0.029804720 0.002632489  -11.321878
+## 20                   Your government  0.000000000          NA          NA
+## 21                 Indep. commission  0.065056568 0.002580643   25.209438
+## 22                    United Nations  0.038172745 0.002649490   14.407580
+## 23                        Greenpeace  0.004689020 0.002607562    1.798239
+## 24                     \20028 per month  0.000000000          NA          NA
+## 25                     \20056 per month -0.084977509 0.002750651  -30.893604
+## 26                     \20084 per month -0.160748210 0.002916213  -55.122247
+## 27                    \200113 per month -0.221878444 0.002925864  -75.833469
+## 28                    \200141 per month -0.294163816 0.002844194 -103.426084
+## 29                         Only rich  0.000000000          NA          NA
+## 30        Prop. to current emissions  0.057662754 0.002699207   21.362849
+## 31     Prop. to history of emissions  0.030679640 0.002714117   11.303730
+## 32 Rich pay more than poor countries  0.074927931 0.002679618   27.962166
+## 33                         20 of 192  0.000000000          NA          NA
+## 34                         80 of 192  0.107154481 0.002265078   47.307193
+## 35                        160 of 192  0.173181493 0.002384032   72.642272
+## 36          40% of current emissions  0.000000000          NA          NA
+## 37          60% of current emissions  0.026132954 0.002205416   11.849446
+## 38          80% of current emissions  0.053053884 0.002258783   23.487818
+## 39                              None  0.000000000          NA          NA
+## 40               \2006 per hh and month  0.047406399 0.002648398   17.900028
+## 41              \20017 per hh and month  0.010933985 0.002724889    4.012635
+## 42              \20023 per hh and month -0.023959166 0.002638535   -9.080480
+## 43                   Your government  0.000000000          NA          NA
+## 44                 Indep. commission  0.077729780 0.002653729   29.290775
+## 45                    United Nations  0.030758786 0.002624494   11.719893
+## 46                        Greenpeace  0.012420581 0.002770108    4.483790
+## 47                     \20028 per month  0.000000000          NA          NA
+## 48                     \20056 per month -0.110733022 0.002903505  -38.137711
+## 49                     \20084 per month -0.191782558 0.003027556  -63.345665
+## 50                    \200113 per month -0.291316540 0.003078639  -94.625104
+## 51                    \200141 per month -0.379787694 0.002882191 -131.770492
+## 52                         Only rich  0.000000000          NA          NA
+## 53        Prop. to current emissions  0.056480847 0.002812594   20.081409
+## 54     Prop. to history of emissions  0.043676581 0.002797188   15.614462
+## 55 Rich pay more than poor countries  0.045401046 0.002744631   16.541766
+## 56                         20 of 192  0.000000000          NA          NA
+## 57                         80 of 192  0.107780809 0.002389605   45.104030
+## 58                        160 of 192  0.185987301 0.002431676   76.485226
+## 59          40% of current emissions  0.000000000          NA          NA
+## 60          60% of current emissions  0.028210800 0.002319342   12.163279
+## 61          80% of current emissions  0.038497022 0.002344981   16.416773
+## 62                              None  0.000000000          NA          NA
+## 63               \2006 per hh and month  0.012309687 0.002686688    4.581734
+## 64              \20017 per hh and month -0.050191678 0.002702107  -18.575015
+## 65              \20023 per hh and month -0.068078009 0.002704177  -25.175133
+## 66                   Your government  0.000000000          NA          NA
+## 67                 Indep. commission  0.065661468 0.002759607   23.793775
+## 68                    United Nations  0.043434121 0.002756915   15.754611
+## 69                        Greenpeace -0.004138694 0.002912058   -1.421227
+## 70                     \20028 per month  0.000000000          NA          NA
+## 71                     \20056 per month -0.105444490 0.002702673  -39.014884
+## 72                     \20084 per month -0.167525238 0.002834364  -59.105046
+## 73                    \200113 per month -0.277525944 0.002803157  -99.004768
+## 74                    \200141 per month -0.359605089 0.002680793 -134.141324
+## 75                         Only rich  0.000000000          NA          NA
+## 76        Prop. to current emissions  0.091203284 0.002550920   35.753099
+## 77     Prop. to history of emissions  0.090070483 0.002543861   35.407003
+## 78 Rich pay more than poor countries  0.077781900 0.002504744   31.053829
+## 79                         20 of 192  0.000000000          NA          NA
+## 80                         80 of 192  0.076940577 0.002208008   34.846146
+## 81                        160 of 192  0.134596041 0.002248790   59.852638
+## 82          40% of current emissions  0.000000000          NA          NA
+## 83          60% of current emissions  0.011423002 0.002160677    5.286770
+## 84          80% of current emissions  0.033988555 0.002148874   15.816911
+## 85                              None  0.000000000          NA          NA
+## 86               \2006 per hh and month  0.012594565 0.002518411    5.000996
+## 87              \20017 per hh and month -0.037280077 0.002515684  -14.819060
+## 88              \20023 per hh and month -0.084672056 0.002479801  -34.144695
+## 89                   Your government  0.000000000          NA          NA
+## 90                 Indep. commission  0.043987035 0.002548830   17.257734
+## 91                    United Nations -0.005622035 0.002735205   -2.055435
+## 92                        Greenpeace -0.032025463 0.002673662  -11.978126
+##                p         lower         upper        country
+## 1             NA            NA            NA         France
+## 2  7.226159e-224 -0.0953750271 -0.0843468956         France
+## 3   0.000000e+00 -0.1681876847 -0.1566846408         France
+## 4   0.000000e+00 -0.2672677610 -0.2558273500         France
+## 5   0.000000e+00 -0.2973349846 -0.2859558578         France
+## 6             NA            NA            NA         France
+## 7   5.370116e-96  0.0490904481  0.0593100036         France
+## 8   4.102248e-47  0.0331171221  0.0435390844         France
+## 9   4.380069e-27  0.0233334208  0.0337061265         France
+## 10            NA            NA            NA         France
+## 11 6.239429e-297  0.0777368097  0.0864757606         France
+## 12  0.000000e+00  0.1322325464  0.1412283848         France
+## 13            NA            NA            NA         France
+## 14  8.036931e-34  0.0225126894  0.0311964449         France
+## 15 9.511109e-152  0.0539294246  0.0626364558         France
+## 16            NA            NA            NA         France
+## 17  6.795136e-70  0.0405550330  0.0506724242         France
+## 18  5.609365e-03  0.0021137003  0.0123450641         France
+## 19  1.022571e-29 -0.0349643037 -0.0246451365         France
+## 20            NA            NA            NA         France
+## 21 3.156501e-140  0.0599985998  0.0701145359         France
+## 22  4.636712e-47  0.0329798393  0.0433656505         France
+## 23  7.213906e-02 -0.0004217066  0.0097997474         France
+## 24            NA            NA            NA        Germany
+## 25 1.455731e-209 -0.0903686852 -0.0795863332        Germany
+## 26  0.000000e+00 -0.1664638827 -0.1550325381        Germany
+## 27  0.000000e+00 -0.2276130332 -0.2161438557        Germany
+## 28  0.000000e+00 -0.2997383334 -0.2885892990        Germany
+## 29            NA            NA            NA        Germany
+## 30 2.961840e-101  0.0523724056  0.0629531032        Germany
+## 31  1.257611e-29  0.0253600694  0.0359992110        Germany
+## 32 4.689630e-172  0.0696759757  0.0801798863        Germany
+## 33            NA            NA            NA        Germany
+## 34  0.000000e+00  0.1027150093  0.1115939518        Germany
+## 35  0.000000e+00  0.1685088765  0.1778541098        Germany
+## 36            NA            NA            NA        Germany
+## 37  2.166183e-32  0.0218104185  0.0304554892        Germany
+## 38 5.433027e-122  0.0486267509  0.0574810175        Germany
+## 39            NA            NA            NA        Germany
+## 40  1.178625e-71  0.0422156343  0.0525971638        Germany
+## 41  6.004460e-05  0.0055933013  0.0162746686        Germany
+## 42  1.080972e-19 -0.0291306001 -0.0187877321        Germany
+## 43            NA            NA            NA        Germany
+## 44 1.359389e-188  0.0725285663  0.0829309931        Germany
+## 45  1.007986e-31  0.0256148727  0.0359026987        Germany
+## 46  7.332889e-06  0.0069912698  0.0178498930        Germany
+## 47            NA            NA            NA United Kingdom
+## 48  0.000000e+00 -0.1164237867 -0.1050422575 United Kingdom
+## 49  0.000000e+00 -0.1977164589 -0.1858486569 United Kingdom
+## 50  0.000000e+00 -0.2973505613 -0.2852825180 United Kingdom
+## 51  0.000000e+00 -0.3854366842 -0.3741387041 United Kingdom
+## 52            NA            NA            NA United Kingdom
+## 53  1.073077e-89  0.0509682645  0.0619934297 United Kingdom
+## 54  5.803241e-55  0.0381941936  0.0491589676 United Kingdom
+## 55  1.835610e-61  0.0400216677  0.0507804240 United Kingdom
+## 56            NA            NA            NA United Kingdom
+## 57  0.000000e+00  0.1030972691  0.1124643479 United Kingdom
+## 58  0.000000e+00  0.1812213035  0.1907532989 United Kingdom
+## 59            NA            NA            NA United Kingdom
+## 60  4.876126e-34  0.0236649738  0.0327566260 United Kingdom
+## 61  1.450801e-60  0.0339009438  0.0430931007 United Kingdom
+## 62            NA            NA            NA United Kingdom
+## 63  4.611371e-06  0.0070438759  0.0175754978 United Kingdom
+## 64  5.119048e-77 -0.0554877102 -0.0448956456 United Kingdom
+## 65 7.501029e-140 -0.0733780984 -0.0627779202 United Kingdom
+## 66            NA            NA            NA United Kingdom
+## 67 3.874082e-125  0.0602527374  0.0710701983 United Kingdom
+## 68  6.385102e-56  0.0380306668  0.0488375744 United Kingdom
+## 69  1.552509e-01 -0.0098462235  0.0015688348 United Kingdom
+## 70            NA            NA            NA  United States
+## 71  0.000000e+00 -0.1107416331 -0.1001473479  United States
+## 72  0.000000e+00 -0.1730804906 -0.1619699863  United States
+## 73  0.000000e+00 -0.2830200319 -0.2720318569  United States
+## 74  0.000000e+00 -0.3648593460 -0.3543508315  United States
+## 75            NA            NA            NA  United States
+## 76 5.921344e-280  0.0862035730  0.0962029943  United States
+## 77 1.332257e-274  0.0850846075  0.0950563580  United States
+## 78 1.012831e-211  0.0728726920  0.0826911090  United States
+## 79            NA            NA            NA  United States
+## 80 4.870184e-266  0.0726129606  0.0812681938  United States
+## 81  0.000000e+00  0.1301884926  0.1390035893  United States
+## 82            NA            NA            NA  United States
+## 83  1.244952e-07  0.0071881530  0.0156578517  United States
+## 84  2.378815e-56  0.0297768386  0.0382002715  United States
+## 85            NA            NA            NA  United States
+## 86  5.703489e-07  0.0076585697  0.0175305610  United States
+## 87  1.103176e-49 -0.0422107276 -0.0323494261  United States
+## 88 1.602925e-255 -0.0895323769 -0.0798117349  United States
+## 89            NA            NA            NA  United States
+## 90  9.787681e-67  0.0389914198  0.0489826509  United States
+## 91  3.983702e-02 -0.0109829381 -0.0002611325  United States
+## 92  4.626637e-33 -0.0372657443 -0.0267851811  United States
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## Analysis of Deviance Table
+## 
+## Model 1: choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + 
+##     sanctions_cj + monitoring_cj
+## Model 2: choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + 
+##     sanctions_cj + monitoring_cj + country + cost_cj:country + 
+##     distrib_cj:country + ctries_cj:country + emissions_cj:country + 
+##     sanctions_cj:country + monitoring_cj:country
+##   Resid. Df Resid. Dev Df Deviance      F    Pr(>F)    
+## 1     67982      15601                                 
+## 2     67928      15555 54   45.983 3.7187 < 2.2e-16 ***
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce_environmentalism-1}
+
+\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce_environmentalism-2}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_reciprocity_reference-1}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce_reciprocity-1}
+
+\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce_reciprocity-2}
+
+\end{knitrout}
+
+\clearpage
+
 \section{Teele et al. (2018) Candidate Experiment}
@@
 \begin{verbatim}
-## R version 3.5.1 (2018-07-02)
+## R version 3.5.3 (2019-03-11)
 ## Platform: x86_64-w64-mingw32/x64 (64-bit)
@@
 ## other attached packages:
-## [1] ggplot2_3.1.0 cregg_0.3.0   rio_0.5.16   
+## [1] gridExtra_2.3 ggplot2_3.1.1 cregg_0.3.1   rio_0.5.16   
 ## 
 ## loaded via a namespace (and not attached):
-##  [1] zip_1.0.0         Rcpp_1.0.0        cellranger_1.1.0 
-##  [4] pillar_1.3.0.9000 compiler_3.5.1    plyr_1.8.4       
-##  [7] bindr_0.1.1       forcats_0.3.0     tools_3.5.1      
-## [10] digest_0.6.18     lattice_0.20-38   ggstance_0.3.1   
-## [13] evaluate_0.12     tibble_1.4.2      gtable_0.2.0     
-## [16] pkgconfig_2.0.2   rlang_0.3.0.1     Matrix_1.2-15    
-## [19] openxlsx_4.1.0    curl_3.2          haven_2.0.0      
-## [22] bindrcpp_0.2.2    withr_2.1.2       stringr_1.3.1    
-## [25] dplyr_0.7.8       knitr_1.20        hms_0.4.2        
-## [28] lmtest_0.9-36     tidyselect_0.2.5  grid_3.5.1       
-## [31] glue_1.3.0        data.table_1.11.8 R6_2.3.0         
-## [34] survival_2.43-3   readxl_1.1.0      foreign_0.8-71   
-## [37] purrr_0.2.5       magrittr_1.5      splines_3.5.1    
-## [40] scales_1.0.0      assertthat_0.2.0  xtable_1.8-3     
-## [43] colorspace_1.3-2  sandwich_2.5-0    survey_3.34      
-## [46] stringi_1.2.4     lazyeval_0.2.1    munsell_0.5.0    
-## [49] crayon_1.3.4      zoo_1.8-4
+##  [1] zip_2.0.1         Rcpp_1.0.1        cellranger_1.1.0 
+##  [4] pillar_1.3.1      compiler_3.5.3    plyr_1.8.4       
+##  [7] forcats_0.4.0     tools_3.5.3       digest_0.6.18    
+## [10] lattice_0.20-38   evaluate_0.13     tibble_2.1.1     
+## [13] gtable_0.3.0      ggstance_0.3.1    pkgconfig_2.0.2  
+## [16] rlang_0.3.4       Matrix_1.2-17     openxlsx_4.1.0   
+## [19] curl_3.3          haven_2.1.0       xfun_0.6         
+## [22] withr_2.1.2       stringr_1.4.0     knitr_1.22       
+## [25] hms_0.4.2         lmtest_0.9-36     grid_3.5.3       
+## [28] data.table_1.12.2 R6_2.4.0          survival_2.44-1.1
+## [31] readxl_1.3.1      foreign_0.8-71    magrittr_1.5     
+## [34] splines_3.5.3     scales_1.0.0      assertthat_0.2.1 
+## [37] xtable_1.8-3      colorspace_1.4-1  sandwich_2.5-1   
+## [40] survey_3.35-1     stringi_1.4.3     lazyeval_0.2.2   
+## [43] munsell_0.5.0     crayon_1.3.4      zoo_1.8-5
 \end{verbatim}

### 2019-04-13 manuscript.Rnw
incorporate changes from James

@@
 
-{\abstract Conjoint analysis is an increasingly prominent tool for studying political preferences.
-The method powerfully disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as political candidates or public policies.
-Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs), which measure the degree to which a given value of a conjoint profile feature increases or decreases respondents' support for the overall profile relative to a baseline, averaging across all respondents and all other profile features.
-While the AMCE has a clear causal interpretation (about the \textit{effect} of features), most published conjoint analyses also use AMCEs to simply describe \textit{levels} of preferences or favorability, often including comparisons of AMCEs between subgroups of respondents.
-We show how this descriptive use of conditional AMCEs can be substantially misleading about the degree of agreement or disagreement between subgroups due the simple property that regression interactions are sensitive to the reference category used in the analysis.
+{\abstract Conjoint analysis is now a common tool for studying political preferences.
+The method disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as political candidates or public policies.
+Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs).
+These measure the degree to which a given value of a conjoint profile feature increases, or decreases, people’s support for the overall profile relative to a baseline, averaging across all respondents and all other profile features.
+While the AMCE has a clear causal interpretation (about the \textit{effect} of features), most published conjoint analyses also use AMCEs to describe \textit{levels} of preferences or favorability.
+This often means comparing AMCEs among subgroups of respondents.
+We show that using conditional AMCEs to describe the degree of agreement among subgroups can be misleading as regression interactions are sensitive to the reference category used in the analysis.
 This leads to inferences about subgroup differences in preferences that have arbitrary sign, size, and significance.
 We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation using two quantities of interest: the marginal mean and the omnibus F-test.
-Amidst the rapidly accelerating use of conjoint analyses, we highlight common pitfalls and offer advice for best practice in the analysis and presentation of conjoint experiments.}
+Given the accelerating use of conjoint analyses in political science, we offer advice for best practice in the analysis and presentation of conjoint experiments.}
 
@@
 
-Amidst the dramatically increased use of experiments within political science \citep{Druckmanetal2006, Mutz2011}, conjoint experimental designs have recently become a prominent methodological tool in political science.
-While survey experiments have traditionally examined just one or two factors that might shape outcomes \citep[see, for reviews,][]{GainesKuklinskiQuirk2007, Sniderman2011}, conjoint designs allow researchers to study the independent effects on preferences of many features of complex, multidimensional objects such as political candidates \citep{Campbelletal2016, TeeleKallaRosenbluth2018}, immigrant admissions \citep{HainmuellerHopkins2015, BansakHainmuellerHangartner2016, WrightLevyCitrin2016}, or public policies \citep{GallegoMarx2017, Hankinson2018}.
-Factorial designs of this sort have a long history but the driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a small-sample, fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE).
-By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit or implicit confounding between features of these objects, giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' favorability toward a packaged conjoint profile relative to a baseline.
-
-While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs not only for \textit{causal} purposes (interpreting AMCEs as effect sizes), but also for \textit{descriptive} purposes: that is, to map levels of favorability toward a multidimensional object across its various features.\footnote{See \citet{Shmueli2010} for an elaboration on the distinctions between explanatory (causal) modelling, descriptive modelling, and predictive modelling.} In this sense, conjoints are often applied like list experiments, using randomization to measure a sample's preferences over something difficult to measure with direct questioning.
-A positive (negative) AMCE for a given feature can be read as a descriptive measure of high (low) favorability toward profiles with that feature.
-Though the quantity is causal, it is often read descriptively.
-
-This is particularly the case when researchers engage in subgroup analyses of conjoint experiments in search of preference heterogeneity.
+One aspect of the dramatic increase in the use of experiments within political science \citep{Druckmanetal2006, Mutz2011} is the establishment of conjoint experimental designs as a prominent methodological tool.
+While survey experiments have traditionally examined just one or two factors that might shape outcomes \citep[see, for reviews,][]{GainesKuklinskiQuirk2007, Sniderman2011}, conjoint designs allow researchers to study the independent effects on preferences of many features of complex, multidimensional objects.
+These include many different types of phenomena, such as political candidates \citep{Campbelletal2016, TeeleKallaRosenbluth2018}, immigrant admissions \citep{HainmuellerHopkins2015, BansakHainmuellerHangartner2016, WrightLevyCitrin2016}, and public policies \citep{GallegoMarx2017, Hankinson2018}.
+Factorial designs of this sort have a long history, but the driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a small-sample, fully randomized conjoint design.
+The associated analytic approach emphasizes a single quantity of interest: the average marginal component effect (AMCE).
+By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit, or implicit, confounding between features of these objects.
+This gives the AMCE a clear causal interpretation: the degree to which a given value of a feature increases, or decreases, respondents' favorability towards a packaged conjoint profile relative to a baseline.
+
+While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs not only for \textit{causal} purposes (interpreting AMCEs as effect sizes), but also for \textit{descriptive} purposes.
+The aim is to map levels of favorability toward a multidimensional object across its various features.\footnote{See \citet{Shmueli2010} for an elaboration on the distinctions between explanatory (causal) modelling, descriptive modelling, and predictive modelling.} In this sense, conjoints are often applied like list experiments, using randomization to measure a sample's preferences over something difficult to measure with direct questioning.
+A positive AMCE for a given feature can be read as a descriptive measure of high favorability towards profiles with that feature.
+The quantity is causal, but it is often read descriptively.
+
+This is particularly the case for subgroup analyses of conjoint experiments.
 Such exercises are an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017, EgamiImai2018}.
-For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their original immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.
+For example, the \citet{HainmuellerHopkinsYamamoto2014} study of immigration attitudes splits the sample in two using a measure of ethnocentrism and then compares AMCEs for the two subgroups.
 Similarly, \citet{BansakHainmuellerHangartner2016} compare preferences toward immigrants across number of binary respondent characteristics: age, education, left-right ideology, and income.
-In a different domain, \citet{BallardRosaMartinScheve2016} compare preferences over tax policies across a number of subgroups defined by demographics and political orientations.
-\citet{BechtelScheve2013} compare AMCEs on climate agreements across four different countries, and across subgroups of respondents.
-\citet{TeeleKallaRosenbluth2018} compare AMCEs for features of male and female political candidates among male and female respondents.
+Other examples abound.
+\citet{BallardRosaMartinScheve2016} compare preferences over tax policies across a number of subgroups defined by demographics and political orientations; \citet{BechtelScheve2013} compare AMCEs on climate agreements across four different countries, and across subgroups of respondents; and \citet{TeeleKallaRosenbluth2018} compare AMCEs for features of male and female political candidates among male and female respondents.
 Most of these comparisons are visual or informal.
@@
 What is not necessarily obvious in such analyses is that differences-in-preferences (that is to say, the difference in degree of favorability toward profiles containing a given feature) are not directly reflected in subgroup differences-in-AMCEs.
-A difference in effect sizes is distinct from a difference in the preferences so affected.
-We show that a difference in two (or more) subgroups' favorability toward a conojoint feature --- like a difference in willingness to support a Syrian immigrant between high and low ethnocentrism respondents --- is only reflected in the difference-in-AMCEs in very rare circumstances.
-As such, no information about the similarity of the subgroups' preferences is provided by comparisons of subgroup AMCEs, yet such comparisons are commonly made in practice.
-
-As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well but where preferences between subgroups diverge in the reference category, the difference-in-AMCEs is a misleading representation of underlying patterns of favorability.
-Given most published conjoint studies appear to report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment, difference-in-AMCEs should not be assumed to be interpretable as differences in subgroup preferences.\footnote{For example, in a comparison of subgroup effects for Democrats and Republicans, Republicans might display a smaller effect because their preferences in the reference category are already very positive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.} The root of this error is likely familiar to many researchers: it is simply a matter of regression specification for models involving interactions between categorical regressors.
+A difference in effect sizes is distinct from a difference in preferences.
+We show that a difference in two (or more) subgroups' favorability toward a conjoint feature --- like a difference in willingness to support a particular type of immigrant between high and low ethnocentrism respondents --- is only rarely reflected in the difference-in-AMCEs.
+In fact, no information about the similarity of the subgroups' preferences is provided by comparisons of subgroup AMCEs, yet such comparisons are commonly made in practice.
+
+As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well.
+The problem occurs when preferences between subgroups diverge in the reference category.
+Here, the difference-in-AMCEs is a misleading representation of underlying patterns of favorability.
+Given most published conjoint studies report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment, difference-in-AMCEs should not be assumed to be interpretable as differences in subgroup preferences.
+The root of this error is likely familiar to many researchers: it is simply a matter of regression specification for models involving interactions between categorical regressors.
 \citet{EgamiImai2018}, for example, provide an extensive discussion of the implications of this property for interpreting causal interactions between randomized features of conjoint profiles.
@@
 In what follows, we demonstrate the challenges of conjoint analysis and remind readers of how reference category choice for profile features creates problems for comparing conditional AMCEs across respondent subgroups.
-We show how the use of an arbitrary reference category means the size, direction, and statistical significance of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features; reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar.
+We show how the use of an arbitrary reference category means the size, direction, and statistical significance of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features.
+Reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar.
 We demonstrate this with examples drawn from the published political science literature (namely experiments by \citealt{HainmuellerHopkinsYamamoto2014, BechtelScheve2013, TeeleKallaRosenbluth2018}).
@@
 In the full-factorial design discussed by \citet{HainmuellerHopkinsYamamoto2014} and now widely used in political science, many or perhaps most cell means are unobserved.
-For example, in their candidate choice experiment, there are $2*6*6*6*2*6*6*6 = 186,624$ cell means but only 3,466 observations so about 98\% of cell means are unobserved.
+For example, in their candidate choice experiment, there are $2*6*6*6*2*6*6*6 = 186,624$ cell means, but only 3,466 observations.
+About 98\% of cell means are unobserved.
 While this would be problematic for attempting to infer pairwise comparisons between cells, conjoint analysts mostly focus on the marginal effects of each feature rather than more complex interactions.
@@
 A marginal mean describes the level of favorability toward profiles that have a particular feature level, ignoring all other features.
-For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities: a marginal mean of 0 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x) = 0$ while a marginal mean of 1 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x)=1$, where $Y$ is a binary outcome and $X$ is a vector of profile features.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany).
+For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities.
+A marginal mean of 0 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x) = 0$.
+While a marginal mean of 1 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x)=1$, where $Y$ is a binary outcome and $X$ is a vector of profile features.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany).
 Instead, the marginal mean can range from the probability of co-occurrence to 1 minus that probability.
@@
 This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature.
-A positive (negative) AMCE is read as higher (lower) favorability but it is only higher (lower) relative to whatever category serves as the baseline.
-For example, in the \citeauthor{HainmuellerHopkinsYamamoto2014} candidate example, choosing a non-religious candidate as a baseline means the AMCEs in the candidate experiment are all expressed relative to this non-religious baseline; the difference (if any) between other pairs of marginal means (e.g., evaluations of Mormon and Evangelical candidates) is not obvious.
-Relatedly, the negative direction (and the size) of the AMCEs for Mormon and Evangelical candidates would be different if the least-liked category (Mormon candidates) were the reference group.
-In that case, the AMCE for Evangelicals would be small and positive and the AMCEs for all other categories (including the presented reference category, ``none'') would be large and positive.
+A positive AMCE is read as higher favorability but it is only higher relative to whatever category serves as the baseline.
+For example, in the \citeauthor{HainmuellerHopkinsYamamoto2014} candidate example, choosing a non-religious candidate as a baseline and interpreting the resulting AMCES means that the differences between other pairs of marginal means (e.g., evaluations of Mormon and Evangelical candidates) are not obvious.
+The negative direction, and the size, of the AMCEs for Mormon and Evangelical candidates would be different if the least-liked category of Mormons were the reference group.
 More trivially, \citet{TeeleKallaRosenbluth2018} describe their comparisons about public preferences for female candidates relative to male candidates, but could have equivalent described patterns of equal size but opposite sign comparing preferences over male relative to female candidates.
@@
 
+% DECIDE WHETHER TO KEEP THIS (AND FIGURE 2):
+
 Though seemingly arbitrary, the choice of reference category for estimating AMCEs can be quite consequential.\footnote{Since this manuscript has been under review, we have been made aware of one working paper by \citet{ClaytonFerwerdaHoriuchi2018}, on the topic of immigration preferences, that correctly notes the need to address the arbitrary reference category in order to compare subgroup preferences.} For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment (again, see \ref{fig:hainmueller_candidate_replication}), the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline.
@@
 
-Given the need to choose a reference category for every feature in order to estimate AMCEs, an important question is: how do researchers decide which of tens of thousands of possible experimental cells should be selected as the reference category?
+How do researchers decide which of tens of thousands of possible experimental cells should be selected as the reference category?
 Examining recently published conjoint analyses, it appears that the choice of reference category is either arbitrary or based upon substantive intuition about the meaning of feature levels.
@@
 Consider, for example, a two-condition candidate choice experiment where Democratic and Republican respondents are exposed to either a male or female candidate and opinions toward the candidate serve as the outcome.
-It is sensible to imagine that effects of candidate sex might differ for the two groups and therefore to compare the size of treatment between the two groups.
+It is reasonable to imagine that effects of candidate sex might differ for the two groups and therefore to compare the size of treatment between the two groups.
 Perhaps Democrats are more responsive to candidate sex than are Republicans, making the causal effect larger for Democrats than Republicans.
@@
 
-Discussions of conditional AMCEs in conjoint analyses often explicitly or implicitly engage in this kind of discussion comparing the size and direction of subgroup causal effects.
-Indeed, Table \ref{tab:papers} reports a list of recently published articles in political science that engage in this form of subgroup analysis.
-Given the common practice of descriptively interpreting conjoint experimental results, such subgroup analyses seem perfectly intuitive and the set of subgroups listed in the last column of Table \ref{tab:papers} contains some unsurprising covariates, such as partisanship, that are of obvious theoretical interest in almost any study of individual preferences.
+As Table \ref{tab:papers} shows, discussions of conditional AMCEs in conjoint analyses often compare the size, and direction, of subgroup causal effects.
+Given the common practice of descriptively interpreting conjoint experimental results, such subgroup analyses seem perfectly intuitive.
+The set of subgroups listed in the last column of Table \ref{tab:papers} contains some unsurprising covariates, such as partisanship, that are of obvious theoretical interest in almost any study of individual preferences.
 If interpreted as a difference in the size of the \textit{causal effect} for two groups, such comparisons are perfectly consistent with more traditional experimental analysis and a perfectly acceptable interpretation of the conjoint results.
@@
 
-Yet, just as analysis of full sample conjoint data is often descriptive in nature, so too do conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally.
+Yet, just as analysis of full sample conjoint data is often descriptive in nature, it is also the case that conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally.
 For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} visually compare the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22).
@@
 
-The selection of a reference category, while earlier an innocuous analytic decisions, becomes substantially consequential for this kind descriptive reading of conditional AMCEs.
-Most obviously, using AMCEs descriptively prevents analysts from describing levels of favorability in the reference category but also can lead to misinterpretations of patterns in preferences.
+The selection of a reference category, while earlier an innocuous analytic decision, becomes substantially consequential for a descriptive reading of conditional AMCEs.
+Most obviously, using AMCEs descriptively prevents any description of the levels of favorability in the reference category.
+It can also lead to misinterpretations of patterns in preferences.
 AMCEs are relative, not absolute, statements about preferences.
@@
 Yet analysts and their readers frequently interpret differences in conditional AMCEs as differences in underlying preferences.
-While AMCEs do provide insight into the descriptive variation in preferences within-group and across-features, and conditional AMCEs do estimate the size of causal effects of features within groups, AMCEs cannot provide direct insight into the pattern of preferences between groups because they do not provide information about \textit{absolute} levels of favorability toward profiles with each feature (or combination of features).
+AMCEs do provide insight into the descriptive variation in preferences within-group and across-features, and conditional AMCEs do estimate the size of causal effects of features within groups.
+But AMCEs cannot provide direct insight into the pattern of preferences between groups because they do not provide information about \textit{absolute} levels of favorability toward profiles with each feature (or combination of features).
 
@@
 The difference-in-AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$.
-Yet the standard AMCE-centric conjoint analysis does not present or characterize absolute favorability in the reference category.
+Yet the standard AMCE-centric conjoint analysis does not present absolute favorability in the reference category.
 Similarity of conditional AMCEs only means similarity of the \textit{causal effect} of the feature across groups, not similarity of \textit{preferences} unless preferences toward profiles with the reference category are equivalent in both groups.
-Given the reference category choice is typically arbitrary or driven by substantive knowledge of the levels, there is never any reason to expect that an arbitrarily selected reference category satisfies this equality requirement.
+Given the reference category choice is typically arbitrary or driven by substantive knowledge of the levels, there is never any reason to expect that the reference category satisfies this equality requirement.
 When using a difference-in-AMCEs comparison to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.
@@
 The second panel shows full sample marginal means.
-The third panel shows conditional AMCEs separately for Democratic and Republican voters, as provided in the original paper and the lower panel shows the results using conditional marginal means for Democratic and Republican voters.\footnote{We opt here for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.} Respondents' preference for female candidates is very apparent in both forms of analysis in the upper two panels because the AMCE definitionally equals the difference in marginal means.
+Respondents' preference for female candidates is very apparent in both forms of analysis in the upper two panels because the AMCE definitionally equals the difference in marginal means.
 But how do Republicans and Democrats differ in their preferences over male and female candidates?
-By requiring a reference category fixed to zero, the conditional AMCE results in the third panel suggest that there is a very large difference in favorability toward female candidates between Republican and Democratic respondents.
+The third panel shows conditional AMCEs separately for Democratic and Republican voters, as provided in the original paper and the lower panel shows the results using conditional marginal means for Democratic and Republican voters.\footnote{We opt here for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.} By requiring a reference category fixed to zero, the conditional AMCE results in the third panel suggest that there is a very large difference in favorability toward female candidates between Republican and Democratic respondents.
 In reality, however, the difference in these conditional AMCEs (0.086) reflects the true difference in favorability toward female candidates (difference: 0.045; Democrats: 0.537, Republicans: 0.492) \textit{plus} the difference in favorability toward male candidates (difference: 0.045; Democrats: 0.463, Republicans: 0.508).
@@
 
-We can also see this bias clearly in a reanalysis of \citeauthor{BechtelScheve2013}'s four-country climate change agreement experiment.
-Figure \ref{fig:bechtel_difference_comparison} shows an analysis for the feature capturing the monthly household cost for a potential international climate agreement, replicating a portion of the results they present comparing high- and low-environmentalism respondents (pooling across countries) \citet[13767 figure 4]{BechtelScheve2013}.
-The original analysis was presented as conditional AMCEs for the two subgroups with 28 Euro per month as the reference category.
-Conditional AMCEs for both groups were presented as negative with conditional AMCEs for low-environmentalism respondents being more negative than the conditional AMCEs for high-environmentalism respondents at every feaure level.
+We can also see this bias in a reanalysis of \citeauthor{BechtelScheve2013}'s four-country climate change agreement experiment.
+Figure \ref{fig:bechtel_difference_comparison} shows an analysis for the feature capturing the monthly household cost for a potential international climate agreement.
+This replicates a portion of their results which compare high- and low-environmentalism respondents pooled across countries (\citet[13767 figure 4]{BechtelScheve2013}.
+The original analysis has conditional AMCEs for the two subgroups with 28 Euro per month as the reference category.
+Conditional AMCEs for both groups are presented as negative with conditional AMCEs for low-environmentalism respondents being more negative than the conditional AMCEs for high-environmentalism respondents at every feature level.
 This implies positive differences in favorability toward each monthly cost between high- and low-environmentalism respondents.
@@
 Even in the 84 Euro per month level, the difference between the two groups is slightly positive.
-Were there a category for which subgroup preferences were exactly equal, that could be sensibly chosen as the reference category in order to be able to interpret differences-in-AMCEs as differences in preferences.
-But there is never any guarantee, however, that such a reference category exists in any given experimental dataset.
+Were there a category for which subgroup preferences were exactly equal, then we could choose that as the reference category and interpret differences-in-AMCEs as differences in preferences.
+But there is never any guarantee that such a reference category exists.
 If multiple subgroup analyses are performed, it is unlikely the same reference category would work well across all analyses, making consistent interpretation difficult.
-And because conjoint analysis generates a sparse feature matrix (where there is never any guarantee that a particular combination of feature levels is observed in the data), it is also not possible to empirically select an appropriate set of reference categories using the observed data.
+And because conjoint analysis generates a sparse feature matrix (where many combinations of feature levels are unobserved in the data), it is rarely possible to empirically select an appropriate set of reference categories using the observed data.
 It is impossible to know which cell --- of the tens of thousands in the design --- is the best choice of reference.
@@
 We suggest that conjoint analyses should report not only average marginal component effects (AMCEs) but also descriptive quantities that better convey underlying preferences over profile features and better convey subgroup differences in those preferences.
-Our intention here is not to substantively undermine any previous set of results but instead to urge researchers moving forward to demonstrate considerable caution in how they design, analyze, and present the results of these types of descriptive experiments.
+Our intention here is not to substantively undermine any previous set of results, but instead to urge researchers moving forward to demonstrate considerable caution in how they design, analyze, and present the results of these types of descriptive experiments.
 We have relatively straightforward and hopefully uncontroversial advice for how analysts of conjoint experiments should proceed:
@@
 \begin{enumerate}
-\item Always report unadjusted marginal means when attempting to provide a \textit{descriptive} summary of respondent preferences in addition to or instead of AMCEs.\footnote{Like the presentation of AMCEs, displaying marginal means in constrained conjoint designs may also distort apparent patterns given that not all features can co-occur.
+\item Always report unadjusted marginal means when attempting to provide a \textit{descriptive} summary of respondent preferences in addition to , or instead of, AMCEs.\footnote{Like the presentation of AMCEs, displaying marginal means in constrained conjoint designs may also distort apparent patterns given that not all features can co-occur.
 Partitioning the design into fractions such that each fraction contains a fully unconstrained design would mitigate any concern with that presentation.}
 
-\item Exercise caution when explicitly or implicitly interpreting differences-in-AMCEs across subgroups.
+\item Exercise caution when explicitly, or implicitly, interpreting differences-in-AMCEs across subgroups.
 Differences-in-AMCEs are differences in effect sizes for subgroups, not statments about the relative favorability of the subgroups toward profiles with a feature.

### 2019-04-13 manuscript.tex
incorporate changes from James

@@
 
-{\abstract Conjoint analysis is an increasingly prominent tool for studying political preferences.
-The method powerfully disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as political candidates or public policies.
-Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs), which measure the degree to which a given value of a conjoint profile feature increases or decreases respondents' support for the overall profile relative to a baseline, averaging across all respondents and all other profile features.
-While the AMCE has a clear causal interpretation (about the \textit{effect} of features), most published conjoint analyses also use AMCEs to simply describe \textit{levels} of preferences or favorability, often including comparisons of AMCEs between subgroups of respondents.
-We show how this descriptive use of conditional AMCEs can be substantially misleading about the degree of agreement or disagreement between subgroups due the simple property that regression interactions are sensitive to the reference category used in the analysis.
+{\abstract Conjoint analysis is now a common tool for studying political preferences.
+The method disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as political candidates or public policies.
+Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs).
+These measure the degree to which a given value of a conjoint profile feature increases, or decreases, people’s support for the overall profile relative to a baseline, averaging across all respondents and all other profile features.
+While the AMCE has a clear causal interpretation (about the \textit{effect} of features), most published conjoint analyses also use AMCEs to describe \textit{levels} of preferences or favorability.
+This often means comparing AMCEs among subgroups of respondents.
+We show that using conditional AMCEs to describe the degree of agreement among subgroups can be misleading as regression interactions are sensitive to the reference category used in the analysis.
 This leads to inferences about subgroup differences in preferences that have arbitrary sign, size, and significance.
 We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation using two quantities of interest: the marginal mean and the omnibus F-test.
-Amidst the rapidly accelerating use of conjoint analyses, we highlight common pitfalls and offer advice for best practice in the analysis and presentation of conjoint experiments.}
-
-\clearpage
-
-Amidst the dramatically increased use of experiments within political science \citep{Druckmanetal2006, Mutz2011}, conjoint experimental designs have recently become a prominent methodological tool in political science.
-While survey experiments have traditionally examined just one or two factors that might shape outcomes \citep[see, for reviews,][]{GainesKuklinskiQuirk2007, Sniderman2011}, conjoint designs allow researchers to study the independent effects on preferences of many features of complex, multidimensional objects such as political candidates \citep{Campbelletal2016, TeeleKallaRosenbluth2018}, immigrant admissions \citep{HainmuellerHopkins2015, BansakHainmuellerHangartner2016, WrightLevyCitrin2016}, or public policies \citep{GallegoMarx2017, Hankinson2018}.
-Factorial designs of this sort have a long history but the driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a small-sample, fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE).
-By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit or implicit confounding between features of these objects, giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' favorability toward a packaged conjoint profile relative to a baseline.
-
-While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs not only for \textit{causal} purposes (interpreting AMCEs as effect sizes), but also for \textit{descriptive} purposes: that is, to map levels of favorability toward a multidimensional object across its various features.\footnote{See \citet{Shmueli2010} for an elaboration on the distinctions between explanatory (causal) modelling, descriptive modelling, and predictive modelling.} In this sense, conjoints are often applied like list experiments, using randomization to measure a sample's preferences over something difficult to measure with direct questioning.
-A positive (negative) AMCE for a given feature can be read as a descriptive measure of high (low) favorability toward profiles with that feature.
-Though the quantity is causal, it is often read descriptively.
-
-This is particularly the case when researchers engage in subgroup analyses of conjoint experiments in search of preference heterogeneity.
+Given the accelerating use of conjoint analyses in political science, we offer advice for best practice in the analysis and presentation of conjoint experiments.}
+
+\clearpage
+
+One aspect of the dramatic increase in the use of experiments within political science \citep{Druckmanetal2006, Mutz2011} is the establishment of conjoint experimental designs as a prominent methodological tool.
+While survey experiments have traditionally examined just one or two factors that might shape outcomes \citep[see, for reviews,][]{GainesKuklinskiQuirk2007, Sniderman2011}, conjoint designs allow researchers to study the independent effects on preferences of many features of complex, multidimensional objects.
+These include many different types of phenomena, such as political candidates \citep{Campbelletal2016, TeeleKallaRosenbluth2018}, immigrant admissions \citep{HainmuellerHopkins2015, BansakHainmuellerHangartner2016, WrightLevyCitrin2016}, and public policies \citep{GallegoMarx2017, Hankinson2018}.
+Factorial designs of this sort have a long history, but the driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a small-sample, fully randomized conjoint design.
+The associated analytic approach emphasizes a single quantity of interest: the average marginal component effect (AMCE).
+By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit, or implicit, confounding between features of these objects.
+This gives the AMCE a clear causal interpretation: the degree to which a given value of a feature increases, or decreases, respondents' favorability towards a packaged conjoint profile relative to a baseline.
+
+While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs not only for \textit{causal} purposes (interpreting AMCEs as effect sizes), but also for \textit{descriptive} purposes.
+The aim is to map levels of favorability toward a multidimensional object across its various features.\footnote{See \citet{Shmueli2010} for an elaboration on the distinctions between explanatory (causal) modelling, descriptive modelling, and predictive modelling.} In this sense, conjoints are often applied like list experiments, using randomization to measure a sample's preferences over something difficult to measure with direct questioning.
+A positive AMCE for a given feature can be read as a descriptive measure of high favorability towards profiles with that feature.
+The quantity is causal, but it is often read descriptively.
+
+This is particularly the case for subgroup analyses of conjoint experiments.
 Such exercises are an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017, EgamiImai2018}.
-For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their original immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups.
+For example, the \citet{HainmuellerHopkinsYamamoto2014} study of immigration attitudes splits the sample in two using a measure of ethnocentrism and then compares AMCEs for the two subgroups.
 Similarly, \citet{BansakHainmuellerHangartner2016} compare preferences toward immigrants across number of binary respondent characteristics: age, education, left-right ideology, and income.
-In a different domain, \citet{BallardRosaMartinScheve2016} compare preferences over tax policies across a number of subgroups defined by demographics and political orientations.
-\citet{BechtelScheve2013} compare AMCEs on climate agreements across four different countries, and across subgroups of respondents.
-\citet{TeeleKallaRosenbluth2018} compare AMCEs for features of male and female political candidates among male and female respondents.
+Other examples abound.
+\citet{BallardRosaMartinScheve2016} compare preferences over tax policies across a number of subgroups defined by demographics and political orientations; \citet{BechtelScheve2013} compare AMCEs on climate agreements across four different countries, and across subgroups of respondents; and \citet{TeeleKallaRosenbluth2018} compare AMCEs for features of male and female political candidates among male and female respondents.
 Most of these comparisons are visual or informal.

### 2019-04-13 manuscript.Rnw
drop bms examples; update and expand SI

@@
 
-<<data_bms>>=
-if (file.exists("data/bms.rds")) {
-    bms <- cj_df(rio::import("data/bms.rds"))
-} else {
-    bms <- cj_df(rio::import("data/ballard-rosa.dta"))
-
-    # setup terms
-    bms$taxrate1 <- factor(rio::characterize(bms$taxrate1),
-                           levels = c("0%", "5%", "15%", "25%"),
-                           labels = c("<10k: 0%", "<10k: 5%", "<10k: 15%", "<10k: 25%"))
-    bms$taxrate2 <- factor(rio::characterize(bms$taxrate2),
-                           levels = c("5%", "15%", "25%", "35%"),
-                           labels = c("10-35k: 5%", "10-35k: 15%", "10-35k: 25%", "10-35k: 35%"))
-    bms$taxrate3 <- factor(rio::characterize(bms$taxrate3),
-                           levels = c("5%", "15%", "25%", "35%"),
-                           labels = c("35-85k: 5%", "35-85k: 15%", "35-85k: 25%", "35-85k: 35%"))
-    bms$taxrate4 <- factor(rio::characterize(bms$taxrate4),
-                           levels = c("5%", "15%", "25%", "35%"),
-                           labels = c("85-175k: 5%", "85-175k: 15%", "85-175k: 25%", "85-175k: 35%"))
-    bms$taxrate5 <- factor(rio::characterize(bms$taxrate5),
-                           levels = c("5%", "15%", "25%", "35%", "45%"),
-                           labels = c("175-375k: 5%", "175-375k: 15%", "175-375k: 25%", "175-375k: 35%", "175-375k: 45%"))
-    bms$taxrate6 <- factor(rio::characterize(bms$taxrate6),
-                           levels = c("5%", "15%", "25%", "35%", "45%", "55%"),
-                           labels = c(">375k: 5%", ">375k: 15%", ">375k: 25%", ">375k: 35%", ">375k: 45%", ">375k: 55%"))
-    bms$taxrev <- factor(rio::characterize(bms$taxrev),
-                         levels = rev(c("Much more revenue (>125%)",
-                                        "More revenue (105-125%)",
-                                        "About the same revenue (95-105%)",
-                                        "Less revenue (75-95%)",
-                                        "Much less revenue (<75%)")),
-                         labels = c("<75%", "75-95%", "95-105%", "105-125%", ">125%"))
-
-    # subset variables
-    bms <- bms[c("chose_plan", "taxrate1", "taxrate2", "taxrate3", "taxrate4", "taxrate5", "taxrate6", "taxrev",
-                 "ineq_averse_dum", "hh_income", "taxes_harm_econ", "work_vs_luck", "race", "above_avg_racial_resentment",
-                 "repub_7pt", "democ_7pt", "indep_7pt", "ID", "weight", "saw_revenue")]
-
-    # subset (according to original do file)
-    bms <- bms[bms$saw_revenue == 1,]
-
-    # label
-    attr(bms$taxrate1, "label") <- "Tax rate for <$10,000"
-    attr(bms$taxrate2, "label") <- "Tax rate for $10,000-$35,000"
-    attr(bms$taxrate3, "label") <- "Tax rate for $25,000-$85,000"
-    attr(bms$taxrate4, "label") <- "Tax rate for $85,000-$175,000"
-    attr(bms$taxrate5, "label") <- "Tax rate for $175,000-$375,000"
-    attr(bms$taxrate6, "label") <- "Tax rate for >$375,000"
-    attr(bms$taxrev, "label") <- "Tax revenue"
-
-    # export
-    rio::export(bms, "data/bms.rds")
-}
-bms$taxes_harm_split <- factor(ifelse(bms$taxes_harm_econ == 1, "Help", ifelse(bms$taxes_harm_econ == 2, "Harm", NA)))
-@
-
 <<data_bechtel>>=
@@
 \citet{EgamiImai2018}, for example, provide an extensive discussion of the implications of this property for interpreting causal interactions between randomized features of conjoint profiles.
-The state of the published literature would suggest the problem remains non-obvious when applied to descriptive analysis of subgroups in conjoint designs.
+The state of the published literature would suggest the problem remains non-obvious when applied to descriptive analysis of subgroups in conjoint designs.\footnote{Since this manuscript has been under review, we have been made aware of one working paper by \citet{ClaytonFerwerdaHoriuchi2018}, on the topic of immigration preferences, that correctly notes the need to address the arbitrary reference category in order to compare subgroup preferences.}
 
@@
 More trivially, \citet{TeeleKallaRosenbluth2018} describe their comparisons about public preferences for female candidates relative to male candidates, but could have equivalent described patterns of equal size but opposite sign comparing preferences over male relative to female candidates.
-
-<<reference_category, dependson=c("data_hainmueller_immigration"), fig.width=8, fig.height=4, fig.cap="Estimated AMCEs for Levels of the `Education' Feature for Each Possible Reference Category from Hainmueller et al.'s (2014) Immigration Experiment">>=
-tmp <- amce_by_reference(hainmueller_immigration, ChosenImmigrant ~ Education, ~ Education, id = ~CaseID)
-ggplot(tmp, aes(x = estimate, y = level, group = BY, colour = BY)) +
-  geom_vline(xintercept = 0, colour = "gray") +
-  geom_point(position = ggstance::position_dodgev(height = 1)) +
-  geom_errorbarh(aes(xmin = lower, xmax = upper),  
-                 size = 0.2, height = 0,
-                 position = ggstance::position_dodgev(height = 1)) + 
-  scale_colour_discrete(
-    guide = ggplot2::guide_legend(
-      title = "Reference Category",
-      title.position = "top",
-      ncol = 2
-    )
-  ) +
-  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
-  ylab("") +
-  xlab("Estimated AMCE") + 
-  theme_minimal() + 
-  ggplot2::theme(
-    legend.position = "bottom",
-    panel.grid.major = ggplot2::element_blank(),
-    panel.grid.minor = ggplot2::element_blank()
-  )
-rm(tmp)
-@
-
-% DECIDE WHETHER TO KEEP THIS (AND FIGURE 2):
-
-Though seemingly arbitrary, the choice of reference category for estimating AMCEs can be quite consequential.\footnote{Since this manuscript has been under review, we have been made aware of one working paper by \citet{ClaytonFerwerdaHoriuchi2018}, on the topic of immigration preferences, that correctly notes the need to address the arbitrary reference category in order to compare subgroup preferences.} For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment (again, see \ref{fig:hainmueller_candidate_replication}), the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline.
-Figure \ref{fig:reference_category} shows how the estimated AMCEs for each level of the education feature would have differed depending on that choice.
-Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline.
-The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.\footnote{In \textit{constrained} conjoint designs, the choice of reference category is even more important.
-Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature.
-Consequently, the AMCE for the ``Escape Persecution'' level (relative to the  ``Reunite with family'' reference category) is only defined for the subset of the design involving countries `China,' `Sudan,' `Somalia,' and `Iraq.' The AMCEs for those four countries (relative to India as a baseline) marginalize across all reasons for application, but the AMCEs for the first six countries marginalize only across the latter two reasons.
-Thus the interpretation of AMCEs --- and the basic ability to estimate them in constrained designs --- depends entirely upon the selection of a reference category where all feature levels can co-occur.
-In a design where \textit{all} features are constrained, then AMCEs are undefined for the design as a whole and only estimable for subsets of the design that are \textit{conditionally} unconstrained.}
-
-%To demonstrate this, Figure \ref{fig:reference_category} shows the estimated AMCEs for the country of origin feature from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, with the analysis repeated ten times each time using a different country as the reference category.
-For example, the top-most set of points and error bars convey the AMCE for Iraq from each of these analyses.
-When Iraq is the reference category, its AMCE is undefined.
-When any other country is chosen as a reference category, the AMCE for Iraq is negative because respondents are more negative toward Iraqi immigrants than they are toward those of other countries.
-Similarly, the bottom set of points and error bars reflects the estimated AMCEs for Germany.
-When Germany is the reference category, its AMCE is undefined but when any other country is used as the reference category, its AMCE is positive.
-
-%These cases are therefore not \textit{directionally} sensitive to the choice of reference category but of course the point estimates vary considerably.
-But the estimated AMCE of countries who are neither strongly disliked or strongly favored by respondents are highly sensitive to choice of reference category.
-Consider, for example, the estimated AMCEs for China (the four set of points from the top).
-When highly disliked countries are chosen as the reference category (like Somalia, Sudan, or Iraq), the AMCE for China is positive; when highly favored countries are chosen (like Germany, Poland, or the Philippines), the AMCE for China is negative.
+Appendix \ref{app:referencecategory} includes some additional illustrations of this point for interested readers.
 
@@
 
+Yet, just as analysis of full sample conjoint data is often descriptive in nature, it is also the case that conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally.
+For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} visually compare the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22).
+\citet{BallardRosaMartinScheve2016} make similar comparisons in their tax policy conjoint: ``While there are few strong differences in preferences for taxing the lower three income groups (the `hard work' group has slightly lower elasticities for taxing the poor), there are strong differences in preferences for taxing the rich'' (12).
+In \citet{BechtelScheve2013} conjoint on support for international climate change agreements in the United States, United Kingdom, Germany, and France, they summarize their results as ``We find that individuals in all four countries largely agree on which dimensions are important and to what extent'' (13765).
+In these examples, the differences between conditional AMCEs are used as a way of descriptively characterizing differences in \textit{preferences} (i.e.
+levels of support) between the groups rather than differences in \textit{causal effects on preferences} in the groups.
+
+The selection of a reference category, while earlier an innocuous analytic decision, becomes substantially consequential for a descriptive reading of conditional AMCEs.
+Most obviously, using AMCEs descriptively prevents any description of the levels of favorability in the reference category.
+It can also lead to misinterpretations of patterns in preferences.
+AMCEs are relative, not absolute, statements about preferences.
+As such, there is simply no predictable connection between subgroup causal effects and the levels of underlying subgroup preferences.
+Yet analysts and their readers frequently interpret differences in conditional AMCEs as differences in underlying preferences.
+AMCEs do provide insight into the descriptive variation in preferences within-group and across-features, and conditional AMCEs do estimate the size of causal effects of features within groups.
+But AMCEs cannot provide direct insight into the pattern of preferences between groups because they do not provide information about \textit{absolute} levels of favorability toward profiles with each feature (or combination of features).
+
+This additional information matters.
+Consider again the simple two-condition experiment in which the effect of a male as opposed to female candidate, $x \in {0,1}$, is compared across a single two-category covariate, $z \in {0,1}$ such as Democratic or Republican self-identification.
+Subgroup regression equations to estimate effects for each group are:
+
+\begin{align*}
+\hat{y} &= \beta_0 + \beta_1 x + \epsilon, \quad \forall z = 0 \\
+\hat{y} &= \beta_2 + \beta_3 x + \epsilon, \quad \forall z = 1
+\end{align*}
+
+\noindent The effect of $x$ when $z=0$ is given by $\beta_1$.
+The effect of $x$ when $z=1$ is given by $\beta_3$.
+These are, in essence, the conditional AMCEs in a conjoint analysis.
+Yet the difference in AMCEs ($\beta_3 - \beta_1$) is not equal to the difference in preferences between the two groups, which is $\bar{y}_{z=1|x=1} - \bar{y}_{z=0|x=1}$ (estimated by $(\beta_2 + \beta_3) - (\beta_0 + \beta_1)$).
+The difference-in-AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$.
+Yet the standard AMCE-centric conjoint analysis does not present absolute favorability in the reference category.
+Similarity of conditional AMCEs only means similarity of the \textit{causal effect} of the feature across groups, not similarity of \textit{preferences} unless preferences toward profiles with the reference category are equivalent in both groups.
+Given the reference category choice is typically arbitrary or driven by substantive knowledge of the levels, there is never any reason to expect that the reference category satisfies this equality requirement.
+When using a difference-in-AMCEs comparison to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.
+
 <<tkr_replication, dependson=c("data_tkr"), fig.height=4.5, fig.width=5, fig.cap="Replication of Results for `Candidate Sex' Feature from Teele et al.
@@
    tkr, 
-   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   winner ~ feature_sex,
    id = ~ responseid,
@@
 
-Yet, just as analysis of full sample conjoint data is often descriptive in nature, it is also the case that conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally.
-For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} visually compare the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22).
-\citet{BallardRosaMartinScheve2016} make similar comparisons in their tax policy conjoint: ``While there are few strong differences in preferences for taxing the lower three income groups (the `hard work' group has slightly lower elasticities for taxing the poor), there are strong differences in preferences for taxing the rich'' (12).
-In \citet{BechtelScheve2013} conjoint on support for international climate change agreements in the United States, United Kingdom, Germany, and France, they summarize their results as ``We find that individuals in all four countries largely agree on which dimensions are important and to what extent'' (13765).
-In these examples, the differences between conditional AMCEs are used as a way of descriptively characterizing differences in \textit{preferences} (i.e.
-levels of support) between the groups rather than differences in \textit{causal effects on preferences} in the groups.
-
-The selection of a reference category, while earlier an innocuous analytic decision, becomes substantially consequential for a descriptive reading of conditional AMCEs.
-Most obviously, using AMCEs descriptively prevents any description of the levels of favorability in the reference category.
-It can also lead to misinterpretations of patterns in preferences.
-AMCEs are relative, not absolute, statements about preferences.
-As such, there is simply no predictable connection between subgroup causal effects and the levels of underlying subgroup preferences.
-Yet analysts and their readers frequently interpret differences in conditional AMCEs as differences in underlying preferences.
-AMCEs do provide insight into the descriptive variation in preferences within-group and across-features, and conditional AMCEs do estimate the size of causal effects of features within groups.
-But AMCEs cannot provide direct insight into the pattern of preferences between groups because they do not provide information about \textit{absolute} levels of favorability toward profiles with each feature (or combination of features).
-
-This additional information matters.
-Consider again the simple two-condition experiment in which the effect of a male as opposed to female candidate, $x \in {0,1}$, is compared across a single two-category covariate, $z \in {0,1}$ such as Democratic or Republican self-identification.
-Subgroup regression equations to estimate effects for each group are:
-
-\begin{align*}
-\hat{y} &= \beta_0 + \beta_1 x + \epsilon, \quad \forall z = 0 \\
-\hat{y} &= \beta_2 + \beta_3 x + \epsilon, \quad \forall z = 1
-\end{align*}
-
-\noindent The effect of $x$ when $z=0$ is given by $\beta_1$.
-The effect of $x$ when $z=1$ is given by $\beta_3$.
-These are, in essence, the conditional AMCEs in a conjoint analysis.
-Yet the difference in AMCEs ($\beta_3 - \beta_1$) is not equal to the difference in preferences between the two groups, which is $\bar{y}_{z=1|x=1} - \bar{y}_{z=0|x=1}$ (estimated by $(\beta_2 + \beta_3) - (\beta_0 + \beta_1)$).
-The difference-in-AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$.
-Yet the standard AMCE-centric conjoint analysis does not present absolute favorability in the reference category.
-Similarity of conditional AMCEs only means similarity of the \textit{causal effect} of the feature across groups, not similarity of \textit{preferences} unless preferences toward profiles with the reference category are equivalent in both groups.
-Given the reference category choice is typically arbitrary or driven by substantive knowledge of the levels, there is never any reason to expect that the reference category satisfies this equality requirement.
-When using a difference-in-AMCEs comparison to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.
-
 To draw this example out more fully, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment for the full sample of respondents.
@@
 The third panel shows conditional AMCEs separately for Democratic and Republican voters, as provided in the original paper and the lower panel shows the results using conditional marginal means for Democratic and Republican voters.\footnote{We opt here for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.} By requiring a reference category fixed to zero, the conditional AMCE results in the third panel suggest that there is a very large difference in favorability toward female candidates between Republican and Democratic respondents.
-In reality, however, the difference in these conditional AMCEs (0.086) reflects the true difference in favorability toward female candidates (difference: 0.045; Democrats: 0.537, Republicans: 0.492) \textit{plus} the difference in favorability toward male candidates (difference: 0.045; Democrats: 0.463, Republicans: 0.508).
-Because Democrats and Republicans actually differ in their views of profiles containing the reference (male) category, AMCEs sum the true differences in preferences for a given feature level with the difference in preferences toward the reference category.\footnote{Another example that clearly demonstrates the discrepancy between the differences in preferences and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature of this experiment (see Supporting Materials).
-The conditional AMCEs correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates.
-Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates).
-In reality, however, the conditional marginal means reveal that actually Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience.
-Democrats are much more sensitive to experience than are Republicans and important differences in preferences between the groups are apparent for very high and very low experience, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.}
-
-<<bechtel_difference_comparison, dependson=c("data_bms"), fig.width=8, fig.height=3, fig.cap="True Difference in Favorability and Implied Preference Differences between High and Low Environmentalism Respondents for `Monthly Cost' Feature from Bechtel and Scheve (2013) Climate Agreement Experiment for Each Possible Reference Category">>=
+In reality, however, the difference in these conditional AMCEs (0.089) reflects the true difference in favorability toward female candidates (difference: 0.045; Democrats: 0.537, Republicans: 0.492) \textit{plus} the difference in favorability toward male candidates (difference: 0.045; Democrats: 0.463, Republicans: 0.508).
+Because Democrats and Republicans actually differ in their views of profiles containing the reference (male) category, AMCEs sum the true differences in preferences for a given feature level with the difference in preferences toward the reference category.\footnote{Another example that clearly demonstrates the discrepancy between the differences in preferences and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature of this experiment (see Appendix \ref{app:tkrpolexperience}).}
+
+<<bechtel_difference_comparison, dependson=c("data_bms"), fig.width=7.5, fig.height=3, fig.cap="True Difference in Favorability and Implied Preference Differences between High and Low Environmentalism Respondents for `Monthly Cost' Feature from Bechtel and Scheve (2013) Climate Agreement Experiment for Each Possible Reference Category">>=
 # reported results
@@
 It is worth highlighting two further features in Figure \ref{fig:bechtel_difference_comparison}.
-First, the alternative differences-in-AMCEs estimates vary mechanically around the difference in marginal means, as the reference category varies (just as the AMCE estimates did in Figure \ref{fig:reference_category}).
+First, the alternative differences-in-AMCEs estimates vary mechanically around the difference in marginal means, as the reference category varies.
 The difference between marginal means for two groups are always fixed in the data, so the differencing of subgroup AMCEs is merely an exercise is centering those differences at arbitrary points along the range of observed differences in marginal means.
@@
 
-\section*{Improved Analysis of Subgroup Preferences in Conjoint Designs}\label{sec:marginalmeans}
+\section*{Improved Subgroup Analyses in Conjoint Designs}\label{sec:marginalmeans}
 
@@
 
-We have shown that subgroup analyses of conjoint designs frequently entail the use of difference-in-AMCE comparisons and we have also shown that such analyses, perhaps counterintuitively, do not demonstrate differences in preferences between groups due the near-impossibility of selecting a non-arbitrary reference category against which to estimate AMCEs.
-Thus the choice of reference category --- while seemingly irrelevant --- has dramatic inferential consequences in conjoint analyses.
+Researchers and consumers of conjoints can avoid the inferential errors that accompany conditional AMCEs by focusing attention on (subgroup) marginal means, differences between subgroup marginal means to infer subgroup differences in preferences toward particular features, and omnibus nested model comparisons to infer subgroup differences across many features.
+To demonstrate each of these three techniques
+
 Here we provide a more complete example, demonstrating the full extent of this problem for interpretation of conjoint results and present alternative forms of analysis that more robustly convey subgroup preferences and the differences (if any) between them.
@@
 In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in preferences between the two subgroups.
-In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.\footnote{The appendix contains comparable plots for experiments by \citet{BallardRosaMartinScheve2016} and \citet{TeeleKallaRosenbluth2018}.}
+In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.\footnote{The appendix contains comparable plots for experiments by \citet{BechtelScheve2013} and \citet{TeeleKallaRosenbluth2018}.}
 
@@
 \begin{enumerate}
-\item Always report unadjusted marginal means when attempting to provide a \textit{descriptive} summary of respondent preferences in addition to , or instead of, AMCEs.\footnote{Like the presentation of AMCEs, displaying marginal means in constrained conjoint designs may also distort apparent patterns given that not all features can co-occur.
+\item Always report unadjusted marginal means when attempting to provide a \textit{descriptive} summary of respondent preferences in addition to, or instead of, AMCEs.\footnote{Like the presentation of AMCEs, displaying marginal means in constrained conjoint designs may also distort apparent patterns given that not all features can co-occur.
 Partitioning the design into fractions such that each fraction contains a fully unconstrained design would mitigate any concern with that presentation.}
@@
 \item Exercise caution when explicitly, or implicitly, interpreting differences-in-AMCEs across subgroups.
-Differences-in-AMCEs are differences in effect sizes for subgroups, not statments about the relative favorability of the subgroups toward profiles with a feature.
+Differences-in-AMCEs are differences in effect sizes for subgroups, not statments about the relative favorability of the subgroups toward profiles with a given feature.
 Heterogeneous effects do not necessarily mean different underlying preferences.
@@
 So, the researcher in this example may prefer to not present the AMCE of being Jewish together with the other results as it does not draw upon the complete set of feature combinations used in other portions of the analysis.
+
+\clearpage
+
+\section{Impact of Reference Category Choice on AMCEs}\label{app:referencecategory}
+
+Though seemingly arbitrary, the choice of reference category for estimating AMCEs can be quite consequential.
+For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment (again, see \ref{fig:hainmueller_candidate_replication}), the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline.
+
+The figure below shows how the estimated AMCEs for each level of the education feature would have differed depending on that choice.
+Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline.
+The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.
+
+<<reference_category, dependson=c("data_hainmueller_immigration"), fig.width=8, fig.height=4, fig.cap="", fig.pos="h">>=
+tmp <- amce_by_reference(hainmueller_immigration, ChosenImmigrant ~ Education, ~ Education, id = ~CaseID)
+ggplot(tmp, aes(x = estimate, y = level, group = BY, colour = BY)) +
+  geom_vline(xintercept = 0, colour = "gray") +
+  geom_point(position = ggstance::position_dodgev(height = 1)) +
+  geom_errorbarh(aes(xmin = lower, xmax = upper),  
+                 size = 0.2, height = 0,
+                 position = ggstance::position_dodgev(height = 1)) + 
+  scale_colour_discrete(
+    guide = ggplot2::guide_legend(
+      title = "Reference Category",
+      title.position = "top",
+      ncol = 2
+    )
+  ) +
+  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
+  ylab("") +
+  xlab("Estimated AMCE") + 
+  theme_minimal() + 
+  ggplot2::theme(
+    legend.position = "bottom",
+    panel.grid.major = ggplot2::element_blank(),
+    panel.grid.minor = ggplot2::element_blank()
+  )
+rm(tmp)
+@
+
+In \textit{constrained} conjoint designs, the choice of reference category is even more important.
+Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature.
+Consequently, the AMCE for the ``Escape Persecution'' level (relative to the  ``Reunite with family'' reference category) is only defined for the subset of the design involving countries `China,' `Sudan,' `Somalia,' and `Iraq.' The AMCEs for those four countries (relative to India as a baseline) marginalize across all reasons for application, but the AMCEs for the first six countries marginalize only across the latter two reasons.
+Thus the interpretation of AMCEs --- and the basic ability to estimate them in constrained designs --- depends entirely upon the selection of a reference category where all feature levels can co-occur.
+In a design where \textit{all} features are constrained, then AMCEs are undefined for the design as a whole and only estimable for subsets of the design that are \textit{conditionally} unconstrained.
+
+\clearpage
+
+\section{Re-analysis of `Political Experience' Feature from Teele et al. (2018)}\label{app:tkrpolexperience}
+
+<<tkr_replication_experience, dependson=c("data_tkr"), fig.height=6, fig.width=7, fig.show="hold", fig.pos="h", message=FALSE>>=
+a <- plot(
+  subset(cj(
+   tkr, 
+   winner ~ feature_experience,
+   id = ~ responseid,
+   estimate = "amce",
+  ), feature == "Political Experience"), 
+  xlab = NULL, feature_headers = FALSE, vline = 0, xlim = c(-0.21, 0.21), size = 2
+) + 
+  ggtitle(NULL, "Full Sample AMCEs") + 
+  scale_colour_manual("Feature", limits = "Political Experience", values = "black") +
+  theme(
+  	legend.position = "none",
+  	panel.border = element_blank(),
+  	axis.line.x = element_blank(),
+	axis.line.y = element_blank()
+  )
+
+b <- plot(
+  subset(cj(
+   tkr, 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "mm",
+  ), feature == "Political Experience"),
+  xlab = NULL, feature_headers = FALSE, vline = 0.5, xlim = c(0.29,0.71), size = 2
+) + 
+  ggtitle(NULL, "Full Sample MMs") + 
+  scale_colour_manual("Feature", limits = "Political Experience", values = "black") +
+  theme(
+   	legend.position = "none",
+   	panel.border = element_blank(),
+   	axis.line.x = element_blank(),
+	axis.line.y = element_blank()
+  )
+
+c <- plot(
+  subset(cj(
+   tkr, 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "amce",
+   by = ~ PartyID
+  ), feature == "Political Experience"), 
+  xlab = NULL, feature_headers = FALSE, vline = 0, group = "PartyID", xlim = c(-0.21, 0.21), size = 2
+) + 
+ annotate("text", y = 1.65, x = -0.04, label = "Republicans", size = 3) + 
+ annotate("text", y = 1.3, x = 0.05, label = "Democrats", size = 3) + 
+ ggtitle(NULL, "Subgroup AMCEs") + 
+ scale_colour_manual(values=rep("black", 2)) +
+ aes(shape = PartyID) + 
+ scale_shape_manual("PartyID", limits = c("Democrat", "Republican"), values = c(15,17)) +
+ theme(
+   legend.position = "none",
+   panel.border = element_blank(),
+   axis.line.x = element_blank(),
+   axis.line.y = element_blank()
+ )
+
+d <- plot(
+  subset(cj(
+   tkr, 
+   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+   id = ~ responseid,
+   estimate = "mm",
+   by = ~ PartyID
+  ), feature == "Political Experience"),
+  xlab = NULL, feature_headers = FALSE, vline = 0.5, group = "PartyID", xlim = c(0.29,0.71), size = 2
+) + 
+ ggtitle(NULL, "Subgroup MMs") + 
+ scale_colour_manual(values=rep("black", 2)) +
+ aes(shape = PartyID) + 
+ scale_shape_manual("PartyID", limits = c("Democrat", "Republican"), values = c(15,17)) +
+ theme(
+  legend.position = "none",
+  panel.border = element_blank(),
+  axis.line.x = element_blank(),
+  axis.line.y = element_blank()
+ )
+
+# combine
+gA = ggplotGrob(a)
+gB = ggplotGrob(b)
+gC = ggplotGrob(c)
+gD = ggplotGrob(d)
+gridExtra::grid.arrange(gA, gB, gC, gD, ncol = 1)
+@
+
+\noindent Conditional AMCEs in this experiment (see 3rd panel, above) correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates.
+Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates).
+Yet the conditional marginal means (4th panel, above) reveal that Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience.
+Democrats are much more sensitive to experience than are Republicans and important differences in preferences between the groups are apparent for very high and very low experience, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.
+
+\clearpage
+
+\section{Hainmueller et al. (2014) Candidate Experiment}
+
+\subsection{Replication using AMCEs}
+
+<<hainmueller_candidate_amce_appendix, dependson=c("data_hainmueller_candidate"), fig.height=8, fig.width=8>>=
+plot(
+  cj(
+   hainmueller_candidate, 
+   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
+   id = ~ resID,
+   estimate = "amce"
+  )
+)
+@
+
+\clearpage
+
+<<hainmueller_candidate_amce_table, dependson=c("data_hainmueller_candidate"), results="asis">>=
+print(xtable::xtable(
+  cj(
+     hainmueller_candidate, 
+     selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
+     id = ~ resID,
+     estimate = "amce"
+  )[c("feature", "level", "estimate", "std.error", "z")],
+    digits = 2, align = c("l", "l", "p{3in}", "r", "r", "r")
+), include.rownames = FALSE, size = "footnotesize")
+@
+
+\clearpage
+
+\subsection{Replication using MMs}
+
+<<hainmueller_candidate_mm_appendix, dependson=c("data_hainmueller_candidate"), fig.height=8, fig.width=8>>=
+plot(
+  cj(
+   hainmueller_candidate, 
+   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
+   id = ~ resID,
+   estimate = "mm",
+   h0 = 0.5
+  ), vline = 0.5
+)
+@
+
+\clearpage
+
+<<hainmueller_candidate_mm_table, dependson=c("data_hainmueller_candidate"), results="asis">>=
+print(xtable::xtable(
+  cj(
+     hainmueller_candidate, 
+     selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
+     id = ~ resID,
+     estimate = "mm",
+     h0 = 0.5
+  )[c("feature", "level", "estimate", "std.error", "z")],
+    digits = 2, align = c("l", "l", "p{3in}", "r", "r", "r")
+), include.rownames = FALSE, size = "footnotesize")
+@
 
@@
 
-\subsection{Subgroup Analysis for Hainmueller et al. (2014) Immigration Experiment using AMCEs}
+\subsection{Subgroup Analysis using AMCEs}
 
@@
 
-\subsection{Subgroup Analysis for Hainmueller et al. (2014) Immigration Experiment using MMs}
+\subsection{Subgroup Analysis using MMs}
 
@@
 
-\section{Hainmueller et al. (2014) Candidate Experiment}
-
-\subsection{Replication using AMCEs}
-
-<<hainmueller_candidate_amce_appendix, dependson=c("data_hainmueller_candidate"), fig.height=8, fig.width=8>>=
-plot(
-  cj(
-   hainmueller_candidate, 
-   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
-   id = ~ resID,
-   estimate = "amce"
-  )
-)
-@
-
-\clearpage
-
-<<hainmueller_candidate_amce_table, dependson=c("data_hainmueller_candidate"), results="asis">>=
-print(xtable::xtable(
-  cj(
-     hainmueller_candidate, 
-     selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
-     id = ~ resID,
-     estimate = "amce"
-  )[c("feature", "level", "estimate", "std.error", "z")],
-    digits = 2, align = c("l", "l", "p{3in}", "r", "r", "r")
-), include.rownames = FALSE, size = "footnotesize")
-@
-
-\clearpage
-
-\subsection{Replication using MMs}
-
-<<hainmueller_candidate_mm_appendix, dependson=c("data_hainmueller_candidate"), fig.height=8, fig.width=8>>=
-plot(
-  cj(
-   hainmueller_candidate, 
-   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
-   id = ~ resID,
-   estimate = "mm",
-   h0 = 0.5
-  ), vline = 0.5
-)
-@
-
-\clearpage
-
-<<hainmueller_candidate_mm_table, dependson=c("data_hainmueller_candidate"), results="asis">>=
-print(xtable::xtable(
-  cj(
-     hainmueller_candidate, 
-     selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
-     id = ~ resID,
-     estimate = "mm",
-     h0 = 0.5
-  )[c("feature", "level", "estimate", "std.error", "z")],
-    digits = 2, align = c("l", "l", "p{3in}", "r", "r", "r")
-), include.rownames = FALSE, size = "footnotesize")
-@
-
-\clearpage
-
-\section{Ballard-Rosa et al. (2016) Tax Preference Experiment}
-
-\subsection{Replication using AMCEs}
-
-<<bms_amce_appendix, dependson=c("data_bms"), fig.height=8, fig.width=8>>=
-plot(
-  cj(bms, chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev, weights = ~ weight, id = ~ ID, estimate = "amce")
-)
-@
-
-\clearpage
-
-<<bms_amce_table, dependson=c("data_bms"), results="asis">>=
-print(xtable::xtable(
-  cj(
-    bms,
-    chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev,
-    weights = ~ weight,
-    id = ~ ID,
-    estimate = "amce"
-   )[c("feature", "level", "estimate", "std.error", "z")],
-     digits = 2, align = c("l", "l", "p{1.5in}", "r", "r", "r")
-), include.rownames = FALSE)
-@
-
-\clearpage
-
-\subsection{Replication using MMs}
-
-<<bms_mm_appendix, dependson=c("data_bms"), fig.height=8, fig.width=8>>=
-plot(
-  cj(bms, chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev, weights = ~ weight, id = ~ ID, estimate = "mm", h0 = 0.5),
-  vline = 0.5
-)
-@
-
-\clearpage
-
-<<bms_mm_table, dependson=c("data_bms"), results="asis">>=
-print(xtable::xtable(
-  cj(
-    bms,
-    chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev,
-    weights = ~ weight,
-    id = ~ ID,
-    estimate = "mm",
-    h0 = 0.5)[c("feature", "level", "estimate", "std.error", "z")],
-  digits = 2, align = c("l", "l", "p{1.5in}", "r", "r", "r")
-), include.rownames = FALSE)
-@
-
-\clearpage
-
-\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by ``Taxes Harm Economy'' Split using AMCEs}
-
-<<bms_subgroup_amce_appendix1, dependson=c("data_bms"), fig.width=8, fig.height=8>>=
-plot(cj(subset(bms, taxes_harm_split %in% c("Help", "Harm")),
-        chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev,
-        id = ~ID,
-        weights = ~weight,
-        estimate = "amce",
-        by = ~ taxes_harm_econ),
-     vline = 0,
-     group = "taxes_harm_econ",
-     legend_title = "Taxes Help/Harm Economy")
-@
-
-\clearpage
-
-\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by ``Taxes Harm Economy'' Split using MMs}
-
-<<bms_subgroup_mm_appendix1, dependson=c("data_bms"), fig.width=8, fig.height=8>>=
-plot(cj(subset(bms, taxes_harm_split %in% c("Help", "Harm")),
-        chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev,
-        id = ~ID,
-        weights = ~weight,
-        estimate = "mm",
-        h0 = 0.5,
-        by = ~ taxes_harm_econ),
-     vline = 0.5,
-     group = "taxes_harm_econ",
-     legend_title = "Taxes Help/Harm Economy")
-@
-
-\clearpage
-
-\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by Inequity Aversion using AMCEs}
-
-<<bms_subgroup_amce_appendix2, dependson=c("data_bms"), fig.width=8, fig.height=8>>=
-plot(cj(subset(bms, !is.na(ineq_averse_dum)),
-        chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev,
-        id = ~ID,
-        weights = ~weight,
-        estimate = "amce",
-        by = ~ ineq_averse_dum),
-     vline = 0,
-     group = "ineq_averse_dum",
-     legend_title = "Inequity Aversion")
-@
-
-\clearpage
-
-\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by Inequity Aversion using MMs}
-
-<<bms_subgroup_mm_appendix2, dependson=c("data_bms"), fig.width=8, fig.height=8>>=
-plot(cj(subset(bms, !is.na(ineq_averse_dum)),
-        chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev,
-        id = ~ID,
-        weights = ~weight,
-        estimate = "mm",
-        h0 = 0.5,
-        by = ~ ineq_averse_dum),
-     vline = 0.5,
-     group = "ineq_averse_dum",
-     legend_title = "Inequity Aversion")
-@
-
-\clearpage
-
-\subsection{Comparison of Alternative Reference Categories for Ballard-Rosa et al. (2016) Tax Preference Experiment, by ``Taxes Harm Economy'' Split}
-
-<<bms_subgroup_example1, dependson=c("data_bms")>>=
-# estimates benchmarked to largest difference between subgroups
-bms.A <- bms
-    bms.A$taxrate1 <- relevel(bms.A$taxrate1, "<10k: 15%")
-    bms.A$taxrate2 <- relevel(bms.A$taxrate2, "10-35k: 35%")
-    bms.A$taxrate3 <- relevel(bms.A$taxrate3, "35-85k: 35%")
-    bms.A$taxrate4 <- relevel(bms.A$taxrate4, "85-175k: 5%")
-    bms.A$taxrate5 <- relevel(bms.A$taxrate5, "175-375k: 45%")
-    bms.A$taxrate6 <- relevel(bms.A$taxrate6, ">375k: 45%")
-    bms.A$taxrev <- relevel(bms.A$taxrev, "<75%")
-# estimates benchmarked to smallest difference between subgroups
-bms.B <- bms
-    bms.B$taxrate1 <- relevel(bms.A$taxrate1, "<10k: 5%")
-    bms.B$taxrate2 <- relevel(bms.A$taxrate2, "10-35k: 25%")
-    bms.B$taxrate3 <- relevel(bms.A$taxrate3, "35-85k: 25%")
-    bms.B$taxrate4 <- relevel(bms.A$taxrate4, "85-175k: 25%")
-    bms.B$taxrate5 <- relevel(bms.A$taxrate5, "175-375k: 25%")
-    bms.B$taxrate6 <- relevel(bms.A$taxrate6, ">375k: 35%")
-    bms.B$taxrev <- relevel(bms.A$taxrev, "95-105%")
-# formula
-f1 <- chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev
-# estimate
-amce_by_harm_1 <- cj(bms.A, f1, id = ~ ID, weights = ~ weight, estimate = "amce", by = ~ taxes_harm_split)
-amce_by_harm_2 <- cj(bms.B, f1, id = ~ ID, weights = ~ weight, estimate = "amce", by = ~ taxes_harm_split)
-# tag datasets and merge
-amce_by_harm_1$dataset <- "A"
-amce_by_harm_2$dataset <- "B"
-amce_ref_bms_merged1 <- rbind(amce_by_harm_1, amce_by_harm_2)
-amce_ref_bms_merged1$level <- factor(amce_ref_bms_merged1$level, levels = with(bms, c(levels(taxrate1), levels(taxrate2), levels(taxrate3), levels(taxrate4), levels(taxrate5), levels(taxrate6), levels(taxrev))))
-@
-
-<<bms_subgroup_example_plot1, dependson=c("data_bms", "bms_subgroup_example1"), fig.width=10, fig.height=10, fig.caption="Alternative Reference Categories Features in Ballard-Rosa et al.
-(2016) Tax Preference Experiment, by ``Taxes Harm Economy'' Split">>=
-plot(amce_ref_bms_merged1, group = "taxes_harm_split", feature_headers = FALSE, legend_title = "Taxes Help/Harm Economy", vline = 0) + 
-  facet_grid(rows = vars(feature), cols = vars(dataset), scales = "free_y", space = "free_y", labeller = function(x) label_value(x, multi_line = FALSE)) +
-  theme(strip.text.x = element_text(size = 8),
-        strip.text.y = element_text(size = 5))
-@
-
-\clearpage
-
-\subsection{Comparison of Alternative Reference Categories for Ballard-Rosa et al. (2016) Tax Preference Experiment, by Inequity Aversion}
-
-<<bms_subgroup_example2, dependson=c("data_bms")>>=
-# estimates benchmarked to largest difference between subgroups
-bms.A <- bms
-    bms.A$taxrate1 <- relevel(bms.A$taxrate1, "<10k: 25%")
-    bms.A$taxrate2 <- relevel(bms.A$taxrate2, "10-35k: 35%")
-    bms.A$taxrate3 <- relevel(bms.A$taxrate3, "35-85k: 35%")
-    bms.A$taxrate4 <- relevel(bms.A$taxrate4, "85-175k: 35%")
-    bms.A$taxrate5 <- relevel(bms.A$taxrate5, "175-375k: 45%")
-    bms.A$taxrate6 <- relevel(bms.A$taxrate6, ">375k: 5%")
-    bms.A$taxrev <- relevel(bms.A$taxrev, "105-125%")
-# estimates benchmarked to smallest difference between subgroups
-bms.B <- bms
-    bms.B$taxrate1 <- relevel(bms.A$taxrate1, "<10k: 5%")
-    bms.B$taxrate2 <- relevel(bms.A$taxrate2, "10-35k: 5%")
-    bms.B$taxrate3 <- relevel(bms.A$taxrate3, "35-85k: 5%")
-    bms.B$taxrate4 <- relevel(bms.A$taxrate4, "85-175k: 15%")
-    bms.B$taxrate5 <- relevel(bms.A$taxrate5, "175-375k: 25%")
-    bms.B$taxrate6 <- relevel(bms.A$taxrate6, ">375k: 25%")
-    bms.B$taxrev <- relevel(bms.A$taxrev, "95-105%")
-# formula
-f1 <- chose_plan ~ taxrate1 + taxrate2 + taxrate3 + taxrate4 + taxrate5 + taxrate6 + taxrev
-# estimate
-amce_by_harm_1 <- cj(subset(bms.A, !is.na(ineq_averse_dum)), f1, id = ~ ID, weights = ~ weight, estimate = "amce", by = ~ ineq_averse_dum)
-amce_by_harm_2 <- cj(subset(bms.B, !is.na(ineq_averse_dum)), f1, id = ~ ID, weights = ~ weight, estimate = "amce", by = ~ ineq_averse_dum)
-# tag datasets and merge
-amce_by_harm_1$dataset <- "A"
-amce_by_harm_2$dataset <- "B"
-amce_ref_bms_merged2 <- rbind(amce_by_harm_1, amce_by_harm_2)
-amce_ref_bms_merged2$level <- factor(amce_ref_bms_merged2$level, levels = with(bms, c(levels(taxrate1), levels(taxrate2), levels(taxrate3), levels(taxrate4), levels(taxrate5), levels(taxrate6), levels(taxrev))))
-@
-
-<<bms_subgroup_example_plot2, dependson=c("data_bms", "bms_subgroup_example2"), fig.width=10, fig.height=10, fig.caption="Alternative Reference Categories Features in Ballard-Rosa et al.
-(2016) Tax Preference Experiment, by Inequity Aversion">>=
-plot(amce_ref_bms_merged2, group = "ineq_averse_dum", feature_headers = FALSE, legend_title = "Inequity Aversion", vline = 0) + 
-  facet_grid(rows = vars(feature), cols = vars(dataset), scales = "free_y", space = "free_y", labeller = function(x) label_value(x, multi_line = FALSE)) +
-  theme(strip.text.x = element_text(size = 8),
-        strip.text.y = element_text(size = 5))
-@
-
-\clearpage
-
-\section{Bechtel and Scheve (2013) Climate Agreement Experiment}
-
-<<bechtel_amce>>=
-cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "amce")
-@
-
-<<bechtel_mm>>=
-cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "mm")
-@
-
-<<bechtel_subgroup_mm>>=
-cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, by = ~ country, estimate = "mm")
-plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, by = ~ country, estimate = "mm"), group = "BY", vline = 0.5)
-@
-
-<<bechtel_subgroup_amce>>=
-cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, by = ~ country, estimate = "amce")
-plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, by = ~ country, estimate = "amce"), group = "BY", vline = 0)
-@
-
-<<bechtel_subgroup_amce_country_anova>>=
-cj_anova(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, id = ~ ID, by = ~ country)
-@
-
-<<bechtel_subgroup_amce_environmentalism>>=
-plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "amce", by = ~ environmentalism), group = "BY", vline = 0)
-plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "mm", by = ~ environmentalism), group = "BY", vline = 0.5)
-@
-
-<<bechtel_reciprocity_reference>>=
-# ``Individuals who pretreatment exhibit reciprocal behavior [...] are almost twice as sensitive to both the number of countries participating and the proportion of emissions represented than individuals who do not'' (13768).
-This sensitivity is accurately stated but the use of conditional AMCEs implies that the subgroup difference is due to differences in favorability toward agreements involving 20 countries and differing opinions over agreements with 80 or 160 countries, while in reality the differences lie in 20-country and 160-country agreements and the groups do not differ in their favorability toward 80-country agreements at all.
-plot(cj(bechtel, choice_cj ~ ctries_cj + emissions_cj, weights = ~ weight, id = ~ ID, estimate = "mm", by = ~ reciprocity), group = "BY", vline = 0.5)
-@
-
-<<bechtel_subgroup_amce_reciprocity>>=
-plot(
-  cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, 
-	 weights = ~ weight, id = ~ ID, estimate = "amce", by = ~ reciprocity
-  ), 
-group = "BY", vline = 0)
-
-plot(
-  cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj,
-     weights = ~ weight, id = ~ ID, estimate = "mm", by = ~ reciprocity
-  ),
-group = "BY", vline = 0.5)
+\subsection{Nested Model Comparison}
+
+<<hainmueller_immigration_anova, dependson=c("data_hainmueller_immigration")>>=
+cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), 
+   ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication,
+   id = ~ CaseID, by = ~ ethnocentrism_split)
 @
@@
 
-\subsection{Subgroup Analysis for Teele et al. (2018) Candidate Experiment using AMCEs}
+\subsection{Subgroup Analysis using AMCEs}
 
@@
 
-\subsection{Subgroup Analysis for Teele et al. (2018) Candidate Experiment using MMs}
+\subsection{Subgroup Analysis using MMs}
 
@@
 
-\subsection{Comparison of Alternative Reference Categories for Teele et al. (2018) Candidate Experiment}
+\subsection{Nested Model Comparison: Male/Female Voters}
+
+<<tkr_subgroup_anova_party_sex, dependson=c("data_tkr")>>=
+cj_anova(subset(tkr, !is.na(Sex)), winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age, id = ~ responseid, by = ~ Sex)
+@
+
+\subsection{Nested Model Comparison: Democratic/Republican Voters}
+
+<<tkr_subgroup_anova_party, dependson=c("data_tkr")>>=
+cj_anova(subset(tkr, !is.na(PartyID)), winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age, id = ~ responseid, by = ~ PartyID)
+@
+
+\clearpage
+
+\subsection{Comparison of Alternative Reference Categories}
 
@@
 
+\section{Bechtel and Scheve (2013) Climate Agreement Experiment}
+
+\subsection{Replication using AMCEs}
+
+<<bechtel_amce, dependson=c("data_bechtel")>>=
+plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "amce"))
+@
+
+\clearpage
+
+<<bechtel_amce_table, dependson=c("data_bechtel"), results="asis", eval=FALSE>>=
+print(xtable::xtable(
+  cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "amce"
+)[c("feature", "level", "estimate", "std.error", "z")],
+    digits = 2, align = c("l", "l", "p{3in}", "r", "r", "r")
+), include.rownames = FALSE, size = "footnotesize")
+@
+
+\clearpage
+
+\subsection{Replication using MMs}
+
+<<bechtel_mm, dependson=c("data_bechtel")>>=
+plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "mm"), vline = 0.5)
+@
+
+\clearpage
+
+<<bechtel_mm_table, dependson=c("data_bechtel"), results="asis", eval=FALSE>>=
+print(xtable::xtable(
+  cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "mm", h0 = 0.5)[c("feature", "level", "estimate", "std.error", "z")],
+    digits = 2, align = c("l", "l", "p{3in}", "r", "r", "r")
+), include.rownames = FALSE, size = "footnotesize")
+@
+
+\clearpage
+
+\subsection{Subgroup Analysis using AMCEs: Country}
+
+<<bechtel_subgroup_amce, dependson=c("data_bechtel")>>=
+plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, by = ~ country, estimate = "amce"), group = "BY", vline = 0)
+@
+
+\clearpage
+
+<<bechtel_subgroup_amce_table, dependson=c("data_bechtel"), results="asis", eval=FALSE>>=
+cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, by = ~ country, estimate = "amce")
+@
+
+\clearpage
+
+\subsection{Subgroup Analysis using MMs: Country}
+
+<<bechtel_subgroup_mm, dependson=c("data_bechtel")>>=
+plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, by = ~ country, estimate = "mm"), group = "BY", vline = 0.5)
+@
+
+\clearpage
+
+<<bechtel_subgroup_mm_table, dependson=c("data_bechtel"), results="asis", eval=FALSE>>=
+cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, by = ~ country, estimate = "mm")
+@
+
+\clearpage
+
+\subsection{Subgroup Analysis using AMCEs: Environmentalism}
+
+<<bechtel_subgroup_amce_environmentalism, dependson=c("data_bechtel")>>=
+plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "amce", by = ~ environmentalism), group = "BY", vline = 0)
+@
+
+\clearpage
+
+\clearpage
+
+<<bechtel_subgroup_mm_environmentalism, dependson=c("data_bechtel")>>=
+plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "mm", by = ~ environmentalism), group = "BY", vline = 0.5)
+@
+
+\clearpage
+
+\clearpage
+
+\subsection{Subgroup Analysis using AMCEs: Reciprocity}
+
+<<bechtel_subgroup_amce_reciprocity, dependson=c("data_bechtel")>>=
+plot(
+  cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, 
+	 weights = ~ weight, id = ~ ID, estimate = "amce", by = ~ reciprocity
+  ), 
+group = "BY", vline = 0)
+@
+
+\clearpage
+
+\clearpage
+
+\subsection{Subgroup Analysis using MMs: Reciprocity}
+
+<<bechtel_subgroup_mm_reciprocity, dependson=c("data_bechtel")>>=
+plot(
+  cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj,
+     weights = ~ weight, id = ~ ID, estimate = "mm", by = ~ reciprocity
+  ),
+group = "BY", vline = 0.5)
+@
+
+\clearpage
+
+\clearpage
+
+\subsection{Nested Model Comparison: Country}
+
+<<bechtel_country_anova>>=
+cj_anova(subset(bechtel, !is.na(country)), choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, id = ~ ID, by = ~ country)
+@
+
+\subsection{Nested Model Comparison: Environmentalism}
+
+<<bechtel_environmentalism_anova>>=
+cj_anova(subset(bechtel, !is.na(environmentalism)), choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, id = ~ ID, by = ~ environmentalism)
+@
+
+\clearpage
+
+\subsection{Nested Model Comparison: Reciprocity}
+
+<<bechtel_reciprocity_anova>>=
+cj_anova(subset(bechtel, !is.na(reciprocity)), choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, id = ~ ID, by = ~ reciprocity)
+@
+
+\clearpage
+
+\subsection{Comparison of Alternative Reference Categories}
+
+<<bechtel_reciprocity_reference>>=
+# ``Individuals who pretreatment exhibit reciprocal behavior [...] are almost twice as sensitive to both the number of countries participating and the proportion of emissions represented than individuals who do not'' (13768).
+This sensitivity is accurately stated but the use of conditional AMCEs implies that the subgroup difference is due to differences in favorability toward agreements involving 20 countries and differing opinions over agreements with 80 or 160 countries, while in reality the differences lie in 20-country and 160-country agreements and the groups do not differ in their favorability toward 80-country agreements at all.
+plot(cj(bechtel, choice_cj ~ ctries_cj + emissions_cj, weights = ~ weight, id = ~ ID, estimate = "mm", by = ~ reciprocity), group = "BY", vline = 0.5)
+@
+
+\clearpage
+
 \section*{}

### 2019-04-13 manuscript.tex
drop bms examples; update and expand SI

@@
 More trivially, \citet{TeeleKallaRosenbluth2018} describe their comparisons about public preferences for female candidates relative to male candidates, but could have equivalent described patterns of equal size but opposite sign comparing preferences over male relative to female candidates.
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/reference_category-1} \caption[Estimated AMCEs for Levels of the `Education' Feature for Each Possible Reference Category from Hainmueller et al.'s (2014) Immigration Experiment]{Estimated AMCEs for Levels of the `Education' Feature for Each Possible Reference Category from Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:reference_category}
-\end{figure}
-
-\end{knitrout}
-
-Though seemingly arbitrary, the choice of reference category for estimating AMCEs can be quite consequential.\footnote{Since this manuscript has been under review, we have been made aware of one working paper by \citet{ClaytonFerwerdaHoriuchi2018}, on the topic of immigration preferences, that correctly notes the need to address the arbitrary reference category in order to compare subgroup preferences.} For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment (again, see \ref{fig:hainmueller_candidate_replication}), the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline.
-Figure \ref{fig:reference_category} shows how the estimated AMCEs for each level of the education feature would have differed depending on that choice.
-Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline.
-The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.\footnote{In \textit{constrained} conjoint designs, the choice of reference category is even more important.
-Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature.
-Consequently, the AMCE for the ``Escape Persecution'' level (relative to the  ``Reunite with family'' reference category) is only defined for the subset of the design involving countries `China,' `Sudan,' `Somalia,' and `Iraq.' The AMCEs for those four countries (relative to India as a baseline) marginalize across all reasons for application, but the AMCEs for the first six countries marginalize only across the latter two reasons.
-Thus the interpretation of AMCEs --- and the basic ability to estimate them in constrained designs --- depends entirely upon the selection of a reference category where all feature levels can co-occur.
-In a design where \textit{all} features are constrained, then AMCEs are undefined for the design as a whole and only estimable for subsets of the design that are \textit{conditionally} unconstrained.}
-
-%To demonstrate this, Figure \ref{fig:reference_category} shows the estimated AMCEs for the country of origin feature from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, with the analysis repeated ten times each time using a different country as the reference category.
-For example, the top-most set of points and error bars convey the AMCE for Iraq from each of these analyses.
-When Iraq is the reference category, its AMCE is undefined.
-When any other country is chosen as a reference category, the AMCE for Iraq is negative because respondents are more negative toward Iraqi immigrants than they are toward those of other countries.
-Similarly, the bottom set of points and error bars reflects the estimated AMCEs for Germany.
-When Germany is the reference category, its AMCE is undefined but when any other country is used as the reference category, its AMCE is positive.
-
-%These cases are therefore not \textit{directionally} sensitive to the choice of reference category but of course the point estimates vary considerably.
-But the estimated AMCE of countries who are neither strongly disliked or strongly favored by respondents are highly sensitive to choice of reference category.
-Consider, for example, the estimated AMCEs for China (the four set of points from the top).
-When highly disliked countries are chosen as the reference category (like Somalia, Sudan, or Iraq), the AMCE for China is positive; when highly favored countries are chosen (like Germany, Poland, or the Philippines), the AMCE for China is negative.
+Appendix \ref{app:referencecategory} includes some additional illustrations of this point for interested readers.
 
@@
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/tkr_replication-1} \caption[Replication of Results for `Candidate Sex' Feature from Teele et al]{Replication of Results for `Candidate Sex' Feature from Teele et al.
-(2018) Candidate Experiment using Full Sample and Subgroup AMCEs and MMs}\label{fig:tkr_replication}
-\end{figure}
-
-\end{knitrout}
-
 Yet, just as analysis of full sample conjoint data is often descriptive in nature, it is also the case that conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally.
@@
 
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/tkr_replication-1} \caption[Replication of Results for `Candidate Sex' Feature from Teele et al]{Replication of Results for `Candidate Sex' Feature from Teele et al.
+(2018) Candidate Experiment using Full Sample and Subgroup AMCEs and MMs}\label{fig:tkr_replication}
+\end{figure}
+
+\end{knitrout}
+
 To draw this example out more fully, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment for the full sample of respondents.
@@
 The third panel shows conditional AMCEs separately for Democratic and Republican voters, as provided in the original paper and the lower panel shows the results using conditional marginal means for Democratic and Republican voters.\footnote{We opt here for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.} By requiring a reference category fixed to zero, the conditional AMCE results in the third panel suggest that there is a very large difference in favorability toward female candidates between Republican and Democratic respondents.
-In reality, however, the difference in these conditional AMCEs (0.086) reflects the true difference in favorability toward female candidates (difference: 0.045; Democrats: 0.537, Republicans: 0.492) \textit{plus} the difference in favorability toward male candidates (difference: 0.045; Democrats: 0.463, Republicans: 0.508).
-Because Democrats and Republicans actually differ in their views of profiles containing the reference (male) category, AMCEs sum the true differences in preferences for a given feature level with the difference in preferences toward the reference category.\footnote{Another example that clearly demonstrates the discrepancy between the differences in preferences and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature of this experiment (see Supporting Materials).
-The conditional AMCEs correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates.
-Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates).
-In reality, however, the conditional marginal means reveal that actually Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience.
-Democrats are much more sensitive to experience than are Republicans and important differences in preferences between the groups are apparent for very high and very low experience, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.}
+In reality, however, the difference in these conditional AMCEs (0.089) reflects the true difference in favorability toward female candidates (difference: 0.045; Democrats: 0.537, Republicans: 0.492) \textit{plus} the difference in favorability toward male candidates (difference: 0.045; Democrats: 0.463, Republicans: 0.508).
+Because Democrats and Republicans actually differ in their views of profiles containing the reference (male) category, AMCEs sum the true differences in preferences for a given feature level with the difference in preferences toward the reference category.\footnote{Another example that clearly demonstrates the discrepancy between the differences in preferences and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature of this experiment (see Appendix \ref{app:tkrpolexperience}).}
 
@@
 So, the researcher in this example may prefer to not present the AMCE of being Jewish together with the other results as it does not draw upon the complete set of feature combinations used in other portions of the analysis.
+
+\clearpage
+
+\section{Impact of Reference Category Choice on AMCEs}\label{app:referencecategory}
+
+Though seemingly arbitrary, the choice of reference category for estimating AMCEs can be quite consequential.
+For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment (again, see \ref{fig:hainmueller_candidate_replication}), the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline.
+
+The figure below shows how the estimated AMCEs for each level of the education feature would have differed depending on that choice.
+Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline.
+The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[h]
+\includegraphics[width=\maxwidth]{figure/reference_category-1} \end{figure}
+
+\end{knitrout}
+
+In \textit{constrained} conjoint designs, the choice of reference category is even more important.
+Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature.
+Consequently, the AMCE for the ``Escape Persecution'' level (relative to the  ``Reunite with family'' reference category) is only defined for the subset of the design involving countries `China,' `Sudan,' `Somalia,' and `Iraq.' The AMCEs for those four countries (relative to India as a baseline) marginalize across all reasons for application, but the AMCEs for the first six countries marginalize only across the latter two reasons.
+Thus the interpretation of AMCEs --- and the basic ability to estimate them in constrained designs --- depends entirely upon the selection of a reference category where all feature levels can co-occur.
+In a design where \textit{all} features are constrained, then AMCEs are undefined for the design as a whole and only estimable for subsets of the design that are \textit{conditionally} unconstrained.
+
+\clearpage
+
+\section{Re-analysis of `Political Experience' Feature from Teele et al. (2018)}\label{app:tkrpolexperience}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/tkr_replication_experience-1}
+
+\end{knitrout}
+
+\noindent Conditional AMCEs in this experiment (see 3rd panel, above) correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates.
+Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates).
+Yet the conditional marginal means (4th panel, above) reveal that Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience.
+Democrats are much more sensitive to experience than are Republicans and important differences in preferences between the groups are apparent for very high and very low experience, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.
+
+\clearpage
+
+\section{Hainmueller et al. (2014) Candidate Experiment}
+
+\subsection{Replication using AMCEs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_amce_appendix-1}
+
+\end{knitrout}
+
+\clearpage
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Nov 25 10:42:42 2018
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lp{3in}rrr}
+  \hline
+feature & level & estimate & std.error & z \\ 
+  \hline
+Military Service & Did Not Serve & 0.00 &  &  \\ 
+  Military Service & Served & 0.09 & 0.02 & 4.95 \\ 
+  Religion & None & 0.00 &  &  \\ 
+  Religion & Jewish & -0.04 & 0.03 & -1.42 \\ 
+  Religion & Catholic & -0.02 & 0.03 & -0.56 \\ 
+  Religion & Mainline protestant & -0.01 & 0.03 & -0.48 \\ 
+  Religion & Evangelical protestant & -0.12 & 0.03 & -3.78 \\ 
+  Religion & Mormon & -0.14 & 0.03 & -4.46 \\ 
+  College & No BA & 0.00 &  &  \\ 
+  College & Baptist college & 0.14 & 0.03 & 4.82 \\ 
+  College & Community college & 0.15 & 0.03 & 5.17 \\ 
+  College & State university & 0.19 & 0.03 & 6.77 \\ 
+  College & Small college & 0.18 & 0.03 & 6.50 \\ 
+  College & Ivy League university & 0.27 & 0.03 & 9.26 \\ 
+  Profession & Business owner & 0.00 &  &  \\ 
+  Profession & Lawyer & -0.02 & 0.03 & -0.71 \\ 
+  Profession & Doctor & -0.02 & 0.03 & -0.53 \\ 
+  Profession & High school teacher & -0.04 & 0.03 & -1.42 \\ 
+  Profession & Farmer & -0.09 & 0.03 & -2.94 \\ 
+  Profession & Car dealer & -0.23 & 0.03 & -7.24 \\ 
+  Income & 32K & 0.00 &  &  \\ 
+  Income & 54K & 0.02 & 0.03 & 0.82 \\ 
+  Income & 65K & 0.06 & 0.03 & 2.26 \\ 
+  Income & 92K & 0.03 & 0.03 & 1.12 \\ 
+  Income & 210K & 0.07 & 0.03 & 2.41 \\ 
+  Income & 5.1M & 0.01 & 0.03 & 0.25 \\ 
+  Race/Ethnicity & White & 0.00 &  &  \\ 
+  Race/Ethnicity & Native American & 0.02 & 0.03 & 0.85 \\ 
+  Race/Ethnicity & Black & 0.03 & 0.03 & 1.22 \\ 
+  Race/Ethnicity & Hispanic & -0.02 & 0.03 & -0.84 \\ 
+  Race/Ethnicity & Caucasian & 0.00 & 0.03 & 0.18 \\ 
+  Race/Ethnicity & Asian American & 0.04 & 0.03 & 1.51 \\ 
+  Age & 36 & 0.00 &  &  \\ 
+  Age & 45 & 0.03 & 0.03 & 0.88 \\ 
+  Age & 52 & 0.02 & 0.03 & 0.78 \\ 
+  Age & 60 & 0.00 & 0.03 & 0.14 \\ 
+  Age & 68 & -0.06 & 0.03 & -2.17 \\ 
+  Age & 75 & -0.15 & 0.03 & -5.06 \\ 
+  Gender & Male & 0.00 &  &  \\ 
+  Gender & Female & 0.00 & 0.02 & 0.09 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\end{table}
+
+\clearpage
+
+\subsection{Replication using MMs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_mm_appendix-1}
+
+\end{knitrout}
+
+\clearpage
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Nov 25 10:42:44 2018
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lp{3in}rrr}
+  \hline
+feature & level & estimate & std.error & z \\ 
+  \hline
+Military Service & Did Not Serve & 0.46 & 0.01 & -3.54 \\ 
+  Military Service & Served & 0.54 & 0.01 & 3.55 \\ 
+  Religion & None & 0.56 & 0.02 & 2.73 \\ 
+  Religion & Jewish & 0.52 & 0.02 & 0.96 \\ 
+  Religion & Catholic & 0.53 & 0.02 & 1.24 \\ 
+  Religion & Mainline protestant & 0.54 & 0.02 & 2.06 \\ 
+  Religion & Evangelical protestant & 0.44 & 0.02 & -3.05 \\ 
+  Religion & Mormon & 0.42 & 0.02 & -4.04 \\ 
+  College & No BA & 0.34 & 0.02 & -8.11 \\ 
+  College & Baptist college & 0.48 & 0.02 & -0.83 \\ 
+  College & Community college & 0.49 & 0.02 & -0.39 \\ 
+  College & State university & 0.53 & 0.02 & 1.39 \\ 
+  College & Small college & 0.52 & 0.02 & 0.99 \\ 
+  College & Ivy League university & 0.62 & 0.02 & 6.27 \\ 
+  Profession & Business owner & 0.57 & 0.02 & 3.35 \\ 
+  Profession & Lawyer & 0.55 & 0.02 & 2.20 \\ 
+  Profession & Doctor & 0.54 & 0.02 & 2.08 \\ 
+  Profession & High school teacher & 0.53 & 0.02 & 1.44 \\ 
+  Profession & Farmer & 0.48 & 0.02 & -0.98 \\ 
+  Profession & Car dealer & 0.33 & 0.02 & -8.64 \\ 
+  Income & 32K & 0.46 & 0.02 & -1.89 \\ 
+  Income & 54K & 0.49 & 0.02 & -0.65 \\ 
+  Income & 65K & 0.53 & 0.02 & 1.33 \\ 
+  Income & 92K & 0.51 & 0.02 & 0.46 \\ 
+  Income & 210K & 0.54 & 0.02 & 1.94 \\ 
+  Income & 5.1M & 0.47 & 0.02 & -1.26 \\ 
+  Race/Ethnicity & White & 0.48 & 0.02 & -0.88 \\ 
+  Race/Ethnicity & Native American & 0.52 & 0.02 & 0.96 \\ 
+  Race/Ethnicity & Black & 0.52 & 0.02 & 0.85 \\ 
+  Race/Ethnicity & Hispanic & 0.47 & 0.02 & -1.59 \\ 
+  Race/Ethnicity & Caucasian & 0.49 & 0.02 & -0.53 \\ 
+  Race/Ethnicity & Asian American & 0.52 & 0.02 & 1.14 \\ 
+  Age & 36 & 0.53 & 0.02 & 1.43 \\ 
+  Age & 45 & 0.55 & 0.02 & 2.21 \\ 
+  Age & 52 & 0.56 & 0.02 & 3.18 \\ 
+  Age & 60 & 0.53 & 0.02 & 1.40 \\ 
+  Age & 68 & 0.45 & 0.02 & -2.31 \\ 
+  Age & 75 & 0.38 & 0.02 & -5.99 \\ 
+  Gender & Male & 0.50 & 0.01 & -0.07 \\ 
+  Gender & Female & 0.50 & 0.01 & 0.07 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\end{table}
 
@@
 
-\section{Hainmueller et al. (2014) Candidate Experiment}
-
-\subsection{Replication using AMCEs}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_amce_appendix-1}
-
-\end{knitrout}
-
-\clearpage
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Nov 25 10:42:42 2018
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lp{3in}rrr}
-  \hline
-feature & level & estimate & std.error & z \\ 
-  \hline
-Military Service & Did Not Serve & 0.00 &  &  \\ 
-  Military Service & Served & 0.09 & 0.02 & 4.95 \\ 
-  Religion & None & 0.00 &  &  \\ 
-  Religion & Jewish & -0.04 & 0.03 & -1.42 \\ 
-  Religion & Catholic & -0.02 & 0.03 & -0.56 \\ 
-  Religion & Mainline protestant & -0.01 & 0.03 & -0.48 \\ 
-  Religion & Evangelical protestant & -0.12 & 0.03 & -3.78 \\ 
-  Religion & Mormon & -0.14 & 0.03 & -4.46 \\ 
-  College & No BA & 0.00 &  &  \\ 
-  College & Baptist college & 0.14 & 0.03 & 4.82 \\ 
-  College & Community college & 0.15 & 0.03 & 5.17 \\ 
-  College & State university & 0.19 & 0.03 & 6.77 \\ 
-  College & Small college & 0.18 & 0.03 & 6.50 \\ 
-  College & Ivy League university & 0.27 & 0.03 & 9.26 \\ 
-  Profession & Business owner & 0.00 &  &  \\ 
-  Profession & Lawyer & -0.02 & 0.03 & -0.71 \\ 
-  Profession & Doctor & -0.02 & 0.03 & -0.53 \\ 
-  Profession & High school teacher & -0.04 & 0.03 & -1.42 \\ 
-  Profession & Farmer & -0.09 & 0.03 & -2.94 \\ 
-  Profession & Car dealer & -0.23 & 0.03 & -7.24 \\ 
-  Income & 32K & 0.00 &  &  \\ 
-  Income & 54K & 0.02 & 0.03 & 0.82 \\ 
-  Income & 65K & 0.06 & 0.03 & 2.26 \\ 
-  Income & 92K & 0.03 & 0.03 & 1.12 \\ 
-  Income & 210K & 0.07 & 0.03 & 2.41 \\ 
-  Income & 5.1M & 0.01 & 0.03 & 0.25 \\ 
-  Race/Ethnicity & White & 0.00 &  &  \\ 
-  Race/Ethnicity & Native American & 0.02 & 0.03 & 0.85 \\ 
-  Race/Ethnicity & Black & 0.03 & 0.03 & 1.22 \\ 
-  Race/Ethnicity & Hispanic & -0.02 & 0.03 & -0.84 \\ 
-  Race/Ethnicity & Caucasian & 0.00 & 0.03 & 0.18 \\ 
-  Race/Ethnicity & Asian American & 0.04 & 0.03 & 1.51 \\ 
-  Age & 36 & 0.00 &  &  \\ 
-  Age & 45 & 0.03 & 0.03 & 0.88 \\ 
-  Age & 52 & 0.02 & 0.03 & 0.78 \\ 
-  Age & 60 & 0.00 & 0.03 & 0.14 \\ 
-  Age & 68 & -0.06 & 0.03 & -2.17 \\ 
-  Age & 75 & -0.15 & 0.03 & -5.06 \\ 
-  Gender & Male & 0.00 &  &  \\ 
-  Gender & Female & 0.00 & 0.02 & 0.09 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\end{table}
-
-\clearpage
-
-\subsection{Replication using MMs}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_mm_appendix-1}
-
-\end{knitrout}
-
-\clearpage
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Nov 25 10:42:44 2018
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lp{3in}rrr}
-  \hline
-feature & level & estimate & std.error & z \\ 
-  \hline
-Military Service & Did Not Serve & 0.46 & 0.01 & -3.54 \\ 
-  Military Service & Served & 0.54 & 0.01 & 3.55 \\ 
-  Religion & None & 0.56 & 0.02 & 2.73 \\ 
-  Religion & Jewish & 0.52 & 0.02 & 0.96 \\ 
-  Religion & Catholic & 0.53 & 0.02 & 1.24 \\ 
-  Religion & Mainline protestant & 0.54 & 0.02 & 2.06 \\ 
-  Religion & Evangelical protestant & 0.44 & 0.02 & -3.05 \\ 
-  Religion & Mormon & 0.42 & 0.02 & -4.04 \\ 
-  College & No BA & 0.34 & 0.02 & -8.11 \\ 
-  College & Baptist college & 0.48 & 0.02 & -0.83 \\ 
-  College & Community college & 0.49 & 0.02 & -0.39 \\ 
-  College & State university & 0.53 & 0.02 & 1.39 \\ 
-  College & Small college & 0.52 & 0.02 & 0.99 \\ 
-  College & Ivy League university & 0.62 & 0.02 & 6.27 \\ 
-  Profession & Business owner & 0.57 & 0.02 & 3.35 \\ 
-  Profession & Lawyer & 0.55 & 0.02 & 2.20 \\ 
-  Profession & Doctor & 0.54 & 0.02 & 2.08 \\ 
-  Profession & High school teacher & 0.53 & 0.02 & 1.44 \\ 
-  Profession & Farmer & 0.48 & 0.02 & -0.98 \\ 
-  Profession & Car dealer & 0.33 & 0.02 & -8.64 \\ 
-  Income & 32K & 0.46 & 0.02 & -1.89 \\ 
-  Income & 54K & 0.49 & 0.02 & -0.65 \\ 
-  Income & 65K & 0.53 & 0.02 & 1.33 \\ 
-  Income & 92K & 0.51 & 0.02 & 0.46 \\ 
-  Income & 210K & 0.54 & 0.02 & 1.94 \\ 
-  Income & 5.1M & 0.47 & 0.02 & -1.26 \\ 
-  Race/Ethnicity & White & 0.48 & 0.02 & -0.88 \\ 
-  Race/Ethnicity & Native American & 0.52 & 0.02 & 0.96 \\ 
-  Race/Ethnicity & Black & 0.52 & 0.02 & 0.85 \\ 
-  Race/Ethnicity & Hispanic & 0.47 & 0.02 & -1.59 \\ 
-  Race/Ethnicity & Caucasian & 0.49 & 0.02 & -0.53 \\ 
-  Race/Ethnicity & Asian American & 0.52 & 0.02 & 1.14 \\ 
-  Age & 36 & 0.53 & 0.02 & 1.43 \\ 
-  Age & 45 & 0.55 & 0.02 & 2.21 \\ 
-  Age & 52 & 0.56 & 0.02 & 3.18 \\ 
-  Age & 60 & 0.53 & 0.02 & 1.40 \\ 
-  Age & 68 & 0.45 & 0.02 & -2.31 \\ 
-  Age & 75 & 0.38 & 0.02 & -5.99 \\ 
-  Gender & Male & 0.50 & 0.01 & -0.07 \\ 
-  Gender & Female & 0.50 & 0.01 & 0.07 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\end{table}
-
-\clearpage
-
-\section{Ballard-Rosa et al. (2016) Tax Preference Experiment}
-
-\subsection{Replication using AMCEs}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bms_amce_appendix-1}
-
-\end{knitrout}
-
-\clearpage
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Nov 25 10:42:47 2018
-\begin{table}[ht]
-\centering
-\begin{tabular}{lp{1.5in}rrr}
-  \hline
-feature & level & estimate & std.error & z \\ 
-  \hline
-Tax rate for $<$\$10,000 & $<$10k: 0\% & 0.00 &  &  \\ 
-  Tax rate for $<$\$10,000 & $<$10k: 5\% & -0.02 & 0.01 & -3.81 \\ 
-  Tax rate for $<$\$10,000 & $<$10k: 15\% & -0.11 & 0.01 & -15.97 \\ 
-  Tax rate for $<$\$10,000 & $<$10k: 25\% & -0.24 & 0.01 & -28.33 \\ 
-  Tax rate for \$10,000-\$35,000 & 10-35k: 5\% & 0.00 &  &  \\ 
-  Tax rate for \$10,000-\$35,000 & 10-35k: 15\% & -0.02 & 0.01 & -2.94 \\ 
-  Tax rate for \$10,000-\$35,000 & 10-35k: 25\% & -0.10 & 0.01 & -9.42 \\ 
-  Tax rate for \$10,000-\$35,000 & 10-35k: 35\% & -0.22 & 0.01 & -15.96 \\ 
-  Tax rate for \$25,000-\$85,000 & 35-85k: 5\% & 0.00 &  &  \\ 
-  Tax rate for \$25,000-\$85,000 & 35-85k: 15\% & 0.00 & 0.01 & 0.03 \\ 
-  Tax rate for \$25,000-\$85,000 & 35-85k: 25\% & -0.07 & 0.01 & -9.18 \\ 
-  Tax rate for \$25,000-\$85,000 & 35-85k: 35\% & -0.13 & 0.01 & -14.55 \\ 
-  Tax rate for \$85,000-\$175,000 & 85-175k: 5\% & 0.00 &  &  \\ 
-  Tax rate for \$85,000-\$175,000 & 85-175k: 15\% & 0.01 & 0.01 & 2.06 \\ 
-  Tax rate for \$85,000-\$175,000 & 85-175k: 25\% & -0.02 & 0.01 & -2.80 \\ 
-  Tax rate for \$85,000-\$175,000 & 85-175k: 35\% & -0.01 & 0.01 & -2.19 \\ 
-  Tax rate for \$175,000-\$375,000 & 175-375k: 5\% & 0.00 &  &  \\ 
-  Tax rate for \$175,000-\$375,000 & 175-375k: 15\% & 0.03 & 0.01 & 5.97 \\ 
-  Tax rate for \$175,000-\$375,000 & 175-375k: 25\% & 0.04 & 0.01 & 6.53 \\ 
-  Tax rate for \$175,000-\$375,000 & 175-375k: 35\% & 0.06 & 0.01 & 9.77 \\ 
-  Tax rate for \$175,000-\$375,000 & 175-375k: 45\% & 0.03 & 0.01 & 4.80 \\ 
-  Tax rate for $>$\$375,000 & $>$375k: 5\% & 0.00 &  &  \\ 
-  Tax rate for $>$\$375,000 & $>$375k: 15\% & 0.06 & 0.01 & 8.22 \\ 
-  Tax rate for $>$\$375,000 & $>$375k: 25\% & 0.09 & 0.01 & 12.18 \\ 
-  Tax rate for $>$\$375,000 & $>$375k: 35\% & 0.11 & 0.01 & 15.44 \\ 
-  Tax rate for $>$\$375,000 & $>$375k: 45\% & 0.11 & 0.01 & 13.23 \\ 
-  Tax rate for $>$\$375,000 & $>$375k: 55\% & 0.08 & 0.01 & 9.55 \\ 
-  Tax revenue & $<$75\% & 0.00 &  &  \\ 
-  Tax revenue & 75-95\% & 0.03 & 0.01 & 3.56 \\ 
-  Tax revenue & 95-105\% & 0.07 & 0.01 & 6.11 \\ 
-  Tax revenue & 105-125\% & 0.09 & 0.01 & 6.33 \\ 
-  Tax revenue & $>$125\% & 0.14 & 0.02 & 7.22 \\ 
-   \hline
-\end{tabular}
-\end{table}
-
-\clearpage
-
-\subsection{Replication using MMs}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bms_mm_appendix-1}
-
-\end{knitrout}
-
-\clearpage
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Nov 25 10:42:56 2018
-\begin{table}[ht]
-\centering
-\begin{tabular}{lp{1.5in}rrr}
-  \hline
-feature & level & estimate & std.error & z \\ 
-  \hline
-Tax rate for $<$\$10,000 & $<$10k: 0\% & 0.57 & 0.01 & 9.37 \\ 
-  Tax rate for $<$\$10,000 & $<$10k: 5\% & 0.56 & 0.01 & 8.06 \\ 
-  Tax rate for $<$\$10,000 & $<$10k: 15\% & 0.49 & 0.01 & -1.11 \\ 
-  Tax rate for $<$\$10,000 & $<$10k: 25\% & 0.37 & 0.01 & -16.07 \\ 
-  Tax rate for \$10,000-\$35,000 & 10-35k: 5\% & 0.54 & 0.01 & 4.75 \\ 
-  Tax rate for \$10,000-\$35,000 & 10-35k: 15\% & 0.54 & 0.01 & 5.55 \\ 
-  Tax rate for \$10,000-\$35,000 & 10-35k: 25\% & 0.50 & 0.01 & 0.39 \\ 
-  Tax rate for \$10,000-\$35,000 & 10-35k: 35\% & 0.42 & 0.01 & -10.62 \\ 
-  Tax rate for \$25,000-\$85,000 & 35-85k: 5\% & 0.53 & 0.01 & 3.45 \\ 
-  Tax rate for \$25,000-\$85,000 & 35-85k: 15\% & 0.54 & 0.01 & 5.37 \\ 
-  Tax rate for \$25,000-\$85,000 & 35-85k: 25\% & 0.49 & 0.01 & -1.27 \\ 
-  Tax rate for \$25,000-\$85,000 & 35-85k: 35\% & 0.44 & 0.01 & -7.50 \\ 
-  Tax rate for \$85,000-\$175,000 & 85-175k: 5\% & 0.50 & 0.01 & 0.00 \\ 
-  Tax rate for \$85,000-\$175,000 & 85-175k: 15\% & 0.51 & 0.01 & 1.42 \\ 
-  Tax rate for \$85,000-\$175,000 & 85-175k: 25\% & 0.49 & 0.01 & -1.00 \\ 
-  Tax rate for \$85,000-\$175,000 & 85-175k: 35\% & 0.50 & 0.01 & -0.46 \\ 
-  Tax rate for \$175,000-\$375,000 & 175-375k: 5\% & 0.46 & 0.01 & -4.37 \\ 
-  Tax rate for \$175,000-\$375,000 & 175-375k: 15\% & 0.50 & 0.01 & -0.47 \\ 
-  Tax rate for \$175,000-\$375,000 & 175-375k: 25\% & 0.51 & 0.01 & 0.84 \\ 
-  Tax rate for \$175,000-\$375,000 & 175-375k: 35\% & 0.53 & 0.01 & 3.11 \\ 
-  Tax rate for \$175,000-\$375,000 & 175-375k: 45\% & 0.51 & 0.01 & 0.80 \\ 
-  Tax rate for $>$\$375,000 & $>$375k: 5\% & 0.41 & 0.01 & -9.57 \\ 
-  Tax rate for $>$\$375,000 & $>$375k: 15\% & 0.47 & 0.01 & -3.30 \\ 
-  Tax rate for $>$\$375,000 & $>$375k: 25\% & 0.51 & 0.01 & 0.97 \\ 
-  Tax rate for $>$\$375,000 & $>$375k: 35\% & 0.54 & 0.01 & 4.48 \\ 
-  Tax rate for $>$\$375,000 & $>$375k: 45\% & 0.55 & 0.01 & 4.75 \\ 
-  Tax rate for $>$\$375,000 & $>$375k: 55\% & 0.53 & 0.01 & 3.12 \\ 
-  Tax revenue & $<$75\% & 0.57 & 0.01 & 8.22 \\ 
-  Tax revenue & 75-95\% & 0.53 & 0.01 & 3.47 \\ 
-  Tax revenue & 95-105\% & 0.51 & 0.01 & 1.18 \\ 
-  Tax revenue & 105-125\% & 0.48 & 0.01 & -2.21 \\ 
-  Tax revenue & $>$125\% & 0.41 & 0.01 & -10.54 \\ 
-   \hline
-\end{tabular}
-\end{table}
-
-\clearpage
-
-\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by ``Taxes Harm Economy'' Split using AMCEs}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bms_subgroup_amce_appendix1-1}
-
-\end{knitrout}
-
-\clearpage
-
-\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by ``Taxes Harm Economy'' Split using MMs}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bms_subgroup_mm_appendix1-1}
-
-\end{knitrout}
-
-\clearpage
-
-\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by Inequity Aversion using AMCEs}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bms_subgroup_amce_appendix2-1}
-
-\end{knitrout}
-
-\clearpage
-
-\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by Inequity Aversion using MMs}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bms_subgroup_mm_appendix2-1}
-
-\end{knitrout}
-
-\clearpage
-
-\subsection{Comparison of Alternative Reference Categories for Ballard-Rosa et al. (2016) Tax Preference Experiment, by ``Taxes Harm Economy'' Split}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bms_subgroup_example_plot1-1}
-
-\end{knitrout}
-
-\clearpage
-
-\subsection{Comparison of Alternative Reference Categories for Ballard-Rosa et al. (2016) Tax Preference Experiment, by Inequity Aversion}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bms_subgroup_example_plot2-1}
-
-\end{knitrout}
-
-\clearpage
-
-\section{Bechtel and Scheve (2013) Climate Agreement Experiment}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{verbatim}
-##      outcome statistic                                 feature
-## 1  choice_cj      amce    Costs to average household per month
-## 2  choice_cj      amce    Costs to average household per month
-## 3  choice_cj      amce    Costs to average household per month
-## 4  choice_cj      amce    Costs to average household per month
-## 5  choice_cj      amce    Costs to average household per month
-## 6  choice_cj      amce                   Distribution of costs
-## 7  choice_cj      amce                   Distribution of costs
-## 8  choice_cj      amce                   Distribution of costs
-## 9  choice_cj      amce                   Distribution of costs
-## 10 choice_cj      amce       Number of participating countries
-## 11 choice_cj      amce       Number of participating countries
-## 12 choice_cj      amce       Number of participating countries
-## 13 choice_cj      amce   Share of global emissions represented
-## 14 choice_cj      amce   Share of global emissions represented
-## 15 choice_cj      amce   Share of global emissions represented
-## 16 choice_cj      amce Sanctions for missing reduction targets
-## 17 choice_cj      amce Sanctions for missing reduction targets
-## 18 choice_cj      amce Sanctions for missing reduction targets
-## 19 choice_cj      amce Sanctions for missing reduction targets
-## 20 choice_cj      amce                           Monitoring by
-## 21 choice_cj      amce                           Monitoring by
-## 22 choice_cj      amce                           Monitoring by
-## 23 choice_cj      amce                           Monitoring by
-##                                level     estimate   std.error           z
-## 1                      \20028 per month  0.000000000          NA          NA
-## 2                      \20056 per month -0.097845284 0.001402351  -69.772319
-## 3                      \20084 per month -0.170008434 0.001468627 -115.760108
-## 4                     \200113 per month -0.263769273 0.001471840 -179.210616
-## 5                     \200141 per month -0.332856845 0.001422455 -234.001744
-## 6                          Only rich  0.000000000          NA          NA
-## 7         Prop. to current emissions  0.065924582 0.001340698   49.171839
-## 8      Prop. to history of emissions  0.052479783 0.001345106   39.015350
-## 9  Rich pay more than poor countries  0.057280714 0.001327647   43.144545
-## 10                         20 of 192  0.000000000          NA          NA
-## 11                         80 of 192  0.092728950 0.001141542   81.231296
-## 12                        160 of 192  0.156435103 0.001175080  133.127175
-## 13          40% of current emissions  0.000000000          NA          NA
-## 14          60% of current emissions  0.022498908 0.001117762   20.128532
-## 15          80% of current emissions  0.045174103 0.001125637   40.132047
-## 16                              None  0.000000000          NA          NA
-## 17               \2006 per hh and month  0.028464249 0.001308130   21.759490
-## 18              \20017 per hh and month -0.018533001 0.001326110  -13.975465
-## 19              \20023 per hh and month -0.053180963 0.001312140  -40.529947
-## 20                   Your government  0.000000000          NA          NA
-## 21                 Indep. commission  0.061714854 0.001323261   46.638460
-## 22                    United Nations  0.024280174 0.001356516   17.898921
-## 23                        Greenpeace -0.006573634 0.001377372   -4.772591
-##                p        lower        upper
-## 1             NA           NA           NA
-## 2   0.000000e+00 -0.100593842 -0.095096727
-## 3   0.000000e+00 -0.172886890 -0.167129978
-## 4   0.000000e+00 -0.266654026 -0.260884521
-## 5   0.000000e+00 -0.335644805 -0.330068886
-## 6             NA           NA           NA
-## 7   0.000000e+00  0.063296862  0.068552302
-## 8   0.000000e+00  0.049843423  0.055116142
-## 9   0.000000e+00  0.054678574  0.059882854
-## 10            NA           NA           NA
-## 11  0.000000e+00  0.090491569  0.094966332
-## 12  0.000000e+00  0.154131988  0.158738218
-## 13            NA           NA           NA
-## 14  4.151128e-90  0.020308135  0.024689682
-## 15  0.000000e+00  0.042967896  0.047380310
-## 16            NA           NA           NA
-## 17 5.616961e-105  0.025900360  0.031028137
-## 18  2.200727e-44 -0.021132129 -0.015933874
-## 19  0.000000e+00 -0.055752710 -0.050609216
-## 20            NA           NA           NA
-## 21  0.000000e+00  0.059121310  0.064308398
-## 22  1.202281e-71  0.021621451  0.026938896
-## 23  1.818711e-06 -0.009273234 -0.003874034
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{verbatim}
-##      outcome statistic                                 feature
-## 1  choice_cj        mm    Costs to average household per month
-## 2  choice_cj        mm    Costs to average household per month
-## 3  choice_cj        mm    Costs to average household per month
-## 4  choice_cj        mm    Costs to average household per month
-## 5  choice_cj        mm    Costs to average household per month
-## 6  choice_cj        mm                   Distribution of costs
-## 7  choice_cj        mm                   Distribution of costs
-## 8  choice_cj        mm                   Distribution of costs
-## 9  choice_cj        mm                   Distribution of costs
-## 10 choice_cj        mm       Number of participating countries
-## 11 choice_cj        mm       Number of participating countries
-## 12 choice_cj        mm       Number of participating countries
-## 13 choice_cj        mm   Share of global emissions represented
-## 14 choice_cj        mm   Share of global emissions represented
-## 15 choice_cj        mm   Share of global emissions represented
-## 16 choice_cj        mm Sanctions for missing reduction targets
-## 17 choice_cj        mm Sanctions for missing reduction targets
-## 18 choice_cj        mm Sanctions for missing reduction targets
-## 19 choice_cj        mm Sanctions for missing reduction targets
-## 20 choice_cj        mm                           Monitoring by
-## 21 choice_cj        mm                           Monitoring by
-## 22 choice_cj        mm                           Monitoring by
-## 23 choice_cj        mm                           Monitoring by
-##                                level  estimate   std.error         z p
-## 1                      \20028 per month 0.6729737 0.004126308 163.09342 0
-## 2                      \20056 per month 0.5753704 0.004309124 133.52375 0
-## 3                      \20084 per month 0.5028766 0.004395792 114.39955 0
-## 4                     \200113 per month 0.4085284 0.004325220  94.45264 0
-## 5                     \200141 per month 0.3394765 0.004148381  81.83349 0
-## 6                          Only rich 0.4570055 0.003911228 116.84452 0
-## 7         Prop. to current emissions 0.5216566 0.003926015 132.87176 0
-## 8      Prop. to history of emissions 0.5087938 0.003917689 129.87090 0
-## 9  Rich pay more than poor countries 0.5127165 0.003924942 130.63032 0
-## 10                         20 of 192 0.4182276 0.003341616 125.15729 0
-## 11                         80 of 192 0.5089863 0.003399306 149.73245 0
-## 12                        160 of 192 0.5737857 0.003373566 170.08288 0
-## 13          40% of current emissions 0.4781113 0.003380328 141.43933 0
-## 14          60% of current emissions 0.4999291 0.003407780 146.70227 0
-## 15          80% of current emissions 0.5222143 0.003402419 153.48325 0
-## 16                              None 0.5106586 0.003932951 129.84109 0
-## 17               \2006 per hh and month 0.5412417 0.003913371 138.30573 0
-## 18              \20017 per hh and month 0.4928567 0.003908225 126.10754 0
-## 19              \20023 per hh and month 0.4552868 0.003914718 116.30129 0
-## 20                   Your government 0.4813399 0.003912654 123.02130 0
-## 21                 Indep. commission 0.5426752 0.003901770 139.08437 0
-## 22                    United Nations 0.5032115 0.003941043 127.68486 0
-## 23                        Greenpeace 0.4725424 0.003920333 120.53630 0
-##        lower     upper
-## 1  0.6648863 0.6810611
-## 2  0.5669247 0.5838161
-## 3  0.4942610 0.5114922
-## 4  0.4000512 0.4170057
-## 5  0.3313459 0.3476072
-## 6  0.4493397 0.4646714
-## 7  0.5139617 0.5293514
-## 8  0.5011153 0.5164723
-## 9  0.5050237 0.5204092
-## 10 0.4116781 0.4247770
-## 11 0.5023238 0.5156488
-## 12 0.5671737 0.5803978
-## 13 0.4714860 0.4847366
-## 14 0.4932500 0.5066083
-## 15 0.5155456 0.5288829
-## 16 0.5029502 0.5183671
-## 17 0.5335716 0.5489118
-## 18 0.4851967 0.5005167
-## 19 0.4476140 0.4629595
-## 20 0.4736712 0.4890085
-## 21 0.5350279 0.5503225
-## 22 0.4954872 0.5109358
-## 23 0.4648587 0.4802262
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_mm-1} 
-\begin{kframe}\begin{verbatim}
-##                BY   outcome statistic
-## 1          France choice_cj        mm
-## 2          France choice_cj        mm
-## 3          France choice_cj        mm
-## 4          France choice_cj        mm
-## 5          France choice_cj        mm
-## 6          France choice_cj        mm
-## 7          France choice_cj        mm
-## 8          France choice_cj        mm
-## 9          France choice_cj        mm
-## 10         France choice_cj        mm
-## 11         France choice_cj        mm
-## 12         France choice_cj        mm
-## 13         France choice_cj        mm
-## 14         France choice_cj        mm
-## 15         France choice_cj        mm
-## 16         France choice_cj        mm
-## 17         France choice_cj        mm
-## 18         France choice_cj        mm
-## 19         France choice_cj        mm
-## 20         France choice_cj        mm
-## 21         France choice_cj        mm
-## 22         France choice_cj        mm
-## 23         France choice_cj        mm
-## 24        Germany choice_cj        mm
-## 25        Germany choice_cj        mm
-## 26        Germany choice_cj        mm
-## 27        Germany choice_cj        mm
-## 28        Germany choice_cj        mm
-## 29        Germany choice_cj        mm
-## 30        Germany choice_cj        mm
-## 31        Germany choice_cj        mm
-## 32        Germany choice_cj        mm
-## 33        Germany choice_cj        mm
-## 34        Germany choice_cj        mm
-## 35        Germany choice_cj        mm
-## 36        Germany choice_cj        mm
-## 37        Germany choice_cj        mm
-## 38        Germany choice_cj        mm
-## 39        Germany choice_cj        mm
-## 40        Germany choice_cj        mm
-## 41        Germany choice_cj        mm
-## 42        Germany choice_cj        mm
-## 43        Germany choice_cj        mm
-## 44        Germany choice_cj        mm
-## 45        Germany choice_cj        mm
-## 46        Germany choice_cj        mm
-## 47 United Kingdom choice_cj        mm
-## 48 United Kingdom choice_cj        mm
-## 49 United Kingdom choice_cj        mm
-## 50 United Kingdom choice_cj        mm
-## 51 United Kingdom choice_cj        mm
-## 52 United Kingdom choice_cj        mm
-## 53 United Kingdom choice_cj        mm
-## 54 United Kingdom choice_cj        mm
-## 55 United Kingdom choice_cj        mm
-## 56 United Kingdom choice_cj        mm
-## 57 United Kingdom choice_cj        mm
-## 58 United Kingdom choice_cj        mm
-## 59 United Kingdom choice_cj        mm
-## 60 United Kingdom choice_cj        mm
-## 61 United Kingdom choice_cj        mm
-## 62 United Kingdom choice_cj        mm
-## 63 United Kingdom choice_cj        mm
-## 64 United Kingdom choice_cj        mm
-## 65 United Kingdom choice_cj        mm
-## 66 United Kingdom choice_cj        mm
-## 67 United Kingdom choice_cj        mm
-## 68 United Kingdom choice_cj        mm
-## 69 United Kingdom choice_cj        mm
-## 70  United States choice_cj        mm
-## 71  United States choice_cj        mm
-## 72  United States choice_cj        mm
-## 73  United States choice_cj        mm
-## 74  United States choice_cj        mm
-## 75  United States choice_cj        mm
-## 76  United States choice_cj        mm
-## 77  United States choice_cj        mm
-## 78  United States choice_cj        mm
-## 79  United States choice_cj        mm
-## 80  United States choice_cj        mm
-## 81  United States choice_cj        mm
-## 82  United States choice_cj        mm
-## 83  United States choice_cj        mm
-## 84  United States choice_cj        mm
-## 85  United States choice_cj        mm
-## 86  United States choice_cj        mm
-## 87  United States choice_cj        mm
-## 88  United States choice_cj        mm
-## 89  United States choice_cj        mm
-## 90  United States choice_cj        mm
-## 91  United States choice_cj        mm
-## 92  United States choice_cj        mm
-##                                    feature
-## 1     Costs to average household per month
-## 2     Costs to average household per month
-## 3     Costs to average household per month
-## 4     Costs to average household per month
-## 5     Costs to average household per month
-## 6                    Distribution of costs
-## 7                    Distribution of costs
-## 8                    Distribution of costs
-## 9                    Distribution of costs
-## 10       Number of participating countries
-## 11       Number of participating countries
-## 12       Number of participating countries
-## 13   Share of global emissions represented
-## 14   Share of global emissions represented
-## 15   Share of global emissions represented
-## 16 Sanctions for missing reduction targets
-## 17 Sanctions for missing reduction targets
-## 18 Sanctions for missing reduction targets
-## 19 Sanctions for missing reduction targets
-## 20                           Monitoring by
-## 21                           Monitoring by
-## 22                           Monitoring by
-## 23                           Monitoring by
-## 24    Costs to average household per month
-## 25    Costs to average household per month
-## 26    Costs to average household per month
-## 27    Costs to average household per month
-## 28    Costs to average household per month
-## 29                   Distribution of costs
-## 30                   Distribution of costs
-## 31                   Distribution of costs
-## 32                   Distribution of costs
-## 33       Number of participating countries
-## 34       Number of participating countries
-## 35       Number of participating countries
-## 36   Share of global emissions represented
-## 37   Share of global emissions represented
-## 38   Share of global emissions represented
-## 39 Sanctions for missing reduction targets
-## 40 Sanctions for missing reduction targets
-## 41 Sanctions for missing reduction targets
-## 42 Sanctions for missing reduction targets
-## 43                           Monitoring by
-## 44                           Monitoring by
-## 45                           Monitoring by
-## 46                           Monitoring by
-## 47    Costs to average household per month
-## 48    Costs to average household per month
-## 49    Costs to average household per month
-## 50    Costs to average household per month
-## 51    Costs to average household per month
-## 52                   Distribution of costs
-## 53                   Distribution of costs
-## 54                   Distribution of costs
-## 55                   Distribution of costs
-## 56       Number of participating countries
-## 57       Number of participating countries
-## 58       Number of participating countries
-## 59   Share of global emissions represented
-## 60   Share of global emissions represented
-## 61   Share of global emissions represented
-## 62 Sanctions for missing reduction targets
-## 63 Sanctions for missing reduction targets
-## 64 Sanctions for missing reduction targets
-## 65 Sanctions for missing reduction targets
-## 66                           Monitoring by
-## 67                           Monitoring by
-## 68                           Monitoring by
-## 69                           Monitoring by
-## 70    Costs to average household per month
-## 71    Costs to average household per month
-## 72    Costs to average household per month
-## 73    Costs to average household per month
-## 74    Costs to average household per month
-## 75                   Distribution of costs
-## 76                   Distribution of costs
-## 77                   Distribution of costs
-## 78                   Distribution of costs
-## 79       Number of participating countries
-## 80       Number of participating countries
-## 81       Number of participating countries
-## 82   Share of global emissions represented
-## 83   Share of global emissions represented
-## 84   Share of global emissions represented
-## 85 Sanctions for missing reduction targets
-## 86 Sanctions for missing reduction targets
-## 87 Sanctions for missing reduction targets
-## 88 Sanctions for missing reduction targets
-## 89                           Monitoring by
-## 90                           Monitoring by
-## 91                           Monitoring by
-## 92                           Monitoring by
-##                                level  estimate   std.error        z
-## 1                      \20028 per month 0.6613316 0.008322408 79.46397
-## 2                      \20056 per month 0.5693159 0.008660576 65.73649
-## 3                      \20084 per month 0.4989851 0.008884067 56.16629
-## 4                     \200113 per month 0.3970867 0.008722819 45.52275
-## 5                     \200141 per month 0.3667680 0.008567482 42.80931
-## 6                          Only rich 0.4694590 0.007936306 59.15334
-## 7         Prop. to current emissions 0.5234480 0.007931229 65.99834
-## 8      Prop. to history of emissions 0.5070668 0.007869017 64.43840
-## 9  Rich pay more than poor countries 0.4998164 0.007880458 63.42479
-## 10                         20 of 192 0.4280902 0.006737716 63.53639
-## 11                         80 of 192 0.5079278 0.006874025 73.89089
-## 12                        160 of 192 0.5652797 0.006810168 83.00524
-## 13          40% of current emissions 0.4714751 0.006806164 69.27178
-## 14          60% of current emissions 0.4972686 0.006865214 72.43307
-## 15          80% of current emissions 0.5316843 0.006854741 77.56447
-## 16                              None 0.4925810 0.007922009 62.17879
-## 17               \2006 per hh and month 0.5433092 0.007813932 69.53084
-## 18              \20017 per hh and month 0.5026263 0.007925773 63.41668
-## 19              \20023 per hh and month 0.4603338 0.007923589 58.09663
-## 20                   Your government 0.4707127 0.007932301 59.34126
-## 21                 Indep. commission 0.5410998 0.007756003 69.76529
-## 22                    United Nations 0.5079832 0.007952899 63.87396
-## 23                        Greenpeace 0.4783606 0.007954893 60.13414
-## 24                     \20028 per month 0.6520203 0.008538989 76.35801
-## 25                     \20056 per month 0.5667114 0.008678489 65.30070
-## 26                     \20084 per month 0.4912437 0.008871631 55.37242
-## 27                    \200113 per month 0.4301405 0.008828618 48.72116
-## 28                    \200141 per month 0.3582373 0.008565178 41.82486
-## 29                         Only rich 0.4600371 0.007930387 58.00941
-## 30        Prop. to current emissions 0.5153914 0.007901516 65.22689
-## 31     Prop. to history of emissions 0.4940093 0.007884299 62.65736
-## 32 Rich pay more than poor countries 0.5312310 0.008045629 66.02727
-## 33                         20 of 192 0.4098216 0.006744866 60.76052
-## 34                         80 of 192 0.5134710 0.006855305 74.90126
-## 35                        160 of 192 0.5787895 0.006863767 84.32534
-## 36          40% of current emissions 0.4723114 0.006837992 69.07165
-## 37          60% of current emissions 0.5007192 0.006884860 72.72757
-## 38          80% of current emissions 0.5275701 0.006914689 76.29700
-## 39                              None 0.4940875 0.007989972 61.83845
-## 40               \2006 per hh and month 0.5402615 0.007912846 68.27651
-## 41              \20017 per hh and month 0.5021986 0.007968977 63.01920
-## 42              \20023 per hh and month 0.4636031 0.007886215 58.78651
-## 43                   Your government 0.4691111 0.007850099 59.75862
-## 44                 Indep. commission 0.5483852 0.007959662 68.89553
-## 45                    United Nations 0.5011726 0.007951130 63.03162
-## 46                        Greenpeace 0.4823303 0.007989396 60.37131
-## 47                     \20028 per month 0.6934878 0.008424386 82.31909
-## 48                     \20056 per month 0.5859726 0.009034648 64.85838
-## 49                     \20084 per month 0.5048116 0.009338115 54.05926
-## 50                    \200113 per month 0.4024743 0.008986324 44.78743
-## 51                    \200141 per month 0.3132586 0.008508073 36.81898
-## 52                         Only rich 0.4661502 0.008199944 56.84798
-## 53        Prop. to current emissions 0.5221721 0.008206555 63.62865
-## 54     Prop. to history of emissions 0.5024308 0.008263298 60.80270
-## 55 Rich pay more than poor countries 0.5095266 0.008245511 61.79443
-## 56                         20 of 192 0.4025534 0.006980412 57.66899
-## 57                         80 of 192 0.5079030 0.007155688 70.97892
-## 58                        160 of 192 0.5899041 0.007002721 84.23928
-## 59          40% of current emissions 0.4795459 0.007060046 67.92391
-## 60          60% of current emissions 0.5032446 0.007215347 69.74642
-## 61          80% of current emissions 0.5176103 0.007113186 72.76772
-## 62                              None 0.5270756 0.008192395 64.33718
-## 63               \2006 per hh and month 0.5405720 0.008214268 65.80890
-## 64              \20017 per hh and month 0.4769717 0.008165885 58.41029
-## 65              \20023 per hh and month 0.4544697 0.008288953 54.82836
-## 66                   Your government 0.4768185 0.008212548 58.05975
-## 67                 Indep. commission 0.5392912 0.008128128 66.34876
-## 68                    United Nations 0.5147711 0.008330945 61.79024
-## 69                        Greenpeace 0.4686105 0.008208476 57.08861
-## 70                     \20028 per month 0.6824518 0.007763555 87.90454
-## 71                     \20056 per month 0.5789579 0.008147606 71.05866
-## 72                     \20084 per month 0.5136585 0.008166584 62.89760
-## 73                    \200113 per month 0.4051599 0.008111491 49.94888
-## 74                    \200141 per month 0.3244207 0.007630904 42.51406
-## 75                         Only rich 0.4375458 0.007282486 60.08192
-## 76        Prop. to current emissions 0.5249692 0.007413118 70.81625
-## 77     Prop. to history of emissions 0.5272909 0.007370877 71.53706
-## 78 Rich pay more than poor countries 0.5112713 0.007298410 70.05243
-## 79                         20 of 192 0.4296274 0.006300652 68.18777
-## 80                         80 of 192 0.5070832 0.006363026 79.69215
-## 81                        160 of 192 0.5636379 0.006344643 88.83682
-## 82          40% of current emissions 0.4870124 0.006373185 76.41585
-## 83          60% of current emissions 0.4988350 0.006362123 78.40701
-## 84          80% of current emissions 0.5141367 0.006379806 80.58813
-## 85                              None 0.5251766 0.007391775 71.04878
-## 86               \2006 per hh and month 0.5408734 0.007408935 73.00285
-## 87              \20017 per hh and month 0.4906273 0.007267688 67.50804
-## 88              \20023 per hh and month 0.4452759 0.007296972 61.02201
-## 89                   Your government 0.5033382 0.007350454 68.47716
-## 90                 Indep. commission 0.5422171 0.007403558 73.23736
-## 91                    United Nations 0.4920508 0.007361504 66.84108
-## 92                        Greenpeace 0.4634591 0.007284021 63.62682
-##                p     lower     upper        country
-## 1   0.000000e+00 0.6450199 0.6776432         France
-## 2   0.000000e+00 0.5523415 0.5862903         France
-## 3   0.000000e+00 0.4815727 0.5163976         France
-## 4   0.000000e+00 0.3799903 0.4141831         France
-## 5   0.000000e+00 0.3499761 0.3835600         France
-## 6   0.000000e+00 0.4539041 0.4850139         France
-## 7   0.000000e+00 0.5079031 0.5389929         France
-## 8   0.000000e+00 0.4916438 0.5224898         France
-## 9   0.000000e+00 0.4843710 0.5152619         France
-## 10  0.000000e+00 0.4148845 0.4412958         France
-## 11  0.000000e+00 0.4944550 0.5214007         France
-## 12  0.000000e+00 0.5519320 0.5786274         France
-## 13  0.000000e+00 0.4581352 0.4848149         France
-## 14  0.000000e+00 0.4838130 0.5107242         France
-## 15  0.000000e+00 0.5182493 0.5451194         France
-## 16  0.000000e+00 0.4770541 0.5081078         France
-## 17  0.000000e+00 0.5279942 0.5586243         France
-## 18  0.000000e+00 0.4870920 0.5181605         France
-## 19  0.000000e+00 0.4448038 0.4758637         France
-## 20  0.000000e+00 0.4551657 0.4862597         France
-## 21  0.000000e+00 0.5258983 0.5563013         France
-## 22  0.000000e+00 0.4923958 0.5235706         France
-## 23  0.000000e+00 0.4627693 0.4939519         France
-## 24  0.000000e+00 0.6352841 0.6687564        Germany
-## 25  0.000000e+00 0.5497018 0.5837209        Germany
-## 26  0.000000e+00 0.4738556 0.5086317        Germany
-## 27  0.000000e+00 0.4128368 0.4474443        Germany
-## 28  0.000000e+00 0.3414499 0.3750248        Germany
-## 29  0.000000e+00 0.4444938 0.4755803        Germany
-## 30  0.000000e+00 0.4999047 0.5308781        Germany
-## 31  0.000000e+00 0.4785564 0.5094622        Germany
-## 32  0.000000e+00 0.5154618 0.5470001        Germany
-## 33  0.000000e+00 0.3966019 0.4230413        Germany
-## 34  0.000000e+00 0.5000348 0.5269071        Germany
-## 35  0.000000e+00 0.5653368 0.5922422        Germany
-## 36  0.000000e+00 0.4589092 0.4857136        Germany
-## 37  0.000000e+00 0.4872251 0.5142132        Germany
-## 38  0.000000e+00 0.5140175 0.5411226        Germany
-## 39  0.000000e+00 0.4784274 0.5097476        Germany
-## 40  0.000000e+00 0.5247526 0.5557704        Germany
-## 41  0.000000e+00 0.4865797 0.5178175        Germany
-## 42  0.000000e+00 0.4481464 0.4790598        Germany
-## 43  0.000000e+00 0.4537252 0.4844970        Germany
-## 44  0.000000e+00 0.5327845 0.5639858        Germany
-## 45  0.000000e+00 0.4855887 0.5167566        Germany
-## 46  0.000000e+00 0.4666714 0.4979892        Germany
-## 47  0.000000e+00 0.6769763 0.7099993 United Kingdom
-## 48  0.000000e+00 0.5682650 0.6036802 United Kingdom
-## 49  0.000000e+00 0.4865092 0.5231140 United Kingdom
-## 50  0.000000e+00 0.3848615 0.4200872 United Kingdom
-## 51 9.175209e-297 0.2965831 0.3299341 United Kingdom
-## 52  0.000000e+00 0.4500786 0.4822218 United Kingdom
-## 53  0.000000e+00 0.5060875 0.5382566 United Kingdom
-## 54  0.000000e+00 0.4862350 0.5186266 United Kingdom
-## 55  0.000000e+00 0.4933657 0.5256875 United Kingdom
-## 56  0.000000e+00 0.3888720 0.4162347 United Kingdom
-## 57  0.000000e+00 0.4938781 0.5219279 United Kingdom
-## 58  0.000000e+00 0.5761791 0.6036292 United Kingdom
-## 59  0.000000e+00 0.4657085 0.4933834 United Kingdom
-## 60  0.000000e+00 0.4891028 0.5173864 United Kingdom
-## 61  0.000000e+00 0.5036687 0.5315519 United Kingdom
-## 62  0.000000e+00 0.5110188 0.5431324 United Kingdom
-## 63  0.000000e+00 0.5244723 0.5566716 United Kingdom
-## 64  0.000000e+00 0.4609668 0.4929765 United Kingdom
-## 65  0.000000e+00 0.4382236 0.4707157 United Kingdom
-## 66  0.000000e+00 0.4607222 0.4929148 United Kingdom
-## 67  0.000000e+00 0.5233604 0.5552221 United Kingdom
-## 68  0.000000e+00 0.4984427 0.5310994 United Kingdom
-## 69  0.000000e+00 0.4525221 0.4846988 United Kingdom
-## 70  0.000000e+00 0.6672355 0.6976681  United States
-## 71  0.000000e+00 0.5629889 0.5949270  United States
-## 72  0.000000e+00 0.4976523 0.5296647  United States
-## 73  0.000000e+00 0.3892617 0.4210581  United States
-## 74  0.000000e+00 0.3094644 0.3393770  United States
-## 75  0.000000e+00 0.4232724 0.4518192  United States
-## 76  0.000000e+00 0.5104398 0.5394987  United States
-## 77  0.000000e+00 0.5128442 0.5417375  United States
-## 78  0.000000e+00 0.4969667 0.5255759  United States
-## 79  0.000000e+00 0.4172784 0.4419765  United States
-## 80  0.000000e+00 0.4946119 0.5195545  United States
-## 81  0.000000e+00 0.5512027 0.5760732  United States
-## 82  0.000000e+00 0.4745211 0.4995036  United States
-## 83  0.000000e+00 0.4863655 0.5113045  United States
-## 84  0.000000e+00 0.5016325 0.5266409  United States
-## 85  0.000000e+00 0.5106890 0.5396642  United States
-## 86  0.000000e+00 0.5263521 0.5553946  United States
-## 87  0.000000e+00 0.4763829 0.5048717  United States
-## 88  0.000000e+00 0.4309741 0.4595777  United States
-## 89  0.000000e+00 0.4889316 0.5177448  United States
-## 90  0.000000e+00 0.5277064 0.5567278  United States
-## 91  0.000000e+00 0.4776225 0.5064791  United States
-## 92  0.000000e+00 0.4491827 0.4777355  United States
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce-1} 
-\begin{kframe}\begin{verbatim}
-##                BY   outcome statistic
-## 1          France choice_cj      amce
-## 2          France choice_cj      amce
-## 3          France choice_cj      amce
-## 4          France choice_cj      amce
-## 5          France choice_cj      amce
-## 6          France choice_cj      amce
-## 7          France choice_cj      amce
-## 8          France choice_cj      amce
-## 9          France choice_cj      amce
-## 10         France choice_cj      amce
-## 11         France choice_cj      amce
-## 12         France choice_cj      amce
-## 13         France choice_cj      amce
-## 14         France choice_cj      amce
-## 15         France choice_cj      amce
-## 16         France choice_cj      amce
-## 17         France choice_cj      amce
-## 18         France choice_cj      amce
-## 19         France choice_cj      amce
-## 20         France choice_cj      amce
-## 21         France choice_cj      amce
-## 22         France choice_cj      amce
-## 23         France choice_cj      amce
-## 24        Germany choice_cj      amce
-## 25        Germany choice_cj      amce
-## 26        Germany choice_cj      amce
-## 27        Germany choice_cj      amce
-## 28        Germany choice_cj      amce
-## 29        Germany choice_cj      amce
-## 30        Germany choice_cj      amce
-## 31        Germany choice_cj      amce
-## 32        Germany choice_cj      amce
-## 33        Germany choice_cj      amce
-## 34        Germany choice_cj      amce
-## 35        Germany choice_cj      amce
-## 36        Germany choice_cj      amce
-## 37        Germany choice_cj      amce
-## 38        Germany choice_cj      amce
-## 39        Germany choice_cj      amce
-## 40        Germany choice_cj      amce
-## 41        Germany choice_cj      amce
-## 42        Germany choice_cj      amce
-## 43        Germany choice_cj      amce
-## 44        Germany choice_cj      amce
-## 45        Germany choice_cj      amce
-## 46        Germany choice_cj      amce
-## 47 United Kingdom choice_cj      amce
-## 48 United Kingdom choice_cj      amce
-## 49 United Kingdom choice_cj      amce
-## 50 United Kingdom choice_cj      amce
-## 51 United Kingdom choice_cj      amce
-## 52 United Kingdom choice_cj      amce
-## 53 United Kingdom choice_cj      amce
-## 54 United Kingdom choice_cj      amce
-## 55 United Kingdom choice_cj      amce
-## 56 United Kingdom choice_cj      amce
-## 57 United Kingdom choice_cj      amce
-## 58 United Kingdom choice_cj      amce
-## 59 United Kingdom choice_cj      amce
-## 60 United Kingdom choice_cj      amce
-## 61 United Kingdom choice_cj      amce
-## 62 United Kingdom choice_cj      amce
-## 63 United Kingdom choice_cj      amce
-## 64 United Kingdom choice_cj      amce
-## 65 United Kingdom choice_cj      amce
-## 66 United Kingdom choice_cj      amce
-## 67 United Kingdom choice_cj      amce
-## 68 United Kingdom choice_cj      amce
-## 69 United Kingdom choice_cj      amce
-## 70  United States choice_cj      amce
-## 71  United States choice_cj      amce
-## 72  United States choice_cj      amce
-## 73  United States choice_cj      amce
-## 74  United States choice_cj      amce
-## 75  United States choice_cj      amce
-## 76  United States choice_cj      amce
-## 77  United States choice_cj      amce
-## 78  United States choice_cj      amce
-## 79  United States choice_cj      amce
-## 80  United States choice_cj      amce
-## 81  United States choice_cj      amce
-## 82  United States choice_cj      amce
-## 83  United States choice_cj      amce
-## 84  United States choice_cj      amce
-## 85  United States choice_cj      amce
-## 86  United States choice_cj      amce
-## 87  United States choice_cj      amce
-## 88  United States choice_cj      amce
-## 89  United States choice_cj      amce
-## 90  United States choice_cj      amce
-## 91  United States choice_cj      amce
-## 92  United States choice_cj      amce
-##                                    feature
-## 1     Costs to average household per month
-## 2     Costs to average household per month
-## 3     Costs to average household per month
-## 4     Costs to average household per month
-## 5     Costs to average household per month
-## 6                    Distribution of costs
-## 7                    Distribution of costs
-## 8                    Distribution of costs
-## 9                    Distribution of costs
-## 10       Number of participating countries
-## 11       Number of participating countries
-## 12       Number of participating countries
-## 13   Share of global emissions represented
-## 14   Share of global emissions represented
-## 15   Share of global emissions represented
-## 16 Sanctions for missing reduction targets
-## 17 Sanctions for missing reduction targets
-## 18 Sanctions for missing reduction targets
-## 19 Sanctions for missing reduction targets
-## 20                           Monitoring by
-## 21                           Monitoring by
-## 22                           Monitoring by
-## 23                           Monitoring by
-## 24    Costs to average household per month
-## 25    Costs to average household per month
-## 26    Costs to average household per month
-## 27    Costs to average household per month
-## 28    Costs to average household per month
-## 29                   Distribution of costs
-## 30                   Distribution of costs
-## 31                   Distribution of costs
-## 32                   Distribution of costs
-## 33       Number of participating countries
-## 34       Number of participating countries
-## 35       Number of participating countries
-## 36   Share of global emissions represented
-## 37   Share of global emissions represented
-## 38   Share of global emissions represented
-## 39 Sanctions for missing reduction targets
-## 40 Sanctions for missing reduction targets
-## 41 Sanctions for missing reduction targets
-## 42 Sanctions for missing reduction targets
-## 43                           Monitoring by
-## 44                           Monitoring by
-## 45                           Monitoring by
-## 46                           Monitoring by
-## 47    Costs to average household per month
-## 48    Costs to average household per month
-## 49    Costs to average household per month
-## 50    Costs to average household per month
-## 51    Costs to average household per month
-## 52                   Distribution of costs
-## 53                   Distribution of costs
-## 54                   Distribution of costs
-## 55                   Distribution of costs
-## 56       Number of participating countries
-## 57       Number of participating countries
-## 58       Number of participating countries
-## 59   Share of global emissions represented
-## 60   Share of global emissions represented
-## 61   Share of global emissions represented
-## 62 Sanctions for missing reduction targets
-## 63 Sanctions for missing reduction targets
-## 64 Sanctions for missing reduction targets
-## 65 Sanctions for missing reduction targets
-## 66                           Monitoring by
-## 67                           Monitoring by
-## 68                           Monitoring by
-## 69                           Monitoring by
-## 70    Costs to average household per month
-## 71    Costs to average household per month
-## 72    Costs to average household per month
-## 73    Costs to average household per month
-## 74    Costs to average household per month
-## 75                   Distribution of costs
-## 76                   Distribution of costs
-## 77                   Distribution of costs
-## 78                   Distribution of costs
-## 79       Number of participating countries
-## 80       Number of participating countries
-## 81       Number of participating countries
-## 82   Share of global emissions represented
-## 83   Share of global emissions represented
-## 84   Share of global emissions represented
-## 85 Sanctions for missing reduction targets
-## 86 Sanctions for missing reduction targets
-## 87 Sanctions for missing reduction targets
-## 88 Sanctions for missing reduction targets
-## 89                           Monitoring by
-## 90                           Monitoring by
-## 91                           Monitoring by
-## 92                           Monitoring by
-##                                level     estimate   std.error           z
-## 1                      \20028 per month  0.000000000          NA          NA
-## 2                      \20056 per month -0.089860961 0.002813351  -31.940905
-## 3                      \20084 per month -0.162436163 0.002934504  -55.353875
-## 4                     \200113 per month -0.261547555 0.002918526  -89.616324
-## 5                     \200141 per month -0.291645421 0.002902892 -100.467203
-## 6                          Only rich  0.000000000          NA          NA
-## 7         Prop. to current emissions  0.054200226 0.002607077   20.789650
-## 8      Prop. to history of emissions  0.038328103 0.002658713   14.416038
-## 9  Rich pay more than poor countries  0.028519774 0.002646147   10.777849
-## 10                         20 of 192  0.000000000          NA          NA
-## 11                         80 of 192  0.082106285 0.002229365   36.829446
-## 12                        160 of 192  0.136730466 0.002294899   59.580169
-## 13          40% of current emissions  0.000000000          NA          NA
-## 14          60% of current emissions  0.026854567 0.002215284   12.122401
-## 15          80% of current emissions  0.058282940 0.002221222   26.239130
-## 16                              None  0.000000000          NA          NA
-## 17               \2006 per hh and month  0.045613729 0.002581015   17.672790
-## 18              \20017 per hh and month  0.007229382 0.002610090    2.769783
-## 19              \20023 per hh and month -0.029804720 0.002632489  -11.321878
-## 20                   Your government  0.000000000          NA          NA
-## 21                 Indep. commission  0.065056568 0.002580643   25.209438
-## 22                    United Nations  0.038172745 0.002649490   14.407580
-## 23                        Greenpeace  0.004689020 0.002607562    1.798239
-## 24                     \20028 per month  0.000000000          NA          NA
-## 25                     \20056 per month -0.084977509 0.002750651  -30.893604
-## 26                     \20084 per month -0.160748210 0.002916213  -55.122247
-## 27                    \200113 per month -0.221878444 0.002925864  -75.833469
-## 28                    \200141 per month -0.294163816 0.002844194 -103.426084
-## 29                         Only rich  0.000000000          NA          NA
-## 30        Prop. to current emissions  0.057662754 0.002699207   21.362849
-## 31     Prop. to history of emissions  0.030679640 0.002714117   11.303730
-## 32 Rich pay more than poor countries  0.074927931 0.002679618   27.962166
-## 33                         20 of 192  0.000000000          NA          NA
-## 34                         80 of 192  0.107154481 0.002265078   47.307193
-## 35                        160 of 192  0.173181493 0.002384032   72.642272
-## 36          40% of current emissions  0.000000000          NA          NA
-## 37          60% of current emissions  0.026132954 0.002205416   11.849446
-## 38          80% of current emissions  0.053053884 0.002258783   23.487818
-## 39                              None  0.000000000          NA          NA
-## 40               \2006 per hh and month  0.047406399 0.002648398   17.900028
-## 41              \20017 per hh and month  0.010933985 0.002724889    4.012635
-## 42              \20023 per hh and month -0.023959166 0.002638535   -9.080480
-## 43                   Your government  0.000000000          NA          NA
-## 44                 Indep. commission  0.077729780 0.002653729   29.290775
-## 45                    United Nations  0.030758786 0.002624494   11.719893
-## 46                        Greenpeace  0.012420581 0.002770108    4.483790
-## 47                     \20028 per month  0.000000000          NA          NA
-## 48                     \20056 per month -0.110733022 0.002903505  -38.137711
-## 49                     \20084 per month -0.191782558 0.003027556  -63.345665
-## 50                    \200113 per month -0.291316540 0.003078639  -94.625104
-## 51                    \200141 per month -0.379787694 0.002882191 -131.770492
-## 52                         Only rich  0.000000000          NA          NA
-## 53        Prop. to current emissions  0.056480847 0.002812594   20.081409
-## 54     Prop. to history of emissions  0.043676581 0.002797188   15.614462
-## 55 Rich pay more than poor countries  0.045401046 0.002744631   16.541766
-## 56                         20 of 192  0.000000000          NA          NA
-## 57                         80 of 192  0.107780809 0.002389605   45.104030
-## 58                        160 of 192  0.185987301 0.002431676   76.485226
-## 59          40% of current emissions  0.000000000          NA          NA
-## 60          60% of current emissions  0.028210800 0.002319342   12.163279
-## 61          80% of current emissions  0.038497022 0.002344981   16.416773
-## 62                              None  0.000000000          NA          NA
-## 63               \2006 per hh and month  0.012309687 0.002686688    4.581734
-## 64              \20017 per hh and month -0.050191678 0.002702107  -18.575015
-## 65              \20023 per hh and month -0.068078009 0.002704177  -25.175133
-## 66                   Your government  0.000000000          NA          NA
-## 67                 Indep. commission  0.065661468 0.002759607   23.793775
-## 68                    United Nations  0.043434121 0.002756915   15.754611
-## 69                        Greenpeace -0.004138694 0.002912058   -1.421227
-## 70                     \20028 per month  0.000000000          NA          NA
-## 71                     \20056 per month -0.105444490 0.002702673  -39.014884
-## 72                     \20084 per month -0.167525238 0.002834364  -59.105046
-## 73                    \200113 per month -0.277525944 0.002803157  -99.004768
-## 74                    \200141 per month -0.359605089 0.002680793 -134.141324
-## 75                         Only rich  0.000000000          NA          NA
-## 76        Prop. to current emissions  0.091203284 0.002550920   35.753099
-## 77     Prop. to history of emissions  0.090070483 0.002543861   35.407003
-## 78 Rich pay more than poor countries  0.077781900 0.002504744   31.053829
-## 79                         20 of 192  0.000000000          NA          NA
-## 80                         80 of 192  0.076940577 0.002208008   34.846146
-## 81                        160 of 192  0.134596041 0.002248790   59.852638
-## 82          40% of current emissions  0.000000000          NA          NA
-## 83          60% of current emissions  0.011423002 0.002160677    5.286770
-## 84          80% of current emissions  0.033988555 0.002148874   15.816911
-## 85                              None  0.000000000          NA          NA
-## 86               \2006 per hh and month  0.012594565 0.002518411    5.000996
-## 87              \20017 per hh and month -0.037280077 0.002515684  -14.819060
-## 88              \20023 per hh and month -0.084672056 0.002479801  -34.144695
-## 89                   Your government  0.000000000          NA          NA
-## 90                 Indep. commission  0.043987035 0.002548830   17.257734
-## 91                    United Nations -0.005622035 0.002735205   -2.055435
-## 92                        Greenpeace -0.032025463 0.002673662  -11.978126
-##                p         lower         upper        country
-## 1             NA            NA            NA         France
-## 2  7.226159e-224 -0.0953750271 -0.0843468956         France
-## 3   0.000000e+00 -0.1681876847 -0.1566846408         France
-## 4   0.000000e+00 -0.2672677610 -0.2558273500         France
-## 5   0.000000e+00 -0.2973349846 -0.2859558578         France
-## 6             NA            NA            NA         France
-## 7   5.370116e-96  0.0490904481  0.0593100036         France
-## 8   4.102248e-47  0.0331171221  0.0435390844         France
-## 9   4.380069e-27  0.0233334208  0.0337061265         France
-## 10            NA            NA            NA         France
-## 11 6.239429e-297  0.0777368097  0.0864757606         France
-## 12  0.000000e+00  0.1322325464  0.1412283848         France
-## 13            NA            NA            NA         France
-## 14  8.036931e-34  0.0225126894  0.0311964449         France
-## 15 9.511109e-152  0.0539294246  0.0626364558         France
-## 16            NA            NA            NA         France
-## 17  6.795136e-70  0.0405550330  0.0506724242         France
-## 18  5.609365e-03  0.0021137003  0.0123450641         France
-## 19  1.022571e-29 -0.0349643037 -0.0246451365         France
-## 20            NA            NA            NA         France
-## 21 3.156501e-140  0.0599985998  0.0701145359         France
-## 22  4.636712e-47  0.0329798393  0.0433656505         France
-## 23  7.213906e-02 -0.0004217066  0.0097997474         France
-## 24            NA            NA            NA        Germany
-## 25 1.455731e-209 -0.0903686852 -0.0795863332        Germany
-## 26  0.000000e+00 -0.1664638827 -0.1550325381        Germany
-## 27  0.000000e+00 -0.2276130332 -0.2161438557        Germany
-## 28  0.000000e+00 -0.2997383334 -0.2885892990        Germany
-## 29            NA            NA            NA        Germany
-## 30 2.961840e-101  0.0523724056  0.0629531032        Germany
-## 31  1.257611e-29  0.0253600694  0.0359992110        Germany
-## 32 4.689630e-172  0.0696759757  0.0801798863        Germany
-## 33            NA            NA            NA        Germany
-## 34  0.000000e+00  0.1027150093  0.1115939518        Germany
-## 35  0.000000e+00  0.1685088765  0.1778541098        Germany
-## 36            NA            NA            NA        Germany
-## 37  2.166183e-32  0.0218104185  0.0304554892        Germany
-## 38 5.433027e-122  0.0486267509  0.0574810175        Germany
-## 39            NA            NA            NA        Germany
-## 40  1.178625e-71  0.0422156343  0.0525971638        Germany
-## 41  6.004460e-05  0.0055933013  0.0162746686        Germany
-## 42  1.080972e-19 -0.0291306001 -0.0187877321        Germany
-## 43            NA            NA            NA        Germany
-## 44 1.359389e-188  0.0725285663  0.0829309931        Germany
-## 45  1.007986e-31  0.0256148727  0.0359026987        Germany
-## 46  7.332889e-06  0.0069912698  0.0178498930        Germany
-## 47            NA            NA            NA United Kingdom
-## 48  0.000000e+00 -0.1164237867 -0.1050422575 United Kingdom
-## 49  0.000000e+00 -0.1977164589 -0.1858486569 United Kingdom
-## 50  0.000000e+00 -0.2973505613 -0.2852825180 United Kingdom
-## 51  0.000000e+00 -0.3854366842 -0.3741387041 United Kingdom
-## 52            NA            NA            NA United Kingdom
-## 53  1.073077e-89  0.0509682645  0.0619934297 United Kingdom
-## 54  5.803241e-55  0.0381941936  0.0491589676 United Kingdom
-## 55  1.835610e-61  0.0400216677  0.0507804240 United Kingdom
-## 56            NA            NA            NA United Kingdom
-## 57  0.000000e+00  0.1030972691  0.1124643479 United Kingdom
-## 58  0.000000e+00  0.1812213035  0.1907532989 United Kingdom
-## 59            NA            NA            NA United Kingdom
-## 60  4.876126e-34  0.0236649738  0.0327566260 United Kingdom
-## 61  1.450801e-60  0.0339009438  0.0430931007 United Kingdom
-## 62            NA            NA            NA United Kingdom
-## 63  4.611371e-06  0.0070438759  0.0175754978 United Kingdom
-## 64  5.119048e-77 -0.0554877102 -0.0448956456 United Kingdom
-## 65 7.501029e-140 -0.0733780984 -0.0627779202 United Kingdom
-## 66            NA            NA            NA United Kingdom
-## 67 3.874082e-125  0.0602527374  0.0710701983 United Kingdom
-## 68  6.385102e-56  0.0380306668  0.0488375744 United Kingdom
-## 69  1.552509e-01 -0.0098462235  0.0015688348 United Kingdom
-## 70            NA            NA            NA  United States
-## 71  0.000000e+00 -0.1107416331 -0.1001473479  United States
-## 72  0.000000e+00 -0.1730804906 -0.1619699863  United States
-## 73  0.000000e+00 -0.2830200319 -0.2720318569  United States
-## 74  0.000000e+00 -0.3648593460 -0.3543508315  United States
-## 75            NA            NA            NA  United States
-## 76 5.921344e-280  0.0862035730  0.0962029943  United States
-## 77 1.332257e-274  0.0850846075  0.0950563580  United States
-## 78 1.012831e-211  0.0728726920  0.0826911090  United States
-## 79            NA            NA            NA  United States
-## 80 4.870184e-266  0.0726129606  0.0812681938  United States
-## 81  0.000000e+00  0.1301884926  0.1390035893  United States
-## 82            NA            NA            NA  United States
-## 83  1.244952e-07  0.0071881530  0.0156578517  United States
-## 84  2.378815e-56  0.0297768386  0.0382002715  United States
-## 85            NA            NA            NA  United States
-## 86  5.703489e-07  0.0076585697  0.0175305610  United States
-## 87  1.103176e-49 -0.0422107276 -0.0323494261  United States
-## 88 1.602925e-255 -0.0895323769 -0.0798117349  United States
-## 89            NA            NA            NA  United States
-## 90  9.787681e-67  0.0389914198  0.0489826509  United States
-## 91  3.983702e-02 -0.0109829381 -0.0002611325  United States
-## 92  4.626637e-33 -0.0372657443 -0.0267851811  United States
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
+\subsection{Nested Model Comparison}
 
@@
 ## 
-## Model 1: choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + 
-##     sanctions_cj + monitoring_cj
-## Model 2: choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + 
-##     sanctions_cj + monitoring_cj + country + cost_cj:country + 
-##     distrib_cj:country + ctries_cj:country + emissions_cj:country + 
-##     sanctions_cj:country + monitoring_cj:country
+## Model 1: ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + 
+##     Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + 
+##     Education:Job + CountryOfOrigin:ReasonForApplication
+## Model 2: ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + 
+##     Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + 
+##     ethnocentrism_split + Education:Job + CountryOfOrigin:ReasonForApplication + 
+##     Gender:ethnocentrism_split + Education:ethnocentrism_split + 
+##     LanguageSkills:ethnocentrism_split + CountryOfOrigin:ethnocentrism_split + 
+##     Job:ethnocentrism_split + JobExperience:ethnocentrism_split + 
+##     JobPlans:ethnocentrism_split + ReasonForApplication:ethnocentrism_split + 
+##     PriorEntry:ethnocentrism_split + Education:Job:ethnocentrism_split + 
+##     CountryOfOrigin:ReasonForApplication:ethnocentrism_split
 ##   Resid. Df Resid. Dev Df Deviance     F Pr(>F)
-## 1     67982      15601                                 
-## 2     67928      15555 54   45.983 3.7187 < 2.2e-16 ***
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+## 1     11402     2500.7                         
+## 2     11304     2475.8 98   24.834 1.157 0.1384
 \end{verbatim}
 \end{kframe}
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce_environmentalism-1}
-
-\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce_environmentalism-2}
-
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bechtel_reciprocity_reference-1}
-
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce_reciprocity-1}
-
-\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce_reciprocity-2}
-
 \end{knitrout}
@@
 
-\subsection{Comparison of Alternative Reference Categories for Teele et al. (2018) Candidate Experiment}
+\subsection{Nested Model Comparison: Male/Female Voters}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## Analysis of Deviance Table
+## 
+## Model 1: winner ~ feature_sex + feature_experience + feature_marital + 
+##     feature_job + feature_children + feature_age
+## Model 2: winner ~ feature_sex + feature_experience + feature_marital + 
+##     feature_job + feature_children + feature_age + Sex + feature_sex:Sex + 
+##     feature_experience:Sex + feature_marital:Sex + feature_job:Sex + 
+##     feature_children:Sex + feature_age:Sex
+##   Resid. Df Resid. Dev Df Deviance      F Pr(>F)
+## 1     12436     2997.2                          
+## 2     12422     2992.2 14   5.0738 1.5046 0.1002
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\subsection{Nested Model Comparison: Democratic/Republican Voters}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## Analysis of Deviance Table
+## 
+## Model 1: winner ~ feature_sex + feature_experience + feature_marital + 
+##     feature_job + feature_children + feature_age
+## Model 2: winner ~ feature_sex + feature_experience + feature_marital + 
+##     feature_job + feature_children + feature_age + PartyID + 
+##     feature_sex:PartyID + feature_experience:PartyID + feature_marital:PartyID + 
+##     feature_job:PartyID + feature_children:PartyID + feature_age:PartyID
+##   Resid. Df Resid. Dev Df Deviance      F    Pr(>F)    
+## 1      9776     2352.8                                 
+## 2      9762     2342.9 14   9.8697 2.9373 0.0001739 ***
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\clearpage
+
+\subsection{Comparison of Alternative Reference Categories}
 
@@
 \includegraphics[width=\maxwidth]{figure/tkr_subgroup_example_plot-1}
+
+\end{knitrout}
+
+\clearpage
+
+\section{Bechtel and Scheve (2013) Climate Agreement Experiment}
+
+\subsection{Replication using AMCEs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_amce-1}
+
+\end{knitrout}
+
+\clearpage
+
+\clearpage
+
+\subsection{Replication using MMs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_mm-1}
+
+\end{knitrout}
+
+\clearpage
+
+\clearpage
+
+\subsection{Subgroup Analysis using AMCEs: Country}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce-1}
+
+\end{knitrout}
+
+\clearpage
+
+\clearpage
+
+\subsection{Subgroup Analysis using MMs: Country}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_mm-1}
+
+\end{knitrout}
+
+\clearpage
+
+\clearpage
+
+\subsection{Subgroup Analysis using AMCEs: Environmentalism}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce_environmentalism-1}
+
+\end{knitrout}
+
+\clearpage
+
+\clearpage
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_mm_environmentalism-1}
+
+\end{knitrout}
+
+\clearpage
+
+\clearpage
+
+\subsection{Subgroup Analysis using AMCEs: Reciprocity}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_amce_reciprocity-1}
+
+\end{knitrout}
+
+\clearpage
+
+\clearpage
+
+\subsection{Subgroup Analysis using MMs: Reciprocity}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_mm_reciprocity-1}
+
+\end{knitrout}
+
+\clearpage
+
+\clearpage
+
+\subsection{Nested Model Comparison: Country}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## Analysis of Deviance Table
+## 
+## Model 1: choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + 
+##     sanctions_cj + monitoring_cj
+## Model 2: choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + 
+##     sanctions_cj + monitoring_cj + country + cost_cj:country + 
+##     distrib_cj:country + ctries_cj:country + emissions_cj:country + 
+##     sanctions_cj:country + monitoring_cj:country
+##   Resid. Df Resid. Dev Df Deviance      F    Pr(>F)    
+## 1     67982      15601                                 
+## 2     67928      15555 54   45.983 3.7187 < 2.2e-16 ***
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\subsection{Nested Model Comparison: Environmentalism}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## Analysis of Deviance Table
+## 
+## Model 1: choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + 
+##     sanctions_cj + monitoring_cj
+## Model 2: choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + 
+##     sanctions_cj + monitoring_cj + environmentalism + cost_cj:environmentalism + 
+##     distrib_cj:environmentalism + ctries_cj:environmentalism + 
+##     emissions_cj:environmentalism + sanctions_cj:environmentalism + 
+##     monitoring_cj:environmentalism
+##   Resid. Df Resid. Dev Df Deviance      F    Pr(>F)    
+## 1     67974      15599                                 
+## 2     67956      15491 18   107.83 26.279 < 2.2e-16 ***
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\clearpage
+
+\subsection{Nested Model Comparison: Reciprocity}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## Analysis of Deviance Table
+## 
+## Model 1: choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + 
+##     sanctions_cj + monitoring_cj
+## Model 2: choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + 
+##     sanctions_cj + monitoring_cj + reciprocity + cost_cj:reciprocity + 
+##     distrib_cj:reciprocity + ctries_cj:reciprocity + emissions_cj:reciprocity + 
+##     sanctions_cj:reciprocity + monitoring_cj:reciprocity
+##   Resid. Df Resid. Dev Df Deviance      F    Pr(>F)    
+## 1     67982      15601                                 
+## 2     67964      15570 18   30.831 7.4767 < 2.2e-16 ***
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\clearpage
+
+\subsection{Comparison of Alternative Reference Categories}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/bechtel_reciprocity_reference-1}
 
@@
 ## [31] readxl_1.3.1      foreign_0.8-71    magrittr_1.5     
-## [34] splines_3.5.3     scales_1.0.0      assertthat_0.2.1 
-## [37] xtable_1.8-3      colorspace_1.4-1  sandwich_2.5-1   
-## [40] survey_3.35-1     stringi_1.4.3     lazyeval_0.2.2   
-## [43] munsell_0.5.0     crayon_1.3.4      zoo_1.8-5
+## [34] codetools_0.2-16  splines_3.5.3     scales_1.0.0     
+## [37] assertthat_0.2.1  xtable_1.8-3      colorspace_1.4-1 
+## [40] sandwich_2.5-1    survey_3.35-1     stringi_1.4.3    
+## [43] lazyeval_0.2.2    munsell_0.5.0     crayon_1.3.4     
+## [46] zoo_1.8-5
 \end{verbatim}

### 2019-04-14 manuscript.Rnw
work on final section; more figure and appendix edits

@@
 <<knitr_options, cache=FALSE, echo=FALSE, results="hide">>=
-knitr::opts_chunk$set(cache = TRUE, echo=FALSE, results="hold", warning=FALSE, error=FALSE)
+knitr::opts_chunk$set(cache = TRUE, echo=FALSE, results="hold", warning=FALSE, error=FALSE, message=FALSE)
 options(scipen = 10)
@@
 \clearpage
+\doublespacing
 
@@
 
-We can also see this bias in a reanalysis of \citeauthor{BechtelScheve2013}'s four-country climate change agreement experiment.
+Visual or numerical similarity of subgroup AMCEs is therefore an analytical artefact, not an accurate statement of the similarity of patterns of preferences.
+We can see this bias in a reanalysis of \citeauthor{BechtelScheve2013}'s four-country climate change agreement experiment.
 Figure \ref{fig:bechtel_difference_comparison} shows an analysis for the feature capturing the monthly household cost for a potential international climate agreement.
-This replicates a portion of their results which compare high- and low-environmentalism respondents pooled across countries (\citet[13767 figure 4]{BechtelScheve2013}.
+This replicates a portion of their results which compare high- and low-environmentalism respondents pooled across countries \citep[13767 figure 4]{BechtelScheve2013}.
 The original analysis has conditional AMCEs for the two subgroups with 28 Euro per month as the reference category.
@@
 \section*{Improved Subgroup Analyses in Conjoint Designs}\label{sec:marginalmeans}
+
+Researchers and consumers of conjoints can avoid the inferential errors that accompany conditional AMCEs by focusing attention on (subgroup) marginal means, differences between subgroup marginal means to infer subgroup differences in preferences toward particular features, and omnibus nested model comparisons to infer subgroup differences across many features.
+To demonstrate each of these three techniques we provide a complete example based upon \citeauthor{HainmuellerHopkinsYamamoto2014}'s analysis of their immigration conjoint by respondent enthnocentrism, which finds that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' \citep[22]{HainmuellerHopkinsYamamoto2014}.
+First, we show how different reference categories could have led to distinctly different conditional AMCEs and, therefore, interpretations of subgroup preference similarity.
+Second, we show how differences in marginal means clearly convey the similarity of these two subgroups without any sensitivity to reference category.
+Finally, we show how tested model comparisons would have provided \citeauthor{HainmuellerHopkinsYamamoto2014} with a statistic test of the claimed similarity in levels of support between these two respondent subgroups.
 
@@
 
-<<hainmueller_subgroup_example_plot, dependson=c("data_hainmueller_immigration", "hainmueller_subgroup_example"), fig.width=8, fig.height=12, fig.cap="Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Hainmueller et al.
+<<hainmueller_subgroup_example_plot, dependson=c("data_hainmueller_immigration", "hainmueller_subgroup_example"), fig.width=8, fig.height=6, fig.cap="Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Hainmueller et al.
 (2014) Immigration Experiment", message=FALSE>>=
-plot(amce_ref_example_merged, group = "ethnocentrism_split", feature_headers = FALSE, legend_title = "Ethnocentrism", vline = 0) + 
-  scale_colour_manual("Ethnocentrism", limits = c("high", "low"), values = c("Red", "Blue")) +
-  facet_grid(rows = vars(feature), cols = vars(dataset), scales = "free_y", space = "free_y", labeller = function(x) label_value(x, multi_line = FALSE)) +
-  theme(strip.text.x = element_text(size = 8),
-        strip.text.y = element_text(size = 5))
-@
-
-Researchers and consumers of conjoints can avoid the inferential errors that accompany conditional AMCEs by focusing attention on (subgroup) marginal means, differences between subgroup marginal means to infer subgroup differences in preferences toward particular features, and omnibus nested model comparisons to infer subgroup differences across many features.
-To demonstrate each of these three techniques
-
-Here we provide a more complete example, demonstrating the full extent of this problem for interpretation of conjoint results and present alternative forms of analysis that more robustly convey subgroup preferences and the differences (if any) between them.
-Specifically, we show how reference category changes can lead to visual patterns of differences-in-AMCEs that provide strikingly different interpretations.
-We then show how to visualize and formally compare subgroup marginal means using simple means comparisons tests to avoid this problem.
-Finally, we demonstrate how to use nested model comparison tests to formally test for omnibus differences between groups.
-
-Consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which show the exact same analysis (comparing AMCEs for high and low ethnocentrism respondents) on the same experimental data from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment.
-In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in preferences between the two subgroups.
-In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.\footnote{The appendix contains comparable plots for experiments by \citet{BechtelScheve2013} and \citet{TeeleKallaRosenbluth2018}.}
-
-Panel A gives the impression that there are significant differences in preferences between high and low ethnocentrism respondents toward immigrants from different countries of origin, with different careers, and with different educational attainments.
-By contrast, Panel B gives the impression that these differences --- indeed all differences --- are negligible.
-The experimental data and analytic approach in the two portrayals is identical; the only difference is the choice of reference category for the profile features.
+plot(
+  subset(
+    amce_ref_example_merged,
+    feature %in% c("Education", "CountryOfOrigin", "Job")
+  ),
+  group = "ethnocentrism_split", 
+  feature_headers = FALSE, 
+  legend_title = "Ethnocentrism", 
+  vline = 0
+) + 
+  scale_colour_manual(
+    "Ethnocentrism", limits = c("high", "low"), values = c("Red", "Blue")
+  ) +
+  facet_grid(
+    rows = vars(feature), 
+    cols = vars(dataset), 
+    scales = "free_y", 
+    space = "free_y", 
+    labeller = function(x) label_value(x, multi_line = FALSE)
+  ) +
+  theme(
+    strip.background = element_rect(fill="white", colour="white"),
+    strip.text.x = element_text(size = 8),
+    strip.text.y = element_blank()
+  )
+@
+
+To begin, consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which shows estimated subgroup AMCEs for three features from the immigration study.
+In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in levels of support between the two subgroups.
+In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.
+
+Panel A gives the impression that there are significant differences in preferences between high and low ethnocentrism respondents toward immigrants from different countries of origin, with different careers, and with different educational attainments because the reference category choice cascades the difference in reference category favorability into AMCEs for all other feature levels.
+By contrast, Panel B gives the impression that these differences are negligible.
+The experimental data and analytic approach in the two portrayals is identical; the only difference is the choice of reference category.
 Given what we have shown about the relationship between differences in conditional AMCEs and differences in conditional marginal means, Panel B is the more truthful visualization \citep{Cairo2016}.
 The differences between subgroup AMCEs there more accurately convey differences in underlying preferences because the reference categories used in Panel B are the most similar between the two groups.
-Yet even this may not \textit{perfectly} convey differences because no feature generates perfect agreement between the subgroups.
-
-<<hainmueller_mm_diffs, dependson=c("data_hainmueller_immigration"), fig.height = 14, fig.width=10, fig.cap="Differences in Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment", message=FALSE>>=
-mm_by_ethnocentrism <- cj(subset(hainmueller_immigration, !is.na(ethnocentrism_split)),
+
+<<hainmueller_mm_diffs, dependson=c("data_hainmueller_immigration"), fig.height = 5, fig.width=8, fig.cap="Differences in Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment", message=FALSE>>=
+mm_by_ethnocentrism <- cj(
+  subset(hainmueller_immigration, !is.na(ethnocentrism_split)),
   ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
@@
   estimate = "mm_diff",
-                          by = ~ ethnocentrism_split)
-plot(mm_by_ethnocentrism, vline = 0, xlim = c(-0.3,0.3), xlab = "Estimated Difference in Marginal Means") +
+  by = ~ ethnocentrism_split
+)
+plot(
+  subset(
+    mm_by_ethnocentrism,
+    feature %in% c("Country of Origin", "Job", "Education")
+  ), 
+  vline = 0, 
+  xlim = c(-0.3,0.3), 
+  xlab = "Estimated Difference in Marginal Means"
+) +
   scale_colour_manual("feature", values = rep("Black", 9)) +
@@
 
-Alternatively presenting subgroup differences using conditional marginal means (as in Figure \ref{fig:hainmueller_mm_diffs}) provides the intended descriptive comparison of subgroup preferences.
-Each dot and error bar represents the conditional marginal mean (and its standard error) for high ethnocentrism (in red) and low ethnocentrism (in blue) respondents.
-This display of conditional marginal means highlights just how similar the preferences are for the two groups.
-For example, in the first set of estimates, both groups of respondents display minimally positive preferences toward female immigrants and minimally negative preferences toward male immigrants, averaging across those immigrants' other profile features.
-The second set of estimates shows both group are also more favorable toward higher-educated immigrants and less favorable toward less-education immigrants with no visually apparent differences.
-The third set of estimates, related to language skills, shows again similar patterns: both groups are more favorable toward immigrants with higher English proficiency than immigrants with lower English proficiency.
-
-These estimates are less obviously identical for the two groups but look quite close.
-To test for pairwise differences between high and low ethnocentrism respondents, we can calculate differences in conditional conditional marginal means at each feature level, with associated significance tests:
-
-\begin{itemize}
-<<hainmueller_mmdiffs_by_ethnocentrism, dependson=c("data_hainmueller_immigration"), results="asis">>=
-mmdiffs_by_ethnocentrism <- cj(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry, id = ~ CaseID, estimate = "mm_diff", by = ~ ethnocentrism_split)
-mmd <- mmdiffs_by_ethnocentrism[mmdiffs_by_ethnocentrism$feature == "Language Skills", c("level", "estimate", "std.error", "z", "p")]
-cat(sprintf("\\item %s: %0.2f (%0.2f, $z_{\\text{diff}}$=%0.2f, $p\\leq %0.2f$)\n", mmd[[1]][1], mmd[[2]][1], mmd[[3]][1], mmd[[4]][1], mmd[[5]][1]))
-cat(sprintf("\\item %s: %0.2f (%0.2f, $z_{\\text{diff}}$=%0.2f, $p\\leq %0.2f$)\n", mmd[[1]][2], mmd[[2]][2], mmd[[3]][2], mmd[[4]][2], mmd[[5]][2]))
-cat(sprintf("\\item %s: %0.2f (%0.2f, $z_{\\text{diff}}$=%0.2f, $p\\leq %0.2f$)\n", mmd[[1]][3], mmd[[2]][3], mmd[[3]][3], mmd[[4]][3], mmd[[5]][3]))
-cat(sprintf("\\item %s: %0.2f (%0.2f, $z_{\\text{diff}}$=%0.2f, $p\\leq %0.2f$)\n", mmd[[1]][4], mmd[[2]][4], mmd[[3]][4], mmd[[4]][4], mmd[[5]][4]))	
-@
-\end{itemize}
-
-<<hainmueller_language_diffs, dependson=c("data_hainmueller_immigration"), eval=TRUE, echo=FALSE>>=
-hainmueller_anova_language <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ LanguageSkills, id = ~ CaseID, by = ~ ethnocentrism_split)
-@
-
-\noindent These pairwise tests show that are our eyes have not deceived us.
-None of the level-specific differences in conditional marginal means are statistically distinguishable from zero.
-Were we interested in an omnibus tests of whether any of these differences were non-zero, we could perform a nested model comparison of two equations: (a) one estimating only marginal effects of the ``Language Skills'' feature levels, and (b) the same model with additional interactions between the subgrouping covariate and the feature levels.
-The test compares the sum of squared residuals for the two equations.
+Next, making a comparison of levels of favorability toward different types of immigrants without using AMCEs would have been even more truthful.
+Figure \ref{fig:hainmueller_mm_diffs} \textit{directly} shows that comparison of preferences as differences in subgroup marginal means between the two groups for these three features, with 95\% confidence intervals for the difference.\footnote{A presentation of subgroup marginal means for all features can be found in Appendix \ref{app:hainmuellerimmigration}.} The two groups indeed have similar preferences, something that would have happened to be clear had the conditional AMCEs in the right panel of Figure \ref{fig:hainmueller_subgroup_example_plot} been presented but that would have been far less obvious were the conditional AMCEs in the left panel of that figure presented.
+Pairwise difference in means tests would provide formal procedures for testing the statistical significance of these differences.
+
+Yet, finally, the similarity of subgroup preferences in conjoints is often characterized in an \textit{omnibus} fashion, as in the quote from \citet{HainmuellerHopkinsYamamoto2014} describing ``patterns of support.'' An appropriate test in such cases is one that evaluates whether a model of support that accounts for group differences better fits the data than a model of support with only conjoint features as predictors.
+This type of test is known as a ``nested model comparison'' which compares the fit of a ``restricted'' regression (the restriction being that interactions between features and a subgroup identifier are held to be zero) nested within an ``unrestricted'' regression that allows for arbitrary interactions between conjoint features and the subgroup identifier.
+Formally, a nested model comparison provides an F-test of the null hypothesis that all interaction terms are equal to zero.\footnote{Like any ANOVA this hypothesis test may yield substantively different insight from a series of tests of pairwise mean differences.
+Figure \ref{fig:hainmueller_mm_diffs} shows three instances where the confidence intervals for pairwise differences in marginal means do not include zero even though the omnibus test fails to reject the null.}
 
@@
 \noindent While Equation \ref{eq:restricted} imposes the constraint that $\beta_4 = \beta_5 = \beta_6 = \beta_7 = 0$, Equation \ref{eq:unrestricted} allows for subgroup differences in favorability.
-The nested model comparison allows us to test the joint null hypothesis that there are no differences between the subgroups in any of the feature levels.
-This entails computing an F-statistic:
+Testing this null entails computing an F-statistic comparing the fit of each equation:
 
@@
 
-\noindent where $SSR_{Restricted}$ is the sum of squared residuals for Equation \ref{eq:restricted}, $SSR_{Unrestricted}$ is the sum of squared residuals for Equation \ref{eq:unrestricted}, where $r$ is the number of restrictions (in the above example, 4), $n$ is the number of cases, and $k$ is the number of feature levels in the unrestricted model.
-Note that this test is not sensitive to reference category used in the regression
+\noindent where $SSR_{Restricted}$ is the sum of squared residuals for Equation \ref{eq:restricted}, $SSR_{Unrestricted}$ is the sum of squared residuals for Equation \ref{eq:unrestricted}, where $r$ is the number of restrictions (in the above example, 4), $n$ is the number of cases, and $k$ is the number of feature levels in the unrestricted model.\footnote{Note that this test is not sensitive to reference category even though it requires specifying a regression equation.}
+
+<<hainmueller_language_diffs, dependson=c("data_hainmueller_immigration"), eval=TRUE, echo=FALSE>>=
+hainmueller_anova_language <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ LanguageSkills, id = ~ CaseID, by = ~ ethnocentrism_split)
+@
 
@@
 Df"]][1], hainmueller_anova_all$F[2], hainmueller_anova_all$"Pr(>F)"[2])}, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.
-By contrast, \citet{BechtelScheve2013} argue in their cross-country conjoint examining climate change agreements ``that individuals in all four countries largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}.
-Yet a nested model comparisons shows the countries do differ in their preferences \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country$Df[2], bechtel_anova_country[["Resid.
-Df"]][1], bechtel_anova_country$F[2], bechtel_anova_country$"Pr(>F)"[2])}.
-This cross-country variation is largely driven by differences in sensitivity to monthly household costs feature, \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country_cost$Df[2], bechtel_anova_country_cost[["Resid.
-Df"]][1], bechtel_anova_country_cost$F[2], bechtel_anova_country_cost$"Pr(>F)"[2])}, with the United Kingdom and United States being more cost sensitive than Germany and France as is plainly visible in a plot of marginal means by country (see SI).
 
@@
 For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9).
-Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to an quite different conclusion.
+Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to a quite different conclusion.
+As an example, \citet{BechtelScheve2013} argue that their conjoint results show ``individuals in all four countries largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}, but a nested model comparison shows the countries do differ in their preferences \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country$Df[2], bechtel_anova_country[["Resid.
+Df"]][1], bechtel_anova_country$F[2], bechtel_anova_country$"Pr(>F)"[2])}.
+This cross-country variation largely driven by differences in sensitivity to monthly household costs feature, \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country_cost$Df[2], bechtel_anova_country_cost[["Resid.
+Df"]][1], bechtel_anova_country_cost$F[2], bechtel_anova_country_cost$"Pr(>F)"[2])}, with the United Kingdom and United States being more cost sensitive than Germany and France.
+Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences, but ulimately there is no guarantee that they do in any particular analysis.
 
@@
 We suggest that conjoint analyses should report not only average marginal component effects (AMCEs) but also descriptive quantities that better convey underlying preferences over profile features and better convey subgroup differences in those preferences.
-Our intention here is not to substantively undermine any previous set of results, but instead to urge researchers moving forward to demonstrate considerable caution in how they design, analyze, and present the results of these types of descriptive experiments.
+Marginal means contain all of the information provided by AMCEs and more.
+Consequently, our intention here is not to substantively undermine any previous set of results, but instead to urge researchers moving forward to demonstrate considerable caution in how they design, analyze, and present the results of these types of descriptive experiments.
 We have relatively straightforward and hopefully uncontroversial advice for how analysts of conjoint experiments should proceed:
@@
 
-\item When descriptively characterizing differences in preferences between subgroups, directly estimate the subgroup difference using conditional marginal means and differences between conditional marginal means, rather than relying on the difference-in-AMCEs.
+\item When descriptively characterizing differences in preference level between subgroups, directly estimate the subgroup difference using conditional marginal means and differences between conditional marginal means, rather than relying on the difference-in-AMCEs.
 
@@
 
-To facilitate such analysis and, especially, to provide easy-to-use tools for calculating marginal means and performing reference category selection diagnostics, we provide software called \textbf{cregg} \citep{Leeper2018cregg} that will perform these analyses and also provides the simple-to-use visualization tools used throughout this article.
+To facilitate such analysis and, especially, to provide easy-to-use tools for calculating marginal means and performing reference category selection diagnostics, we provide software called \textbf{cregg} \citep{Leeper2018cregg} available from the Comprehensive R Archive Network; this manuscript is written as a reproducible knitr document \citep{Xie2015} that contains complete code examples that will perform all analyses and visualization used throughout this article.
 With that resource in-hand, researchers should be well-equipped to analyze conjoint designs without running into the analytic challenges discussed here.
@@
 
-\section{Hainmueller et al. (2014) Candidate Experiment}
-
-\subsection{Replication using AMCEs}
+\section{Hainmueller et al. (2014) Candidate Experiment}\label{app:hainmuellercandidate}
+
+\subsection{Replication using AMCEs and MMs}
 
 <<hainmueller_candidate_amce_appendix, dependson=c("data_hainmueller_candidate"), fig.height=8, fig.width=8>>=
-plot(
-  cj(
+p1 <- plot(
+  cregg::cj(
    hainmueller_candidate, 
@@
    estimate = "amce"
-  )
-)
-@
-
-\clearpage
+  ), vline = 0
+) + 
+  ggplot2::scale_x_continuous(
+    limits = c(-0.4, 0.4), 
+    breaks = c(-0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4)
+  ) + 
+  ggplot2::geom_text(
+    aes(label = ifelse(is.na(std.error), "", sprintf("%0.2f (%0.2f)", estimate, std.error))),
+    colour = "black", 
+    size = 2,
+    position = position_nudge(y = .5)
+ ) + 
+ theme(legend.position="none")
+p2 <- plot(
+  cregg::cj(
+   hainmueller_candidate, 
+   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
+   id = ~ resID,
+   estimate = "mm"
+  ), vline = 0.5
+) + 
+  ggplot2::scale_x_continuous(
+    limits = c(0.1, 0.9), 
+    breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
+  ) + 
+  ggplot2::geom_text(
+    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
+    colour = "black", 
+    size = 2,
+    position = position_nudge(y = .5)
+  ) + 
+  theme(legend.position="none")
+gridExtra::grid.arrange(p1, p2, ncol=2)
+@
+
+\clearpage
+
+\subsection{Numerical Results: AMCEs}
 
@@
 
-\subsection{Replication using MMs}
-
-<<hainmueller_candidate_mm_appendix, dependson=c("data_hainmueller_candidate"), fig.height=8, fig.width=8>>=
-plot(
-  cj(
-   hainmueller_candidate, 
-   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
-   id = ~ resID,
-   estimate = "mm",
-   h0 = 0.5
-  ), vline = 0.5
-)
-@
-
-\clearpage
+\subsection{Numerical Results: MMs}
 
@@
 
-\section{Hainmueller et al. (2014) Immigration Experiment}
-
-\subsection{Replication using AMCEs}
+\section{Hainmueller et al. (2014) Immigration Experiment}\label{app:hainmuellerimmigration}
+
+\subsection{Replication using AMCEs and MMs}
 
 <<hainmueller_immigration_amce_appendix, dependson=c("data_hainmueller_immigration"), fig.height=8, fig.width=8>>=
-plot(
-  cj(
+p1 <- plot(
+  cregg::cj(
      hainmueller_immigration, 
@@
      id = ~ CaseID
-  )
-)
+  ), vline = 0
+) + 
+  ggplot2::scale_x_continuous(
+    limits = c(-0.4, 0.4), 
+    breaks = c(-0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4)
+  ) + 
+  ggplot2::geom_text(
+    aes(label = ifelse(is.na(std.error), "", sprintf("%0.2f (%0.2f)", estimate, std.error))),
+    colour = "black", 
+    size = 2,
+    position = position_nudge(y = .5)
+ ) + 
+ theme(legend.position="none")
+p2 <- plot(
+  cregg::cj(
+     hainmueller_immigration, 
+     ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
+     id = ~ CaseID,
+     estimate = "mm"
+  ), vline = 0.5
+) + 
+  ggplot2::scale_x_continuous(
+    limits = c(0.1, 0.9), 
+    breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
+  ) + 
+  ggplot2::geom_text(
+    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
+    colour = "black", 
+    size = 2,
+    position = position_nudge(y = .5)
+  ) + 
+  theme(legend.position="none")
+#gridExtra::grid.arrange(p1, p2, ncol=2)
+p1
+p2
 @
@@
 
+\subsection{Numerical Results: AMCEs}
+
 <<hainmueller_amce_table, dependson=c("data_hainmueller_immigration"), results="asis">>=
@@
     digits = 2, align = c("l", "l", "p{3in}", "r", "r", "r")
-), include.rownames = FALSE, size = "footnotesize")
-@
-
-\clearpage
-
-\subsection{Replication using MMs}
-
-<<hainmueller_immigration_mm_appendix, dependson=c("data_hainmueller_immigration"), fig.height=8, fig.width=8>>=
-plot(
-  cj(
-   hainmueller_immigration, 
-   ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication,
-   id = ~ CaseID,
-   estimate = "mm",
-   h0 = 0.5
-  ), vline = 0.5
-)
-@
-
-\clearpage
+), include.rownames = FALSE, size = "scriptsize")
+@
+
+\clearpage
+
+\subsection{Numerical Results: MMs}
 
@@
     digits = 2, align = c("l", "l", "p{3in}", "r", "r", "r")
-), include.rownames = FALSE, size = "footnotesize")
+), include.rownames = FALSE, size = "scriptsize")
 @
@@
 
-\section{Teele et al. (2018) Candidate Experiment}
-
-\subsection{Replication using AMCEs}
+\section{Teele et al. (2018) Candidate Experiment}\label{app:tkr}
+
+\subsection{Replication using AMCEs and MMs}
 
 <<tkr_amce_appendix, dependson=c("data_tkr"), fig.height=5, fig.width=8>>=
-plot(
-  cj(
+p1 <- plot(
+  cregg::cj(
      tkr, 
@@
      estimate = "amce"
-  ),
-)
-@
-
-\clearpage
+  ), vline = 0
+) + 
+  ggplot2::scale_x_continuous(
+    limits = c(-0.3, 0.3), 
+    breaks = c(-0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3)
+  ) + 
+  ggplot2::geom_text(
+    aes(label = ifelse(is.na(std.error), "", sprintf("%0.2f (%0.2f)", estimate, std.error))),
+    colour = "black", 
+    size = 2,
+    position = position_nudge(y = .5)
+ ) + 
+ theme(legend.position="none")
+p2 <- plot(
+  cregg::cj(
+     tkr, 
+     winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
+     id = ~ responseid,
+     estimate = "mm",
+     h0 = 0.5
+  ), vline = 0.5
+) + 
+  ggplot2::scale_x_continuous(
+    limits = c(0.2, 0.8), 
+    breaks = c(0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8)
+  ) + 
+  ggplot2::geom_text(
+    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
+    colour = "black", 
+    size = 2,
+    position = position_nudge(y = .5)
+  ) + 
+  theme(legend.position="none")
+gridExtra::grid.arrange(p1, p2, ncol=2)
+@
+
+\clearpage
+
+\subsection{Numerical Results: AMCEs}
 
@@
 
-\subsection{Replication using MMs}
-
-<<tkr_mm_appendix, dependson=c("data_tkr"), fig.height=5, fig.width=8>>=
-plot(
-  cj(
-   tkr, 
-   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
-   id = ~ responseid,
-   estimate = "mm",
-   h0 = 0.5
-  ), vline = 0.5
-)
-@
-
-\clearpage
+\subsection{Numerical Results: MMs}
 
@@
 
-\section{Bechtel and Scheve (2013) Climate Agreement Experiment}
-
-\subsection{Replication using AMCEs}
-
-<<bechtel_amce, dependson=c("data_bechtel")>>=
-plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "amce"))
-@
-
-\clearpage
+\section{Bechtel and Scheve (2013) Climate Agreement Experiment}\label{app:bechtel}
+
+\subsection{Replication using AMCEs and MMs}
+
+<<bechtel_amce, dependson=c("data_bechtel"), fig.height=8, fig.width=7>>=
+p1 <- plot(
+  cregg::cj(
+     bechtel, 
+     choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj,
+     weights = ~ weight,
+     id = ~ ID,
+     estimate = "amce"
+  ), vline = 0
+) + 
+  ggplot2::scale_x_continuous(
+    limits = c(-0.4, 0.4), 
+    breaks = c(-0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4)
+  ) + 
+  ggplot2::geom_text(
+    aes(label = ifelse(is.na(std.error), "", sprintf("%0.2f (%0.2f)", estimate, std.error))),
+    colour = "black", 
+    size = 2,
+    position = position_nudge(y = .5)
+ ) + 
+ theme(legend.position="none")
+p2 <- plot(
+  cregg::cj(
+     bechtel, 
+     choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj,
+     weights = ~ weight,
+     id = ~ ID,
+     estimate = "mm",
+     h0 = 0.5
+  ), vline = 0.5
+) + 
+  ggplot2::scale_x_continuous(
+    limits = c(0.1, 0.9), 
+    breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
+  ) + 
+  ggplot2::geom_text(
+    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
+    colour = "black", 
+    size = 2,
+    position = position_nudge(y = .5)
+  ) + 
+  theme(legend.position="none")
+gridExtra::grid.arrange(p1, p2, ncol=1, nrow=2)
+@
+
+\clearpage
+
+\subsection{Numerical Results: AMCEs}
 
@@
 
-\subsection{Replication using MMs}
-
-<<bechtel_mm, dependson=c("data_bechtel")>>=
-plot(cj(bechtel, choice_cj ~ cost_cj + distrib_cj + ctries_cj + emissions_cj + sanctions_cj + monitoring_cj, weights = ~ weight, id = ~ ID, estimate = "mm"), vline = 0.5)
-@
-
-\clearpage
+\subsection{Numerical Results: MMs}
 

### 2019-04-14 manuscript.tex
work on final section; more figure and appendix edits

@@
 
+Researchers and consumers of conjoints can avoid the inferential errors that accompany conditional AMCEs by focusing attention on (subgroup) marginal means, differences between subgroup marginal means to infer subgroup differences in preferences toward particular features, and omnibus nested model comparisons to infer subgroup differences across many features.
+To demonstrate each of these three techniques we provide a complete example based upon \citeauthor{HainmuellerHopkinsYamamoto2014}'s analysis of their immigration conjoint by respondent enthnocentrism, which finds that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' \citep[22]{HainmuellerHopkinsYamamoto2014}.
+First, we show how different reference categories could have led to distinctly different conditional AMCEs and, therefore, interpretations of subgroup preference similarity.
+Second, we show how differences in marginal means clearly convey the similarity of these two subgroups without any sensitivity to reference category.
+Finally, we show how tested model comparisons would have provided \citeauthor{HainmuellerHopkinsYamamoto2014} with a statistic test of the claimed similarity in levels of support between these two respondent subgroups.
+
 \begin{knitrout}
@@
 
-Researchers and consumers of conjoints can avoid the inferential errors that accompany conditional AMCEs by focusing attention on (subgroup) marginal means, differences between subgroup marginal means to infer subgroup differences in preferences toward particular features, and omnibus nested model comparisons to infer subgroup differences across many features.
-To demonstrate each of these three techniques
-
-Here we provide a more complete example, demonstrating the full extent of this problem for interpretation of conjoint results and present alternative forms of analysis that more robustly convey subgroup preferences and the differences (if any) between them.
-Specifically, we show how reference category changes can lead to visual patterns of differences-in-AMCEs that provide strikingly different interpretations.
-We then show how to visualize and formally compare subgroup marginal means using simple means comparisons tests to avoid this problem.
-Finally, we demonstrate how to use nested model comparison tests to formally test for omnibus differences between groups.
-
-Consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which show the exact same analysis (comparing AMCEs for high and low ethnocentrism respondents) on the same experimental data from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment.
-In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in preferences between the two subgroups.
-In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.\footnote{The appendix contains comparable plots for experiments by \citet{BechtelScheve2013} and \citet{TeeleKallaRosenbluth2018}.}
-
-Panel A gives the impression that there are significant differences in preferences between high and low ethnocentrism respondents toward immigrants from different countries of origin, with different careers, and with different educational attainments.
-By contrast, Panel B gives the impression that these differences --- indeed all differences --- are negligible.
-The experimental data and analytic approach in the two portrayals is identical; the only difference is the choice of reference category for the profile features.
+To begin, consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which shows estimated subgroup AMCEs for three features from the immigration study.
+In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in levels of support between the two subgroups.
+In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.
+
+Panel A gives the impression that there are significant differences in preferences between high and low ethnocentrism respondents toward immigrants from different countries of origin, with different careers, and with different educational attainments because the reference category choice cascades the difference in reference category favorability into AMCEs for all other feature levels.
+By contrast, Panel B gives the impression that these differences are negligible.
+The experimental data and analytic approach in the two portrayals is identical; the only difference is the choice of reference category.
 Given what we have shown about the relationship between differences in conditional AMCEs and differences in conditional marginal means, Panel B is the more truthful visualization \citep{Cairo2016}.
 The differences between subgroup AMCEs there more accurately convey differences in underlying preferences because the reference categories used in Panel B are the most similar between the two groups.
-Yet even this may not \textit{perfectly} convey differences because no feature generates perfect agreement between the subgroups.
 
@@
 
-Alternatively presenting subgroup differences using conditional marginal means (as in Figure \ref{fig:hainmueller_mm_diffs}) provides the intended descriptive comparison of subgroup preferences.
-Each dot and error bar represents the conditional marginal mean (and its standard error) for high ethnocentrism (in red) and low ethnocentrism (in blue) respondents.
-This display of conditional marginal means highlights just how similar the preferences are for the two groups.
-For example, in the first set of estimates, both groups of respondents display minimally positive preferences toward female immigrants and minimally negative preferences toward male immigrants, averaging across those immigrants' other profile features.
-The second set of estimates shows both group are also more favorable toward higher-educated immigrants and less favorable toward less-education immigrants with no visually apparent differences.
-The third set of estimates, related to language skills, shows again similar patterns: both groups are more favorable toward immigrants with higher English proficiency than immigrants with lower English proficiency.
-
-These estimates are less obviously identical for the two groups but look quite close.
-To test for pairwise differences between high and low ethnocentrism respondents, we can calculate differences in conditional conditional marginal means at each feature level, with associated significance tests:
-
-\begin{itemize}
-\item spoke fluent English: 0.02 (0.02, $z_{\text{diff}}$=1.30, $p\leq 0.20$)
-\item spoke broken English: 0.01 (0.02, $z_{\text{diff}}$=0.71, $p\leq 0.48$)
-\item tried to speak English but was unable: -0.01 (0.02, $z_{\text{diff}}$=-0.78, $p\leq 0.43$)
-\item spoke [language] and used an interpreter: -0.02 (0.02, $z_{\text{diff}}$=-1.22, $p\leq 0.22$)
-
-\end{itemize}
-
-\noindent These pairwise tests show that are our eyes have not deceived us.
-None of the level-specific differences in conditional marginal means are statistically distinguishable from zero.
-Were we interested in an omnibus tests of whether any of these differences were non-zero, we could perform a nested model comparison of two equations: (a) one estimating only marginal effects of the ``Language Skills'' feature levels, and (b) the same model with additional interactions between the subgrouping covariate and the feature levels.
-The test compares the sum of squared residuals for the two equations.
+Next, making a comparison of levels of favorability toward different types of immigrants without using AMCEs would have been even more truthful.
+Figure \ref{fig:hainmueller_mm_diffs} \textit{directly} shows that comparison of preferences as differences in subgroup marginal means between the two groups for these three features, with 95\% confidence intervals for the difference.\footnote{A presentation of subgroup marginal means for all features can be found in Appendix \ref{app:hainmuellerimmigration}.} The two groups indeed have similar preferences, something that would have happened to be clear had the conditional AMCEs in the right panel of Figure \ref{fig:hainmueller_subgroup_example_plot} been presented but that would have been far less obvious were the conditional AMCEs in the left panel of that figure presented.
+Pairwise difference in means tests would provide formal procedures for testing the statistical significance of these differences.
+
+Yet, finally, the similarity of subgroup preferences in conjoints is often characterized in an \textit{omnibus} fashion, as in the quote from \citet{HainmuellerHopkinsYamamoto2014} describing ``patterns of support.'' An appropriate test in such cases is one that evaluates whether a model of support that accounts for group differences better fits the data than a model of support with only conjoint features as predictors.
+This type of test is known as a ``nested model comparison'' which compares the fit of a ``restricted'' regression (the restriction being that interactions between features and a subgroup identifier are held to be zero) nested within an ``unrestricted'' regression that allows for arbitrary interactions between conjoint features and the subgroup identifier.
+Formally, a nested model comparison provides an F-test of the null hypothesis that all interaction terms are equal to zero.\footnote{Like any ANOVA this hypothesis test may yield substantively different insight from a series of tests of pairwise mean differences.
+Figure \ref{fig:hainmueller_mm_diffs} shows three instances where the confidence intervals for pairwise differences in marginal means do not include zero even though the omnibus test fails to reject the null.}
 
@@
 
-\noindent where $SSR_{Restricted}$ is the sum of squared residuals for Equation \ref{eq:restricted}, $SSR_{Unrestricted}$ is the sum of squared residuals for Equation \ref{eq:unrestricted}, where $r$ is the number of restrictions (in the above example, 4), $n$ is the number of cases, and $k$ is the number of feature levels in the unrestricted model.
-Note that this test is not sensitive to reference category used in the regression
+\noindent where $SSR_{Restricted}$ is the sum of squared residuals for Equation \ref{eq:restricted}, $SSR_{Unrestricted}$ is the sum of squared residuals for Equation \ref{eq:unrestricted}, where $r$ is the number of restrictions (in the above example, 4), $n$ is the number of cases, and $k$ is the number of feature levels in the unrestricted model.\footnote{Note that this test is not sensitive to reference category even though it requires specifying a regression equation.}
 
@@
 The result of that test for differences by ethnocentrism from the immigration experiment is: F(98, 11402)=1.16, $p\leq0.14$, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.
-By contrast, \citet{BechtelScheve2013} argue in their cross-country conjoint examining climate change agreements ``that individuals in all four countries largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}.
-Yet a nested model comparisons shows the countries do differ in their preferences F(54, 67982)=3.72, $p\leq0.00$.
-This cross-country variation is largely driven by differences in sensitivity to monthly household costs feature, F(15, 67995)=3.80, $p\leq0.00$, with the United Kingdom and United States being more cost sensitive than Germany and France as is plainly visible in a plot of marginal means by country (see SI).
 
@@
 For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9).
-Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to an quite different conclusion.
+Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to a quite different conclusion.
+As an example, \citet{BechtelScheve2013} argue that their conjoint results show ``individuals in all four countries largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}, but a nested model comparison shows the countries do differ in their preferences F(54, 67982)=3.72, $p\leq0.00$.
+This cross-country variation largely driven by differences in sensitivity to monthly household costs feature, F(15, 67995)=3.80, $p\leq0.00$, with the United Kingdom and United States being more cost sensitive than Germany and France.
+Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences, but ulimately there is no guarantee that they do in any particular analysis.
 
@@
 
-\section{Hainmueller et al. (2014) Candidate Experiment}
-
-\subsection{Replication using AMCEs}
+\section{Hainmueller et al. (2014) Candidate Experiment}\label{app:hainmuellercandidate}
+
+\subsection{Replication using AMCEs and MMs}
 
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Nov 25 10:42:42 2018
+\subsection{Numerical Results: AMCEs}
+
+% latex table generated in R 3.5.3 by xtable 1.8-3 package
+% Sun Apr 14 20:35:25 2019
 \begin{table}[ht]
@@
 
-\subsection{Replication using MMs}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_mm_appendix-1}
-
-\end{knitrout}
-
-\clearpage
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Nov 25 10:42:44 2018
+\subsection{Numerical Results: MMs}
+
+% latex table generated in R 3.5.3 by xtable 1.8-3 package
+% Sun Apr 14 20:35:25 2019
 \begin{table}[ht]
@@
 
-\section{Hainmueller et al. (2014) Immigration Experiment}
-
-\subsection{Replication using AMCEs}
+\section{Hainmueller et al. (2014) Immigration Experiment}\label{app:hainmuellerimmigration}
+
+\subsection{Replication using AMCEs and MMs}
 
@@
 
+\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_amce_appendix-2}
+
 \end{knitrout}
@@
 
-% latex table generated in R 3.5.2 by xtable 1.8-3 package
-% Fri Mar 15 15:56:01 2019
+\subsection{Numerical Results: AMCEs}
+
+% latex table generated in R 3.5.3 by xtable 1.8-3 package
+% Sun Apr 14 20:35:34 2019
 \begin{table}[ht]
 \centering
-\begingroup\footnotesize
+\begingroup\scriptsize
 \begin{tabular}{lp{3in}rrr}
@@
 
-\subsection{Replication using MMs}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_mm_appendix-1}
-
-\end{knitrout}
-
-\clearpage
-
-% latex table generated in R 3.5.2 by xtable 1.8-3 package
-% Fri Mar 15 15:56:08 2019
+\subsection{Numerical Results: MMs}
+
+% latex table generated in R 3.5.3 by xtable 1.8-3 package
+% Sun Apr 14 20:35:37 2019
 \begin{table}[ht]
 \centering
-\begingroup\footnotesize
+\begingroup\scriptsize
 \begin{tabular}{lp{3in}rrr}
@@
 
-\section{Teele et al. (2018) Candidate Experiment}
-
-\subsection{Replication using AMCEs}
+\section{Teele et al. (2018) Candidate Experiment}\label{app:tkr}
+
+\subsection{Replication using AMCEs and MMs}
 
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Nov 25 10:43:16 2018
+\subsection{Numerical Results: AMCEs}
+
+% latex table generated in R 3.5.3 by xtable 1.8-3 package
+% Sun Apr 14 20:35:47 2019
 \begin{table}[ht]
@@
 
-\subsection{Replication using MMs}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/tkr_mm_appendix-1}
-
-\end{knitrout}
-
-\clearpage
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Nov 25 10:43:19 2018
+\subsection{Numerical Results: MMs}
+
+% latex table generated in R 3.5.3 by xtable 1.8-3 package
+% Sun Apr 14 20:35:48 2019
 \begin{table}[ht]
@@
 
-\section{Bechtel and Scheve (2013) Climate Agreement Experiment}
-
-\subsection{Replication using AMCEs}
+\section{Bechtel and Scheve (2013) Climate Agreement Experiment}\label{app:bechtel}
+
+\subsection{Replication using AMCEs and MMs}
 
@@
 
-\clearpage
-
-\subsection{Replication using MMs}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/bechtel_mm-1}
-
-\end{knitrout}
-
-\clearpage
+\subsection{Numerical Results: AMCEs}
+
+\clearpage
+
+\subsection{Numerical Results: MMs}
 
@@
 ## [31] readxl_1.3.1      foreign_0.8-71    magrittr_1.5     
-## [34] codetools_0.2-16  splines_3.5.3     scales_1.0.0     
-## [37] assertthat_0.2.1  xtable_1.8-3      colorspace_1.4-1 
-## [40] sandwich_2.5-1    survey_3.35-1     stringi_1.4.3    
-## [43] lazyeval_0.2.2    munsell_0.5.0     crayon_1.3.4     
-## [46] zoo_1.8-5
+## [34] splines_3.5.3     scales_1.0.0      assertthat_0.2.1 
+## [37] xtable_1.8-3      colorspace_1.4-1  sandwich_2.5-1   
+## [40] survey_3.35-1     stringi_1.4.3     lazyeval_0.2.2   
+## [43] munsell_0.5.0     crayon_1.3.4      zoo_1.8-5
 \end{verbatim}

### 2019-04-15 manuscript.Rnw
almost done with revision

@@
 \citet{BallardRosaMartinScheve2016} make similar comparisons in their tax policy conjoint: ``While there are few strong differences in preferences for taxing the lower three income groups (the `hard work' group has slightly lower elasticities for taxing the poor), there are strong differences in preferences for taxing the rich'' (12).
-In \citet{BechtelScheve2013} conjoint on support for international climate change agreements in the United States, United Kingdom, Germany, and France, they summarize their results as ``We find that individuals in all four countries largely agree on which dimensions are important and to what extent'' (13765).
+In the \citet{BechtelScheve2013} conjoint on support for international climate change agreements in the United States, United Kingdom, Germany, and France, they summarize their results as ``We find that individuals in all four countries largely agree on which dimensions are important and to what extent'' (13765).
 In these examples, the differences between conditional AMCEs are used as a way of descriptively characterizing differences in \textit{preferences} (i.e.
@@
 The difference between marginal means for two groups are always fixed in the data, so the differencing of subgroup AMCEs is merely an exercise is centering those differences at arbitrary points along the range of observed differences in marginal means.
-Differences-in-AMCEs for a given feature level must therefore necessarily sometimes be positive and sometimes be negative, depending on the reference category used in estimating them.
-The direction of the difference per se conveys no information about underlying pattern of preferences in the two groups.
-
 Second, and more practically, because there is no category for which the preferences of the two subgroups in this example are identical, no choice of reference category would have led to inferences from differences-in-AMCEs that accurately reflect the underlying difference in preferences.
@@
 But there is never any guarantee that such a reference category exists.
-If multiple subgroup analyses are performed, it is unlikely the same reference category would work well across all analyses, making consistent interpretation difficult.
-And because conjoint analysis generates a sparse feature matrix (where many combinations of feature levels are unobserved in the data), it is rarely possible to empirically select an appropriate set of reference categories using the observed data.
-It is impossible to know which cell --- of the tens of thousands in the design --- is the best choice of reference.
-Indeed it is possible that there is no such cell for which preferences are identical in the two groups; such a cell may exist, but there is no reason to expect that it should exist in any given application or that it would happen to be observed.
 Thus, there is no way to use conditional AMCEs or differences between those conditional AMCEs to convey the underlying similarity or differences in preferences across sample subgroups.
@@
 
-Researchers and consumers of conjoints can avoid the inferential errors that accompany conditional AMCEs by focusing attention on (subgroup) marginal means, differences between subgroup marginal means to infer subgroup differences in preferences toward particular features, and omnibus nested model comparisons to infer subgroup differences across many features.
+Researchers and consumers of conjoints interested in describing levels of respondent favorability toward profiles with varying features can avoid the inferential errors that accompany conditional AMCEs by focusing attention on (subgroup) marginal means, differences between subgroup marginal means to infer subgroup differences in preferences toward particular features, and omnibus nested model comparisons to infer subgroup differences across many features.
 To demonstrate each of these three techniques we provide a complete example based upon \citeauthor{HainmuellerHopkinsYamamoto2014}'s analysis of their immigration conjoint by respondent enthnocentrism, which finds that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' \citep[22]{HainmuellerHopkinsYamamoto2014}.
@@
 
-<<hainmueller_subgroup_example_plot, dependson=c("data_hainmueller_immigration", "hainmueller_subgroup_example"), fig.width=8, fig.height=6, fig.cap="Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Hainmueller et al.
-(2014) Immigration Experiment", message=FALSE>>=
+<<hainmueller_subgroup_example_plot, dependson=c("data_hainmueller_immigration", "hainmueller_subgroup_example"), fig.width=8, fig.height=6, fig.cap="Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Three Features from Hainmueller et al.'s (2014) Immigration Experiment", message=FALSE>>=
 plot(
@@
   scale_colour_manual(
-    "Ethnocentrism", limits = c("high", "low"), values = c("Red", "Blue")
+    "Ethnocentrism", limits = c("high", "low"), values = c("Black", "Gray")
   ) +
@@
 To begin, consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which shows estimated subgroup AMCEs for three features from the immigration study.
-In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in levels of support between the two subgroups.
+In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in levels of support between the two subgroups thus distorting the size of differences at all other levels.
 In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.
@@
 
-<<hainmueller_mm_diffs, dependson=c("data_hainmueller_immigration"), fig.height = 5, fig.width=8, fig.cap="Differences in Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment", message=FALSE>>=
+<<hainmueller_mm_diffs, dependson=c("data_hainmueller_immigration"), fig.height = 5, fig.width=8, fig.cap="Differences in Conditional Marginal Means, by Ethnocentrism, for Three Features From Hainmueller et al.'s (2014) Immigration Experiment", message=FALSE>>=
 mm_by_ethnocentrism <- cj(
@@
 
-<<hainmueller_language_diffs, dependson=c("data_hainmueller_immigration"), eval=TRUE, echo=FALSE>>=
-hainmueller_anova_language <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ LanguageSkills, id = ~ CaseID, by = ~ ethnocentrism_split)
-@
-
-For the \citeauthor{HainmuellerHopkinsYamamoto2014} language feature, the resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_language$Df[2], hainmueller_anova_language[["Resid.
-Df"]][1], hainmueller_anova_language$F[2], hainmueller_anova_language$"Pr(>F)"[2])}.
-We could repeat such pairwise comparisons or omnibus comparisons for each feature in the design.
-
-Furthermore, we could also directly visualize differences in conditional marginal means for this feature --- and all features --- as in Figure \ref{fig:hainmueller_mm_diffs}.
-This provides a more direct presentation of \textit{differences} between subgroup preferences as the vertical line indicates feature levels for which there is no difference between the two groups.
-Positive values to the right of the line indicate positive differences (high ethnocentrism respondents are more favorable toward immigrants with this feature than low ethnocentrism respondents) and negative value to the left of zero convey the opposite.
-A further advantage of this plot is that unlike displays of conditional AMCEs, differences in conditional marginal means communicate subgroup differences for all feature levels including the reference categories.
-This display makes readily clear what was only indirectly apparent in Figure \ref{fig:hainmueller_mm_diffs}: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.
-
-<<hainmueller_all_diffs, dependson=c("data_hainmueller_immigration"), eval=TRUE, echo=FALSE>>=
-hainmueller_anova_all <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Gender + Job*Education + LanguageSkills + CountryOfOrigin*ReasonForApplication + JobExperience + JobPlans + PriorEntry, id = ~ CaseID, by = ~ ethnocentrism_split)
-@
+<<hainmueller_anovas, dependson=c("data_hainmueller_immigration"), eval=TRUE, echo=FALSE>>=
+hainmueller_anova_education <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Education, id = ~ CaseID, by = ~ ethnocentrism_split)
+hainmueller_anova_country <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, by = ~ ethnocentrism_split)
+hainmueller_anova_job <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Job, id = ~ CaseID, by = ~ ethnocentrism_split)
+hainmueller_anova_all <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication, id = ~ CaseID, by = ~ ethnocentrism_split)
+@
+
+For the education feature, the resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_education$Df[2], hainmueller_anova_education[["Resid.
+Df"]][1], hainmueller_anova_education$F[2], hainmueller_anova_education$"Pr(>F)"[2])}.
+We could repeat such pairwise comparisons or omnibus comparisons for each feature in the design --- for country of origin (\Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_country$Df[2], hainmueller_anova_country[["Resid.
+Df"]][1], hainmueller_anova_country$F[2], hainmueller_anova_country$"Pr(>F)"[2])}) or job (\Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_job$Df[2], hainmueller_anova_job[["Resid.
+Df"]][1], hainmueller_anova_job$F[2], hainmueller_anova_job$"Pr(>F)"[2])}) --- or for all features as a whole (\Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_all$Df[2], hainmueller_anova_all[["Resid.
+Df"]][1], hainmueller_anova_all$F[2], hainmueller_anova_all$"Pr(>F)"[2])}).
+
+This visual display in Figure \ref{fig:hainmueller_mm_diffs} and these statistical tests make clear what could not be directly inferred from conditional AMCEs alone: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.
 
@@
 
-As before, we can perform an omnibus tests for the presence of any subgroup differences across all features, again using nested model comparison of two equations: (a) one estimating only effects of the features, and (b) the same model with additional interactions between the subgrouping covariate and all features.
-The result of that test for differences by ethnocentrism from the immigration experiment is: \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_all$Df[2], hainmueller_anova_all[["Resid.
-Df"]][1], hainmueller_anova_all$F[2], hainmueller_anova_all$"Pr(>F)"[2])}, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.
-
 This kind of nested model comparison test can also be used to assess heterogeneity across conjoint features \citep[see also][]{EgamiImai2018}.
 For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9).
-Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to a quite different conclusion.
-As an example, \citet{BechtelScheve2013} argue that their conjoint results show ``individuals in all four countries largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}, but a nested model comparison shows the countries do differ in their preferences \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country$Df[2], bechtel_anova_country[["Resid.
+Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to quite different inferences.
+As an example, \citet{BechtelScheve2013} argue that their conjoint results show ``individuals in all four countries [Germany, France, United States, United Kingdom] largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}, but a nested model comparison shows the countries do differ in their preferences \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country$Df[2], bechtel_anova_country[["Resid.
 Df"]][1], bechtel_anova_country$F[2], bechtel_anova_country$"Pr(>F)"[2])}.
-This cross-country variation largely driven by differences in sensitivity to monthly household costs feature, \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country_cost$Df[2], bechtel_anova_country_cost[["Resid.
+This cross-country variation is largely driven by differences in sensitivity to monthly household costs feature, \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country_cost$Df[2], bechtel_anova_country_cost[["Resid.
 Df"]][1], bechtel_anova_country_cost$F[2], bechtel_anova_country_cost$"Pr(>F)"[2])}, with the United Kingdom and United States being more cost sensitive than Germany and France.
-Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences, but ulimately there is no guarantee that they do in any particular analysis.
+Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences (as in the \citeauthor{HainmuellerHopkinsYamamoto2014} case), but ulimately there is no guarantee that they do in any particular analysis.
 
@@
 This article has identified several challenges related to the analysis and reporting of conjoint experimental designs, particularly analyses of subgroup differences.
-We suggest that conjoint analyses should report not only average marginal component effects (AMCEs) but also descriptive quantities that better convey underlying preferences over profile features and better convey subgroup differences in those preferences.
+We suggest that conjoint analyses should report not only average marginal component effects (AMCEs) but also descriptive quantities about levels of favorability that better convey underlying preferences over profile features and better convey subgroup differences in those preferences.
 Marginal means contain all of the information provided by AMCEs and more.
-Consequently, our intention here is not to substantively undermine any previous set of results, but instead to urge researchers moving forward to demonstrate considerable caution in how they design, analyze, and present the results of these types of descriptive experiments.
+Consequently, our intention here is not to substantively undermine any previous set of results, but instead to urge researchers moving forward to demonstrate considerable caution in how they design, analyze, and present the results of these types of descriptive experiments and how they test for differences in preferences between subgroups.
+
 We have relatively straightforward and hopefully uncontroversial advice for how analysts of conjoint experiments should proceed:
@@
 The now-common practice of descriptively interpreting conjoints requires more caution than is immediately obvious.
-This paper has demonstrated several such challenges and hopefully provides useful advice for how researchers should proceed with the analysis of such designs.
-
-To facilitate such analysis and, especially, to provide easy-to-use tools for calculating marginal means and performing reference category selection diagnostics, we provide software called \textbf{cregg} \citep{Leeper2018cregg} available from the Comprehensive R Archive Network; this manuscript is written as a reproducible knitr document \citep{Xie2015} that contains complete code examples that will perform all analyses and visualization used throughout this article.
-With that resource in-hand, researchers should be well-equipped to analyze conjoint designs without running into the analytic challenges discussed here.
+
+To facilitate improved analysis and, especially, to provide easy-to-use tools for calculating marginal means and performing reference category selection diagnostics, we provide software called \textbf{cregg} \citep{Leeper2018cregg} available from the Comprehensive R Archive Network.
+Additionally, this manuscript is written as a reproducible knitr document \citep{Xie2015} that contains complete code examples that will perform all analyses and visualization used throughout this article.
+With these resources in-hand, researchers should be well-equipped to analyze subgroup preferences in conjoint designs without running into the analytic challenges discussed here.
 
@@
 
-\subsection{Replication using AMCEs and MMs}
+\subsection{Replication using AMCEs}
 
@@
  theme(legend.position="none")
-p2 <- plot(
-  cregg::cj(
-     hainmueller_immigration, 
-     ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
-     id = ~ CaseID,
-     estimate = "mm"
-  ), vline = 0.5
-) + 
-  ggplot2::scale_x_continuous(
-    limits = c(0.1, 0.9), 
-    breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
-  ) + 
-  ggplot2::geom_text(
-    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
-    colour = "black", 
-    size = 2,
-    position = position_nudge(y = .5)
-  ) + 
-  theme(legend.position="none")
-#gridExtra::grid.arrange(p1, p2, ncol=2)
 p1
-p2
-@
-
-\clearpage
-
-<<hainmueller_immigration_amce_appendix_split, dependson=c("data_hainmueller_immigration"), fig.height=4, fig.width=8>>=
-plot(
-  rbind(
-    within(cj(
-      subset(hainmueller_immigration, constraint1constrained), 
-      ChosenImmigrant ~ CountryOfOrigin + ReasonForApplication,
-      id = ~ CaseID,
-      estimate = "mm"
-    ), Constraint <- "Constrained"),
-    within(cj(
-      subset(hainmueller_immigration, constraint1unconstrained), 
-      ChosenImmigrant ~ CountryOfOrigin + ReasonForApplication,
-      id = ~ CaseID,
-      estimate = "mm"
-    ), Constraint <- "Unconstrained")
-  ), vline = 0.5
-) + facet_wrap(~Constraint)
-
-plot(
-  rbind(
-    within(cj(
-      subset(hainmueller_immigration, constraint2constrained), 
-      ChosenImmigrant ~ Job + Education,
-      id = ~ CaseID,
-      estimate = "mm"
-    ), Constraint <- "Constrained"),
-    within(cj(
-      subset(hainmueller_immigration, constraint2unconstrained), 
-      ChosenImmigrant ~ Job + Education,
-      id = ~ CaseID,
-      estimate = "mm"
-    ), Constraint <- "Unconstrained")
-  ), vline = 0.5
-) + facet_wrap(~Constraint)
 @
@@
 ), include.rownames = FALSE, size = "scriptsize")
+@
+
+\clearpage
+
+\subsection{Replication using MMs}
+
+<<hainmueller_immigration_mm_appendix, dependson=c("data_hainmueller_immigration"), fig.height=8, fig.width=8>>=
+p2 <- plot(
+  cregg::cj(
+     hainmueller_immigration, 
+     ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
+     id = ~ CaseID,
+     estimate = "mm"
+  ), vline = 0.5
+) + 
+  ggplot2::scale_x_continuous(
+    limits = c(0.1, 0.9), 
+    breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
+  ) + 
+  ggplot2::geom_text(
+    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
+    colour = "black", 
+    size = 2,
+    position = position_nudge(y = .5)
+  ) + 
+  theme(legend.position="none")
+p2
 @
@@
 (2018) Candidate Experiment">>=
-plot(amce_ref_tkr_merged, group = "PartyID", feature_headers = FALSE, legend_title = "Party Identification", vline = 0) + 
-  facet_grid(rows = vars(feature), cols = vars(dataset), scales = "free_y", space = "free_y", labeller = function(x) label_value(x, multi_line = FALSE)) +
-  theme(strip.text.x = element_text(size = 8),
-        strip.text.y = element_text(size = 5))
+plot(
+  amce_ref_tkr_merged, 
+  group = "PartyID", 
+  feature_headers = FALSE, 
+  legend_title = "Party Identification", 
+  vline = 0
+) + 
+  facet_grid(
+    rows = vars(feature), 
+    cols = vars(dataset), 
+    scales = "free_y", 
+    space = "free_y", 
+    labeller = function(x) label_value(x, multi_line = FALSE)
+  ) +
+  theme(
+      strip.background = element_rect(fill="white", colour="white"),
+      strip.text.x = element_text(size = 8),
+      strip.text.y = element_blank()
+    )
 @
@@
 
-\clearpage
-
-\subsection{Numerical Results: AMCEs}
+%\clearpage
+
+%\subsection{Numerical Results: AMCEs}
 
@@
 
-\clearpage
-
-\subsection{Numerical Results: MMs}
+%\clearpage
+
+%\subsection{Numerical Results: MMs}
 
@@
 
-\clearpage
+%\clearpage
 
@@
 
-\clearpage
+\subsection{Subgroup Analysis using MMs: Environmentalism}
 
@@
 @
-
-\clearpage
 
@@
 
-\clearpage
-
 \subsection{Subgroup Analysis using MMs: Reciprocity}
@@
 
-\clearpage
-
 \subsection{Nested Model Comparison: Country}
@@
 
-<<bechtel_reciprocity_reference>>=
+<<bechtel_reciprocity_reference, fig.height=5, fig.width=7>>=
 # ``Individuals who pretreatment exhibit reciprocal behavior [...] are almost twice as sensitive to both the number of countries participating and the proportion of emissions represented than individuals who do not'' (13768).

### 2019-04-15 manuscript.tex
almost done with revision

@@
 
-For the \citeauthor{HainmuellerHopkinsYamamoto2014} language feature, the resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: F(4, 11496)=1.06, $p\leq0.37$.
-We could repeat such pairwise comparisons or omnibus comparisons for each feature in the design.
-
-Furthermore, we could also directly visualize differences in conditional marginal means for this feature --- and all features --- as in Figure \ref{fig:hainmueller_mm_diffs}.
-This provides a more direct presentation of \textit{differences} between subgroup preferences as the vertical line indicates feature levels for which there is no difference between the two groups.
-Positive values to the right of the line indicate positive differences (high ethnocentrism respondents are more favorable toward immigrants with this feature than low ethnocentrism respondents) and negative value to the left of zero convey the opposite.
-A further advantage of this plot is that unlike displays of conditional AMCEs, differences in conditional marginal means communicate subgroup differences for all feature levels including the reference categories.
-This display makes readily clear what was only indirectly apparent in Figure \ref{fig:hainmueller_mm_diffs}: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.
-
-As before, we can perform an omnibus tests for the presence of any subgroup differences across all features, again using nested model comparison of two equations: (a) one estimating only effects of the features, and (b) the same model with additional interactions between the subgrouping covariate and all features.
-The result of that test for differences by ethnocentrism from the immigration experiment is: F(98, 11402)=1.16, $p\leq0.14$, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.
+For the education feature, the resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: F(7, 11493)=0.68, $p\leq0.69$.
+We could repeat such pairwise comparisons or omnibus comparisons for each feature in the design --- for country of origin (F(10, 11490)=1.56, $p\leq0.11$) or job (F(11, 11489)=0.87, $p\leq0.56$) --- or for all features as a whole (F(98, 11402)=1.16, $p\leq0.14$).
+
+This visual display in Figure \ref{fig:hainmueller_mm_diffs} and these statistical tests make clear what could not be directly inferred from conditional AMCEs alone: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.
 
@@
 For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9).
-Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to a quite different conclusion.
-As an example, \citet{BechtelScheve2013} argue that their conjoint results show ``individuals in all four countries largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}, but a nested model comparison shows the countries do differ in their preferences F(54, 67982)=3.72, $p\leq0.00$.
-This cross-country variation largely driven by differences in sensitivity to monthly household costs feature, F(15, 67995)=3.80, $p\leq0.00$, with the United Kingdom and United States being more cost sensitive than Germany and France.
-Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences, but ulimately there is no guarantee that they do in any particular analysis.
+Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to quite different inferences.
+As an example, \citet{BechtelScheve2013} argue that their conjoint results show ``individuals in all four countries [Germany, France, United States, United Kingdom] largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}, but a nested model comparison shows the countries do differ in their preferences F(54, 67982)=3.72, $p\leq0.00$.
+This cross-country variation is largely driven by differences in sensitivity to monthly household costs feature, F(15, 67995)=3.80, $p\leq0.00$, with the United Kingdom and United States being more cost sensitive than Germany and France.
+Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences (as in the \citeauthor{HainmuellerHopkinsYamamoto2014} case), but ulimately there is no guarantee that they do in any particular analysis.
 
@@
 \includegraphics[width=\maxwidth]{figure/hainmueller_immigration_amce_appendix-1}
-
-\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_amce_appendix-2}
-
-\end{knitrout}
-
-\clearpage
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_amce_appendix_split-1}
-
-\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_amce_appendix_split-2}
 
@@
 
+\subsection{Replication using MMs}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_mm_appendix-1}
+
+\end{knitrout}
+
+\clearpage
+
 \subsection{Numerical Results: MMs}
@@
 
-\clearpage
-
-\subsection{Numerical Results: AMCEs}
-
-\clearpage
-
-\subsection{Numerical Results: MMs}
+%\clearpage
+
+%\subsection{Numerical Results: AMCEs}
+
+%\clearpage
+
+%\subsection{Numerical Results: MMs}
 
@@
 
-\clearpage
-
 \subsection{Subgroup Analysis using AMCEs: Reciprocity}
@@
 \end{knitrout}
-
-\clearpage
 

### 2019-04-16 manuscript.Rnw
rebuild everything from scratch for resubmission

@@
 Formally, a nested model comparison provides an F-test of the null hypothesis that all interaction terms are equal to zero.\footnote{Like any ANOVA this hypothesis test may yield substantively different insight from a series of tests of pairwise mean differences.
-Figure \ref{fig:hainmueller_mm_diffs} shows three instances where the confidence intervals for pairwise differences in marginal means do not include zero even though the omnibus test fails to reject the null.}
+Figure \ref{fig:hainmueller_mm_diffs} shows three instances where the 95\% confidence intervals for pairwise differences in marginal means do not include zero even though the omnibus test fails to reject the null at $\alpha = 0.05$.}
 
@@
 \begin{equation}\label{eq:restricted}
-Y = \beta_0 + \beta_1 Level_1 + \beta_2 Level_2 + \beta_3 Level_3 + u
+Y = \beta_0 + \beta_1 Level_2 + \beta_2 Level_3 + \beta_3 Level_4 + u
 \end{equation}
@@
 \begin{split}
-Y = & \beta_0 + \beta_1 Level_1 + \beta_2 Level_2 + \beta_3 Level_3 + \beta_4 Group + \\
-& \beta_5 Level_1 * Group + \beta_6 Level_2 * Group + \beta_7 Level_3 * Group + u
+Y = & \beta_0 + \beta_1 Level_2 + \beta_2 Level_3 + \beta_3 Level_4 + \beta_4 Group + \\
+& \beta_5 Level_2 * Group + \beta_6 Level_3 * Group + \beta_7 Level_4 * Group + u
 \end{split}
@@
 Df"]][1], bechtel_anova_country_cost$F[2], bechtel_anova_country_cost$"Pr(>F)"[2])}, with the United Kingdom and United States being more cost sensitive than Germany and France.
-Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences (as in the \citeauthor{HainmuellerHopkinsYamamoto2014} case), but ulimately there is no guarantee that they do in any particular analysis.
+Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences (as in the \citeauthor{HainmuellerHopkinsYamamoto2014} case), but ultimately there is no guarantee that they do in any particular analysis.
 
@@
 \begin{enumerate}
-\item Always report unadjusted marginal means when attempting to provide a \textit{descriptive} summary of respondent preferences in addition to, or instead of, AMCEs.\footnote{Like the presentation of AMCEs, displaying marginal means in constrained conjoint designs may also distort apparent patterns given that not all features can co-occur.
+\item Always report unadjusted marginal means when attempting to provide a \textit{descriptive} summary of respondent preferences in addition to, or instead of, AMCEs.%\footnote{Like the presentation of AMCEs, displaying marginal means in constrained conjoint designs may also distort apparent patterns given that not all features can co-occur.
 Partitioning the design into fractions such that each fraction contains a fully unconstrained design would mitigate any concern with that presentation.}
@@
 \item Exercise caution when explicitly, or implicitly, interpreting differences-in-AMCEs across subgroups.
-Differences-in-AMCEs are differences in effect sizes for subgroups, not statments about the relative favorability of the subgroups toward profiles with a given feature.
+Differences-in-AMCEs are differences in effect sizes for subgroups, not statements about the relative favorability of the subgroups toward profiles with a given feature.
 Heterogeneous effects do not necessarily mean different underlying preferences.
@@
 
-\item To formally test for group differences in preferences, regression with interaction terms between the subgrouping covariate and all feature levels will generate estimates of level-specific differences in preferences via the coefficients on the interaction terms.\footnote{The analysis is slightly more complicated in constrained designs.} A nested model comparison between this equation against one without such interactions provides an omnibus test of subgroup differences, which should be reported when characterizing overall patterns of subgroup differences.
+\item To formally test for group differences in preferences, regression with interaction terms between the subgrouping covariate and all feature levels will generate estimates of level-specific differences in preferences via the coefficients on the interaction terms.
+A nested model comparison between this equation against one without such interactions provides an omnibus test of subgroup differences, which should be reported when characterizing overall patterns of subgroup differences.
 \end{enumerate}
@@
 The now-common practice of descriptively interpreting conjoints requires more caution than is immediately obvious.
-
 To facilitate improved analysis and, especially, to provide easy-to-use tools for calculating marginal means and performing reference category selection diagnostics, we provide software called \textbf{cregg} \citep{Leeper2018cregg} available from the Comprehensive R Archive Network.

### 2019-04-16 manuscript.tex
rebuild everything from scratch for resubmission

@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/hainmueller_subgroup_example_plot-1} \caption[Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Hainmueller et al]{Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Hainmueller et al.
-(2014) Immigration Experiment}\label{fig:hainmueller_subgroup_example_plot}
+\includegraphics[width=\maxwidth]{figure/hainmueller_subgroup_example_plot-1} \caption[Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Three Features from Hainmueller et al.'s (2014) Immigration Experiment]{Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Three Features from Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:hainmueller_subgroup_example_plot}
 \end{figure}
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/hainmueller_mm_diffs-1} \caption[Differences in Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment]{Differences in Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:hainmueller_mm_diffs}
+\includegraphics[width=\maxwidth]{figure/hainmueller_mm_diffs-1} \caption[Differences in Conditional Marginal Means, by Ethnocentrism, for Three Features From Hainmueller et al.'s (2014) Immigration Experiment]{Differences in Conditional Marginal Means, by Ethnocentrism, for Three Features From Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:hainmueller_mm_diffs}
 \end{figure}
@@
 This cross-country variation is largely driven by differences in sensitivity to monthly household costs feature, F(15, 67995)=3.80, $p\leq0.00$, with the United Kingdom and United States being more cost sensitive than Germany and France.
-Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences (as in the \citeauthor{HainmuellerHopkinsYamamoto2014} case), but ulimately there is no guarantee that they do in any particular analysis.
+Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences (as in the \citeauthor{HainmuellerHopkinsYamamoto2014} case), but ultimately there is no guarantee that they do in any particular analysis.
 
@@
 % latex table generated in R 3.5.3 by xtable 1.8-3 package
-% Sun Apr 14 20:35:25 2019
+% Tue Apr 16 22:40:04 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.3 by xtable 1.8-3 package
-% Sun Apr 14 20:35:25 2019
+% Tue Apr 16 22:40:05 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.3 by xtable 1.8-3 package
-% Sun Apr 14 20:35:34 2019
+% Tue Apr 16 22:40:09 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.3 by xtable 1.8-3 package
-% Sun Apr 14 20:35:37 2019
+% Tue Apr 16 22:40:15 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.3 by xtable 1.8-3 package
-% Sun Apr 14 20:35:47 2019
+% Tue Apr 16 22:40:25 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.3 by xtable 1.8-3 package
-% Sun Apr 14 20:35:48 2019
+% Tue Apr 16 22:40:27 2019
 \begin{table}[ht]
@@
 ## [28] data.table_1.12.2 R6_2.4.0          survival_2.44-1.1
-## [31] readxl_1.3.1      foreign_0.8-71    magrittr_1.5     
-## [34] splines_3.5.3     scales_1.0.0      assertthat_0.2.1 
-## [37] xtable_1.8-3      colorspace_1.4-1  sandwich_2.5-1   
-## [40] survey_3.35-1     stringi_1.4.3     lazyeval_0.2.2   
-## [43] munsell_0.5.0     crayon_1.3.4      zoo_1.8-5
+## [31] readxl_1.3.1      foreign_0.8-71    reshape2_1.4.3   
+## [34] readr_1.3.1       magrittr_1.5      codetools_0.2-16 
+## [37] splines_3.5.3     scales_1.0.0      assertthat_0.2.1 
+## [40] xtable_1.8-3      colorspace_1.4-1  labeling_0.3     
+## [43] sandwich_2.5-1    survey_3.35-1     stringi_1.4.3    
+## [46] lazyeval_0.2.2    munsell_0.5.0     crayon_1.3.4     
+## [49] zoo_1.8-5
 \end{verbatim}

### 2019-04-16 manuscript.Rnw
trim abstract for resubmission

@@
 
-{\abstract Conjoint analysis is now a common tool for studying political preferences.
-The method disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as political candidates or public policies.
-Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs).
-These measure the degree to which a given value of a conjoint profile feature increases, or decreases, people’s support for the overall profile relative to a baseline, averaging across all respondents and all other profile features.
-While the AMCE has a clear causal interpretation (about the \textit{effect} of features), most published conjoint analyses also use AMCEs to describe \textit{levels} of preferences or favorability.
-This often means comparing AMCEs among subgroups of respondents.
-We show that using conditional AMCEs to describe the degree of agreement among subgroups can be misleading as regression interactions are sensitive to the reference category used in the analysis.
+{\abstract Conjoint analysis is a common tool for studying political preferences.
+The method disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as candidates or policies.
+Most conjoints rely upon a fully randomized design to generate average marginal component effects (AMCEs).
+These measure the degree to which a given value of a conjoint profile feature increases, or decreases, respondents' support for the overall profile relative to a baseline, averaging across all respondents and other features.
+While the AMCE has a clear causal interpretation (about the \textit{effect} of features), most published conjoint analyses also use AMCEs to describe \textit{levels} of favorability.
+This often means comparing AMCEs among respondent subgroups.
+We show that using conditional AMCEs to describe the degree of subgroup agreement can be misleading as regression interactions are sensitive to the reference category used in the analysis.
 This leads to inferences about subgroup differences in preferences that have arbitrary sign, size, and significance.
-We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation using two quantities of interest: the marginal mean and the omnibus F-test.
-Given the accelerating use of conjoint analyses in political science, we offer advice for best practice in the analysis and presentation of conjoint experiments.}
+We demonstrate the problem using examples drawn from published articles and provide suggestions for improved reporting and interpretation using marginal means and an omnibus F-test.
+Given the accelerating use of these designs in political science, we offer advice for best practice in analysis and presentation of results.}
 

### 2019-04-16 manuscript.tex
trim abstract for resubmission

@@
 ## [28] data.table_1.12.2 R6_2.4.0          survival_2.44-1.1
-## [31] readxl_1.3.1      foreign_0.8-71    reshape2_1.4.3   
-## [34] readr_1.3.1       magrittr_1.5      codetools_0.2-16 
-## [37] splines_3.5.3     scales_1.0.0      assertthat_0.2.1 
-## [40] xtable_1.8-3      colorspace_1.4-1  labeling_0.3     
-## [43] sandwich_2.5-1    survey_3.35-1     stringi_1.4.3    
-## [46] lazyeval_0.2.2    munsell_0.5.0     crayon_1.3.4     
-## [49] zoo_1.8-5
+## [31] readxl_1.3.1      foreign_0.8-71    magrittr_1.5     
+## [34] splines_3.5.3     scales_1.0.0      assertthat_0.2.1 
+## [37] xtable_1.8-3      colorspace_1.4-1  sandwich_2.5-1   
+## [40] survey_3.35-1     stringi_1.4.3     lazyeval_0.2.2   
+## [43] munsell_0.5.0     crayon_1.3.4      zoo_1.8-5
 \end{verbatim}

### 2019-05-06 manuscript.Rnw
update README

@@
 
-\title{Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}}
+\title{Measuring Subgroup Preferences in Conjoint Experiments%\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}
+}
 \author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}

### 2019-05-24 data/hainmueller.R
rm old Hainmueller files

@@ -1,669 +1,0 @@
-
-# scripts for plots in Causal Inference in Conjoint Analysis:
-# Understanding Multidimensional Choices via Stated Preference Experiments
-# Jens Hainmueller, Daniel Hopkins, Teppei Yamamoto
-rm(list=ls())
-library("ggplot2")
-
-# Figure 2: Candidate Conjoint
-results   <- c("Candrating.txt","Candchoiche.txt")
-ffilenames<- c("Fig2a","Fig2b")
-yylabs <- c("Change: Candidate Rating (0 'never support' - 1 'always support')",
-            "Change: Pr(Prefer Candidate for President)")
-yylims <- list(c(-.2, .2),c(-.4, .4))
-
-for(i in 1:2){
-
-# load estimatesfrom Stata 
-d <- read.table(paste(results[i]))
-ffilename <- ffilenames[i]
-yylab <- yylabs[i]
-yylim <- yylims[[i]]
-
-d$var <- rownames(d)
-colnames(d)[2] <- c("se")
-colnames(d) <- c("pe","se","var")
-
-# compute Cis
-d$upper <-d$pe + 1.96*d$se
-d$lower <-d$pe - 1.96*d$se
-
-# group vars
-Military     <- paste(c("1b",2),".atmilitary",sep="")
-Religion     <- paste(c("1b",2:6),".atreligion",sep="")
-Education    <- paste(c("1b",2:6),".ated",sep="")
-Profession   <- paste(c("1b",2:6),".atprof",sep="")
-Gender       <- paste(c("1b",2),".atmale",sep="")
-Income       <- paste(c("1b",2:6),".atinc",sep="")
-Race         <- paste(c("1b",2:6),".atrace",sep="")
-Age          <- paste(c("1b",2:6),".atage",sep="")
-
-d$gruppe <- NA
-d$gruppe[d$var %in% Military]       <- "Military"
-d$gruppe[d$var %in% Religion]       <- "Religion"
-d$gruppe[d$var %in% Education]       <- "Education"
-d$gruppe[d$var %in% Profession]       <- "Profession"
-d$gruppe[d$var %in% Gender]       <- "Gender"
-d$gruppe[d$var %in% Income]       <- "Income"
-d$gruppe[d$var %in% Race]       <- "Race"
-d$gruppe[d$var %in% Age]       <- "Age"
-
-offset <- c("   ")
-
[…]

### 2019-05-24 manuscript.Rnw
final PA submission

--- 2019-04-16 manuscript.Rnw
@@
 \usepackage{mathpazo}
-%\usepackage{times}
 \usepackage{booktabs}
@@
 \usepackage{floatrow}
+\usepackage[hidelinks]{hyperref}
 \floatsetup[figure]{capposition=top}
@@
 
-\title{Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}}
+\title{Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.
+Replication data and code for this article are available from the \textit{Political Analysis} Dataverse: \url{https://doi.org/10.7910/DVN/ARHZU4}.
+This work was funded, in part, by the United Kingdom Economic and Social Research Council (Grant ES/R000573/1).}
+}
 \author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}
@@
 
-<<hidden, eval=FALSE, echo=FALSE, results="hide">>=
-# setwd("c:/users/thomas/dropbox/brexit identity/papers/subgroupanalysis")
-# knitr::knit2pdf("manuscript.Rnw", quiet = TRUE)
-@
-
 <<knitr_options, cache=FALSE, echo=FALSE, results="hide">>=
-knitr::opts_chunk$set(cache = TRUE, echo=FALSE, results="hold", warning=FALSE, error=FALSE, message=FALSE)
+knitr::opts_chunk$set(
+  cache = TRUE,
+  echo=FALSE,
+  results="hold",
+  warning=FALSE,
+  error=FALSE,
+  message=FALSE
+)
 options(scipen = 10)
@@
 The paper then provides suggestions for improved conjoint reporting and interpretation based around two quantities of interest drawn from the factorial experimentation literature: (a) unadjusted marginal means, a quantity measuring favorability toward a given feature, and (b) an omnibus F-test, measuring differences therein.
-Software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment --- is demonstrated throughout.
+Software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment \citep{Leeper2018cregg} --- is demonstrated throughout using example data \citep{LeeperHoboltTilley2019}.
 We conclude with advice for best practices in the analysis and presentation of conjoint results.
@@
 <<tkr_replication, dependson=c("data_tkr"), fig.height=4.5, fig.width=5, fig.cap="Replication of Results for `Candidate Sex' Feature from Teele et al.
-(2018) Candidate Experiment using Full Sample and Subgroup AMCEs and MMs", fig.show="hold", message=FALSE>>=
+(2018) Candidate Experiment using Full Sample AMCEs and MMs and Subgroup AMCEs and MMs for Democrats and Republicans", fig.show="hold", message=FALSE>>=
 a <- plot(
@@
 ) + 
- annotate("text", y = 1.65, x = -0.04, label = "Republicans", size = 3) + 
- annotate("text", y = 1.3, x = 0.05, label = "Democrats", size = 3) + 
+ annotate("text", y = 1.7, x = -0.04, label = "Republicans", size = 3) + 
+ annotate("text", y = 1.35, x = 0.05, label = "Democrats", size = 3) + 
  ggtitle(NULL, "Subgroup AMCEs") + 
@@
 ) + 
+ annotate("text", y = 1.8, x = 0.48, label = "Rep.", size = 3) + 
+ annotate("text", y = 0.8, x = 0.52, label = "Rep.", size = 3) + 
+ annotate("text", y = 2.2, x = 0.55, label = "Dem.", size = 3) + 
+ annotate("text", y = 1.2, x = 0.45, label = "Dem.", size = 3) + 
  ggtitle(NULL, "Subgroup MMs") + 
@@
 The experimental data and analytic approach in the two portrayals is identical; the only difference is the choice of reference category.
-Given what we have shown about the relationship between differences in conditional AMCEs and differences in conditional marginal means, Panel B is the more truthful visualization \citep{Cairo2016}.
+Given what we have shown about the relationship between differences in conditional AMCEs and differences in conditional marginal means, Panel B is a more ``truthful'' visualization, which \citet{Cairo2016} uses to mean avoidance of self-deception in the presentation of data, and a more ``functional'' visualization, by which \citeauthor{Cairo2016} means choosing graphics based on how they will be interpreted by the visualization's consumers.
 The differences between subgroup AMCEs there more accurately convey differences in underlying preferences because the reference categories used in Panel B are the most similar between the two groups.
@@
 \appendix
+\setcounter{page}{1}
+
+\noindent {\large ``Measuring Subgroup Preferences in Conjoint Experiments: Supplemental Information''}
+
+\vspace{0.5em}
+
+\noindent Thomas J. Leeper, Sara B. Hobolt, and James Tilley\\
+\noindent 2019-05-24
+
+\renewcommand{\contentsname}{}
+\vspace{-2em}
 \tableofcontents
@@
  theme(
-   legend.position = "none",
+   legend.position = c(0.1,0.8),
+   legend.title=element_blank(),
    panel.border = element_blank(),
@@
  theme(
-  legend.position = "none",
+  legend.position = c(0.1,0.8),
+  legend.title=element_blank(),
   panel.border = element_blank(),

### 2019-05-24 manuscript.tex
final PA submission

--- 2019-04-16 manuscript.tex
@@
 \includegraphics[width=\maxwidth]{figure/tkr_replication-1} \caption[Replication of Results for `Candidate Sex' Feature from Teele et al]{Replication of Results for `Candidate Sex' Feature from Teele et al.
-(2018) Candidate Experiment using Full Sample and Subgroup AMCEs and MMs}\label{fig:tkr_replication}
+(2018) Candidate Experiment using Full Sample AMCEs and MMs and Subgroup AMCEs and MMs for Democrats and Republicans}\label{fig:tkr_replication}
 \end{figure}
@@
 
-% latex table generated in R 3.5.3 by xtable 1.8-3 package
-% Tue Apr 16 22:40:04 2019
+% latex table generated in R 3.6.0 by xtable 1.8-4 package
+% Fri May 24 16:19:30 2019
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.3 by xtable 1.8-3 package
-% Tue Apr 16 22:40:05 2019
+% latex table generated in R 3.6.0 by xtable 1.8-4 package
+% Fri May 24 16:19:31 2019
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.3 by xtable 1.8-3 package
-% Tue Apr 16 22:40:09 2019
+% latex table generated in R 3.6.0 by xtable 1.8-4 package
+% Fri May 24 16:19:34 2019
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.3 by xtable 1.8-3 package
-% Tue Apr 16 22:40:15 2019
+% latex table generated in R 3.6.0 by xtable 1.8-4 package
+% Fri May 24 16:19:41 2019
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.3 by xtable 1.8-3 package
-% Tue Apr 16 22:40:25 2019
+% latex table generated in R 3.6.0 by xtable 1.8-4 package
+% Fri May 24 16:19:51 2019
 \begin{table}[ht]
@@
 
-% latex table generated in R 3.5.3 by xtable 1.8-3 package
-% Tue Apr 16 22:40:27 2019
+% latex table generated in R 3.6.0 by xtable 1.8-4 package
+% Fri May 24 16:19:52 2019
 \begin{table}[ht]
@@
 \begin{verbatim}
-## R version 3.5.3 (2019-03-11)
+## R version 3.6.0 (2019-04-26)
 ## Platform: x86_64-w64-mingw32/x64 (64-bit)
@@
 ## other attached packages:
-## [1] gridExtra_2.3 ggplot2_3.1.1 cregg_0.3.1   rio_0.5.16   
+## [1] gridExtra_2.3 ggplot2_3.1.1 cregg_0.3.0   rio_0.5.16   
 ## 
@@
 ##  [1] zip_2.0.1         Rcpp_1.0.1        cellranger_1.1.0 
-##  [4] pillar_1.3.1      compiler_3.5.3    plyr_1.8.4       
-##  [7] forcats_0.4.0     tools_3.5.3       digest_0.6.18    
-## [10] lattice_0.20-38   evaluate_0.13     tibble_2.1.1     
-## [13] gtable_0.3.0      ggstance_0.3.1    pkgconfig_2.0.2  
+##  [4] pillar_1.3.1      compiler_3.6.0    plyr_1.8.4       
+##  [7] forcats_0.4.0     tools_3.6.0       digest_0.6.18    
+## [10] lattice_0.20-38   ggstance_0.3.1    evaluate_0.13    
+## [13] tibble_2.1.1      gtable_0.3.0      pkgconfig_2.0.2  
 ## [16] rlang_0.3.4       Matrix_1.2-17     openxlsx_4.1.0   
-## [19] curl_3.3          haven_2.1.0       xfun_0.6         
-## [22] withr_2.1.2       stringr_1.4.0     knitr_1.22       
-## [25] hms_0.4.2         lmtest_0.9-36     grid_3.5.3       
-## [28] data.table_1.12.2 R6_2.4.0          survival_2.44-1.1
-## [31] readxl_1.3.1      foreign_0.8-71    magrittr_1.5     
-## [34] splines_3.5.3     scales_1.0.0      assertthat_0.2.1 
-## [37] xtable_1.8-3      colorspace_1.4-1  sandwich_2.5-1   
-## [40] survey_3.35-1     stringi_1.4.3     lazyeval_0.2.2   
-## [43] munsell_0.5.0     crayon_1.3.4      zoo_1.8-5
+## [19] DBI_1.0.0         curl_3.3          haven_2.1.0      
+## [22] xfun_0.6          withr_2.1.2       stringr_1.4.0    
+## [25] dplyr_0.8.0.1     knitr_1.22        mitools_2.4      
+## [28] hms_0.4.2         lmtest_0.9-36     grid_3.6.0       
+## [31] tidyselect_0.2.5  glue_1.3.1        data.table_1.12.2
+## [34] R6_2.4.0          survival_2.44-1.1 readxl_1.3.1     
+## [37] foreign_0.8-71    purrr_0.3.2       magrittr_1.5     
+## [40] splines_3.6.0     scales_1.0.0      assertthat_0.2.1 
+## [43] xtable_1.8-4      colorspace_1.4-1  sandwich_2.5-1   
+## [46] survey_3.36       stringi_1.4.3     lazyeval_0.2.2   
+## [49] munsell_0.5.0     crayon_1.3.4      zoo_1.8-5
 \end{verbatim}
